### 2017-01-22 LatticeOptics/latticeOptics.tex
initial

% -*- mode: Latex -*-
% Time-stamp: "2015-02-18 17:55:40 sb"

\documentclass[twocolumn,aps,pra,showpacs,preprintnumbers,bibnotes]{revtex4-1}

\usepackage[T1]{fontenc}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{color}
\usepackage{amsmath}

%% Keep track of changes
%\usepackage[final]{changes}
\usepackage[draft]{changes}
\definechangesauthor[color=green]{AM}
\definechangesauthor[color=blue]{SB}

\DeclareMathOperator{\re}{Re}
\DeclareMathOperator{\im}{Im}

\newcommand\avg[1]{\left\langle#1\right\rangle}

\newcommand\unit[2]{\ensuremath{#1~\mathrm{{#2}}}}

\newcommand\Ket[1]{\ensuremath{|{#1}\rangle}}
\newcommand\Bra[1]{\ensuremath{\langle{#1}|}}

\newcommand\Isotope[2]{\ensuremath{^{#1}\mathrm{#2}}}
\newcommand\Li{\Isotope{6}{Li}}
\newcommand\K{\Isotope{40}{K}}
\newcommand\Rb{\Isotope{87}{Rb}}
\newcommand\Sr{\Isotope{87}{Sr}}
\newcommand\Yb{\Isotope{171}{Yb}}
\newcommand\Er{\Isotope{167}{Er}}
\newcommand\Dy{\Isotope{161}{Dy}}

\renewcommand{\vec}[1]{\ensuremath{\bm{#1}}}

\newcommand\NA{\ensuremath{\mathrm{NA}}}
\newcommand{\osim}{\ensuremath{\mathord{\sim}}}
\newcommand{\Erecl}{\ensuremath{E_\mathrm{rec}}}
\newcommand{\Ereca}{\ensuremath{E_\mathrm{rec}^\mathrm{(a)}}}
\newcommand\FIXME{{\color{red}\ensuremath{\mathrm{FIXME}}}}

\newcommand\TrapFreq{\ensuremath{\nu_t}}
\newcommand\RecoilEnergy{\ensuremath{E_\mathrm{rec}}}

\begin{document}

\title{Optical lattices with low decoherence for ultracold \Li{}}

\author{Li Microscope Collective}
\author{M. Greiner}
\affiliation{
  Department of Physics, Harvard University,
  Cambridge, Massachusetts, 02138, USA}

\date{\today}
\begin{abstract}
We describe the design of a stable high power 1064 nm laser for use in optical lattice experiments. The system is based on a high quality mephisto NPRO seeding an array of four heavily modified fiber amplifiers. The intensity of every beam is stabilized with a low noise, nonlinear feedback system, and the waist can be smoothly controlled. 
\end{abstract}
\maketitle
\section{Introduction}
Trapping atoms in an array of optical lattices is a mature and powerful technique for manipulation and control of quantum many-body systems. The use of neutral atoms trapped in an optical lattice has facilitated precision measurements, creation of interesting many body states, and implementation of quantum gates in neutral atoms.

Optical lattices rely on the optical dipole force of light on neutral atoms and the interference of light. Depending on the laser wavelength and the atomic species used, atoms can be drawn toward or repelled by regions of high intensity.

\begin{equation}
    V(\pmb{x}) = \alpha(\omega)|\pmb{E}(\pmb{r})|^2
\end{equation}

When two or more laser beams are interfered, the interference pattern has a spacing $l>\lambda/2$. Different interference geometries provide a wide variety of lattice geometries that have been demonstrated.

By FIGURE - high level block diagram of system
\begin{itemize}
	\item why cold atoms are great, and why you need lattice: clocks, hubbard etc
	\item what are the requirements of lattice
	\item what have we built
\end{itemize}

\section{Measuring Intensity Noise}
\subsection{Photodiodes}
FIGURE: Transimpedance amplifier, with our parameters
\begin{itemize}
	\item Transimpedance amplifier - typical parameters
	\item design criteria, part numbers, typical voltage levels
	\item cutting off windows
	\item thermal stuff (inGas)
	\item lens or no
	\item using photodiodes for looking at these things
\end{itemize}

\subsection{Measuring Power Spectral Density}
FIGURE - maybe WINDOW FUNCTION
\begin{itemize}
\item FFT machine, spectrum analyzer 
window functions revisited, 
-resolution, video bandwidth
\end{itemize}

\subsection{Residual Intensity Noise}
RIN:
\begin{itemize}
\item what is it and how do you measure it
\item easy to measure, enters into parametric heating effects
\end{itemize}

\subsection{Heating Effects}
\begin{itemize}
	\item Trap shaking, parametric heating
\end{itemize}

\section{Fiber Amplifier System}

\section{Mephisto Seed Laser}

Mephisto:
\begin{itemize}
	\item Mephisto basics - what is it and how does it work
	\item noise coming out of laser (w,w/0 noiseeater)
	\item noise coming out of a fiber (into nufern)
	\item Schematic of beam splitting
\end{itemize}

\begin{figure}
    \caption{(a) Layout of the seed source of the high power laser system, (b) Noise spectra of the Mephisto laser in various configurations}\label{fig:seed}
\end{figure}

The high power laser system is seeded by a single Innolight Mephisto 1064 nm, ultra-narrow, low noise, non-planar-ring-oscillator (NPRO) laser. Figure \ref{fig:seed} shows the basic layout of the system. Polarizing beam splitters and half wave plates are used to split the light into five beams. One is for general purpose use, while four are split between four fiber amplifiers. It is important that individual lattices do not interfere at timescales relevant to our experiments. Typical experiments in our systems are insensitive to frequencies above $\approx 10$ MHz. For this reason, acousto-optic modulators (AOM) are used to shift the four beams away from each other by the AOM carrier frequencies (typically $\approx 80$ MHz).

The relative intensity noise of the mephisto seed laser was also studied, both to verify that the laser performed as specified, and that the measurement procedure was sound. The RIN curves shown in figure \ref{fig:seed} closely match the specified values. The mephisto has a relaxation oscillation that causes a substantial increase in the noise near \FIXME 0.6 MHz. An internal ``noise-eater'' can suppress this noise. Unless otherwise specified, we oprate the laser with the noise eater on.

\section{Fiber Amplifier Modifications}
We chose to use \textit{Nufern} 50 W fiber amplifier systems (part number \FIXME), due to their inexpensive price and relatively high performance in terms of power and intensity noise. In their default configuration, however, the fiber amplifiers suffer from several severe problems:
\begin{enumerate}
    \item A large number of noise spurs at low frequencies.
    \item A 30 \FIXME dB noise spur at the switching power supply frequency.
    \item A built in power supply containing a cooling fan that vibrationally couples to the gain fiber.
    \item An inconvenient USB digital interface.
\end{enumerate}

In order to address these problems, the fiber amplifier had to be heavily modified. First, the two power supplies required by the fiber amplifier were moved outside its immediate enclosure an connected with 15 foot long AWG \FIXME cables. The pump diode driver, part number \FIXME was unmodified, but the general purpose power supply was replaced with a low noise switching supply from Acopian Corporation, part number \FIXME. A high power line filter, part number \FIXME, was added to reduce the switching supply spike on the fiber amplifier by \FIXME dB.

Further, the control of the fiber amplifiers is done by a pair of printed circuit boards, where one primarily handles the USB communications, and the other communicates the power supplies and interlocks. The USB board was replaced by a custom board compatible with out experimental control system.

\section{Lattice Beam Optics}
Each fiber amplifier can output a maximum of 50 W of optical power into a single gaussian mode out of the large mode field diameter output fiber. Collimating this high power beam presents a challenge - the light intensity is sufficient to trap dust particles, and bring them towards the fiber tip. For this reason, a custom, stable, monolithic mount was designed for the collimation stage, which holds the collimation lens and fiber tip in a fully enclosed chamber. The collimating lens is a \FIXME 20 mm focal length, air spaced, fused silica triplet from optosigma \FIXME part number. The fiber is held at an angle, to compensate for the angle of the cleave.

\begin{itemize}
\item How to collimate and reject cladding modes - no dust in hp areas, 
\item FC compensate for cleave
\item mechanical stable

\item evidence of fiber tip shaking if there were fans inside
changing collimator dist wrt fiber - focus about 80 cm - focus through aom - no movable optics between AOM and chuck
\item mode quality - quote $m^2$
\item mode shape changes dramatically with pump current (output power)
\item thermal settling - run at full power continuously
\item dump cladding modes
\item optics have to handle full power - BK7 bad, fused silica good
\item high quality IBS sputtered optics if you care
\item brewster polarizers - glued cubes are terrible (contacted cubes expensive, supression ratio not as good) - 10k:1
\item brewster plates walk the beam
\end{itemize}

\subsection{Isolation}
\begin{itemize}
\item backreflections are bad,
\item retroreflection -> 2 stages
\item as seen in ligo Yttg isolation decreases with optical intensity - coupling between optical effects and faraday
\item not as bad as ligo, since not in vacuum.
\item thorlabs -> high power 5mm aperture -> BK7 bad
\item waveplate ibs coating
\item Can of mumetal for physics reasons
\item attenuation of field is XXXXX
\item watercooling
\item stack 2x
\end{itemize}

DUMPING
-watercooled beamdumps far removed from the optics for thermal reasons
\subsection{Intensity Control}
2 Step intensity control

\subsubsection{Berek Compensator}
\begin{itemize}
\item high dyn range actuator
\item berek compensator
\end{itemize}

custom coating quartz plate that is z-cut mounted on camtech galvo
can act as translates rotation into polarization rotation
with brewster polarizers can act as variable attenuation
bias with waveplates
BW = XXX
attenuation = XXX
induces walkoff

BEAM with well defined polarization on optical table 
$M^2$ = this, waist focused 80cm to a 650um, which is consistent with ABCD tracing

\subsubsection{AcoustoOptic Modulation}

\begin{itemize}
    \item AOM is this 80MHZ, TeO2
    \item large active area AOM to reduce intenisty going through
    \item thermal problems
    \item watercooled
    \item custom flexure mount to minimize motional degrees of freedom.
    \item obtain a diffraction efficiency of $M^2$
    \item 20cm in front of AOM - diffraction process changes this - characterize this
    \item AOM's thermal effects pointing noise mostly. BW is traveling wave such and such speed of sound.
    \item shut off time is 500ns
    \item polarization is negligible
    \item POINTING is stable.
\end{itemize}

\section{Feedback}
\begin{itemize}
    \item galvo
    \item aom
    \item AR pickoff
    \item PD - lenses and imaging
    \item Loop filter sqrt
    \item Exponential
    \item Pump current
\end{itemize}

\section{Feedback}

\subsection{Acousto-optic Modulation}

FIGURE - RIN OF MEPHISTO, driven by difft oscillators
Mephisto+oscillators
\begin{itemize}
	\item how does the RIN spectrum change as a function of oscillators
\end{itemize}
\section{Fiber Amplifier system}
FIGURE - BLOCK DIAGRAM OF FIB AMP SYSTEM

\subsection{Fiber Amplifier Modifications}
FIGURE - SBS DATA
\begin{itemize}
	\item Mephisto+Fiber amplifiers
\item fiber amplifiers work like so so
\item schematic what it looks like and does
\item Modifications
	\begin{itemize}
		\item electronics control board,
		\item PSU's
		\item filters
		\item switching spikes removed
		\item fan noise stopped
	\end{itemize}
\item Two stage amplifier
	\begin{itemize}
		\item second stage has this special fiber 
		\item large mode area fibers
		\item leakage into cladding modes 
		\item sbs (cut off)
	\end{itemize}
\item SBS data
\end{itemize}
\section{Telescope}
-beam parameters such and such

\section{Alignment Tricks}

\section{Waist Control}
\section{Appendix: Fourier Transforms and Power Spectral Densities}
\begin{itemize}
	\item FT
	\item PSD
	\item FFT? 
	\item Window functions, discretization effects
\end{itemize}
\section{Appendix: Feedback Theory}
mini feedback tutorial

\end{document}

### 2017-01-22 LatticeOptics/latticeOpticsV2.tex
initial

--- 2017-01-22 LatticeOptics/latticeOptics.tex
@@
 \section{Introduction}
-Trapping atoms in an array of optical lattices is a mature and powerful technique for manipulation and control of quantum many-body systems.
+Trapping atoms in an array of optical lattices is a powerful technique for manipulation and control of quantum many-body systems. 
 The use of neutral atoms trapped in an optical lattice has facilitated precision measurements, creation of interesting many body states, and implementation of quantum gates in neutral atoms.
-
-Optical lattices rely on the optical dipole force of light on neutral atoms and the interference of light.
-Depending on the laser wavelength and the atomic species used, atoms can be drawn toward or repelled by regions of high intensity.
-
-\begin{equation}
-    V(\pmb{x}) = \alpha(\omega)|\pmb{E}(\pmb{r})|^2
-\end{equation}
-
-When two or more laser beams are interfered, the interference pattern has a spacing $l>\lambda/2$.
-Different interference geometries provide a wide variety of lattice geometries that have been demonstrated.
+CITATIONS.
+However, a dominant trend in cold atom experiments has been the need to attain colder temperatures at energy scales approaching the Hz level.
+Such experiments are limited by heating rates arising from positional, phase and intensity noise of the optical lattice.
 
 By FIGURE - high level block diagram of system
+
 \begin{itemize}
-	\item why cold atoms are great, and why you need lattice: clocks, hubbard etc
-	\item what are the requirements of lattice
+	\item requirements 
 	\item what have we built
 \end{itemize}
+
+We demonstrate high power lattice
+
+\section{Mephisto}
+The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately 2 W of 1064 nm light. 
+This commercial laser utilizes a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability.
+This source is split into four fibers (Thorlabs XXX) by means of polarizing beam splitters.
+Figure 1 shows the mechanical layout of this system, as well as the intensity noise performance (see supplementary material).
+
+\section{Nufern Fiber Amplifiers}
+Quantum gas microscopy of Li requires single site trap frequencies of approximately 1 MHz. 
+Such trap frequencies may only be attained using tightly focused high power beams, which requires that the seed power be amplified to approximately 30 W per lattice axis, which is done using
 
@@
 	\item lens or no
-	\item using photodiodes for looking at these things
-\end{itemize}
-
-\subsection{Measuring Power Spectral Density}
-FIGURE - maybe WINDOW FUNCTION
-\begin{itemize}
-\item FFT machine, spectrum analyzer 
-window functions revisited, 
--resolution, video bandwidth
+	\item using photodiodes for looking at these thing
 \end{itemize}
@@
 \end{itemize}
-
-\section{Fiber Amplifier System}
 

### 2017-01-23 LatticeOptics/latticeOpticsV2.tex
text changes

@@
 
-\title{Optical lattices with low decoherence for ultracold \Li{}}
+\title{Design and Implementation of Low }
 
@@
 \section{Introduction}
-Trapping atoms in an array of optical lattices is a powerful technique for manipulation and control of quantum many-body systems. 
-The use of neutral atoms trapped in an optical lattice has facilitated precision measurements, creation of interesting many body states, and implementation of quantum gates in neutral atoms.
-CITATIONS.
+Trapping ultracold atoms in an array of optical traps, known as an optical lattice, is a powerful technique for manipulation and control of quantum many-body systems. 
+It has facilitated precision measurements, engineering of interesting many body states, and is a possible quantum computing platform.
 However, a dominant trend in cold atom experiments has been the need to attain colder temperatures at energy scales approaching the Hz level.
@@
 This commercial laser utilizes a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability.
-This source is split into four fibers (Thorlabs XXX) by means of polarizing beam splitters.
+This source is split into four fibers (Thorlabs XXX) by means of polarizing beam splitters, where two of the fibers are detuned from each other by XXX MHz, to prevent interference of the lattice beams.
 Figure 1 shows the mechanical layout of this system, as well as the intensity noise performance (see supplementary material).
@@
 \section{Nufern Fiber Amplifiers}
-Quantum gas microscopy of Li requires single site trap frequencies of approximately 1 MHz. 
-Such trap frequencies may only be attained using tightly focused high power beams, which requires that the seed power be amplified to approximately 30 W per lattice axis, which is done using
+Quantum gas microscopy of Li requires single site trap frequencies of approximately 1 MHz \cite{single site paper}.
+Such trap frequencies may only be attained using tightly focused high power beams, which requires that the seed power be amplified to approximately 30 W per lattice axis, which is done using Nufern Fiber amplifiers (PART NUMBER XXX).
+These amplifiers can amplify 150 mW to up to approximately 45 W (depending on pump diode current) by using a length of fiber doped with XXX (erbium or ytterbium) and pumped with xxx nm light from fiber coupled diode sources to provide a gain medium for 1064 nm light.
+The amplification is performed using a two stage amplifier design, where the stages are contolled using separate power supplies and electronics.
+The high powers supplied by the fiber amplifiers raise two engineering difficulties.
+First, the fiber amplification process is inherently noisy, due to acoustic coupling of the fiber to the environment, electrical design of the amplifier, and spontaneous Brillouin scattering (SBS).
 
-\section{Measuring Intensity Noise}
-\subsection{Photodiodes}
+The NUFERN MODEL NUMBER suffers from several problems: it is controlled via a USB interface, requiring a digital ground on the control PCB inside the device.
+Further, this digital ground is not isolated from the remainder of the electronics leading to potential ground loops between the controlling computer and the fiber amplifier.
+We solve this problem by replacing the USB control board with a custom-designed, ethernet based solution that is compatible with our custom control system. 
+There are two power supplies in the fiber amplifier - a general purpose supply for the control electronics and first stage and a high current supply for the second stage. 
+Further, despite the presence of a water-cooled coldplate to cool the fiber and pump diodes, the high power supply is air cooled using a fan approximately 20 cm away from the gain fiber and has been thought to lead to increased noise at acoustic frequencies.
+To reduce acoustic coupling and reduce switching power supply noise, both power supplies were removed from the fiber amplifier enclosure, the low power supply was replaced by acopian XXXX PSU and the high power supply was filtered using an XXX line filter.
+Combined, these changes serve to suppress certain noise spurs measured in the relative intensity noise (RIN) of the fiber amplifier, as seen in figure 1. 
+The measurements were carried out on two fiber amplifiers from the same manufacturing batch, one with the modifications and one without.
+
+\section{Mode and beam shaping}
+The free-space propagation of the fiber amplifier output presents several challenges (1) the high power is sufficient to induce substantial thermal lensing, (2) the positional fluctuations of the waist at the atoms cannot exceed
+a few microns from shot to shot, (3) by construction, the beam is retroreflected, which threatens the lifetime of the amplifier unless sufficient isolation is used (4) approximately 1 W of power leaks into the undesired cladding modes of the fiber.
+To condition the beam into a desired shape, a train of optical elements is used, shown in figure \ref{fig:opticalelements}, which shapes the beam. 
+Due to the high laser power, fused silica glass is used everywhere but in the acousto-optic modulator, Berek compensator and optical isolators, to minimze thermal lensing.
+For the same reason, IBS coatings are used wherever possible, due to the higher damage thresholds.
+The large-diameter fiber tip is mounted in a monolithic, oxygen-depleted copper mount, and the beam is collimated using an XXX 20 mm fused-sileca triplet collimator from Opto-Sigma, which produces a beam with $m^2 = XXX(X)$.
+Then, the polarization is cleaned up using an IBS coated Brewster plate polarizer, which has the added benefit of rejecting the undesired cladding modes. 
+The fact that the lattice is retro-reflected, combined with the observation that optical isolation falls with applied optical power\cite{LIGO} means that two stages of optical isolators must be used.
+The optical isolators are based on the 5 mm diameter Faraday rotators from Thorlabs.
+The optical isolators are located approximately 1 m away from the ultracold atomic system, meaning that undesired stray fields can have a dramatic effect.
+To overcome this problem the isolators are enclosed in mu-metal shielding.
+
+\section{Berek Compensator}
+
+\section{Photodiodes}
 FIGURE: Transimpedance amplifier, with our parameters
@@
 
-\section{Mephisto Seed Laser}
-
-Mephisto:
-\begin{itemize}
-	\item Mephisto basics - what is it and how does it work
-	\item noise coming out of laser (w,w/0 noiseeater)
-	\item noise coming out of a fiber (into nufern)
-	\item Schematic of beam splitting
-\end{itemize}
-
-\begin{figure}
-    \caption{(a) Layout of the seed source of the high power laser system, (b) Noise spectra of the Mephisto laser in various configurations}\label{fig:seed}
-\end{figure}
-
-The high power laser system is seeded by a single Innolight Mephisto 1064 nm, ultra-narrow, low noise, non-planar-ring-oscillator (NPRO) laser.
-Figure \ref{fig:seed} shows the basic layout of the system.
-Polarizing beam splitters and half wave plates are used to split the light into five beams.
-One is for general purpose use, while four are split between four fiber amplifiers.
-It is important that individual lattices do not interfere at timescales relevant to our experiments.
-Typical experiments in our systems are insensitive to frequencies above $\approx 10$ MHz.
-For this reason, acousto-optic modulators (AOM) are used to shift the four beams away from each other by the AOM carrier frequencies (typically $\approx 80$ MHz).
-
-The relative intensity noise of the mephisto seed laser was also studied, both to verify that the laser performed as specified, and that the measurement procedure was sound.
-The RIN curves shown in figure \ref{fig:seed} closely match the specified values.
-The mephisto has a relaxation oscillation that causes a substantial increase in the noise near \FIXME 0.6 MHz.
-An internal ``noise-eater'' can suppress this noise.
-Unless otherwise specified, we oprate the laser with the noise eater on.
-
-\section{Fiber Amplifier Modifications}
-We chose to use \textit{Nufern} 50 W fiber amplifier systems (part number \FIXME), due to their inexpensive price and relatively high performance in terms of power and intensity noise.
-In their default configuration, however, the fiber amplifiers suffer from several severe problems:
-\begin{enumerate}
-    \item A large number of noise spurs at low frequencies.
-    \item A 30 \FIXME dB noise spur at the switching power supply frequency.
-    \item A built in power supply containing a cooling fan that vibrationally couples to the gain fiber.
-    \item An inconvenient USB digital interface.
-\end{enumerate}
-
-In order to address these problems, the fiber amplifier had to be heavily modified.
-First, the two power supplies required by the fiber amplifier were moved outside its immediate enclosure an connected with 15 foot long AWG \FIXME cables.
-The pump diode driver, part number \FIXME was unmodified, but the general purpose power supply was replaced with a low noise switching supply from Acopian Corporation, part number \FIXME.
-A high power line filter, part number \FIXME, was added to reduce the switching supply spike on the fiber amplifier by \FIXME dB.
-
-Further, the control of the fiber amplifiers is done by a pair of printed circuit boards, where one primarily handles the USB communications, and the other communicates the power supplies and interlocks.
-The USB board was replaced by a custom board compatible with out experimental control system.
-
 \section{Lattice Beam Optics}
-Each fiber amplifier can output a maximum of 50 W of optical power into a single gaussian mode out of the large mode field diameter output fiber.
-Collimating this high power beam presents a challenge - the light intensity is sufficient to trap dust particles, and bring them towards the fiber tip.
-For this reason, a custom, stable, monolithic mount was designed for the collimation stage, which holds the collimation lens and fiber tip in a fully enclosed chamber.
-The collimating lens is a \FIXME 20 mm focal length, air spaced, fused silica triplet from optosigma \FIXME part number.
-The fiber is held at an angle, to compensate for the angle of the cleave.
 
 \begin{itemize}
-\item How to collimate and reject cladding modes - no dust in hp areas, 
-\item FC compensate for cleave
-\item mechanical stable
-
 \item evidence of fiber tip shaking if there were fans inside
 changing collimator dist wrt fiber - focus about 80 cm - focus through aom - no movable optics between AOM and chuck
-\item mode quality - quote $m^2$
 \item mode shape changes dramatically with pump current (output power)
-\item thermal settling - run at full power continuously
-\item dump cladding modes
-\item optics have to handle full power - BK7 bad, fused silica good
-\item high quality IBS sputtered optics if you care
-\item brewster polarizers - glued cubes are terrible (contacted cubes expensive, supression ratio not as good) - 10k:1
-\item brewster plates walk the beam
 \end{itemize}
@@
 
-\section{Waist Control}
-\section{Appendix: Fourier Transforms and Power Spectral Densities}
-\begin{itemize}
-	\item FT
-	\item PSD
-	\item FFT? 
-	\item Window functions, discretization effects
-\end{itemize}
-\section{Appendix: Feedback Theory}
-mini feedback tutorial
-
 \end{document}

### 2017-01-24 LatticeOptics/latticeOpticsV2.tex
text revisions

@@
 The optical isolators are located approximately 1 m away from the ultracold atomic system, meaning that undesired stray fields can have a dramatic effect.
-To overcome this problem the isolators are enclosed in mu-metal shielding.
+To overcome this problem the isolators are enclosed in mu-metal shielding, reducing the field outside the can by an estimated factor of XXX.
 
-\section{Berek Compensator}
+\section{Feedback}
+
+With an appropriately shaped and isolated beam, it is now important to consider two aspects of the desired experiment: (1) the lattice power must be continuously tunable from around 10 $\mu$W to around 20 W, (2) the location of the minimum gaussian beam waist must be accurately positioned to overlap the other lattices and dipole traps present in the experiment, and must remain there for the duration of the collection process (typically hours).
+To appease the first of these requirements, a two-stage feedback system is implemented.
+The reason for the two stages is simple: the experiment typically operates in one of two regimes, which we will term \textit{detection} and \textit{interaction}.
+In the interaction phase of the experiment, the lattice is relatively shallow (depths of $\approx 10 E_R$, where $E_R$ is the geometric recoil of the lattice), allowing atoms to tunnel and interact with other atoms.
+In this regime, fine and potentially fast control is required.
+In the detection phase, the depth of the lattice is dramatically raised ($\approx 2000 E_R$), isolating atoms in their individual wells so that Raman sideband imaging can be performed \cite{parsons2015}.
+In this regime, the control need not be fast, and the passive stability of the Mephisto laser ensures that noise is low at relevant frequency scales.
+Thus, two loops are utilized, a fast loop that uses an acousto-optic modulator to actuate the laser power at low powers, and a slow loop which uses a Berek compensator, to actuate in the high power mode.
+
+After the isolation stage, we use the sequence of optical elements shown in figure \ref{fig1}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs XXX) half-wave plate, and polarizer.
+The berek compensator is a simple $z$-cut quartz plate coated to be anti-reflecting at 1064 nm.
+By tilting the plate about its vertical axis, the extraordinary axis is mixed into the propagation of the beam, leading to a tilt-dependent bi-refringence that can be tuned from a zero-wave plate past a half-wave plate.
+Combined with the surrounding polarization optics, rotation of the Berek compensator changes the transmitted power with perfect contrast and transmitted power as a function of the tilt angle is shown in figure \ref{fig2}.
+If the half-wave plates in the Berek compensator are tuned to precisely 45 degrees from the angle of the tilt, the modulation contrast of the transmission is perfect, however, we purposefully detune from this configuration such that the minimum power transmitted through this system is approximately 1 W for each lattice axis.
+Thus, when the system is in \textit{interaction} mode, tilt noise on the Berek compensator is strongly suppressed by positioning the system at the minimum.
+
+Past the Berek compensator we use a water-cooled, high power TeO$_2$ AOM (part number XXXX), where the power of the RF supplied to the AOM is used to actuate the fast, low power feedback loop.
+The local oscillator (LO) RF source is a custom-built printed circuit board (PCB) using a phase locked loop (PLL) based on the ADF4002 IC and XXX voltage controlled oscillator (VCO), preamplified with the XXX low noise amplifier.
+This RF power is actuated using a mixer (Minicircuits XXX), which functions down to DC and a high-isolation RF switch (Minicircuits XXX), followed by a power amplifier stage (RF-bay XXX).
+After the AOM, the beam is sampled twice using a single beam sampler (Thorlabs BSF-10C), by taking the reflections from the front and rear facets of the optic, which are conveniently angled away from each other by XXX.
+One of the sampled beams is further attenuated by a factor of approximately 4\% by reflecing off an uncoated fused-silica plate, and the two sampled beams are directed toward a pair of identical photo-diodes.
+
+The design of the photodiodes is exceedingly important for both the continued successful operation of the feedback loops as well as the characterization of the performance.
+The typical feedback loop used in the experiment is based on a simple trans-impedance amplifier design, combined with a low noise, linear, small active area photodiode.
+MORE DESIGN STUFF HERE
 
@@
 \begin{itemize}
-    \item galvo
     \item aom
@@
 \end{itemize}
-
-\section{Feedback}
 

### 2017-01-25 LatticeOptics/latticeOpticsV2.tex
camera stuff

@@
 
-\title{Design and Implementation of Low }
+\title{Design and Implementation of Stable High Power Optical Lattices for Quantum Gas Microscopy}
 
@@
 \end{itemize}
+\section{Beam Monitoring}
+A major recent direction of ultracold atoms experiments is the ability to use very few, individually-addressible atoms\cite{AFM paper, quantum walks few body} that are simultaneously held by several lattice axes in addition to auxilliary traps.
+Unfortunately, such experiments require superb stability, where the underlying harmonic confinement does not shift by more than approximately 2-3 micron from experiment to experiment.
+
+The required positional stability is acheived through a combination of passive stability and active monitoring. 
+Passive stability is ensured by using stable optomechanics (largely from the Thorlabs Polaris line), mounted on short posts, ensuring a low (2 inch) beam height relative to the optical table, which is floating to minimze vibrations.
+In order to further improve stability, the beam is enclosed with 1 inch beam tubes wherever possible throughtout its path, and the entire setup is covered by an aluminum plate, sanded to prevent undesired specular reflections.
+To isolate the experimental setup from the environment the entire optical table is contained within an aluminum enclosure, however, opening this enclosure has been observed to change the thermal state of the system and induce misalignment.
+For this reason, each lattice axis is fitted with a remotely actuated mirror, controlled over the ethernet network, allowing for non-invasive realignment of the system.
+
+Passive stability, while critical, has been found to be insufficient to ensure smoothe operation over many hours.
+Changes in weather conditions, load on the water-cooling systems and other external effects can lead to a slow drift in the pointing of the laser beams.
+To prevent external influences from contaminating large data sets, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
+This system is based on picking off a small portion of the beam shortly before it reaches the atomic system and imaging it onto a camera in the same plane as the atoms. 
+While the position of the atoms is dictated by the potential generated from the ingoing and retro-reflected laser beams and the monitoring camera only observes the position of the ingoing beam.
+In order to verify that the monitor camera \dots
+purposeful misalignment of the ingoing beam shows a clear correlation between the monitor camera signal and the
+
+Typical operation of the experiment involves repeated realizations of the ultracold atomic system, with a cycle time of 10s of seconds, with a lattice duty cycle of about 10\%.
+
 \section{Telescope}

### 2017-01-29 LatticeOptics/latticeOpticsV2.tex
text change

@@
 \section{Photodiodes}
+Fast, low-noise photodiodes are required both to provide the monitoring arm of the feedback loop and to characterize the RIN of the system.
+An ideal device would have a bandwidth up to approximately 3 MHz, with a noise floor below approximately -150 dBc over that range.
+To approach these specifications, we use a custom designed PCB that implements a simple trans-impedance amplifier in a convenient physical package, providing a bandwidth (BW) between XXX and XXX, depending on the transimpedance gain, which can be set by a resistor.
+The photodiode can be safely operated up to incident powers of approximately 10 mW, which sets a XXX dBc shot noise limit on the RIN that can be detected.
+A photodiode with a BW of XXX MHz is used to characterize the system, while photodiodes with a bandwidth of XXX and correspondingly higher gain are used for feedback.
+
+The chosen photodiode (Hamamatsu XXX) is an InGaS based, small-area, low-noise design with a high efficiency at 1064 nm.
+Prior to use, the protective window is removed from the photodiode to prevent interference effects.
+Further, to reduce the capacitance of the system, a reverse bias of XXX V is applied to the photodiode by a temperature-stabilized voltage reference (Digi-key XXX).
+The transimpedance circuit is shown in figure XXX - it converts the photo-current supplied by the photodiode to a voltage signal using the low noise XXX operational amplifier. 
+The electronic assembly is housed in a metal enclosure to minimize interference effects, but is mounted to the optical table using isolating mica posts, to prevent ground loops.
+
+Light is focused onto the photodiode using a 25.4 mm lens such that the beam at the photodiode is significantly smaller than the photodiode diameter, to prevent pointing fluctuations from registering as positional fluctuations.
+An iris and interference filter (Semrock XXX) are used to elimnate stray sources of light.
+
 FIGURE: Transimpedance amplifier, with our parameters
@@
 Changes in weather conditions, load on the water-cooling systems and other external effects can lead to a slow drift in the pointing of the laser beams.
-To prevent external influences from contaminating large data sets, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
+To prevent external influences from contaminating large data sets, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams and eliminate experimental realizations when the system was in an undesired state.
 This system is based on picking off a small portion of the beam shortly before it reaches the atomic system and imaging it onto a camera in the same plane as the atoms.
-While the position of the atoms is dictated by the potential generated from the ingoing and retro-reflected laser beams and the monitoring camera only observes the position of the ingoing beam.
-In order to verify that the monitor camera \dots
-purposeful misalignment of the ingoing beam shows a clear correlation between the monitor camera signal and the
 
-Typical operation of the experiment involves repeated realizations of the ultracold atomic system, with a cycle time of 10s of seconds, with a lattice duty cycle of about 10\%.
+A limitation of this scheme is that the position of the atoms is dictated by the potential generated by the overlap of the ingoing and retro-reflected beams, while the monitoring camera only observes the position of the ingoing beam.
+In order to verify that the monitor camera could be correlated with the true position of the atoms, purposeful misalignment of the incoming beams was introduced to the system, and the position of the atoms was compared to the monitor system reading, where the comparison is shown in figure XXX.
+The position of the atoms was assumed to be related to the monitor camera by an affine transformation and a fit was performed, which implied that the monitor camera could predict the position of the atoms to within XX $\mu$m.
+
+Further, Figure xxx shows the performance of the system in action during a long dataset, where the system performance was thought to have degraded due to environmental factors toward the end of the set.
 

### 2017-01-30 LatticeOptics/latticeOpticsV2.tex
feedback text

@@
 \section{Introduction}
-Trapping ultracold atoms in an array of optical traps, known as an optical lattice, is a powerful technique for manipulation and control of quantum many-body systems. 
-It has facilitated precision measurements, engineering of interesting many body states, and is a possible quantum computing platform.
-However, a dominant trend in cold atom experiments has been the need to attain colder temperatures at energy scales approaching the Hz level.
-Such experiments are limited by heating rates arising from positional, phase and intensity noise of the optical lattice.
+Ultracold atoms in optical lattices have become a powerful platform for experiments ranging from investigations of strongly correlated systems, quantum state engineering, quantum computing architectures and precision metrology, among others.
+Further, the recent advent of quantum gas microscopy has enabled studies that exhibit unprecedented control over few atom systems that function at extremely low energy scales, down to the Hz level and below.
+Unfortunately, this rapid progress places ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
+Specifically, in experiments taking place at low temperatures, heating due to intensity noise on a lattice cannot be allowed to approach the thermalization timescales.
+Similarly, in experiments that rely on a small number of atoms contained by multiple traps cannot proceed until all traps are stable relative to each other down to a few-site leve.
+We demonstrate a high power lattice system that exhibits levels of intensity noise below -120 dBc between 1 kHz and 3 MHz, and is positionally stable at the XXX site level. 
+This system has been successfully used in a Fermi gas microscope to investigate the charge and spin sectors of the Hubbard model with unprecedented control and fidelity.
 
-By FIGURE - high level block diagram of system
-
-\begin{itemize}
-	\item requirements 
-	\item what have we built
-\end{itemize}
-
-We demonstrate high power lattice
+\section{The atoms}
 
@@
 For the same reason, IBS coatings are used wherever possible, due to the higher damage thresholds.
+Further, even small reflections pose both a danger to the users and the thermal equillibrium of the system.
+To alleviate this danger, all undesired beams above a 100 mW are directed to water cooled beam-dumps that are removed from the beam paths as far as possible.
+
 The large-diameter fiber tip is mounted in a monolithic, oxygen-depleted copper mount, and the beam is collimated using an XXX 20 mm fused-sileca triplet collimator from Opto-Sigma, which produces a beam with $m^2 = XXX(X)$.
@@
 
-\section{Feedback}
+\section{High power feedback}
 
-With an appropriately shaped and isolated beam, it is now important to consider two aspects of the desired experiment: (1) the lattice power must be continuously tunable from around 10 $\mu$W to around 20 W, (2) the location of the minimum gaussian beam waist must be accurately positioned to overlap the other lattices and dipole traps present in the experiment, and must remain there for the duration of the collection process (typically hours).
+After the beam has been cleaned up and isolated, it is important to consider two aspects of the desired experiment: (1) the lattice power must be continuously tunable from around 10 $\mu$W to around 20 W, (2) the location of the minimum gaussian beam waist must be accurately positioned to overlap the other lattices and dipole traps present in the experiment, and must remain there for the duration of the collection process (typically hours).
 To appease the first of these requirements, a two-stage feedback system is implemented.
@@
 Thus, when the system is in \textit{interaction} mode, tilt noise on the Berek compensator is strongly suppressed by positioning the system at the minimum.
+Naturally, rotation of a parallel plate in the beam path induces a shift of the beam, but this is acceptable because the Berek compensator is only active during the imaging phase of the experiment, when the position of the underlying harmonic trap is largely irrelevant.
 
-Past the Berek compensator we use a water-cooled, high power TeO$_2$ AOM (part number XXXX), where the power of the RF supplied to the AOM is used to actuate the fast, low power feedback loop.
+Past the Berek compensator we high power TeO$_2$ AOM (part number XXXX), where the power of the RF supplied to the AOM is used to actuate the fast, low power feedback loop.
+The AOM material is chosen for its ultra-low thermal lensing and easily-accessible required RF powers, and the AOM itself is mounted on a custom-built, monolithic, water-cooled flexure mount that allows optimization of the AOM efficiency, but that has been found to be stable over approximately two years of operation.
 The local oscillator (LO) RF source is a custom-built printed circuit board (PCB) using a phase locked loop (PLL) based on the ADF4002 IC and XXX voltage controlled oscillator (VCO), preamplified with the XXX low noise amplifier.
@@
 One of the sampled beams is further attenuated by a factor of approximately 4\% by reflecing off an uncoated fused-silica plate, and the two sampled beams are directed toward a pair of identical photo-diodes.
-
-The design of the photodiodes is exceedingly important for both the continued successful operation of the feedback loops as well as the characterization of the performance.
-The typical feedback loop used in the experiment is based on a simple trans-impedance amplifier design, combined with a low noise, linear, small active area photodiode.
-MORE DESIGN STUFF HERE
 
@@
 
-FIGURE: Transimpedance amplifier, with our parameters
-\begin{itemize}
-	\item Transimpedance amplifier - typical parameters
-	\item design criteria, part numbers, typical voltage levels
-	\item cutting off windows
-	\item thermal stuff (inGas)
-	\item lens or no
-	\item using photodiodes for looking at these thing
-\end{itemize}
+\section{Loop Filter}
+Having covered the actuation and monitoring mechanisms of the feedback system, the only remaining part is the loop filter component of the feedback circuit, which compares the \textit{setpoint} signal supplied by the experimental control system, $v_s(t)$ and the monitoring signals $v_m(t)$, to adjust the actuation accordingly.
+We use a simple, purely integrating design based on the XXX opamp, in three stages, as seen in figure XXX.
+The first stage computes an error signal, $e(t)=v_m(t)-v_s(t)$, which is integrated by the second stage, with a manually tunable gain, set by a low-drift trimpot (digikey xxx). 
+The third stage is used to accomodate the fact that the actuation arm is in nonlinear - the optical power transmitted by the AOM is proportional to the RF power incident on it $P_{\mathrm{rf}}\propto v_{if}^2$, where $v_{if}$ is the actuation signal supplied to the IF port of the mixer.
+In effect, if the rest of the feedback system was linear, this would correspond to a quadratically increasing gain until the AOM is saturated, which could lead to slow behavior at low signal levels and ringing at higher signal levels.
+Thus, the third amplification stage primarily serves to approximately linearize the response of the feedback system by increasing the gain at low signal levels and suppress it at high signal levels, which is accomplished by adding a diode (Digi-Key XXX) in series with a resistor $R_h$ in parallel to the usual gain resistor $R_l$ in the feedback arm of the operational amplifier.
+This can be clearly seen to acheive the desired effect in two exreme cases - far below the diode drop, the diode is an open circuit and the gain is set by $R_l$, where above the diode drop it is a closed circuit where the gain is set by the resistor $R_h$.
+Naturally, the voltage drop over the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode (3.3 V).
+Another function of the last stage is to clamp the voltage to zero, in order to prevent an unstable positive feedback behavior due to the quadratic nature of the mixer.
+Last of all, since the mixer is a current driven device the last stage of the feedback loop uses an OPA627 (Digi-Key XXX) as a current buffer.
+
+A common behavior of analog feedback systems with integration components is termed \textit{integrator wind-up}, and occurs when the feedback loop is manually broken, and the actuator can no longer adjust the state of the controlled parameter.
+In this regime, the integrator accumulates a large positive or negative value, such that when control is restored, the system is uncontrolled until the integrator reaches the desired value.
+In this case, \textit{integrator wind-up} occurs when the high-isolation RF switch is open during the initial cooling procedure, and closed when the lattice is desired. 
+Since the lattice must usually be applied adiabatically, fast transients due to integrator windup are highly destructive.
+To solve this system, a bypass switch (Digi-Key XXX) is placed accross the capacitor of the second stage of the feedback circut, which bleeds the charge off the capacitor when the lattice is inactive.
 
@@
 
-\begin{itemize}
-\item evidence of fiber tip shaking if there were fans inside
-changing collimator dist wrt fiber - focus about 80 cm - focus through aom - no movable optics between AOM and chuck
-\item mode shape changes dramatically with pump current (output power)
-\end{itemize}
+\subsection{Intensity Control}
 
-\subsection{Isolation}
-\begin{itemize}
-\item backreflections are bad,
-\item retroreflection -> 2 stages
-\item as seen in ligo Yttg isolation decreases with optical intensity - coupling between optical effects and faraday
-\item not as bad as ligo, since not in vacuum.
-\item thorlabs -> high power 5mm aperture -> BK7 bad
-\item waveplate ibs coating
-\item Can of mumetal for physics reasons
-\item attenuation of field is XXXXX
-\item watercooling
-\item stack 2x
-\end{itemize}
-
-DUMPING
--watercooled beamdumps far removed from the optics for thermal reasons
-\subsection{Intensity Control}
 2 Step intensity control
-
-\subsubsection{Berek Compensator}
-\begin{itemize}
-\item high dyn range actuator
-\item berek compensator
-\end{itemize}
 

### 2017-02-02 LatticeOptics/latticeOpticsV2.tex
text

@@
 Ultracold atoms in optical lattices have become a powerful platform for experiments ranging from investigations of strongly correlated systems, quantum state engineering, quantum computing architectures and precision metrology, among others.
-Further, the recent advent of quantum gas microscopy has enabled studies that exhibit unprecedented control over few atom systems that function at extremely low energy scales, down to the Hz level and below.
-Unfortunately, this rapid progress places ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
-Specifically, in experiments taking place at low temperatures, heating due to intensity noise on a lattice cannot be allowed to approach the thermalization timescales.
-Similarly, in experiments that rely on a small number of atoms contained by multiple traps cannot proceed until all traps are stable relative to each other down to a few-site leve.
+Further, the recent advent of quantum gas microscopy has enabled studies that exhibit unprecedented control over few atom systems that function at extremely low energy scales.
+However, this rapid progress places ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
+For example, in experiments at low temperatures, heating due to the intensity noise of a lattice cannot be allowed to approach the thermalization timescales lest the system fail to thermalize at the required temperature.
+Similarly, experiments that rely on a small number of atoms held by multiple traps places stringent requirements on the relative stability of the traps.
 We demonstrate a high power lattice system that exhibits levels of intensity noise below -120 dBc between 1 kHz and 3 MHz, and is positionally stable at the XXX site level. 
-This system has been successfully used in a Fermi gas microscope to investigate the charge and spin sectors of the Hubbard model with unprecedented control and fidelity.
+This system has been successfully used in a Fermi gas microscope to investigate the charge and spin sectors of the Hubbard model with unprecedented control.
 
-\section{The atoms}
+\section{High level Overview}
+The system requirements:
+
+The architecture of the system is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers.
+These amplifiers provide a sufficient amount of light but also substantially increase the noise of the light and degrade the mode shape. 
+The fiber amplifier output provides light is controlled to two feedback
 
@@
 Combined, these changes serve to suppress certain noise spurs measured in the relative intensity noise (RIN) of the fiber amplifier, as seen in figure 1. 
-The measurements were carried out on two fiber amplifiers from the same manufacturing batch, one with the modifications and one without.
+The measurements were carried out on a single fiber amplifier, prior to and after the modifications.
+The initial and final noise spectra were verified to be consistent between amplifiers coming from the same manufacturing batch.
+
+(WARNING: THIS SECTION IS BEING BUILT) The operation of the Nufern fiber amplifiers can be further optimized by finely controlling the cooling water required, by tuning the waveleng of the light supplied by the diodes that optically pump the gain fiber.
+Optimizing the temperature is advantageous because (1) the maximum output power of the fiber amplifier is increased due to the improved efficiency of the pump light and (2) the lifetime of the device is increased because less stray pump light needs to be absorbed when the pump light is separated from the desired light, reducing the thermal load.
+This is possible because the pump diodes are fixed directly to the water-cooling plate without temperature regulation.
+Adding a Peltier TEC and regulating to the optimal wavelength is possible, but is technically difficult as it requires large cooling power of $\approx100$ W per each of the three pump diodes and the associated complexity of three feedback loops.
+We use a single XXX heat exchanger to supply cooling water to an array of four fiber amplifiers and tune the temperature such that the average power supplied by the amplifiers supplying the $X$ and $Y$ lattices is optimized.
 

### 2017-06-09 LatticeOptics/latticeOpticsV3.tex
new version

% -*- mode: Latex -*-
% Time-stamp: "2015-02-18 17:55:40 sb"

\documentclass[twocolumn,aps,pra,showpacs,preprintnumbers,bibnotes]{revtex4-1}

\usepackage[T1]{fontenc}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{color}
\usepackage{amsmath}

%% Keep track of changes
%\usepackage[final]{changes}
\usepackage[draft]{changes}
\definechangesauthor[color=green]{AM}
\definechangesauthor[color=blue]{SB}

\DeclareMathOperator{\re}{Re}
\DeclareMathOperator{\im}{Im}

\newcommand\avg[1]{\left\langle#1\right\rangle}

\newcommand\unit[2]{\ensuremath{#1~\mathrm{{#2}}}}

\newcommand\Ket[1]{\ensuremath{|{#1}\rangle}}
\newcommand\Bra[1]{\ensuremath{\langle{#1}|}}

\newcommand\Isotope[2]{\ensuremath{^{#1}\mathrm{#2}}}
\newcommand\Li{\Isotope{6}{Li}}
\newcommand\K{\Isotope{40}{K}}
\newcommand\Rb{\Isotope{87}{Rb}}
\newcommand\Sr{\Isotope{87}{Sr}}
\newcommand\Yb{\Isotope{171}{Yb}}
\newcommand\Er{\Isotope{167}{Er}}
\newcommand\Dy{\Isotope{161}{Dy}}

\renewcommand{\vec}[1]{\ensuremath{\bm{#1}}}

\newcommand\NA{\ensuremath{\mathrm{NA}}}
\newcommand{\osim}{\ensuremath{\mathord{\sim}}}
\newcommand{\Erecl}{\ensuremath{E_\mathrm{rec}}}
\newcommand{\Ereca}{\ensuremath{E_\mathrm{rec}^\mathrm{(a)}}}
\newcommand\FIXME{{\color{red}\ensuremath{\mathrm{FIXME}}}}

\newcommand\TrapFreq{\ensuremath{\nu_t}}
\newcommand\RecoilEnergy{\ensuremath{E_\mathrm{rec}}}

\graphicspath{{./figures/}}
\begin{document}

\title{Design and Implementation of Stable High Power Optical Lattices for Quantum Gas Microscopy}

\author{Li Microscope Collective}
\author{M. Greiner}
\affiliation{
  Department of Physics, Harvard University,
  Cambridge, Massachusetts, 02138, USA}

\date{\today}
\begin{abstract}
We describe the design of a stable high power 1064 nm laser for use in optical lattice experiments. The system is based on a high quality mephisto NPRO seeding an array of four heavily modified fiber amplifiers. The intensity of every beam is stabilized with a low noise, nonlinear feedback system, and the waist can be smoothly controlled. 
\end{abstract}
\maketitle

\section{Introduction}
Ultracold atoms in optical lattices have become a powerful platform for experiments ranging from investigations of strongly correlated systems, quantum state engineering, quantum computing architectures, and precision metrology.
Further, the recent advent of quantum gas microscopy has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales.
However, this rapid progress places ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
For example, heating due to the intensity noise of any laser cannot be allowed to approach the longest thermalization timescales, lest the system fail to thermalize~\cite{Savard1997}. 
Since thermalization timescales generally grow with falling temperature, this complicates attaining low temperatures.
Similarly, experiments that rely on a small number of atoms held by multiple traps places stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.

In this note, we describe a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
It also exhibits positional stability of the lattice phase at the $<0.5\,\mu$m level and of the harmonic confinement at the few site level over the course of hours.

The architecture of the system is based on a single low-power, low-noise seed laser (Innolight Mephisto) that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices)\cite{Parsons2015}.
Each fiber amplifier (Nufern NuAmp SUB1174-34) provides approximately 30 W, required to attain sufficient trap frequencies.
The fiber amplifier output is controlled by two feedback loops which stabilize the light in the low power and high power regimes.
After stabilization, the laser is mode-shaped to produce a desired waist when focused in the atom plane. 
Just before the beam is launched toward the atoms, a small sample of it is imaged by a camera to monitor the pointing.

To avoid interference effects among the lattice axes, AOM's are used to detune the fiber amplifier seeds away from each other.
These amplifiers can amplify 150 mW of seed light to up to approximately 45 W at the expense of dramatically raised levels of noise. 
The noise stems partially from stimulated Brillouin scattering, which is intrinsic, and several technical sources, which are not.

The NuAmp suffers from several problems: it is controlled via a USB interface, which is suspected to cause ground loops which add noise and interference to the analog systems, as seen in figure \ref{fig:noises}.
We solve this problem by replacing the USB control board with a custom solution that is compatible with our custom control system and that carefully avoids ground loops. 
There are two power supplies in the fiber amplifier - a general purpose supply for the control electronics and first amplification stage and a high power current supply for the second stage. 
Despite the presence of a water-cooled cold-plate to cool the optical fiber and pump diodes, the high power supply is air cooled using a fan approximately $20$ cm away from the gain fiber. 
This fan is suspected to lead to increased noise at acoustic frequencies.
In order to reduce acoustic coupling and reduce switching power supply noise, both power supplies were removed from the fiber amplifier chassis, and the low power supply was replaced by a linear PSU (Acopian A24MT350M). 
Further, a high current line filter (MPE DS26387) was added to the high-power PSU (Lumina LDD-600-60-10-5VP/M).
Combined, these changes serve to suppress many of the noise spurs measured in the RIN of the fiber amplifier, as seen in figure \ref{fig:noises}. 
The measurements in parts (a)-(d) were carried out on a single fiber amplifier, prior to and after the modifications. The initial and final noise spectra were verified to be consistent between amplifiers coming from the same manufacturing batch.
The figure is based on fiber amplifiers from a relatively new batch, which, even in its unmodified configuration does not exhibit a large switching supply spur. 
This is not the case for certain older batches, where the spur is approximately 30 dB higher than the background.

The operation of the Nufern fiber amplifiers can be further optimized by finely controlling the cooling water required, which by tunes the wavelength of the light supplied by the diodes that optically pump the gain fiber.
Optimizing the temperature is advantageous because (1) the maximum output power of the fiber amplifier is increased due to the improved efficiency of the pump light and (2) the lifetime of the device is increased because less stray pump light needs to be absorbed when the pump light is separated from the desired light, reducing the thermal load on the system.

This is possible because the pump diodes are fixed directly to the water-cooling plate without additional temperature regulation.
Adding a Peltier TEC and regulating to the optimal wavelength is possible, but is technically difficult as it requires large cooling power of $\approx100$ W per each of the three pump diodes and carries the associated complexity of three feedback loops.
We use a single, dedicated heat exchanger (TermoTek P21518970) to supply cooling water to an array of four fiber amplifiers and tune the temperature such that the average power supplied by the amplifiers supplying the $X$ and $Y$ lattices is optimized, while simultaneously keeping the temperature of the amplifier well within a safe range.
Experimentally, we have found that more power can be gained by running the amplifiers at hotter temperature, but we have avoided doing this in an effort to increase the lifetime.
We have experimentally found that there is variation in the sensitivity to the cooling water temperature between fiber amplifiers.

\begin{figure}
  \begin{center}
    \includegraphics{fig/fig3_combined.pdf}
    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed. (b) Shows the open (OL) and closed (CL) loop behavior of the high power feedback loop. (c) Shows open loop behavior of the low power feedback loop after making the modifications. (d) Closed loop behavior of the loop system without additional filtering, measured on the same setup as (c).}\label{fig:noises}
  \end{center}
\end{figure}

\subsection{Mode and beam shaping}

\begin{figure}
  \begin{center}
    \includegraphics{fig/optical_layout_wide.pdf}
    \caption{\textbf{Optical layout of the optical lattice system for beam shaping and modulation.}}\label{fig:optical_layout}
  \end{center}
\end{figure}

The free-space propagation of the fiber amplifier output presents several technical challenges:
\begin{enumerate}
  \item The high optical power poses a significant danger to users and equipment.
  \item The high optical power is sufficient to induce substantial thermal lensing in some optics. 
  \item The positional fluctuations of the waist at the atoms cannot be allowed to exceed a few microns from shot to shot. 
\item By construction, the beam is retro-reflected, threatening the lifetime of the amplifier unless sufficient isolation is used. 
\item Approximately $1$ W of power leaks into the undesired cladding modes of the fiber. 
  \end{enumerate}

In order to address these challenges, we carefully engineered an optical system, shown in figure \ref{fig:optical_layout}, that cleans up the beam, controls its intensity between $10\,\mu$W and $20$ W, and ensures good pointing stability.
Due to the high laser power, fused silica glass is used wherever possible.
%except in the acousto-optic modulator (which is TeO$_2$), Berek compensator (which is quartz), and optical isolators, to minimze thermal lensing.
For the same reason, IBS coatings are used wherever possible, due to the higher damage thresholds.
Further, even small reflections pose both a danger to the users and risk damaging cables or starting a fire, so to alleviate this danger, all undesired beams above $100$ mW are directed to water cooled beam-dumps, which are placed as far as possible from critical beam paths. 
Weaker beams are dumped on uncooled diffusive beam catchers.

The large-diameter fiber tip at the output of the fiber amplifier is mounted in a monolithic mount made from oxygen-depleted copper.
The beam is collimated using an $f=20$ mm fused-silica, air-spaced triplet collimator (Opto-Sigma HFTLSQ-15-20PF1).
Then, the polarization is cleaned up using an IBS coated thin-film plate polarizer (Precision photonics PO1056-FY), which has the added benefit of rejecting the undesired cladding modes. 
The fact that the lattice is retro-reflected, combined with the observation that optical isolation falls with applied optical power~\cite{Yoshida1999} means that two stages of optical isolators must be used. 
The optical isolators are based on $5$ mm diameter isolators from Thorlabs (IO-5-1064-VHP), with the default cube polarizers replaced by IBS coated thin-film plate polarizers. 
Since the isolators are located approximately $1$ m away from the ultracold atomic system, undesired stray fields can have a dramatic effect.
To overcome this problem the isolators are enclosed in mu-metal shielding.

\subsection{High power feedback}

After the beam has been cleaned up and isolated, it is important to consider two aspects of the desired experiment: 
\begin{enumerate}
\item The lattice power must be continuously tunable from around $10$ $\mu$W to around $20$ W. 
\item The location of the minimum Gaussian beam waist must be accurately positioned to overlap the other lattices and dipole traps present in the experiment, and must remain there for the duration of the collection process (hours to days).
\end{enumerate}
To satisfy the first of these requirements, a two-stage feedback system is implemented. The reason for the two stages is simple: the experiment typically operates in one of two regimes, which we will term \textit{detection} and \textit{interaction}. 
In the interaction phase of the experiment, the lattice is relatively shallow ($\approx 100-200$mW, corresponding to depths of $\approx 10 E_R$, where $E_R$ is the geometric recoil of the lattice), allowing atoms to tunnel and interact with other atoms. 
In this regime, fine and potentially fast control is required.
In the detection phase, the depth of the lattice is dramatically raised ($\approx 2000 E_R$), isolating atoms in their individual wells so that Raman sideband imaging can be performed~\cite{Parsons2015}.
In the detection regime, the control need not be fast, and the passive stability of the Mephisto laser ensures that noise is low at relevant frequency scales ($\approx 2$ MHz).
Thus, two loops are utilized, a fast loop that uses an acousto-optic modulator to actuate the laser power at low powers, and a slow loop which uses a Berek compensator, to actuate in the high power mode.

After the isolation stage, we use the sequence of optical elements shown in figure \ref{fig:optical_layout}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs GVS002, or Camtech 8320K, depending on beam path) half-wave plate, and polarizer. 
The Berek compensator is a simple $z$-cut quartz plate coated to be anti-reflecting at 1064 nm. 
By tilting the plate about its vertical axis, the extraordinary axis is mixed into the propagation of the beam, leading to a tilt-dependent bi-refringence that can be tuned from a zero-wave plate past a half-wave plate.
Combined with the subsequent polarization optics, rotation of the Berek compensator changes the transmitted power with perfect contrast and transmitted power as a function of the tilt angle is shown in figure \ref{fig:berek}.

Full modulation contrast is achieved when the fast axes of the waveplates around the Berek compensator $\theta$ are at $22.5^\circ$ to the rotation axis of the Berek compensator.
In that case, if the Berek compensator does not change the polarization, the light is fully transmitted. 
If it functions as a half-wave plate, the light is fully rejected, with a smooth crossover between the two cases as the Berek angle, $\phi$, is adjusted.
This contrast can be reduced by varying $\theta$, to the limiting case where $\theta=0$, where the rotation of the Berek compensator does nothing, since the polarization of the light is parallel to the rotation axis of the quartz.

\begin{figure}
  \begin{center}
    \includegraphics{fig/step_response.pdf}
    \caption{\textbf{Berek compensator based feedback loop} performance showing the impulse response (a) at relatively low powers and the corresponding Bode plots (b-c).}\label{fig:berek_step_response}
  \end{center}
\end{figure}
A key point is that, as seen in figure \ref{fig:berek}, if the two waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
The waveplates are detuned such that the maximum power needed in \textit{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator. 
Naturally, rotation of a parallel plate in the beam path induces a shift of the beam, but this is acceptable because the Berek compensator is only active during the imaging phase of the experiment, when the position of the underlying harmonic trap is largely irrelevant.
Fortunately, the spatial phase of the optical lattice is set by the retro-reflector mirror, which does not move, and is not affected by the rotation of the Berek compensator.
This system functions as the actuator arm of a feedback loop, where the power of the beam is measured using a low noise photodiode. This feedback loop regulates the lattice between $1$ W of optical power and its maximum value (which depends on the amplifier, but is $\approx20$ W).
The step response and corresponding Bode plots~\cite{Bechhoefer2005} are shown in figure \ref{fig:berek_step_response}.
A polarization rotation by $2 \pi$ is produced by approximately $3^\circ$ of axial rotation of the quartz plate. 
Since we never need to rotate the plate outside this range, the position is constrained to this window in software.

\subsection{Low power feedback}
%The high power feedback used in the \textit{imaging} phase of the experiment and is exceedingly robust
%, and allows the user to raise the power and ensure an adequate Lamb-Dicke parameter\cite{Parsons2015}. 
The high power feedback used in the \textit{imaging} phase of the experiment is exceedingly robust because the heating rate from scattered resonant imaging light far exceeds any technical heating from the loop.
Even if the loop was designed by your worst enemy\footnote{I have received a number of comments about this particular statement. Yes, it was a hyperbole, and I concur - most likely readers of this thesis could design a system that would result in a heating rate exceeding the cooling, but you would definitely have to be malicious to do so.}, the heating would be entirely compensated by the simultaneous Raman cooling~\cite{Parsons2015}.

In contrast, the low power loop that controls the lattice laser during the \textit{interaction} phase of the experiment is critically important:
\begin{enumerate}
  \item Its RIN is one of the factors limiting the system temperature.
  \item It cannot affect the pointing.
  \item It must have closed loop bandwidths of $\geq1\mathrm{\,kHz}$, and open loop modulation bandwidths $\geq 100\mathrm{\,kHz}$.
\end{enumerate}
To this end, we use actuate the optical power using a TeO$_2$ AOM (Gooch \& Housego AOMO 3080-198), where the power of the RF supplied to the AOM is used to actuate the fast, low power feedback loop.
The AOM was chosen for its low thermal lensing and easily-accessible RF powers. 
It is mounted on a custom-built, monolithic, water-cooled flexure mount that allows optimization of the AOM efficiency, that has been found to remain stable over years of operation.

\begin{figure}
  \begin{center}
    \includegraphics{fig/circuits.pdf}
    \caption{\textbf{Feedback circuits.} (a) The reverse-biased photodiode. (b) Externally referenced phase-locked loop. (c) Nonlinear loop filter. (d) RF power modulation using a mixer.}\label{fig:circuits}
  \end{center}
\end{figure}
The feedback circuit is shown in figure \ref{fig:circuits}a. A pair of low noise photodiodes measures the optical power of the beam sampled with a weakly reflective optic (Thorlabs BSF10-C). 
The beam sampler is wedged in such a way that the two reflections diverge from one another, allowing us to illuminate both photodiodes. 
One of the sampled beams is attenuated by a factor of $20\times$ by reflection off of an uncoated fused silica glass plate, such that the dynamic range of its photodiode covers $0-20$ W of the beam directed at the atoms, and controls the Berek compensator based, high-power, feedback loop. 
The other beam is not attenuated, save by the beam sampler, and its dynamic range covers $0-1$ W.
To prevent damage to this photodiode when the system is at its highest powers, a shutter (Stanford Research Systems SR475) blocks the light when the high power loop is active.
The low power photodiode passes its signal $V_{\mathrm{pd}}$ to a loop filter circuit, which compares it to the control system's set-point, generated by digital to analog converter.
The loop filter's output controls the IF port of a microwave mixer (Minicircuits ZFM-2-S+), effectively modulating the RF power supplied by a low noise phase-locked loop (PLL).
The resulting RF signal is then amplified and sent to the AOM.
Let us now consider every part of this signal chain individually.

\subsubsection{Phase-locked loop (PLL)}
The local oscillator (LO) RF source is a custom-built printed circuit board (PCB) implementing a phase locked loop (PLL) based on the ADF4002 IC and Crystek's CVCO55CL-0060-0110 voltage controlled oscillator (VCO), preamplified with a low noise amplifier (Minicircuits PSA4-5043+\footnote{This part has a plastic case which melts slightly if placed in a reflow oven, but still works as specified.}). 
To ensure frequency stability (which translates directly into beam pointing of the laser), the PLL is locked to the $10$ MHz clock distributed around the lab.
In addition to PLL functionality, the board also contains two, digitally-controllable, high-isolation RF switches, giving a total isolation exceeding $90$ dB.

The spectrum and relative intensity noise of the PLL can be found in figure \ref{fig:pll}. 
Vitally, the spectrum of the PLL exhibits phase noise comparable to that of typical VCO\footnote{Strictly speaking, a $-90$ dB phase noise is worse than specified. 
However, the measurement was carried out in ``peak detection'' mode on the spectrum analyzer, which artificially inflates the numbers by approximately 10 dB. 
This happens because the power at multiple frequency bands is measured within each frequency step on this plot, and in ``peak detection'', the highest is reported (all noise measurements in this work were carried out in ``RMS detection'', which is more suited for that purpose). The other reason that the phase noise appears worse than specified is that the dynamic range of the spectrum analyzer used is 100 dB, and we approach close to that limit.}, without the slow frequency drift characteristic to these devices.
Elimination of the carrier drift is worth the added phase noise because any drift of the frequency affects the steering of the laser beam passing through the AOM, which is entirely unacceptable since it would misalign the optical lattice.

\begin{figure}
  \begin{center}
    \includegraphics{fig/pll.pdf}
    \caption{\textbf{PLL performance} (a) The spectrum of the PLL, exhibiting phase noise of better than $-90$ dBc $100$ kHz away from the carrier. (b) The RIN of the local oscillator based on the PLL. The noise level is seen to be at or below the noise floor of the measurement device.}\label{fig:pll}
  \end{center}
\end{figure}

\subsubsection{Photodiode}

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.1]{fig/cut_photodiode.jpg}
    \caption{\textbf{Photodiode photo} showing that the ``can'' of the photodiode has been cut, to prevent etalon-like behavior.}\label{fig:cut_pd}
  \end{center}
\end{figure}

Fast, low-noise photodiodes are required both to provide the monitoring arm of the feedback loop and to characterize the RIN of the system.
An ideal device would have a bandwidth up to approximately 3 MHz\footnote{The maximum attainable trap frequencies in the system are around 1.5 MHz, and parametric heating is driven by $2\times$ the trap frequency}, with a noise floor below approximately -150 dBc over that range.
To approach these specifications, we use a custom designed PCB that implements a simple trans-impedance amplifier~\cite{Graeme1995} in a convenient physical package, providing a bandwidths in the 0.1-10 MHz range, depending on the trans-impedance gain set by a resistor. 
The photodiode can be safely operated up to incident powers of approximately 10 mW, which sets a -164 dBc/Hz shot noise limit on the RIN that can be detected. 
In practice, we typically operate the photodiodes with $\approx 5$ mW of incident power.
A photodiode with a bandwidth (BW) of 6 MHz is used to characterize the system, while photodiodes with a bandwidth of 330 kHz (and correspondingly higher gain) are used to perform the feedback.

The chosen photodiode (Hamamatsu G8370-01) is an InGaS based, small-area, low-noise design with a high efficiency at 1064 nm.
Prior to use, the protective window is removed from the photodiode to prevent interference effects, as seen in figure \ref{fig:cut_pd}.
Further, to reduce the capacitance of the system, a reverse bias of 6.9 V is applied to the photodiode by a temperature-stabilized voltage reference (Linear Technology LM399).
The trans-impedance circuit is shown in figure \ref{fig:circuits}. 
It converts the photo-current supplied by the photodiode to a voltage signal using the low noise Texas Instruments OPA843 op-amp. 
To reduce electrical pickup and prevent ground loops, the electronic assembly is housed in a metal enclosure and mounted to the optical table using electrically insulating mica posts.

Light is focused onto the photodiode using a 25.4 mm lens such that the beam at the photodiode is significantly smaller than the photodiode diameter, to prevent pointing fluctuations from registering as amplitude fluctuations. 
An iris and interference filter (Semrock FF01-1020/LP25) are used to eliminate stray sources of light.

\subsubsection{Digital to analog converter}
The digital to analog converter (DAC, Texas Instruments DAC9881) connects the experimental digital control system to the analog control loop for the lattice. 
By definition, an ideal control loop would translate any noise on the analog signal from the DAC to the laser light, meaning that a poorly designed DAC would inherently limit the lattice laser performance.
The noise on the DAC, when it is programmed to output a constant voltage is shown in figure \ref{fig:da_rin}, and is found to be roughly constant at a level of $-150$ dBc - more than acceptable.
When the state of the DAC is changed, such as during a ramp, this noise level may be higher, due to the so-called ``glitch'' energy, as seen in the figure.
The transient noise, while unfortunate, is mitigated by two factors: (1) it is only present when the lattice power is altered, which happens during lattice loading - a lattice at a fixed power will have negligible RIN contributions from the DAC. Further, (2) the loop filter will filter the noise at these frequencies.

\begin{figure}
  \begin{center}
    \includegraphics{fig/da_rin_scan.pdf}
    \caption{\textbf{Relative intensity noise of the digital to analog converter} at a fixed output voltage and while changing values. To measure the transient RIN, a $20$ ms, triangle wave with a DC offset and modulation depth of $15$\% of the DC offset was produced by the device. The triangle wave accounts for the series of spurs at low frequencies that fall with increasing frequencies. At frequencies above approximately $4$ kHz, the spectrum is dominated by noise due to transient ``glitches'' that emerge when the device changes its output state.}\label{fig:da_rin}
  \end{center}
\end{figure}

\subsubsection{Loop filter}

The connection between the actuation and monitoring mechanisms of the feedback system is the loop filter, which compares the \textit{set-point} signal, $v_s(t)$, supplied by the experimental control system and the monitoring signals $v_m(t)$, to adjust the actuation accordingly.
We use a simple, purely integrating design based in three stages, as seen in figure \ref{fig:circuits}, based on TI's OPA211 op-amp.
The first stage computes and amplifies an error signal, $e(t)=v_m(t)-v_s(t)$, which is integrated by the second stage. 
The integral gain is set using a low-drift trim-pot. 
This is the case because within relevant frequency ranges, the AOM can be well approximated by a pure time delay process (with delay given by the RF travel time across the crystal $\approx 1 \mu\mathrm{s}$).
In this scenario, the $P$ term must be small to avoid instability at the $\pi$ phase shift point, and a pure $I$ controller is optimal~\cite{Skogestad2001}.
For debugging purposes, the loop filter features buffered photodiode monitor and error signal monitor outputs.

The third stage of the loop filter is used to accommodate the fact that the actuation arm is in nonlinear - the optical power transmitted by the AOM is proportional to the RF power incident on it $P_{\mathrm{rf}}\propto v_{if}^2$, where $v_{if}$ is the actuation signal supplied to the IF port of the mixer.
In effect, if the rest of the feedback system was linear, this would correspond to a quadratically increasing gain until the AOM is saturated, which could lead to slow behavior at low signal levels and ringing at higher signal levels.
Even worse, since the mixer is insensitive to the sign of the voltage applied, the gain is actually negative for negative voltages, resulting in an unstable system, which thus requires a current clamp.
This stage linearizes the response by increasing the gain at low signal levels and suppressing it at high signal levels by using a diode (Digi-Key BAT54S) in the feedback arm.
This can be seen by considering two extreme cases - far below the diode drop, the diode is an open circuit and the gain is set by $R_l$, where above the diode drop it is a closed circuit where the gain is set by the resistor $R_h$. 
Naturally, the voltage drop over the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode ($3.3$ V).
Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in figure \ref{fig:bandwidth}.
Were it not for the linearization, the gain of the mixer would change by $10\times$ over a dynamic range spanning two orders of magnitude.
Another function of the last stage is to clamp the voltage to be strictly $>0$, in order to prevent an unstable positive feedback behavior, which is done using diode clamp on the output arm~\cite{Horowitz2015}.
Last of all, since the mixer is a current driven device, the last stage of the feedback loop uses TI's OPA627 op-amp which is able to supply tens of mA of current at an output impedance of $50$ $\Omega$.

\begin{figure}
  \begin{center}
    \includegraphics{fig/low_power_bandwidths.pdf}
    \caption{\textbf{Loop bandwidth dependence on the set-point}. (a) shows the $3$ dB and $\pi$ phase shift points for the $X$ lattice (also known internally as the ``northeast'' lattice. (b) shows the same for the $Y$ lattice, known as the ``northwest''.}\label{fig:bandwidth}
  \end{center}
\end{figure}

A common behavior of analog feedback systems with integration components is termed \textit{integral wind-up}~\cite{Bechhoefer2005}, and occurs when the feedback loop is manually broken, and the actuator can no longer adjust the state of the controlled parameter. 
In this regime, the integrator accumulates a large positive or negative value, such that when control is restored, the system is uncontrolled until the integrator reaches the desired value.
In our case, \textit{integrator wind-up} occurs when the high-isolation RF switch is open during the state preparation procedure, and closed when the lattice is desired. 
Since the lattice must usually be applied adiabatically, fast transients due to this windup can result in heating.
To solve this system, a bypass switch (Maxim MAX4503) is placed across the capacitor of the second stage of the feedback circuit, which siphons the charge off the capacitor when the lattice is inactive.
Even when the switch is closed, its resistance is nonzero (due to a protection resistor which limits the current that can pass through the switch), the conditions leading to integral windup in an unprotected system still lead to charge accumulation on the integral capacitor, albeit at a much reduced level.
Thus, in addition to the switch, when the system is inactive, the set-point is set to within ($\approx 200$ $\mu$V) of the dark signal from the photodiode, making the error signal very small.

To avoid a so-called ``servo bump'' in the noise spectrum, and because there is little need for fast, closed-loop control, the loop filter is tuned very conservatively, to a bandwidth of approximately 10 kHz over most of the range.
However, a small amount of tuning can raise this to up to $\approx150$ kHz, which is limited by the acoustic wave propagation delay of the AOM.
Although fast, closed-loop control is impossible in the current configuration, the last stage of the loop filter features an adder, connected to an optional ``feed-forward'' port, which can be used to modulate the RF power at frequencies above the bandwidth.

Although it is an essential part of the system, the loop filter is also one of its major limitations. Figure \ref{fig:noises} shows the noise performance of the output of the fiber amplifiers in open loop as compared to the noise in closed loop. Although noise near DC is lowered (as expected from a closed loop system), noise outside the loop bandwidth is increased in the range of $10$ to $450$ kHz as seen in subfigures (c) and (d).
This can be explained by the Johnson noise~\cite{Horowitz2015} on the $1$ k$\Omega$ input resistors, amplified by the amplification stages of the loop filter\footnote{This seems like a small quantity (-174 dBm), but there are several levels of amplification, and the voltage supplied to the mixer is small ($\approx 0.1 V$), all of which works against the experimentalist.}. 
The sharp drop off at the $450$ kHz point is due to the low-pass filter centered there, placed on the output of the loop filter.
When this was determined to be a problem, and we decided that a bandwidth of higher than $10$ kHz was not required in the near term, a first order low pass with a $3$ dB frequency of $10$ kHz, was also added, leading to the noise spectrum seen in subfigure (b), as compared to (a) in figure \ref{fig:low_pass_noises}\footnote{The fiber amplifier used to take this data was different from the one used for \ref{fig:noises} different fiber amplifiers, which explains the small discrepancies.}.

\begin{figure}
  \begin{center}
    \includegraphics{fig/low_pass_filters.pdf}
    \caption{\textbf{Laser noise of the lattice system with and without additional low pass filters} (a) Closed loop laser made a fiber amplifier (different than the one in figure \ref{fig:noises}. (b) Noise on the same system as (a), but with extra filters.}\label{fig:low_pass_noises}
  \end{center}
\end{figure}

\subsubsection{Beam shaping}
After the beam has passed through the feedback optics, it must be applied to the atoms. To that end, we use a $2f$ telescope of short focal length triplet collimator lenses to expand the beam, and then focus it with a long focal length lens.
We focus the lattice to a $70-90$\,$\mu$m waist at the position of the atoms.
In order to verify that the waist is positioned correctly, we use a temporary mirror to redirect the beam away from the glass cell and onto a camera positioned in the plane that would correspond to the position of the atoms had it not been for the temporary mirror.
The resulting beam at the atoms has an $m^2\leq1.4$.

To prevent unwanted interference, the lattice beams enter the glass cell at an angle. 
Unfortunately, due to the angle of incidence, the beam contains both $S$ and $P$ polarizations, which are reflected differently, altering the polarization state of the beam.
Even worse, this happens on both the initial and retro-reflected pass through the glass cell.
For this reason, we use a QWP and HWP to optimize the interference contrast of each lattice\footnote{We do this by optimizing on the trap frequency of lattice, measured using parametric heating. This is a relatively tedious procedure.}.

\section{Beam monitoring and alignment}

Improved spatial resolution and control have given experimentalists the ability to use relatively few atoms~\cite{Preiss2015, Choi2016, Mazurenko2016} that are simultaneously addressed by multiple beams and held by multiple traps.
Such experiments place stringent bounds on the requisite stability.

The absolute positions of lattice sites cannot be allowed to change by more than approximately $10\%$ from experimental shot to shot.
Fortunately, this is relatively straightforward to ensure via careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which can be close to the position of the atoms and be made very stable~\cite{Huber2014}. 
We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours.

The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement, which, in turn, is determined by the positions of the ingoing and retro-reflected beams. 
In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in this work, \cite{Mazurenko2016} or \cite{Choi2016}), drift or fluctuation of the lattice position can pose a severe limitation.

The required positional stability is achieved through a combination of passive stability and active monitoring. 
Passive stability is ensured by using stable optomechanics (from the Thorlabs Polaris line), mounted at a low ($2$ in) beam height relative to the floating optical table.
The beam is enclosed with aluminum tubes throughout its path and the entire setup is enclosed, to suppress air currents.

Passive stability alone has been found to be insufficient to ensure smooth operation over many hours because external factors can lead to a slow drift in the pointing of the laser beams. 
To address this concern, each lattice axis is fitted with a remotely actuated mirror connected to the control software.
The actuators are Newport brand ``Picomotors'' (model 8302), fitted into a customized $2$ in mirror mount.

\end{document}

### 2017-06-19 LatticeOptics/latticeOpticsV4.tex
new version

--- 2017-06-09 LatticeOptics/latticeOpticsV3.tex
@@
-% -*- mode: Latex -*-
-% Time-stamp: "2015-02-18 17:55:40 sb"
-
 \documentclass[twocolumn,aps,pra,showpacs,preprintnumbers,bibnotes]{revtex4-1}
@@
 
-\title{Design and Implementation of Stable High Power Optical Lattices for Quantum Gas Microscopy}
+\title{Implementation of a stable, high-power optical lattice for quantum gas microscopy}
 
-\author{Li Microscope Collective}
+\author{A.M., S.B., F.H., M.P., C.C., G.J., D.G., M.G.}
 \author{M. Greiner}
@@
 \begin{abstract}
-We describe the design of a stable high power 1064 nm laser for use in optical lattice experiments.
-The system is based on a high quality mephisto NPRO seeding an array of four heavily modified fiber amplifiers.
-The intensity of every beam is stabilized with a low noise, nonlinear feedback system, and the waist can be smoothly controlled.
+We describe the design of a stable high power $1064\,$nm laser system for use in optical lattice experiments.
+The system is based on a low noise seed laser amplified with an array of four heavily modified \textit{Nufern} fiber amplifiers.
+The intensity of every beam is stabilized with a low noise, nonlinear feedback loop.
+The positional stability of the system is characterized and monitored in real time.
 \end{abstract}
@@
 
-\section{Introduction}
-Ultracold atoms in optical lattices have become a powerful platform for experiments ranging from investigations of strongly correlated systems, quantum state engineering, quantum computing architectures, and precision metrology.
+Ultracold atoms trapped in an optical lattice has become a powerful platform for experiments ranging from investigations of strongly correlated systems, quantum state engineering, quantum computing architectures and precision metrology\cite{Ye}.
 Further, the recent advent of quantum gas microscopy has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales.
@@
 
-In this note, we describe a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
-It also exhibits positional stability of the lattice phase at the $<0.5\,\mu$m level and of the harmonic confinement at the few site level over the course of hours.
+To address these concerns, we discuss a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
+The positional stability of the lattice phase is at the $<0.5\mu$m level and the stability of the harmonic confinement is at the few site level, measured over the course of hours.
 
-The architecture of the system is based on a single low-power, low-noise seed laser (Innolight Mephisto) that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices)\cite{Parsons2015}.
-Each fiber amplifier (Nufern NuAmp SUB1174-34) provides approximately 30 W, required to attain sufficient trap frequencies.
-The fiber amplifier output is controlled by two feedback loops which stabilize the light in the low power and high power regimes.
+\begin{figure}
+  \begin{center}
+    \includegraphics{fig/figure1/figure1.pdf}
+    \caption{\textbf{High level overview} showing the major components of the lattice laser feedback system.}
+  \end{center}
+\end{figure}
+
+The architecture is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices).
+These amplifiers generate enough light to perform site resolved imaging~\cite{Parsons2016}, but also substantially increase the level of noise and degrade the mode shape. 
+The fiber amplifier output is controlled by two feedback loops, which stabilize the light in the low power and high power regimes.
 After stabilization, the laser is mode-shaped to produce a desired waist when focused in the atom plane. 
@@
 
-To avoid interference effects among the lattice axes, AOM's are used to detune the fiber amplifier seeds away from each other.
-These amplifiers can amplify 150 mW of seed light to up to approximately 45 W at the expense of dramatically raised levels of noise. 
-The noise stems partially from stimulated Brillouin scattering, which is intrinsic, and several technical sources, which are not.
+\section{Laser system}
+The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately 2 W of 1064 nm light. 
+This commercial laser utilizes a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability.
+This source is split into four fibers (Thorlabs PM980-XP) using polarizing beam splitters (PBS).
+To avoid interference of the lattice beams, two of the beam paths pass through acousto-optic modulators (AOM), which detunes the lattice frequencies from each other.
+Figure \ref{fig:noises} shows the noise performance of only this subsystem.
+
+Quantum gas microscopy of \Li{} requires single site trap frequencies of approximately 1 MHz~\cite{Parsons2015} in order to be in the Lamb-Dicke regime, which is necessary to perform Raman sideband cooling.
+Such trap frequencies may only be attained using tightly focused high power beams, which requires that the seed power be amplified to approximately 30 W per lattice axis, which is done using Nufern Fiber amplifiers (NuAmp SUB1174-34).
+These amplifiers can amplify 150 mW of seed light to up to approximately 45 W. They use a length of doped fiber pumped with 808 nm light from fiber coupled diode sources to amplify 1064 nm light. 
+The amplification is performed using a two stage amplifier design, where the stages are controlled using separate power supplies and electronics.
+The high optical powers supplied by the fiber amplifiers raise two engineering difficulties:
+\begin{enumerate}
+  \item The fiber amplification process is susceptible to many technical noise sources, such as acoustic coupling of the fiber to the environment and electrical design of the amplifier, 
+  \item Stimulates Brillouin scattering (SBS) places a hard lower bound on the noise floor~\cite{Agrawal2013}. 
+\end{enumerate}
 
 The NuAmp suffers from several problems: it is controlled via a USB interface, which is suspected to cause ground loops which add noise and interference to the analog systems, as seen in figure \ref{fig:noises}.
-We solve this problem by replacing the USB control board with a custom solution that is compatible with our custom control system and that carefully avoids ground loops. 
+We solve this problem by replacing the USB control board with a custom-designed, Ethernet based solution that is compatible with our custom control system and that carefully avoids ground loops. 
 There are two power supplies in the fiber amplifier - a general purpose supply for the control electronics and first amplification stage and a high power current supply for the second stage. 
@@
 We have experimentally found that there is variation in the sensitivity to the cooling water temperature between fiber amplifiers. 
+%Figure\ref{fig:pow_and_noise}c. shows the responses of the fiber amplifiers currently in the system.
 
-\begin{figure}
+\begin{figure*}
   \begin{center}
@@
   \end{center}
-\end{figure}
+\end{figure*}
 
-\subsection{Mode and beam shaping}
-
-\begin{figure}
+\begin{figure*}
   \begin{center}
@@
   \end{center}
-\end{figure}
+\end{figure*}
 
@@
 
-\subsection{High power feedback}
+\section{Feedback System}
 
@@
 Combined with the subsequent polarization optics, rotation of the Berek compensator changes the transmitted power with perfect contrast and transmitted power as a function of the tilt angle is shown in figure \ref{fig:berek}.
-
+\begin{figure}
+  \begin{center}
+    \includegraphics{fig/berek_sim.pdf}
+    \caption{\textbf{Berek compensator} performance as a function of the Berek tilt angle $\phi$ and waveplate tilt angles.}\label{fig:berek}
+  \end{center}
+\end{figure}
 Full modulation contrast is achieved when the fast axes of the waveplates around the Berek compensator $\theta$ are at $22.5^\circ$ to the rotation axis of the Berek compensator.
@@
 
-\begin{figure}
+\begin{figure*}
   \begin{center}
@@
   \end{center}
-\end{figure}
+\end{figure*}
 A key point is that, as seen in figure \ref{fig:berek}, if the two waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
@@
 The high power feedback used in the \textit{imaging} phase of the experiment is exceedingly robust because the heating rate from scattered resonant imaging light far exceeds any technical heating from the loop.
-Even if the loop was designed by your worst enemy\footnote{I have received a number of comments about this particular statement.
-Yes, it was a hyperbole, and I concur - most likely readers of this thesis could design a system that would result in a heating rate exceeding the cooling, but you would definitely have to be malicious to do so.}, the heating would be entirely compensated by the simultaneous Raman cooling~\cite{Parsons2015}.
+Even if the loop was exceedingly noisy, the heating would be entirely compensated by the simultaneous Raman cooling~\cite{Parsons2015}.
 
@@
 \subsubsection{Phase-locked loop (PLL)}
-The local oscillator (LO) RF source is a custom-built printed circuit board (PCB) implementing a phase locked loop (PLL) based on the ADF4002 IC and Crystek's CVCO55CL-0060-0110 voltage controlled oscillator (VCO), preamplified with a low noise amplifier (Minicircuits PSA4-5043+\footnote{This part has a plastic case which melts slightly if placed in a reflow oven, but still works as specified.}).
+The local oscillator (LO) RF source is a custom-built printed circuit board (PCB) implementing a phase locked loop (PLL) based on the ADF4002 IC and Crystek's CVCO55CL-0060-0110 voltage controlled oscillator (VCO), preamplified with a low noise amplifier (Minicircuits PSA4-5043+).
 To ensure frequency stability (which translates directly into beam pointing of the laser), the PLL is locked to the $10$ MHz clock distributed around the lab.
@@
 The spectrum and relative intensity noise of the PLL can be found in figure \ref{fig:pll}. 
-Vitally, the spectrum of the PLL exhibits phase noise comparable to that of typical VCO\footnote{Strictly speaking, a $-90$ dB phase noise is worse than specified. 
-However, the measurement was carried out in ``peak detection'' mode on the spectrum analyzer, which artificially inflates the numbers by approximately 10 dB. 
-This happens because the power at multiple frequency bands is measured within each frequency step on this plot, and in ``peak detection'', the highest is reported (all noise measurements in this work were carried out in ``RMS detection'', which is more suited for that purpose).
-The other reason that the phase noise appears worse than specified is that the dynamic range of the spectrum analyzer used is 100 dB, and we approach close to that limit.}, without the slow frequency drift characteristic to these devices.
+Vitally, the spectrum of the PLL exhibits phase noise comparable to that of typical VCO, without the slow frequency drift characteristic to these devices. 
 Elimination of the carrier drift is worth the added phase noise because any drift of the frequency affects the steering of the laser beam passing through the AOM, which is entirely unacceptable since it would misalign the optical lattice.
@@
   \begin{center}
-    \includegraphics[scale=0.1]{fig/cut_photodiode.jpg}
+    \includegraphics[width=\columnwidth]{fig/cut_photodiode.jpg}
     \caption{\textbf{Photodiode photo} showing that the ``can'' of the photodiode has been cut, to prevent etalon-like behavior.}\label{fig:cut_pd}
@@
 Fast, low-noise photodiodes are required both to provide the monitoring arm of the feedback loop and to characterize the RIN of the system.
-An ideal device would have a bandwidth up to approximately 3 MHz\footnote{The maximum attainable trap frequencies in the system are around 1.5 MHz, and parametric heating is driven by $2\times$ the trap frequency}, with a noise floor below approximately -150 dBc over that range.
+An ideal device would have a bandwidth up to approximately 3 MHz (since trap frequencies in the system are $\approx1.5\,$MHz), with a noise floor below approximately -150 dBc over that range.
 To approach these specifications, we use a custom designed PCB that implements a simple trans-impedance amplifier~\cite{Graeme1995} in a convenient physical package, providing a bandwidths in the 0.1-10 MHz range, depending on the trans-impedance gain set by a resistor.
@@
 Although noise near DC is lowered (as expected from a closed loop system), noise outside the loop bandwidth is increased in the range of $10$ to $450$ kHz as seen in subfigures (c) and (d).
-This can be explained by the Johnson noise~\cite{Horowitz2015} on the $1$ k$\Omega$ input resistors, amplified by the amplification stages of the loop filter\footnote{This seems like a small quantity (-174 dBm), but there are several levels of amplification, and the voltage supplied to the mixer is small ($\approx 0.1 V$), all of which works against the experimentalist.}.
+This can be explained by the Johnson noise~\cite{Horowitz2015} on the $1$ k$\Omega$ input resistors, amplified by the amplification stages of the loop filter.
 The sharp drop off at the $450$ kHz point is due to the low-pass filter centered there, placed on the output of the loop filter.
-When this was determined to be a problem, and we decided that a bandwidth of higher than $10$ kHz was not required in the near term, a first order low pass with a $3$ dB frequency of $10$ kHz, was also added, leading to the noise spectrum seen in subfigure (b), as compared to (a) in figure \ref{fig:low_pass_noises}\footnote{The fiber amplifier used to take this data was different from the one used for \ref{fig:noises} different fiber amplifiers, which explains the small discrepancies.}.
+When this was determined to be a problem, and we decided that a bandwidth of higher than $10$ kHz was not required in the foreseeable future, a first order low pass with a $3$ dB frequency of $10$ kHz was  added, leading to the noise spectrum seen in subfigure (b), as compared to (a) in figure \ref{fig:low_pass_noises} (the fiber amplifier used to take this data was different from the one used for \ref{fig:noises} different fiber amplifiers, which explains the small discrepancies).
 
-\begin{figure}
+\begin{figure*}
   \begin{center}
@@
 
+\subsection{Heating rates}
+We have used the band mapping technique, described in \ref{sec:bloch}, to characterize the heating rates in the lattice at different powers~\cite{Blatt2015}.
+To do this, the cloud was held in a given lattice for a varied period of time, before band mapping was performed.
+Band mapping directly reveals the band occupations, and the lifetime of atoms in the ground band is closely related to the temperature.
+The results, shown in figure \ref{fig:heating_rates} revealed that lifetimes as high as tens of seconds can be achieved, but that the heating rates are consistently dominated by parametric heating induced transitions.
+This analysis was performed prior to adding extra 10 kHz filters to the system, and later measurements have revealed that heating rates in the $0.01-0.5$ W are approximately a factor of $2-5\times$ lower.
+
 \section{Beam monitoring and alignment}
-
 Improved spatial resolution and control have given experimentalists the ability to use relatively few atoms~\cite{Preiss2015, Choi2016, Mazurenko2016} that are simultaneously addressed by multiple beams and held by multiple traps.
@@
 
-The absolute positions of lattice sites cannot be allowed to change by more than approximately $10\%$ from experimental shot to shot.
-Fortunately, this is relatively straightforward to ensure via careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which can be close to the position of the atoms and be made very stable~\cite{Huber2014}.
-We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours.
+The absolute positions of lattice sites cannot be allowed to change by more than a small fraction ($\approx 10\%$) from experimental shot to shot.
+Conveniently, this is relatively straightforward to ensure via careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which can be close to the position of the atoms and be made very stable~\cite{Huber2014}.
+We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours, as seen in figure \ref{fig:averaged_mott}.
 
-The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement, which, in turn, is determined by the positions of the ingoing and retro-reflected beams.
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=\columnwidth]{fig/averaged_mott.png}
+    \caption{\textbf{Averaged images of Mott insulators}.
+A series of Mott insulators was created over the course of approximately one hour, and the average image is shown\cite{Greif2016}.
+If the lattice fluctuated across more than a small fraction of a lattice site, the modulation contrast would be quickly washed out.
+The absence of this effect means that the phase of the optical lattice is very stable.}\label{fig:averaged_mott}
+  \end{center}
+\end{figure}
+
+The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement. 
 In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in this work, \cite{Mazurenko2016} or \cite{Choi2016}), drift or fluctuation of the lattice position can pose a severe limitation.
@@
 The required positional stability is achieved through a combination of passive stability and active monitoring. 
-Passive stability is ensured by using stable optomechanics (from the Thorlabs Polaris line), mounted at a low ($2$ in) beam height relative to the floating optical table.
-The beam is enclosed with aluminum tubes throughout its path and the entire setup is enclosed, to suppress air currents.
+Passive stability is ensured by using stable optomechanics (largely from the Thorlabs Polaris line), mounted on short optical posts, ensuring a low ($2$ in) beam height relative to the optical table, which is floated to minimize vibrations.
+In order to further improve stability, the beam is enclosed with $1$ in aluminum tubes throughout its path and the entire setup is enclosed by metal plates\footnote{all plates are sanded to produce a rough finish, producing diffuse rather than specular reflections.}.
+To further isolate the experimental setup, the optical table is contained within an aluminum enclosure.
+As detailed in prior sections, care has been taken to minimize thermal lensing and drift in optics encountered by the lattice beam.
 
-Passive stability alone has been found to be insufficient to ensure smooth operation over many hours because external factors can lead to a slow drift in the pointing of the laser beams. 
-To address this concern, each lattice axis is fitted with a remotely actuated mirror connected to the control software.
-The actuators are Newport brand ``Picomotors'' (model 8302), fitted into a customized $2$ in mirror mount.
+Passive stability alone has been found to be insufficient to ensure smooth operation over many hours.
+Changes in weather conditions, load on the water-cooling systems and other external effects can lead to a slow drift in the pointing of the laser beams.
+The situation is further complicated by the fact that opening the enclosure changes the thermal state of the system, inducing misalignment. 
+For these reasons, each lattice axis is fitted with a remotely actuated mirror, controlled by the experimental control software over the Ethernet network, allowing for non-invasive, digital alignment of the system.
+The remote actuators are Newport brand ``Picomotors'' (model 8302), fitted into a customized $2$ in mirror mount, and work in a ``fire and forget'' manner, remaining passively stable when not in active use.
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics{fig/pointing_figure.pdf}
+    \caption{\textbf{Short term positional stability.} (a) A histogram of shot-to-shot step sizes along the transverse and longitudinal directions, with a Gaussian fit.
+(b) Correlations between the step size of subsequent shots.
+(c) Calibration data for the ``affine fit'' of the conversion from camera pixels to lattice dimentions.
+(d) Predicted location versus measured location along the transverse and longitudinal directions.
+(e,f) The measured position and predicted position of the atomic cloud.}\label{fig:stability}
+  \end{center}
+\end{figure*}
+
+To prevent external influences from contaminating large data sets, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams and eliminate (via post-selection) experimental realizations when the system was in an undesired state.
+A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the same plane as the atoms, producing a Gaussian image that is identical to that incident on the atoms.
+Naturally, the position of the atoms is dictated by the light field of both the incoming and retro-reflected beams, while the monitoring camera only observes the position of the in-going beam.
+To verify that the monitor camera could predict the true position of the atoms, the beam and the atoms were imaged simultaneously while a purposeful misalignment of the incoming beams was introduced.
+This was done by adiabatically loading one of the lattice beams ensuring that the atoms settle to its center, prior to performing site-resolved imaging~\cite{Parsons2015}.
+
+Over the course of 250 sequential experimental realizations, we monitored the position of the beam on the camera and the position of the atoms. 
+First, we characterized the passive stability of the optical axis along the transverse $x_t$ and longitudinal $x_l$ directions. 
+Figure \ref{fig:stability} a shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$($0.98(4)$) sites along the $x_t$($x_l$) directions, where this discrepancy is consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
+The means of both distributions are consistent with zero.
+If the trap followed a random walk with these step sizes, the experiment would be in trouble, since after only $100$ experimental shots, the trap would move by more than $10$ lattice sites.
+The situation is more fortunate, however, since the steps are heavily anti-correlated, as shown in figure \ref{fig:stability} (b).
+Once this correlation is taken into account, we estimate a drift of $8(1)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the transverse direction and $12(2)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the axial direction, compared to a beam waist of approximately $80$ $\mu$m ($\approx 140$ sites).
+
+In a real experiment, we cannot directly measure the position of the atoms and must rely on the measurement performed by the camera, related by an affine transformation.
+To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in figure \ref{fig:stability} c.
+
+Unfortunately, while this fit is acceptable for a short while ($\approx30\mathrm{ shots}$), the quality of the fit degrades over time, correspondingly degrading the predictive power. 
+The most likely culprit is thermal drift of the camera, since a displacement of approximately a pixel is very substantial to the predicted position, and each pixel is approximately 3 $\mu$m. 
+The camera housing is not engineered for low drift mounting, and the camera produces a substantial amount of heat\footnote{It heats up by a few degrees Celcius during operation}, making a few $\mu$m drift very likely.
+To deal with this problem, we point out that the affine transform is composed of three distinct parts - the rotation, scaling and offset. 
+Of these, only the offset is likely to drift with time.
+As a result, we developed a way of updating the calibration over time.
+To test this procedure, we analyzed the data set of camera measurements and atomic positions in the following way: we split the data set into sequential blocks of $20$ shots, each followed by a block of $8$ shots.
+The large blocks were treated as ``masked'' data, which we tried to predict, while the small blocks were treated as ``updating'' events used to update the offsets of the calibration.
+The results are shown in figure \ref{fig:stability} (d-f), showing a large degree of tracking between the predicted positions and measured position - the average displacement between the predicted position and measured position was $0.7$ lattice sites.
+
+The purpose of developing this system was twofold - to reduce measurement noise by filtering experimental shots that suffered any sort of positional fluctuation of either lattice beam, and to minimize the frequency of such events.
+As it stands, for the purpose of most measurements, the experiment can perform hundreds of cycles before the thermal drift becomes a problem.
+Further, if future experiments require the optical lattice to be more positionally stable than it is now, the monitoring and actuation system could be used in closed loop with no hardware changes to the experiment.
+Naturally, the transfer function of any such loop would have to be carefully engineered to account for the correlated behavior of the jumps and the timescale of the drift, but these are very solvable problems.
+
+\section{Long-term stability of the lattice structure}
+An interesting benefit of site-resolved imaging is that every measurement of the atomic distribution is also a direct measurement of the underlying lattice structure. 
+As discussed in the supplementary material of~\cite{Parsons2016, Greif2016}, the Fourier transform of an atomic distribution contains distinct peaks corresponding to the lattice structure, and these peaks can be used to extract the phase, relative angle, and spacing of the lattices.
+For this reason, I looked back at nine months of data spanning June 2016 through April 2017, in order to learn how these parameters change over time.
+Several interesting features can be seen from this figure \ref{fig:long_term_stability}.
+\begin{enumerate}
+  \item During the summer of 2016, the lattice spacing appears to have slowly varied over as much as 10\%.
+    This can be attributed to unexplained drifts of the optical system that required daily refocusing of the imaging system using an auxiliary lens, which simultaneously changed the magnification. 
+  \item The imaging system was simplified in September 2016, causing a sudden change in the magnification. 
+  \item The system has been more stable in the spring of 2017 - the lattice spacing $|v|$ exhibits fractional fluctuations $\sigma_{|v|}/\mu_{|v|}\leq 0.005$.
+  \item Unlike magnification, which sensitively depends on the imaging system focus, the angle is unlikely to be affected by the imaging system unless the camera is mechanically rotated.
+We measure that in the spring of 2017, the relative angle of the lattices has exhibited fluctuations with an RMS of $0.06^\circ$.
+  \item The behavior of the phase (not shown in figure \ref{fig:long_term_stability}) is consistent with being random, most likely due to the substantial drifts of the apparent magnitude of the lattice constant.
+\end{enumerate}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics{fig/lattice_stability.pdf}
+    \caption{\textbf{Long term positional stability over approximately nine months.}}\label{fig:long_term_stability}
+  \end{center}
+\end{figure}
+
+\section{Conclusion}
+We have presented the design and specifications of an optical lattice system that has been successfully used for quantum gas microscopy of low temperature phases of the Hubbard model.
+In this design, key emphasis has been placed on the stability of the pointing and the intensity of the optical lattice, of particular importance to the underlying physics.
+To improve performance, the system can be improved in a variety of ways, such as by:
+\begin{enumerate}
+  \item Replacement of the \textit{Nufern} fiber amplifiers with a lower noise model.
+  \item Replacement of the analog feedback loop by a low-noise digital loop.
+  \item Monitoring the position of the lattice laser beam in the Fourier, as well as image plane.
+  \item Active stabilization of the laser pointing.
+\end{enumerate}
+Even without these improvements, the system has exhibited robust and reliable performance in performing a wide variety of experiments.
+
+\bibliography{LatticeOpticsV4}
 

### 2017-06-21 LatticeOptics/latticeOpticsV4.tex
new revision

@@
 
-\author{A.M., S.B., F.H., M.P., C.C., G.J., D.G., M.G.}
-\author{M. Greiner}
+\author{A.M., S.B., F.H., M.F.P., C.S.C., G.J., D.G.}
+\author{M. G.}
 \affiliation{
@@
   We describe the design of a stable high power $1064\,$nm laser system for use in optical lattice experiments.
-The system is based on a low noise seed laser amplified with an array of four heavily modified \textit{Nufern} fiber amplifiers.
-The intensity of every beam is stabilized with a low noise, nonlinear feedback loop.
-The positional stability of the system is characterized and monitored in real time.
+The system is based on a low noise laser amplified by an array of four heavily modified, high-power fiber amplifiers.
+The intensity of every beam is stabilized using a nonlinear feedback loop.
+The position of the produced optical lattice is monitored in real time and its stability is characterized\footnote{This work is adapted from the PhD thesis of A.Mazurenko}.
 \end{abstract}
@@
 
-Ultracold atoms trapped in an optical lattice has become a powerful platform for experiments ranging from investigations of strongly correlated systems, quantum state engineering, quantum computing architectures and precision metrology\cite{Ye}.
+Optical lattice holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations, including strongly correlated systems, quantum state engineering, quantum computing and precision metrology.
 Further, the recent advent of quantum gas microscopy has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales.
-However, this rapid progress places ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
-For example, heating due to the intensity noise of any laser cannot be allowed to approach the longest thermalization timescales, lest the system fail to thermalize~\cite{Savard1997}. 
-Since thermalization timescales generally grow with falling temperature, this complicates attaining low temperatures.
-Similarly, experiments that rely on a small number of atoms held by multiple traps places stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.
+However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
+For example, heating due to the intensity noise cannot be allowed to approach the longest thermalization timescales, lest the system fail to thermalize~\cite{Savard1997}.
+Even if the system thermalizes, heating rates can limit the interrogation time available to probe a low-temperature state.
+In a similar vein, experiments that rely on a small number of atoms held by multiple traps place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity~\cite{Mazurenko2016}.
 
 To address these concerns, we discuss a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
-The positional stability of the lattice phase is at the $<0.5\mu$m level and the stability of the harmonic confinement is at the few site level, measured over the course of hours.
+The stability of the lattice phase is below the single site level and the stability of the harmonic confinement is at the few site level.
 
@@
     \includegraphics{fig/figure1/figure1.pdf}
-    \caption{\textbf{High level overview} showing the major components of the lattice laser feedback system.}
+    \caption{\textbf{High level overview} showing the major components of the lattice laser feedback system.}\label{fig:high_level}
   \end{center}
@@
 
-The architecture is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices).
-These amplifiers generate enough light to perform site resolved imaging~\cite{Parsons2016}, but also substantially increase the level of noise and degrade the mode shape. 
-The fiber amplifier output is controlled by two feedback loops, which stabilize the light in the low power and high power regimes.
-After stabilization, the laser is mode-shaped to produce a desired waist when focused in the atom plane. 
-Just before the beam is launched toward the atoms, a small sample of it is imaged by a camera to monitor the pointing.
+The coarse architecture of the system is shown in figure \ref{fig:high_level} and is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Parsons2016}).
+These amplifiers generate enough light to perform site resolved imaging~\cite{Parsons2015}, but also substantially increase the level of intensity and pointing noise. 
+The fiber amplifier output is controlled by two feedback loops, which stabilize the light in low power and high power regimes, discussed later.
+After intensity stabilization, the laser is mode-shaped to a desired waist.
+The optical system is engineered to be passively stable in terms of pointing, but the position and phase of the optical lattice are monitored in real time, and beam pointing can be controlled with remotely actuated mirrors.
 
 \section{Laser system}
-The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately 2 W of 1064 nm light. 
+\subsection{Seed laser system}
+The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately $2\,$W of $1064\,$nm light. 
 This commercial laser utilizes a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability. 
-This source is split into four fibers (Thorlabs PM980-XP) using polarizing beam splitters (PBS).
-To avoid interference of the lattice beams, two of the beam paths pass through acousto-optic modulators (AOM), which detunes the lattice frequencies from each other.
-Figure \ref{fig:noises} shows the noise performance of only this subsystem.
+This source is split into four fibers (Thorlabs PM980-XP), each connected to a fiber amplifier. 
+Three of these fiber amplifiers are used to produce the 3D optical lattice~\cite{Parsons2016}, and a fourth is used for transport~\cite{Huber2014}.
+To avoid interference of the lattice beams, two of the beam paths pass through acousto-optic modulators (AOM), which detuning the lattice frequencies from each other.
 
-Quantum gas microscopy of \Li{} requires single site trap frequencies of approximately 1 MHz~\cite{Parsons2015} in order to be in the Lamb-Dicke regime, which is necessary to perform Raman sideband cooling.
-Such trap frequencies may only be attained using tightly focused high power beams, which requires that the seed power be amplified to approximately 30 W per lattice axis, which is done using Nufern Fiber amplifiers (NuAmp SUB1174-34).
-These amplifiers can amplify 150 mW of seed light to up to approximately 45 W. They use a length of doped fiber pumped with 808 nm light from fiber coupled diode sources to amplify 1064 nm light. 
-The amplification is performed using a two stage amplifier design, where the stages are controlled using separate power supplies and electronics.
+\subsection{Fiber amplifier system}
+Quantum gas microscopy of \Li{} requires single site trap frequencies of approximately $1\,$MHz~\cite{Parsons2015} in order to be in the Lamb-Dicke regime necessary for Raman sideband cooling.
+Such trap frequencies may only be attained using tightly focused, high-power beams. 
+In practical terms, this requires approximately $30\,$W per lattice axis, which we attain using \textit{Nufern} Fiber amplifiers (NuAmp SUB1174-34).
+These amplifiers can amplify $150\,$mW of seed light to up to approximately $45\,$W.
+They use a length of doped fiber pumped with $808\,$nm light from fiber coupled diode sources to amplify $1064\,$nm light.
+The amplification is performed using a two stage design, where the stages are controlled and powered using separate power supplies and electronics.
+
 The high optical powers supplied by the fiber amplifiers raise two engineering difficulties:
@@
 
-The NuAmp suffers from several problems: it is controlled via a USB interface, which is suspected to cause ground loops which add noise and interference to the analog systems, as seen in figure \ref{fig:noises}.
-We solve this problem by replacing the USB control board with a custom-designed, Ethernet based solution that is compatible with our custom control system and that carefully avoids ground loops. 
-There are two power supplies in the fiber amplifier - a general purpose supply for the control electronics and first amplification stage and a high power current supply for the second stage. 
-Despite the presence of a water-cooled cold-plate to cool the optical fiber and pump diodes, the high power supply is air cooled using a fan approximately $20$ cm away from the gain fiber. 
-This fan is suspected to lead to increased noise at acoustic frequencies.
+The NuAmp suffers from several technical problems. 
+It is controlled via a USB interface, which complicates communications with an array of these devices.  
+Worse yet, it is suspected of causing ground loops which add noise and interference to the analog systems. 
+This added noise can be seen in figure \ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser.
+We solve this problem by replacing the USB control board with a custom-designed solution  that is compatible with our custom control system and engineered to avoid ground loops.
+
+Further sources of technicl noise arise from the design of the amplifier.
+There are two power supplies in the fiber amplifier - a general purpose power supply (PSU) for the control electronics and the first, low-power amplification stage and a high power supply for the second, high-power stage.
+Despite the presence of a water-cooled cold-plate for the gain fiber and pump diodes, the high power PSU is air cooled by an internal fan.
+This fan is expected to increase noise at acoustic frequencies and degrade pointing stability by increasing vibrations.
 In order to reduce acoustic coupling and reduce switching power supply noise, both power supplies were removed from the fiber amplifier chassis, and the low power supply was replaced by a linear PSU (Acopian A24MT350M).
 Further, a high current line filter (MPE DS26387) was added to the high-power PSU (Lumina LDD-600-60-10-5VP/M).
-Combined, these changes serve to suppress many of the noise spurs measured in the RIN of the fiber amplifier, as seen in figure \ref{fig:noises}. 
+
+These upgrades serve to suppress many of the noise spurs measured in the relative intensity noise (RIN) of the fiber amplifier, as seen in figure \ref{fig:noises}. 
 The measurements in parts (a)-(d) were carried out on a single fiber amplifier, prior to and after the modifications.
@@
 
-The operation of the Nufern fiber amplifiers can be further optimized by finely controlling the cooling water required, which by tunes the wavelength of the light supplied by the diodes that optically pump the gain fiber.
-Optimizing the temperature is advantageous because (1) the maximum output power of the fiber amplifier is increased due to the improved efficiency of the pump light and (2) the lifetime of the device is increased because less stray pump light needs to be absorbed when the pump light is separated from the desired light, reducing the thermal load on the system.
-
-This is possible because the pump diodes are fixed directly to the water-cooling plate without additional temperature regulation.
-Adding a Peltier TEC and regulating to the optimal wavelength is possible, but is technically difficult as it requires large cooling power of $\approx100$ W per each of the three pump diodes and carries the associated complexity of three feedback loops.
-We use a single, dedicated heat exchanger (TermoTek P21518970) to supply cooling water to an array of four fiber amplifiers and tune the temperature such that the average power supplied by the amplifiers supplying the $X$ and $Y$ lattices is optimized, while simultaneously keeping the temperature of the amplifier well within a safe range.
-Experimentally, we have found that more power can be gained by running the amplifiers at hotter temperature, but we have avoided doing this in an effort to increase the lifetime.
-We have experimentally found that there is variation in the sensitivity to the cooling water temperature between fiber amplifiers. 
-%Figure\ref{fig:pow_and_noise}c. shows the responses of the fiber amplifiers currently in the system.
+The SBS noise is fundamental to the fiber amplifier architecture and cannot be entirely avoided.
+However, since it is a function of fiber length and optical power, it can be minimized.
+To this end, we use custom-ordered amplifiers with a $0.5\,$m length output fiber, compared to the few meter standard lengths.
+In addition, we set the lowest pump diode current that yields enough power to perform imaging. 
+The rise of the noise floor as a function of the pump diode current can be seen in figure \ref{fig:noises}(a).
 
@@
 
+The operation of the Nufern fiber amplifiers can be further optimized by finely controlling the cooling water.
+The water temperature tunes the wavelength of the light supplied by the diodes that optically pump the gain fiber.
+Optimizing the temperature is advantageous because (1) the maximum output power of the fiber amplifier is increased due to the improved efficiency of pump light conversion and (2) the lifetime of the amplifier is increased because less stray pump light needs to be absorbed when the pump light is separated from the output, reducing the thermal load.
+
+This is possible because the pump diodes are fixed directly to the water-cooling plate without additional temperature regulation.
+Adding a Peltier TEC and regulating to the optimal wavelength is possible, but technically challenging (requiring cooling power of $\approx100\,$W per each of the three pump diodes).
+We use a single, dedicated heat exchanger (TermoTek P21518970) to supply cooling water to an array of four fiber amplifiers. 
+We tune the water temperature such that the average power supplied by the amplifiers supplying the $X$ and $Y$ lattices is optimized, while simultaneously keeping all reported amplifier temperatures below $\leq 30^\circ\mathrm{C}$\footnote{As recommended by a \textit{Nuferm} support engineer.}.
+Experimentally, we have found that more power can be gained by running the amplifiers at hotter temperature.
+
 \begin{figure*}
@@
 
-The free-space propagation of the fiber amplifier output presents several technical challenges:
+\subsection{Optical system}
+The free-space propagation of the fiber amplifier output presents several technical challenges and constraints:
 \begin{enumerate}
@@
   \item The high optical power is sufficient to induce substantial thermal lensing in some optics. 
-  \item The positional fluctuations of the waist at the atoms cannot be allowed to exceed a few microns from shot to shot. 
-\item By construction, the beam is retro-reflected, threatening the lifetime of the amplifier unless sufficient isolation is used. 
-\item Approximately $1$ W of power leaks into the undesired cladding modes of the fiber. 
+  \item The positional fluctuations of the waist at the atoms cannot be allowed to exceed a few microns between experimental realizations.
+\item By construction, the beam is retro-reflected, threatening the lifetime of the amplifier. 
   \end{enumerate}
 
-In order to address these challenges, we carefully engineered an optical system, shown in figure \ref{fig:optical_layout}, that cleans up the beam, controls its intensity between $10\,\mu$W and $20$ W, and ensures good pointing stability.
-Due to the high laser power, fused silica glass is used wherever possible.
-%except in the acousto-optic modulator (which is TeO$_2$), Berek compensator (which is quartz), and optical isolators, to minimze thermal lensing.
-For the same reason, IBS coatings are used wherever possible, due to the higher damage thresholds.
-Further, even small reflections pose both a danger to the users and risk damaging cables or starting a fire, so to alleviate this danger, all undesired beams above $100$ mW are directed to water cooled beam-dumps, which are placed as far as possible from critical beam paths.
+In order to address these challenges, we use a carefully engineered an optical system, shown in figure \ref{fig:optical_layout}, that collimates and polarizes the beam, controls its intensity between $10\,\mu$W and $20$ W, and ensures good pointing stability.
+Due to the high laser power, fused silica glass and IBS coatings are used wherever possible.
+Since reflections pose a danger to the users and equipment, all undesired beams above $100\,$ mW are directed to water cooled beam-dumps (to prevent temperature gradients on the table) placed as far as practical from critical beam paths.
 Weaker beams are dumped on uncooled diffusive beam catchers.
@@
 The large-diameter fiber tip at the output of the fiber amplifier is mounted in a monolithic mount made from oxygen-depleted copper.
-The beam is collimated using an $f=20$ mm fused-silica, air-spaced triplet collimator (Opto-Sigma HFTLSQ-15-20PF1).
-Then, the polarization is cleaned up using an IBS coated thin-film plate polarizer (Precision photonics PO1056-FY), which has the added benefit of rejecting the undesired cladding modes. 
+The beam is collimated using an $f=20\,$mm fused-silica, air-spaced triplet collimator (Opto-Sigma HFTLSQ-15-20PF1).
+The polarization is set using an IBS coated thin-film plate polarizer (Precision photonics PO1056-FY), which has the added benefit of rejecting the undesired cladding modes of the fiber, which carry about $1\,$W of light.
 The fact that the lattice is retro-reflected, combined with the observation that optical isolation falls with applied optical power~\cite{Yoshida1999} means that two stages of optical isolators must be used.
 The optical isolators are based on $5$ mm diameter isolators from Thorlabs (IO-5-1064-VHP), with the default cube polarizers replaced by IBS coated thin-film plate polarizers. 
-Since the isolators are located approximately $1$ m away from the ultracold atomic system, undesired stray fields can have a dramatic effect.
+The isolators are located approximately $1\,$m away from the ultracold atoms which are susceptible to  undesired stray fields.
 To overcome this problem the isolators are enclosed in mu-metal shielding.
+Actuation of the power is performed after the optical isolators, meaning that the full fiber amplifier output is continually passed through them. 
+This is advantageous because there are no thermalization transients introduced during the experimental sequence.
 
@@
 To satisfy the first of these requirements, a two-stage feedback system is implemented. 
-The reason for the two stages is simple: the experiment typically operates in one of two regimes, which we will term \textit{detection} and \textit{interaction}.
-In the interaction phase of the experiment, the lattice is relatively shallow ($\approx 100-200$mW, corresponding to depths of $\approx 10 E_R$, where $E_R$ is the geometric recoil of the lattice), allowing atoms to tunnel and interact with other atoms.
+Two stages are used because the experiment typically operates in one of two regimes, which we term \textit{detection} and \textit{interaction}. 
+In the interaction phase of the experiment, the lattice is relatively shallow ($\approx 100\,$mW, corresponding to depths of $\approx 10 E_R$, where $E_R$ is the geometric recoil of the lattice), allowing atoms to tunnel and interact with each other.
 In this regime, fine and potentially fast control is required.
@@
 In the detection regime, the control need not be fast, and the passive stability of the Mephisto laser ensures that noise is low at relevant frequency scales ($\approx 2$ MHz).
-Thus, two loops are utilized, a fast loop that uses an acousto-optic modulator to actuate the laser power at low powers, and a slow loop which uses a Berek compensator, to actuate in the high power mode.
+Thus, two control loops are utilized, a fast loop that uses an acousto-optic modulator to actuate the laser power at low powers, and a slow loop which uses a Berek compensator to actuate the laser in high power mode.
 
 After the isolation stage, we use the sequence of optical elements shown in figure \ref{fig:optical_layout}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs GVS002, or Camtech 8320K, depending on beam path) half-wave plate, and polarizer.
-The Berek compensator is a simple $z$-cut quartz plate coated to be anti-reflecting at 1064 nm. 
-By tilting the plate about its vertical axis, the extraordinary axis is mixed into the propagation of the beam, leading to a tilt-dependent bi-refringence that can be tuned from a zero-wave plate past a half-wave plate.
-Combined with the subsequent polarization optics, rotation of the Berek compensator changes the transmitted power with perfect contrast and transmitted power as a function of the tilt angle is shown in figure \ref{fig:berek}.
+The Berek compensator is a $z$-cut quartz plate coated to be anti-reflecting at $1064\,$nm. 
+By tilting the plate about its vertical axis by a few degrees, the extraordinary axis is mixed into the propagation of the beam, leading to  tilt-dependent bi-refringence that can be tuned from a zero-wave plate past a half-wave plate, represented by a retardation angle $\phi$.
+Combined with the subsequent polarization optics, rotation of the Berek compensator can vary the transmitted power with perfect contrast. 
+Figure \ref{fig:berek} shows the transmitted power as a function of retrardation angle $\phi$ and fast-axis angle $\theta$ of the waveplates surrounding the compensator.
 \begin{figure}
@@
 \end{figure}
-Full modulation contrast is achieved when the fast axes of the waveplates around the Berek compensator $\theta$ are at $22.5^\circ$ to the rotation axis of the Berek compensator.
-In that case, if the Berek compensator does not change the polarization, the light is fully transmitted. 
-If it functions as a half-wave plate, the light is fully rejected, with a smooth crossover between the two cases as the Berek angle, $\phi$, is adjusted.
-This contrast can be reduced by varying $\theta$, to the limiting case where $\theta=0$, where the rotation of the Berek compensator does nothing, since the polarization of the light is parallel to the rotation axis of the quartz.
+
+Full modulation contrast is achieved when $\theta=22.5^\circ$ to the rotation axis of the Berek compensator.
+This contrast can be reduced by varying $\theta$, to the limiting case where $\theta=0$, where the rotation of the Berek compensator does nothing, since the polarization of the light is parallel to the rotation axis of the quartz plate.
 
@@
 \end{figure*}
-A key point is that, as seen in figure \ref{fig:berek}, if the two waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
+A key point, as seen in figure \ref{fig:berek}, is that if the waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
 The waveplates are detuned such that the maximum power needed in \textit{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator.
@@
 Fortunately, the spatial phase of the optical lattice is set by the retro-reflector mirror, which does not move, and is not affected by the rotation of the Berek compensator.
-This system functions as the actuator arm of a feedback loop, where the power of the beam is measured using a low noise photodiode.
+This system functions as the actuator arm of a digital feedback loop, where the power of the beam is measured using a low noise photodiode.
 This feedback loop regulates the lattice between $1$ W of optical power and its maximum value (which depends on the amplifier, but is $\approx20$ W).
@@
 Since we never need to rotate the plate outside this range, the position is constrained to this window in software.
+Since two feedback loops are present in the system (the second one detailed in the next section), care must be taken so that they do not function simultaneously. 
+To accomplish this, the low power loop is always manually railed to its high extreme when the high power loop is active, and the digital high power loop is disabled when the low power loop is active.
 
 \subsection{Low power feedback}
-%The high power feedback used in the \textit{imaging} phase of the experiment and is exceedingly robust
-%, and allows the user to raise the power and ensure an adequate Lamb-Dicke parameter\cite{Parsons2015}. 
 The high power feedback used in the \textit{imaging} phase of the experiment is exceedingly robust because the heating rate from scattered resonant imaging light far exceeds any technical heating from the loop.
@@
 \begin{enumerate}
-  \item Its RIN is one of the factors limiting the system temperature.
-  \item It cannot affect the pointing.
+  \item Its RIN can limit the system temperature.
+  \item It can affect the pointing.
   \item It must have closed loop bandwidths of $\geq1\mathrm{\,kHz}$, and open loop modulation bandwidths $\geq 100\mathrm{\,kHz}$.
 \end{enumerate}
-To this end, we use actuate the optical power using a TeO$_2$ AOM (Gooch \& Housego AOMO 3080-198), where the power of the RF supplied to the AOM is used to actuate the fast, low power feedback loop.
+To this end, we use an all-custom loop based on a TeO$_2$ AOM (Gooch \& Housego AOMO 3080-198), where the power of the RF supplied to the AOM is used to actuate the fast, low power feedback loop.
 The AOM was chosen for its low thermal lensing and easily-accessible RF powers. 
@@
 \end{figure}
-The feedback circuit is shown in figure \ref{fig:circuits}a. A pair of low noise photodiodes measures the optical power of the beam sampled with a weakly reflective optic (Thorlabs BSF10-C). 
+The feedback circuit is shown in figure \ref{fig:circuits}a.
+As seen in figure \ref{fig:optical_layout}, a pair of low noise photodiodes measures the optical power of the beam sampled with a weakly reflective optic (Thorlabs BSF10-C).
 The beam sampler is wedged in such a way that the two reflections diverge from one another, allowing us to illuminate both photodiodes. 
-One of the sampled beams is attenuated by a factor of $20\times$ by reflection off of an uncoated fused silica glass plate, such that the dynamic range of its photodiode covers $0-20$ W of the beam directed at the atoms, and controls the Berek compensator based, high-power, feedback loop.
+One of the sampled beams is attenuated by an additional factor of $20\times$ by reflection off of an uncoated fused silica glass plate, such that the dynamic range of its photodiode covers $0-20$ W of the beam directed at the atoms, and controls the Berek compensator based, high-power, feedback loop.
 The other beam is not attenuated, save by the beam sampler, and its dynamic range covers $0-1$ W.
-To prevent damage to this photodiode when the system is at its highest powers, a shutter (Stanford Research Systems SR475) blocks the light when the high power loop is active.
+To prevent damage to the low power photodiode when the system is at its highest powers, a shutter (Stanford Research Systems SR475) blocks the light when the high power loop is in use.
 The low power photodiode passes its signal $V_{\mathrm{pd}}$ to a loop filter circuit, which compares it to the control system's set-point, generated by digital to analog converter.
@@
 To ensure frequency stability (which translates directly into beam pointing of the laser), the PLL is locked to the $10$ MHz clock distributed around the lab.
-In addition to PLL functionality, the board also contains two, digitally-controllable, high-isolation RF switches, giving a total isolation exceeding $90$ dB.
+In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total isolation exceeding $90$ dB.
 
 The spectrum and relative intensity noise of the PLL can be found in figure \ref{fig:pll}. 
-Vitally, the spectrum of the PLL exhibits phase noise comparable to that of typical VCO, without the slow frequency drift characteristic to these devices. 
-Elimination of the carrier drift is worth the added phase noise because any drift of the frequency affects the steering of the laser beam passing through the AOM, which is entirely unacceptable since it would misalign the optical lattice.
+Vitally, the spectrum of the PLL exhibits phase noise comparable to (albeit worse than) that of a typical VCO, without the slow frequency drift characteristic to these devices. 
+Elimination of the carrier drift is worth the added phase noise, however, because any drift of the frequency affects the pointing of the laser beam passing through the AOM, which would misalign the optical lattice.
 
@@
 The photodiode can be safely operated up to incident powers of approximately 10 mW, which sets a -164 dBc/Hz shot noise limit on the RIN that can be detected. 
-In practice, we typically operate the photodiodes with $\approx 5$ mW of incident power.
+In practice, we typically operate the photodiodes with $\approx 1-5$ mW of incident power.
 A photodiode with a bandwidth (BW) of 6 MHz is used to characterize the system, while photodiodes with a bandwidth of 330 kHz (and correspondingly higher gain) are used to perform the feedback.
@@
 Prior to use, the protective window is removed from the photodiode to prevent interference effects, as seen in figure \ref{fig:cut_pd}.
-Further, to reduce the capacitance of the system, a reverse bias of 6.9 V is applied to the photodiode by a temperature-stabilized voltage reference (Linear Technology LM399).
+Further, to reduce the capacitance of the system, a reverse bias of $6.9\,$V is applied to the photodiode by a temperature-stabilized voltage reference (Linear Technology LM399).
 The trans-impedance circuit is shown in figure \ref{fig:circuits}. 
@@
 
-Light is focused onto the photodiode using a 25.4 mm lens such that the beam at the photodiode is significantly smaller than the photodiode diameter, to prevent pointing fluctuations from registering as amplitude fluctuations.
+Light is focused onto the photodiode using a $25.4\,$mm lens such that the beam at the photodiode is significantly smaller than the photodiode diameter, to prevent pointing fluctuations from registering as amplitude fluctuations.
 An iris and interference filter (Semrock FF01-1020/LP25) are used to eliminate stray sources of light.
@@
 When the state of the DAC is changed, such as during a ramp, this noise level may be higher, due to the so-called ``glitch'' energy, as seen in the figure.
-The transient noise, while unfortunate, is mitigated by two factors: (1) it is only present when the lattice power is altered, which happens during lattice loading - a lattice at a fixed power will have negligible RIN contributions from the DAC.
-Further, (2) the loop filter will filter the noise at these frequencies.
+The transient noise, while unfortunate, is mitigated by two factors: (1) it is only present when the lattice power is changing, which does not happen for most of the sequence, and a lattice at fixed power will have negligible RIN contributions.
+Further, (2) the loop filter eliminates the noise at higher frequencies.
 
@@
 The integral gain is set using a low-drift trim-pot. 
-This is the case because within relevant frequency ranges, the AOM can be well approximated by a pure time delay process (with delay given by the RF travel time across the crystal $\approx 1 \mu\mathrm{s}$).
+This is the case because within relevant frequency ranges, the AOM can be coarsely approximated by a pure time delay process (with delay given by the RF travel time across the crystal $\approx 1 \mu\mathrm{s}$).
 In this scenario, the $P$ term must be small to avoid instability at the $\pi$ phase shift point, and a pure $I$ controller is optimal~\cite{Skogestad2001}.
@@
 
-The third stage of the loop filter is used to accommodate the fact that the actuation arm is in nonlinear - the optical power transmitted by the AOM is proportional to the RF power incident on it $P_{\mathrm{rf}}\propto v_{if}^2$, where $v_{if}$ is the actuation signal supplied to the IF port of the mixer.
+The third stage of the loop filter is used to accommodate the fact that the actuation arm is nonlinear - the optical power transmitted by the AOM is proportional to the RF power incident on it $P_{\mathrm{rf}}\propto v_{if}^2$, where $v_{if}$ is the actuation signal supplied to the IF port of the mixer.
 In effect, if the rest of the feedback system was linear, this would correspond to a quadratically increasing gain until the AOM is saturated, which could lead to slow behavior at low signal levels and ringing at higher signal levels.
@@
 This can be seen by considering two extreme cases - far below the diode drop, the diode is an open circuit and the gain is set by $R_l$, where above the diode drop it is a closed circuit where the gain is set by the resistor $R_h$.
-Naturally, the voltage drop over the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode ($3.3$ V).
+Naturally, the voltage drop over the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode ($3.3\,$V).
 Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in figure \ref{fig:bandwidth}.
@@
 Another function of the last stage is to clamp the voltage to be strictly $>0$, in order to prevent an unstable positive feedback behavior, which is done using diode clamp on the output arm~\cite{Horowitz2015}.
-Last of all, since the mixer is a current driven device, the last stage of the feedback loop uses TI's OPA627 op-amp which is able to supply tens of mA of current at an output impedance of $50$ $\Omega$.
+Last of all, since the mixer is a current driven device, the last stage of the feedback loop uses TI's OPA627 op-amp which is able to supply tens of mA of current at an output impedance of $50\,\Omega$.
 
@@
     \includegraphics{fig/low_power_bandwidths.pdf}
-    \caption{\textbf{Loop bandwidth dependence on the set-point}.
-(a) shows the $3$ dB and $\pi$ phase shift points for the $X$ lattice (also known internally as the ``northeast'' lattice.
-(b) shows the same for the $Y$ lattice, known as the ``northwest''.}\label{fig:bandwidth}
+    \caption{\textbf{Loop bandwidth dependence on the set-point}. (a) shows the $3$ dB and $\pi$ phase shift points for the $X$ lattice. (b) shows the same for the $Y$ lattice.}\label{fig:bandwidth}
   \end{center}
@@
 
-A common behavior of analog feedback systems with integration components is termed \textit{integral wind-up}~\cite{Bechhoefer2005}, and occurs when the feedback loop is manually broken, and the actuator can no longer adjust the state of the controlled parameter.
-In this regime, the integrator accumulates a large positive or negative value, such that when control is restored, the system is uncontrolled until the integrator reaches the desired value.
+A common behavior of analog feedback systems with integration components is termed \textit{integral wind-up}~\cite{Bechhoefer2005}, and occurs when the feedback loop is manually broken, meaning that the actuator can no longer adjust the state of the controlled parameter.
+In this regime, the integrator accumulates a large positive or negative value, such that when control is restored, the system appears to briefly rail, before control is restored.
 In our case, \textit{integrator wind-up} occurs when the high-isolation RF switch is open during the state preparation procedure, and closed when the lattice is desired. 
-Since the lattice must usually be applied adiabatically, fast transients due to this windup can result in heating.
-To solve this system, a bypass switch (Maxim MAX4503) is placed across the capacitor of the second stage of the feedback circuit, which siphons the charge off the capacitor when the lattice is inactive.
-Even when the switch is closed, its resistance is nonzero (due to a protection resistor which limits the current that can pass through the switch), the conditions leading to integral windup in an unprotected system still lead to charge accumulation on the integral capacitor, albeit at a much reduced level.
-Thus, in addition to the switch, when the system is inactive, the set-point is set to within ($\approx 200$ $\mu$V) of the dark signal from the photodiode, making the error signal very small.
+Since the lattice must usually be applied to the atoms adiabatically, fast transients due to this windup can result in heating.
+To solve this issue, a bypass switch (Maxim MAX4503) is placed across the capacitor of the second stage of the feedback circuit, which siphons off the charge when the lattice is inactive.
+Even when the switch is closed, its resistance is nonzero (due to a protection resistor that limits the current that can pass through the switch), the conditions leading to integral windup in an unprotected system still lead to charge accumulation on the integral capacitor, albeit at a much reduced level.
+Thus, in addition to the switch, when the system is inactive, the set-point is set to within ($\approx 200\,\mu$V) of the dark signal from the photodiode, making the error signal very small.
 
-To avoid a so-called ``servo bump'' in the noise spectrum, and because there is little need for fast, closed-loop control, the loop filter is tuned very conservatively, to a bandwidth of approximately 10 kHz over most of the range.
+To avoid a so-called ``servo bump'' in the noise spectrum, and because there is little need for fast, closed-loop control, the loop filter is tuned very conservatively, to a bandwidth of approximately $10\,$kHz over most of the range.
 However, a small amount of tuning can raise this to up to $\approx150$ kHz, which is limited by the acoustic wave propagation delay of the AOM.
-Although fast, closed-loop control is impossible in the current configuration, the last stage of the loop filter features an adder, connected to an optional ``feed-forward'' port, which can be used to modulate the RF power at frequencies above the bandwidth.
+Although fast, closed-loop control is not available in the current configuration, the last stage of the loop filter features an adder connected to an optional ``feed-forward'' port. 
+This port can be used to modulate the RF power at frequencies above the bandwidth.
 
@@
 This can be explained by the Johnson noise~\cite{Horowitz2015} on the $1$ k$\Omega$ input resistors, amplified by the amplification stages of the loop filter.
-The sharp drop off at the $450$ kHz point is due to the low-pass filter centered there, placed on the output of the loop filter.
-When this was determined to be a problem, and we decided that a bandwidth of higher than $10$ kHz was not required in the foreseeable future, a first order low pass with a $3$ dB frequency of $10$ kHz was  added, leading to the noise spectrum seen in subfigure (b), as compared to (a) in figure \ref{fig:low_pass_noises} (the fiber amplifier used to take this data was different from the one used for \ref{fig:noises} different fiber amplifiers, which explains the small discrepancies).
+The sharp drop off at the $450$ kHz point is due to the a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.
+When this was determined to be a problem, we decided that a bandwidth of higher than $10\,$ kHz was not required in the foreseeable future. 
+As a result, we added a first order low pass with a $3$ dB frequency of $10$ kHz leading to the improvement shown in figure \ref{fig:low_pass_noises} (the fiber amplifier used to take this data was different from the one used for \ref{fig:noises}, although their performance is comparable.
 
@@
 
-\subsubsection{Beam shaping}
+\subsection{Beam shaping}
 After the beam has passed through the feedback optics, it must be applied to the atoms.
@@
 We focus the lattice to a $70-90$\,$\mu$m waist at the position of the atoms.
-In order to verify that the waist is positioned correctly, we use a temporary mirror to redirect the beam away from the glass cell and onto a camera positioned in the plane that would correspond to the position of the atoms had it not been for the temporary mirror.
+In order to verify that the waist is positioned correctly, we use a temporary mirror to redirect the beam away from the glass cell and onto a camera positioned in the plane corresponding to the position of the atoms.
 The resulting beam at the atoms has an $m^2\leq1.4$.
@@
 Even worse, this happens on both the initial and retro-reflected pass through the glass cell.
-For this reason, we use a QWP and HWP to optimize the interference contrast of each lattice\footnote{We do this by optimizing on the trap frequency of lattice, measured using parametric heating.
-This is a relatively tedious procedure.}.
-
-\subsection{Heating rates}
-We have used the band mapping technique, described in \ref{sec:bloch}, to characterize the heating rates in the lattice at different powers~\cite{Blatt2015}.
-To do this, the cloud was held in a given lattice for a varied period of time, before band mapping was performed.
-Band mapping directly reveals the band occupations, and the lifetime of atoms in the ground band is closely related to the temperature.
-The results, shown in figure \ref{fig:heating_rates} revealed that lifetimes as high as tens of seconds can be achieved, but that the heating rates are consistently dominated by parametric heating induced transitions.
-This analysis was performed prior to adding extra 10 kHz filters to the system, and later measurements have revealed that heating rates in the $0.01-0.5$ W are approximately a factor of $2-5\times$ lower.
+For this reason, we use a QWP and HWP to optimize the interference contrast of each lattice.
+This is done by optimizing the on-site trap frequency of lattice, measured using parametric heating.
 
@@
 The absolute positions of lattice sites cannot be allowed to change by more than a small fraction ($\approx 10\%$) from experimental shot to shot.
-Conveniently, this is relatively straightforward to ensure via careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which can be close to the position of the atoms and be made very stable~\cite{Huber2014}.
+This is ensured via careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately $3\,$cm from the atoms~\cite{Huber2014}.
 We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours, as seen in figure \ref{fig:averaged_mott}.
@@
 A series of Mott insulators was created over the course of approximately one hour, and the average image is shown\cite{Greif2016}.
-If the lattice fluctuated across more than a small fraction of a lattice site, the modulation contrast would be quickly washed out.
-The absence of this effect means that the phase of the optical lattice is very stable.}\label{fig:averaged_mott}
+If the lattice fluctuated across more than a small fraction of a lattice site, the modulation contrast would be washed out.
+The absence of this effect means that the phase of the optical lattice is stable.}\label{fig:averaged_mott}
   \end{center}
@@
 The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement. 
-In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in this work, \cite{Mazurenko2016} or \cite{Choi2016}), drift or fluctuation of the lattice position can pose a severe limitation.
+In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in \cite{Mazurenko2016} or \cite{Choi2016}), drift or fluctuation of the lattice position can pose a severe limitation.
 
-The required positional stability is achieved through a combination of passive stability and active monitoring. 
-Passive stability is ensured by using stable optomechanics (largely from the Thorlabs Polaris line), mounted on short optical posts, ensuring a low ($2$ in) beam height relative to the optical table, which is floated to minimize vibrations.
-In order to further improve stability, the beam is enclosed with $1$ in aluminum tubes throughout its path and the entire setup is enclosed by metal plates\footnote{all plates are sanded to produce a rough finish, producing diffuse rather than specular reflections.}.
-To further isolate the experimental setup, the optical table is contained within an aluminum enclosure.
+The required positional stability of the underlying harmonic trap is achieved through a combination of passive stability and active monitoring. 
+Passive stability is ensured by using stable optomechanics (largely from the Thorlabs Polaris line), mounted on short optical posts ($2$ in beam height relative to the floated optical table).
+To further improve stability, the beam is enclosed with $1\,$in aluminum tubes throughout its path and the entire setup is covered by metal plates.
+As a final measure to isolate the experimental setup, the optical table is contained within an aluminum enclosure.
 As detailed in prior sections, care has been taken to minimize thermal lensing and drift in optics encountered by the lattice beam.
@@
 Passive stability alone has been found to be insufficient to ensure smooth operation over many hours.
-Changes in weather conditions, load on the water-cooling systems and other external effects can lead to a slow drift in the pointing of the laser beams.
-The situation is further complicated by the fact that opening the enclosure changes the thermal state of the system, inducing misalignment. 
-For these reasons, each lattice axis is fitted with a remotely actuated mirror, controlled by the experimental control software over the Ethernet network, allowing for non-invasive, digital alignment of the system.
-The remote actuators are Newport brand ``Picomotors'' (model 8302), fitted into a customized $2$ in mirror mount, and work in a ``fire and forget'' manner, remaining passively stable when not in active use.
+Changes in weather conditions, load on the water-cooling systems and other external conditions can lead to a slow drift in the laser pointing.
+The situation is further complicated by the fact that opening the enclosure changes the thermal state of the system, meaning that manual alignment can induce misalignment. 
+For these reasons, each lattice axis is fitted with a remotely actuated mirror, controlled by the experimental control software over the lab network, allowing for non-invasive, digital alignment of the system.
+The remote actuators are Newport brand ``Picomotors'' (model 8302), fitted into a customized $2$ in mirror mount.
+They work in a ``fire and forget'' manner, remaining passively stable when not in active use.
 
@@
 
-To prevent external influences from contaminating large data sets, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams and eliminate (via post-selection) experimental realizations when the system was in an undesired state.
-A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the same plane as the atoms, producing a Gaussian image that is identical to that incident on the atoms.
+Changing external constions can contaminate large datasets if the prepared state sensitively depends on laser pointing. 
+To prevent this contamination, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams and eliminate (via post-selection) experimental realizations when the system was in an undesired state.
+A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the plane corresponding to the atomic system, producing a Gaussian image identical to that of the optical lattice.
 Naturally, the position of the atoms is dictated by the light field of both the incoming and retro-reflected beams, while the monitoring camera only observes the position of the in-going beam.
-To verify that the monitor camera could predict the true position of the atoms, the beam and the atoms were imaged simultaneously while a purposeful misalignment of the incoming beams was introduced.
-This was done by adiabatically loading one of the lattice beams ensuring that the atoms settle to its center, prior to performing site-resolved imaging~\cite{Parsons2015}.
+To verify that the monitor camera could predict the true position of the harmonic trap, the beam and the atoms were imaged simultaneously while a purposeful misalignment of the incoming beams was introduced.
+During this process, one of the lattice beams was adiabatically loaded, ensuring that the atoms settled to its center, prior to performing site-resolved imaging~\cite{Parsons2015}.
 
@@
 First, we characterized the passive stability of the optical axis along the transverse $x_t$ and longitudinal $x_l$ directions. 
-Figure \ref{fig:stability} a shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$($0.98(4)$) sites along the $x_t$($x_l$) directions, where this discrepancy is consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
+Figure \ref{fig:stability} a shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$($0.98(4)$) sites along the $x_t$($x_l$) directions.
+The difference between displacements along is a geometric effect consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
 The means of both distributions are consistent with zero.
 If the trap followed a random walk with these step sizes, the experiment would be in trouble, since after only $100$ experimental shots, the trap would move by more than $10$ lattice sites.
-The situation is more fortunate, however, since the steps are heavily anti-correlated, as shown in figure \ref{fig:stability} (b).
+The situation is more fortunate, however, since subsequent steps are correlated, as shown in figure \ref{fig:stability} (b).
 Once this correlation is taken into account, we estimate a drift of $8(1)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the transverse direction and $12(2)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the axial direction, compared to a beam waist of approximately $80$ $\mu$m ($\approx 140$ sites).
@@
 In a real experiment, we cannot directly measure the position of the atoms and must rely on the measurement performed by the camera, related by an affine transformation.
-To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in figure \ref{fig:stability} c.
+To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in figure \ref{fig:stability} (c).
 
 Unfortunately, while this fit is acceptable for a short while ($\approx30\mathrm{ shots}$), the quality of the fit degrades over time, correspondingly degrading the predictive power. 
-The most likely culprit is thermal drift of the camera, since a displacement of approximately a pixel is very substantial to the predicted position, and each pixel is approximately 3 $\mu$m. 
-The camera housing is not engineered for low drift mounting, and the camera produces a substantial amount of heat\footnote{It heats up by a few degrees Celcius during operation}, making a few $\mu$m drift very likely.
+The most likely culprit is thermal drift of the camera, since a displacement of only a pixel caused the predicted position to change by approximately $1\,$site, and each camera pixel is about $3\,\mu$m accross.
+The camera housing is not engineered for low drift mounting, and the camera heats up by a few degrees Celcius, making a few $\mu$m drift very possible.
 To deal with this problem, we point out that the affine transform is composed of three distinct parts - the rotation, scaling and offset. 
@@
 To test this procedure, we analyzed the data set of camera measurements and atomic positions in the following way: we split the data set into sequential blocks of $20$ shots, each followed by a block of $8$ shots.
-The large blocks were treated as ``masked'' data, which we tried to predict, while the small blocks were treated as ``updating'' events used to update the offsets of the calibration.
-The results are shown in figure \ref{fig:stability} (d-f), showing a large degree of tracking between the predicted positions and measured position - the average displacement between the predicted position and measured position was $0.7$ lattice sites.
+The large blocks were treated as ``masked'' data, which we tried to predict, while the small blocks were treated as ``updating'' events used to update the calibration offsets.
+The results are shown in figure \ref{fig:stability} (d-f), showing a large degree of tracking between the predicted positions and measured position - the average displacement between the predicted position and measured position was $0.7\,$lattice sites.
 
@@
 Further, if future experiments require the optical lattice to be more positionally stable than it is now, the monitoring and actuation system could be used in closed loop with no hardware changes to the experiment.
-Naturally, the transfer function of any such loop would have to be carefully engineered to account for the correlated behavior of the jumps and the timescale of the drift, but these are very solvable problems.
+Naturally, the transfer function of any such loop would have to be carefully engineered to account for the correlated behavior of the jumps and the timescale of the drift.
 
 \section{Long-term stability of the lattice structure}
-An interesting benefit of site-resolved imaging is that every measurement of the atomic distribution is also a direct measurement of the underlying lattice structure. 
+A benefit of site-resolved imaging is that every measurement of the atomic distribution is also a direct measurement of the underlying lattice structure. 
 As discussed in the supplementary material of~\cite{Parsons2016, Greif2016}, the Fourier transform of an atomic distribution contains distinct peaks corresponding to the lattice structure, and these peaks can be used to extract the phase, relative angle, and spacing of the lattices.
-For this reason, I looked back at nine months of data spanning June 2016 through April 2017, in order to learn how these parameters change over time.
+For this reason, we looked back at nine months of data spanning June 2016 through April 2017 in order to learn how these parameters change over time.
 Several interesting features can be seen from this figure \ref{fig:long_term_stability}.
@@
 We measure that in the spring of 2017, the relative angle of the lattices has exhibited fluctuations with an RMS of $0.06^\circ$.
-  \item The behavior of the phase (not shown in figure \ref{fig:long_term_stability}) is consistent with being random, most likely due to the substantial drifts of the apparent magnitude of the lattice constant.
 \end{enumerate}
 
-\begin{figure}
+\begin{figure*}
   \begin{center}

### 2017-11-12 LatticeOptics/latticeOpticsV2.tex
added figure
V4 of paper

@@
 
+\graphicspath{{./figures/}}
 \begin{document}
@@
 This system has been successfully used in a Fermi gas microscope to investigate the charge and spin sectors of the Hubbard model with unprecedented control. 
+\begin{figure}
+    \includegraphics{figures/figure1/figure1.pdf}
+    \caption{High level overview showing the major components of the lattice laser feedback system}
+\end{figure}
 
@@
 \section{Nufern Fiber Amplifiers}
-Quantum gas microscopy of Li requires single site trap frequencies of approximately 1 MHz \cite{single site paper}.
+Quantum gas microscopy of Li requires single site trap frequencies of approximately 1 MHz \cite{Parsons2015}.
 Such trap frequencies may only be attained using tightly focused high power beams, which requires that the seed power be amplified to approximately 30 W per lattice axis, which is done using Nufern Fiber amplifiers (PART NUMBER XXX).
@@
 \item what is it and how do you measure it
-\item easy to measure, enters into parametric heating effects
+\item easy to measure, enters into parametric heating effects\cite{Savard1997}
 \end{itemize}
@@
 \section{Beam Monitoring}
-A major recent direction of ultracold atoms experiments is the ability to use very few, individually-addressible atoms\cite{AFM paper, quantum walks few body} that are simultaneously held by several lattice axes in addition to auxilliary traps.
+A major recent direction of ultracold atoms experiments is the ability to use very few, individually-addressible atoms\cite{Mazurenko2016, Farhi} that are simultaneously held by several lattice axes in addition to auxilliary traps.
 Unfortunately, such experiments require superb stability, where the underlying harmonic confinement does not shift by more than approximately 2-3 micron from experiment to experiment.

### 2017-11-12 LatticeOptics/latticeOpticsV4.tex
V4 of paper

@@
 \begin{abstract}
-  We describe the design of a stable high power $1064\,$nm laser system for use in optical lattice experiments.
+ We describe the design of a stable high power $1064\,$nm laser system for practical use in optical lattice experiments.
 The system is based on a low noise laser amplified by an array of four heavily modified, high-power fiber amplifiers.
-The intensity of every beam is stabilized using a nonlinear feedback loop.
-The position of the produced optical lattice is monitored in real time and its stability is characterized\footnote{This work is adapted from the PhD thesis of A.Mazurenko}.
+The beam intensity is stabilized with a nonlinear feedback loop.
+The position of the produced optical lattice is monitored in real time and its stability is characterized.
 \end{abstract}
@@
 
-Optical lattice holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations, including strongly correlated systems, quantum state engineering, quantum computing and precision metrology.
-Further, the recent advent of quantum gas microscopy has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales.
+Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation \cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.%, strongly correlated systems, quantum state engineering, quantum computing and precision metrology.
+Further, the recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian ~\cite{Hubbard1963}.
 However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
@@
 Even if the system thermalizes, heating rates can limit the interrogation time available to probe a low-temperature state.
-In a similar vein, experiments that rely on a small number of atoms held by multiple traps place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity~\cite{Mazurenko2016}.
+In a similar vein, experiments that rely on a small number of atoms held by multiple traps place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.%~\cite{Mazurenko2016}.FIXME: CITATIONS
 
 To address these concerns, we discuss a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
-The stability of the lattice phase is below the single site level and the stability of the harmonic confinement is at the few site level.
-
+The stability of the lattice position is below the single site level and the stability of the harmonic confinement is at the few site level.
 \begin{figure}
@@
 Three of these fiber amplifiers are used to produce the 3D optical lattice~\cite{Parsons2016}, and a fourth is used for transport~\cite{Huber2014}.
-To avoid interference of the lattice beams, two of the beam paths pass through acousto-optic modulators (AOM), which detuning the lattice frequencies from each other.
+To avoid interference of the lattice beams, two of the beam paths pass through acousto-optic modulators (AOM), which detune the lattice frequencies from each other.
 
@@
 
-These upgrades serve to suppress many of the noise spurs measured in the relative intensity noise (RIN) of the fiber amplifier, as seen in figure \ref{fig:noises}. 
+These upgrades serve to suppress many of the noise spurs measured in the relative intensity noise (RIN) of the fiber amplifier. 
+This can be as seen by comparing figure \ref{fig:noises} (a) and (b), particularly in the region of approximately $10$ kHz. 
 The measurements in parts (a)-(d) were carried out on a single fiber amplifier, prior to and after the modifications.
@@
 
-In order to address these challenges, we use a carefully engineered an optical system, shown in figure \ref{fig:optical_layout}, that collimates and polarizes the beam, controls its intensity between $10\,\mu$W and $20$ W, and ensures good pointing stability.
+In order to address these challenges, we use a carefully engineered the optical system shown in figure \ref{fig:optical_layout}.
+This system collimates and polarizes the beam, controls its intensity and ensures good pointing stability.
 Due to the high laser power, fused silica glass and IBS coatings are used wherever possible.
@@
 \begin{enumerate}
-\item The lattice power must be continuously tunable from around $10$ $\mu$W to around $20$ W. 
+\item The lattice power must be continuously tunable from around $10$ $\mu$W to around $20$ W, corresponding to lattice depths in the approximate range of $10^-3$ to $2(10^3)\,E_R$. 
 \item The location of the minimum Gaussian beam waist must be accurately positioned to overlap the other lattices and dipole traps present in the experiment, and must remain there for the duration of the collection process (hours to days).
@@
 The Berek compensator is a $z$-cut quartz plate coated to be anti-reflecting at $1064\,$nm. 
-By tilting the plate about its vertical axis by a few degrees, the extraordinary axis is mixed into the propagation of the beam, leading to  tilt-dependent bi-refringence that can be tuned from a zero-wave plate past a half-wave plate, represented by a retardation angle $\phi$.
+By tilting the plate about its vertical axis by a few degrees, the extraordinary axis is mixed into the propagation of the beam, leading to  tilt-dependent birefringence that can be tuned from a zero-wave plate past a half-wave plate, represented by a retardation angle $\phi$.
 Combined with the subsequent polarization optics, rotation of the Berek compensator can vary the transmitted power with perfect contrast. 
@@
     \includegraphics{fig/berek_sim.pdf}
-    \caption{\textbf{Berek compensator} performance as a function of the Berek tilt angle $\phi$ and waveplate tilt angles.}\label{fig:berek}
+    \caption{\textbf{Berek compensator} transmission as a function of the Berek tilt angle $\phi$ and waveplate tilt angles.}\label{fig:berek}
   \end{center}
@@
     \includegraphics{fig/step_response.pdf}
-    \caption{\textbf{Berek compensator based feedback loop} performance showing the impulse response (a) at relatively low powers and the corresponding Bode plots (b-c).}\label{fig:berek_step_response}
+    \caption{\textbf{Berek compensator based feedback loop}.
+This Berek compensator based feedback loop is used to vary the beam intensity at relatively high power.
+(a) Shows the small signal impulse response and (b-c) show the corresponding Bode plots.}\label{fig:berek_step_response}
   \end{center}
@@
 The beam sampler is wedged in such a way that the two reflections diverge from one another, allowing us to illuminate both photodiodes. 
-One of the sampled beams is attenuated by an additional factor of $20\times$ by reflection off of an uncoated fused silica glass plate, such that the dynamic range of its photodiode covers $0-20$ W of the beam directed at the atoms, and controls the Berek compensator based, high-power, feedback loop.
+One of the sampled beams is attenuated by an additional factor of $20\times$ by reflection off of an uncoated fused silica glass plate, such that the dynamic range of its photodiode covers $0-20$ W of the beam directed at the atoms, and controls the Berek compensator based, high-power feedback loop.
 The other beam is not attenuated, save by the beam sampler, and its dynamic range covers $0-1$ W.
@@
 Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in figure \ref{fig:bandwidth}.
-Were it not for the linearization, the gain of the mixer would change by $10\times$ over a dynamic range spanning two orders of magnitude.
+Were it not for the linearization, the gain of the mixer would change by a factor of $10$ over a dynamic range spanning two orders of magnitude.
 Another function of the last stage is to clamp the voltage to be strictly $>0$, in order to prevent an unstable positive feedback behavior, which is done using diode clamp on the output arm~\cite{Horowitz2015}.
@@
 This can be explained by the Johnson noise~\cite{Horowitz2015} on the $1$ k$\Omega$ input resistors, amplified by the amplification stages of the loop filter.
-The sharp drop off at the $450$ kHz point is due to the a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.
+The sharp drop off at the $450$ kHz point is due to a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.
 When this was determined to be a problem, we decided that a bandwidth of higher than $10\,$ kHz was not required in the foreseeable future. 
@@
 After the beam has passed through the feedback optics, it must be applied to the atoms.
-To that end, we use a $2f$ telescope of short focal length triplet collimator lenses to expand the beam, and then focus it with a long focal length lens.
+To that end, we use a $2f$ telescope of short focal length triplet collimator lenses to expand the beam, and then focus it with a long focal length singlet lens.
 We focus the lattice to a $70-90$\,$\mu$m waist at the position of the atoms.
 In order to verify that the waist is positioned correctly, we use a temporary mirror to redirect the beam away from the glass cell and onto a camera positioned in the plane corresponding to the position of the atoms.
-The resulting beam at the atoms has an $m^2\leq1.4$.
+%The resulting beam at the atoms has an $m^2\leq1.4$.
 
@@
 The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement. 
-In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in \cite{Mazurenko2016} or \cite{Choi2016}), drift or fluctuation of the lattice position can pose a severe limitation.
+In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in \cite{Mazurenko2016} or \cite{Choi2016}), drift or fluctuation of the lattice position is important.
 
@@
 (d) Predicted location versus measured location along the transverse and longitudinal directions.
-(e,f) The measured position and predicted position of the atomic cloud.}\label{fig:stability}
+(e,f) The measured position and predicted position of the atomic cloud, based on refitting the offset every $20$ experimental realizations.}\label{fig:stability}
   \end{center}
@@
 
-Changing external constions can contaminate large datasets if the prepared state sensitively depends on laser pointing. 
-To prevent this contamination, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams and eliminate (via post-selection) experimental realizations when the system was in an undesired state.
+Changing external conditions can contaminate large datasets if the prepared state sensitively depends on laser pointing. 
+In order to watch for this contamination, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
+This monitoring system could potentially allow us to eliminate (via post-selection) experimental realizations when the system was in an undesired state.
 A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the plane corresponding to the atomic system, producing a Gaussian image identical to that of the optical lattice.
@@
 The difference between displacements along is a geometric effect consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
-The means of both distributions are consistent with zero.
+The distributions are centered within $1\sigma$ of zero along both directions ($-.03(4)$ and $0.01(5)$ sites for transverse and longitudinal, respectively).
 If the trap followed a random walk with these step sizes, the experiment would be in trouble, since after only $100$ experimental shots, the trap would move by more than $10$ lattice sites.
@@
 \section{Long-term stability of the lattice structure}
+FIXME: I PROPOSE MOVING THIS INTO THE SUPPLEMENTARY MATERIALS: IT MAY BE INTERESTING TO EXPERTS, BUT IS A LITTLE TOO ``ANECDOTAL'' FOR THE MAINTEXT.
 A benefit of site-resolved imaging is that every measurement of the atomic distribution is also a direct measurement of the underlying lattice structure. 
@@
   \item Replacement of the analog feedback loop by a low-noise digital loop.
-  \item Monitoring the position of the lattice laser beam in the Fourier, as well as image plane.
   \item Active stabilization of the laser pointing.

### 2017-11-12 LatticeOptics/figure_source_scripts/BerekCompensator/berek.py

@@ -1,0 +1,62 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+
+
+def berek(theta0, theta1, phi):
+    return np.square(np.absolute(np.exp(1j*phi)*np.cos(2*theta0)*np.cos(2*theta1) - np.sin(2*theta0)*np.sin(2*theta1)))
+
+
+def generate_berek_scan(retardation_range=(0, 2*np.pi),
+                        theta_angles=[0, np.pi/4/8, np.pi/16, np.pi*3/4/8, np.pi/8],
+                        n_phi=1e3):
+    phi = np.linspace(retardation_range[0], retardation_range[1], n_phi)
+    return phi, [berek(theta, theta, phi) for theta in theta_angles]
+
+
+if __name__ == "__main__":
+    labeled_angles = [(r"\pi/32", np.pi/32), (r"\pi/16", np.pi/16), (r"3\pi/32", 3*np.pi/32), (r"\pi/8", np.pi/8)]
+    angle_labels, angles = zip(*labeled_angles)
+    phi, intensities = generate_berek_scan(theta_angles=angles)
+
+    rcParams.update({})
+    scl = 1/1.61
+    fig_width = 3.37
+    fig_height = scl*fig_width
+
+    rcpars.update({
+        "figure.autolayout": True,
+        "figure.figsize": (fig_width, fig_height),
+        "figure.subplot.left": .25,
+        "figure.subplot.right": .94,
+        "figure.subplot.bottom": .2,
+        "figure.subplot.top": .95,
+    })
+
+    pl.rcParams.update(rcpars)
+
+    init_plt()
+    fig = pl.figure()
+    w_a = 0.10    # width of a) figures
+    h_a = w_a/scl  # height of a) figures
+    ow_a = w_a + 0.015
+    oh_a = h_a + 0.068
+    ow_a0 = 0.065
+    oh_a0 = 0.22
+    ax = fig.add_subplot(1, 1, 1)
+    ax.set_xlabel('$\phi$')
+    ax.set_ylabel('$I/I_0$')
+    ax.set_xlim((0, np.max(phi)))
+    ax.set_ylim((0, 1.39))
+
+    for idx, intensity in enumerate(intensities):
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/BerekCompensator/risetime.py

@@ -1,0 +1,104 @@
+import numpy as np
+import scipy as sp
+import pandas as pd
+import matplotlib.pyplot as plt
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+import brewer2mpl as cb
+import cmocean as cm
+import matplotlib.gridspec as gridspec
+from bandwidth_analyzer import *
+
+if __name__ == "__main__":
+    fig_name = "step_response"
+    step_data = pd.read_csv('data//berek_bw.csv')[3:]
+    step_data = step_data.rename(columns={'x-axis':'t', '2':'v'})
+    step_data = step_data.astype(float)
+    print step_data[:100].v.mean()
+    print step_data[-100:].v.mean()
+    rcParams.update({})
+    scl = 1/1.61
+    fig_width = 5.5
+    fig_height = scl*fig_width
+
+    rcpars.update({
+        "figure.autolayout": True,
+        "figure.figsize": (fig_width, fig_height),
+        "figure.subplot.left": .1,
+        "figure.subplot.right": .94,
+        "figure.subplot.bottom": .2,
+        "figure.subplot.top": .95,
+    })
+
+    pl.rcParams.update(rcpars)
+
+    init_plt()
+    fig = pl.figure()
+    gs0 = gridspec.GridSpec(2, 2, wspace=.1, hspace=.1)
+    ax0 = plt.subplot(gs0[0:, 0])
+    ax0.set_xlabel('time (ms)')
+    ax0.set_ylabel('$P$ (arb)')
+    ax0.set_xlim([-1, 2])
+    ax0.set_ylim([0, .8])
+
+    ax0.plot(1e3*step_data.t+.148, step_data.v, color=color_or_rd) # the .148 is to trigger from the fungen edge, not the arbitrary t=0
+    ax0.grid(zorder=-1, color=color_grey)
+    xy = (-.25, 1)
+    ax0.annotate('(a)', xy=xy, xytext=xy, xycoords='axes fraction', fontsize=12)
+
+    ax1 = plt.subplot(gs0[0, 1])#fig.add_subplot(3, 1, 2)
+
+    step_data = pd.read_csv('data//berek_bw.csv')[3:]
+    step_data = step_data.rename(columns={'x-axis': 't', '2': 'v'})
+    step_data = step_data.astype(float)
+    start = step_data[:100].v.mean()
+    stop = step_data[-100:].v.mean()
+    step_data.v -= start
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/latticeStability/LatticeCameraMonitoring/analyze_data.py

@@ -1,0 +1,245 @@
+import numpy as np
+import pyfits
+import os
+import matplotlib.pyplot as plt
+import plastia.analysis.fit as pfit # internal Greinerlab fitting suite
+import pandas as pd
+
+data_dir = "data"
+
+"""
+First axis always the "narrow" axis of the cloud for nw beam
+"""
+
+
+def running_mean(x, n=20):
+    return np.convolve(x, np.ones((n,)) / n, mode='valid')
+
+
+def load_pointing(name):
+    """
+    Get the pointing data from the data subdir
+    :param name:
+    :return:
+    """
+    pointing_data = np.loadtxt(os.path.join(data_dir, '{}.csv'.format(name)), delimiter=',')[:, 1:3]
+    return pointing_data
+
+
+def load_atom_matrixes(name):
+    """
+    Get the atom matrixes from the data subdir
+    :param name:
+    :return:
+    """
+    hdulist = pyfits.open(os.path.join(data_dir, '{}.fits'.format(name)))#, ignore_missing_end=True)
+    data_list = [hdulist[i].data for i in range(1, len(hdulist))]
+    return data_list
+
+
+def get_fitted_centers(matrix_list):
+    centroids = []
+    for matrix in matrix_list:
+        fit = pfit.FitFunctionGaussian2D()
+        fit.guess_matrix(matrix)
+        fit.fit_matrix(matrix)
+        print fit.result.parameters
+        print fit.result
+        centroids.append(map(lambda x: x.bare_value, fit.result.parameters)[2:4][::-1])
+    return reduce(lambda x, y: np.vstack((x, y)), centroids)
+
+
+def get_centroids(matrix_list, is_plot =False):
+    if is_plot:
+        plt.imshow(matrix_list[0])
+        plt.show()
+    centroids = [np.divide(np.argwhere(mat == 1).sum(0), np.sum(mat)) for mat in matrix_list]
+    stdvs = [np.std(np.argwhere(mat == 1), axis=0) for mat in matrix_list]
+    return reduce(lambda x, y: np.vstack((x, y)), centroids)
+
+
+def affine_fit(p0, p1):
+    """
+    finds an affine fit between p0 and p1
+    :param p0: N by 2 array representing points in plane 0
+    :param p1: N by 2 array representing points in plane 1
+    :return: an affine fit matrix
+    """
+    assert np.shape(p0) == np.shape(p1)
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/latticeStability/LatticeCameraMonitoring/get_data.py

@@ -1,0 +1,82 @@
+import numpy as np
+import pickle as pkl
+import pyfits
+import os
+import re
+import matplotlib.pyplot as plt
+
+"""
+the data was scans 16 (calibration) 17-19 (data) on April 3, 2017.
+"""
+def binarize(amp_mat, threshold=0.21):
+    return (amp_mat > threshold).astype(np.float32)
+
+
+def get_camera_pointing_data(scans, runlog_dir="W:\\RunLog", name="data", log_regex = 'log-0\.csv'):
+    compiled_pointing = []
+    for datevec in scans:
+        beam_mon_data_path = '%s\\%04d\\%02d\\%02d\\%04d%02d%02d-%04d\\beam_mon' % (runlog_dir, datevec[0], datevec[1], datevec[2],
+                                                                                datevec[0], datevec[1], datevec[2], datevec[3])#,
+                                                                                #datevec[0], datevec[1], datevec[2], datevec[3])
+        print os.listdir(beam_mon_data_path)
+        data_list = filter(lambda x: re.match(log_regex, x), os.listdir(beam_mon_data_path))
+        print data_list
+        scan_measurements = []
+        for pointing in data_list:
+            pd = np.loadtxt(os.path.join(beam_mon_data_path, pointing), delimiter=',')
+            scan_measurements.append(pd)
+        compiled_pointing.append(reduce(lambda x, y: np.hstack((x, y)), scan_measurements))
+
+    compiled_data = reduce(lambda x, y: np.vstack((x, y)), compiled_pointing)
+    np.savetxt('{}.csv'.format(name), compiled_data, delimiter=',')
+    return 0
+
+
+def get_single_site_data(scans, runlog_dir="W:\\RunLog", name="data", threshold=0.19):
+    """
+    gets the site analyzed, binarized data from all the specified scans, dunps them into a fitfile
+    :param scans: (year,month,day,scan tuple)
+    :param runlog_dir:
+    :return:
+    """
+    binary_occupations = [pyfits.PrimaryHDU(np.array(scans))]
+    for datevec in scans:
+        print datevec
+        ss_data_path = '%s\\%04d\\%02d\\%02d\\%04d%02d%02d-%04d\\FitResults' % (runlog_dir, datevec[0], datevec[1], datevec[2],
+                                                                                datevec[0], datevec[1], datevec[2], datevec[3])#,
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/latticeStability/LatticeCameraMonitoring/get_imfit_errorbars.py

@@ -1,0 +1,47 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import misc
+import os
+import re
+from plastia.analysis import fit
+
+DATA_DIR = 'data'
+
+
+def find_files(dir, axis):
+    """
+    looks for all files in the format "img-[num]-[axis].png" in the dirname directoy under data
+    returns dict of shot to filename
+    """
+    all_files = os.listdir(dir)
+    regex = re.compile('img-([0-9]*)-{}\.png'.format(axis))
+    file_ids = {}
+    for f in all_files:
+        m = regex.match(f)
+        id = int(m.groups()[0]) if m else None
+        if id:
+            file_ids[id] = f
+    return file_ids
+
+
+def get_errorbars(dirname, axis=0):
+    """
+    looks for all files in the format "img-[num]-[axis].png" in the dirname directoy under data
+    returns the fitted parameters in a dataframe
+    :param dirname:
+    :return:
+    """
+    dirname = os.path.join(DATA_DIR, dirname)
+    file_ids = find_files(dirname, axis=axis)
+    for shot_num, filename in file_ids.iteritems():
+        im = misc.imread(os.path.join(dirname, filename))
+        f = fit.FitFunctionGaussian2D()
+        f.guess_matrix(im)
+        f.fit_matrix(im)
+        print f.result
+        #plt.imshow(im)
+        #plt.show()
+
+
+if __name__ == "__main__":
+    get_errorbars('20170407-0055beam_mon', axis=0)

### 2017-11-12 LatticeOptics/figure_source_scripts/latticeStability/LatticeCameraMonitoring/plot_data_extended.py

@@ -1,0 +1,206 @@
+import numpy as np
+import scipy as sp
+from scipy.optimize import curve_fit
+import matplotlib.pyplot as plt
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+import brewer2mpl as cb
+import cmocean as cm
+import pandas as pd
+import matplotlib.gridspec as gridspec
+import matplotlib.lines as mlines
+
+
+def fit_hist_gauss(data, **kwargs):
+    guess = kwargs.pop('guess', [0, 1])
+    kwargs.update({'density': True})
+    fit_fun = lambda x, mu, sig: 1.0/np.sqrt(2*np.pi*np.square(sig))*np.exp(-1*np.divide(np.square(x-mu),
+                                                                                        2*np.square(sig)))
+    weights, bin_edges = np.histogram(data, **kwargs)
+    bin_centers = 0.5 * (bin_edges[:-1] + bin_edges[1:])
+    popt, pcov = curve_fit(fit_fun, bin_centers, weights, p0=guess)
+    return popt, np.sqrt(np.diag(pcov)), fit_fun
+
+
+if __name__ == "__main__":
+    calibration_data = pd.read_csv('calibration_data_comparison.csv')
+    oos_data = pd.read_csv('out_of_sample_data_with_p20_s4.csv')
+    xdiffs = oos_data.diff()[1:][['x_t', 'x_l']]
+    n_step = 5
+    xdiffs5 = oos_data.diff(n_step)[1:][['x_t', 'x_l']][n_step::n_step]
+    print xdiffs.corr()
+    xtfit = fit_hist_gauss(xdiffs.x_t)
+    xlfit = fit_hist_gauss(xdiffs.x_l)
+    print xtfit
+    print xlfit
+    print xdiffs['x_t'].autocorr(lag=1)
+    print xdiffs['x_l'].autocorr(lag=1)
+    mean_xt, mean_xl = np.mean(oos_data.x_t), np.mean(oos_data.x_l)
+    print xdiffs5.x_t
+    #print "5 site correlations"
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/latticeStability/LatticeCameraMonitoring/plot_data_v2.py

@@ -1,0 +1,153 @@
+import numpy as np
+import scipy as sp
+from scipy.optimize import curve_fit
+import matplotlib.pyplot as plt
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+import brewer2mpl as cb
+import cmocean as cm
+import pandas as pd
+import matplotlib.gridspec as gridspec
+import matplotlib.lines as mlines
+
+
+def fit_hist_gauss(data, **kwargs):
+    guess = kwargs.pop('guess', [0, 1])
+    kwargs.update({'density': True})
+    fit_fun = lambda x, mu, sig: 1.0/np.sqrt(2*np.pi*np.square(sig))*np.exp(-1*np.divide(np.square(x-mu),
+                                                                                        2*np.square(sig)))
+    weights, bin_edges = np.histogram(data, **kwargs)
+    bin_centers = 0.5 * (bin_edges[:-1] + bin_edges[1:])
+    popt, pcov = curve_fit(fit_fun, bin_centers, weights, p0=guess)
+    return popt, np.sqrt(np.diag(pcov)), fit_fun
+
+
+if __name__ == "__main__":
+    calibration_data = pd.read_csv('calibration_data_comparison.csv')
+    oos_data = pd.read_csv('out_of_sample_data_with_p20_s4.csv')
+    xdiffs = oos_data.diff()[1:][['x_t', 'x_l']]
+    n_step=5
+    xdiffs5 = oos_data.diff(n_step)[1:][['x_t', 'x_l']][n_step::n_step]
+    print xdiffs.corr()
+    xtfit = fit_hist_gauss(xdiffs.x_t)
+    xlfit = fit_hist_gauss(xdiffs.x_l)
+    print xdiffs['x_t'].autocorr(lag=1)
+    print xdiffs['x_l'].autocorr(lag=1)
+    mean_xt, mean_xl = np.mean(oos_data.x_t), np.mean(oos_data.x_l)
+    print xdiffs5.x_t
+    print fit_hist_gauss(xdiffs5.x_t)
+
+    fig_name = "pointing_figure"
+    rcParams.update({})
+    scl = 1/1.61
+    fig_width = 5
+    fig_height = scl*fig_width
+
+
+    rcpars.update({
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/latticeStability/LatticeCameraMonitoring/plot_regression.py

@@ -1,0 +1,57 @@
+import numpy as np
+from scipy import stats
+import matplotlib.pyplot as plt
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+import brewer2mpl as cb
+import cmocean as cm
+import pandas as pd
+import matplotlib.gridspec as gridspec
+import matplotlib.lines as mlines
+
+if __name__ == "__main__":
+    oos_data = pd.read_csv('out_of_sample_data_with_p20_s4.csv')
+    xdiffs = oos_data.diff()[1:][['x_t', 'x_l']]
+    print xdiffs.corr()
+
+    mean_xt, mean_xl = np.mean(oos_data.x_t), np.mean(oos_data.x_l)
+    oos_data.x_t -= mean_xt
+    oos_data.x_ct -= mean_xt
+    oos_data.x_l -= mean_xl
+    oos_data.x_cl -= mean_xl
+
+    scl = 1/1.61
+    fig_width = 3
+    fig_height = scl*fig_width
+
+    rcpars.update({
+        "figure.autolayout": True,
+        "figure.figsize": (fig_width, fig_height),
+        "figure.subplot.left": .1,
+        "figure.subplot.right": .94,
+        "figure.subplot.bottom": .05,
+        "figure.subplot.top": .95,
+    })
+
+    pl.rcParams.update(rcpars)
+
+    labels = ['a', 'b', 'c']
+    init_plt()
+    fig = pl.figure()
+    ax0 = fig.add_subplot(1, 1, 1)
+    slope, intercept, r_value, p_value, std_err = stats.linregress(oos_data.x_ct, oos_data.x_t)
+    print slope
+    print intercept
+
+    print r_value
+    print p_value
+
+    xlin = np.linspace(oos_data.min().x_t, oos_data.max().x_t, 10)
+
+    ax0.plot(oos_data.x_ct, oos_data.x_t, linewidth=0, marker = 'o')
+    ax0.plot(xlin, slope*xlin + intercept, linewidth=0, marker = 'o')
+    plt.show()
+

### 2017-11-12 LatticeOptics/figure_source_scripts/latticeStability/month_spacing_pointing.py

@@ -1,0 +1,174 @@
+import numpy as np
+import pyfits
+import matplotlib.pyplot as plt
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+import brewer2mpl as cb
+import cmocean as cm
+import matplotlib.gridspec as gridspec
+import pickle as pkl
+import os
+import re
+import pandas as pd
+
+def find_matching_dirs(base_dir, regex=".*", conditions=[]):
+    """
+    given a directory, returns paths to all subdirectories whose name satisfies the regex
+    :param base_dir:
+    :param regex:
+    :param condition: list of lambda functions used in a filter that must all be satisfied
+    :return:
+    """
+    sub_dir_names = [name for name in os.listdir(base_dir) if os.path.isdir(os.path.join(base_dir, name))]
+    sub_dir_nums = filter(lambda x: re.match(regex, x), sub_dir_names)
+    for condition in conditions:
+        sub_dir_nums = filter(condition, sub_dir_nums)
+    num_dirs = map(lambda x: os.path.join(base_dir, x), sub_dir_nums)
+    return zip(num_dirs, sub_dir_nums)
+
+def sample_cmap(cmap, n_pts, bottom=0.0, top=1.0, gamma=1):
+    """
+    Produces n_pts colors sampled from the given cmap
+    :param cmap: colormap to be sampled from. Assume it is a function on [0, 1] that maps to a color tuple
+    :param n_pts: number of points to sample
+    :param bottom: minimum input
+    :param top: maximum input
+    :param gamma: corresponds to nonlinearity
+    :return: list of color tuples sampled from cmap
+    """
+    assert top <= 1
+    assert bottom >= 0
+    assert top >= bottom
+    rng = float(top) - float(bottom)
+    return map(cmap, bottom + rng*np.power(np.linspace(0, 1, n_pts), 1))
+
+def extract_stabilities(runlog_dir="W:\\RunLog"):
+    dated_lvecs = []
+    years = find_matching_dirs(runlog_dir, regex="[0-9]{4}")#, conditions=[lambda x: int(x) in [2016]])
+    for year, n_year in years:
+        months = find_matching_dirs(year, regex="[0-9]{2}")#, conditions=[lambda x: int(x) in [6]])
+        for month, n_month in months:
+            days = find_matching_dirs(month, regex="[0-9]{2}")
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/lattice_bandwidth/make_bandwidth_fig.py

@@ -1,0 +1,115 @@
+import numpy as np
+import scipy as sp
+import pandas as pd
+import os
+import matplotlib.pyplot as plt
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+import brewer2mpl as cb
+import cmocean as cm
+import matplotlib.gridspec as gridspec
+
+def plot_errorbar(ax, df, columns, outer_colors, inner_colors, labels=None,
+                  xlabel=None, ylabel=None, xlim=None, ylim=None):
+    """
+    plots the selected columns of df against their index on ax
+    :param ax:
+    :param df:
+    :param colunmns:
+    :param colors:
+    :param light_fac: lightness factor
+    :return:
+    """
+
+    for idx, column in enumerate(columns):
+        cd = outer_colors[idx]
+        cl = inner_colors[idx]
+        #cl = tuple([(x+light_fac)/(1+light_fac) for x in list(cd)])
+        #cl = tuple([(x+light_fac)/(1+light_fac) for x in list(cd)])
+
+        pars = {'linewidth': 1,
+                'fmt': 'o',
+                'ms': 3,  # marker size
+                'mew': 1,  # marker edge width
+                'c': cl,
+                'mec': cd,
+                'mfc': cl,
+                'capsize': 0,
+                'zorder': .2*idx+3,
+                'yerr': df[column+'_err'],
+                'label': column if labels is None else labels[column]}
+
+        ax.errorbar(df.index.values, df[column].values, **pars)
+    if xlabel is not None:
+        ax.set_xlabel(xlabel)
+    if ylabel is not None:
+        ax.set_ylabel(ylabel)
+    if xlim is not None:
+        ax.set_xlim(xlim)
+    if ylim is not None:
+        ax.set_ylim(ylim)
+    legend = ax.legend(loc=3, frameon=True)
+    legend.get_frame().set_linewidth(0)
+
+
+    ax.grid(zorder=0, color=color_grey)
+
+if __name__ == "__main__":
+    data_ne = pd.read_csv(os.path.join('results', 'ne_results.csv'))
+    data_ne = data_ne.set_index('power')
+    data_ne = data_ne/1e3  # let's work in kHz, not Hz
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/lattice_bandwidth/transfer_functions.py

@@ -1,0 +1,251 @@
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+import pandas as pd
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+
+def fourier_ser(ser, n_pad=10000, is_window=True, time_shift=0):
+    """
+    performs a fourier transform in the context of the pandas package
+    :param ser: time series input data. The index is assumed to be the time
+    :param n_pad: how much to pad the array (edge mode)
+    :param is_window: whether to apply the blackman window
+    :param time_shift: by convention, fft assumes t=0 at the first sample point. If you want t=0 to be referenced to a
+    different time (e.g. when working with impulse or step responses), timeshift let's you set that time. Only affects phases
+    :return: series of frequencies (index) to complex vals
+    """
+    data = np.pad(ser.values, (n_pad, n_pad), 'edge')  # pad to deal with fft artifacts from finite sampling time
+    n = data.size
+    window = np.blackman(n)
+    data = np.multiply(window, data)
+    fourier = np.fft.fftshift(np.fft.fft(data))
+    timestep = np.mean(ser.index[1:].values - ser.index[0:-1].values)
+    freqs = np.fft.fftshift(np.fft.fftfreq(n, d=timestep))
+    df = pd.DataFrame(data=np.transpose(np.vstack((np.abs(fourier),
+                                                     (np.angle(fourier) + 2*np.pi*freqs*(time_shift+timestep*n_pad) + np.pi) % (2*np.pi) - np.pi))),
+                        index=freqs, columns=['amp', 'angle'])
+    #print df[-20000:20000]
+    return df
+
+def get_transfer_function(filename, data_dir='data'):
+    df = pd.read_csv(os.path.join(data_dir, filename), delimiter=',', header=2, names=['time', 'setpoint', 'response'])
+    # The scope occasionally outputs garbage for the first datapoint, that's why that line is skipped by header = 2
+    df = df.set_index('time')
+    df -= df.setpoint.min()
+    ft_setpoint = fourier_ser(df['setpoint'], n_pad=10000)
+    ft_response = fourier_ser(df['response'], n_pad=10000)
+    transfer_function = ft_response
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/noiseplots/NoiseAnalysis20160312NE_IL_OL.py

@@ -1,0 +1,51 @@
+'''
+Created on Jan 22, 2016
+
+@author: anton
+'''
+
+
+"""
+This script outputs the noise curves for the 80048 nufern fiber amplifier in and out of loop, within the system and
+at high power
+"""
+
+from collections import OrderedDict
+from NoiseCurve import *
+import brewer2mpl as cb
+import numpy as np
+import cmocean
+
+
+if __name__ == '__main__':
+    print cmocean.cm.haline
+
+    # In loop
+    noise_curves_80048_IL = OrderedDict()
+    noise_curves_80048_IL['50 mW'] = NoiseCurve('20160312_NE_RIN_80048\\data', 2.00, lo_filename='50mW_lo.txt', med_filename='50mW_med.txt', hi_filename='measurement(174).csv', hi_rbw = 100)
+    noise_curves_80048_IL['100 mW'] = NoiseCurve('20160312_NE_RIN_80048\\data', 2.00, lo_filename='100mW_lo.txt', med_filename='100mW_med.txt', hi_filename='measurement(176).csv', hi_rbw = 100)
+    noise_curves_80048_IL['200 mW'] = NoiseCurve('20160312_NE_RIN_80048\\data', 2.00, lo_filename='200mW_lo.txt', med_filename='200mW_med.txt', hi_filename='measurement(178).csv', hi_rbw = 100)
+    noise_curves_80048_IL['400 mW'] = NoiseCurve('20160312_NE_RIN_80048\\data', 2.00, lo_filename='400mW_lo.txt', med_filename='400mW_med.txt', hi_filename='measurement(180).csv', hi_rbw = 100)
+    noise_curves_80048_IL['800 mW'] = NoiseCurve('20160312_NE_RIN_80048\\data', 2.00, lo_filename='800mW_lo.txt', med_filename='800mW_med.txt', hi_filename='measurement(182).csv', hi_rbw = 100)
+
+    colors = sample_cmap(cmocean.cm.haline, 5, gamma=1, top=0.75)
+    make_rin_plot(noise_curves_80048_IL, is_save=True, save_name='80048_NE_IL', colors=colors)
+
+    # Out of loop
+    noise_curves_80048_OL = OrderedDict()
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/noiseplots/NoiseAnalysis20160629.py

@@ -1,0 +1,46 @@
+'''
+Created on Jan 22, 2016
+
+@author: anton
+'''
+from NoiseCurve import *
+import collections
+import numpy as np
+from collections import OrderedDict
+import cmocean
+
+"""
+README:
+WE VARIED THE CURRENTS OF NW LATTICE 9213, in an effort to reduce the RIN - did not make huge difference
+We measured the RIN in closed loop at 100, 200 and 400 mW, always at 2 V offset voltage - consistent with NE
+We measured the RIN in closed loop, with at 2 kHz filter in addition to the cutoff filter.
+"""
+
+if __name__ == '__main__':
+
+    #CLOSED LOOP MEASUREMENT, with LOW PASS
+    noise_curves_9213_cl_LP = OrderedDict()
+    noise_curves_9213_cl_LP['100mW'] = NoiseCurve('20160629_RIN\\data', 2, lo_filename= '100mW_lo_LP.txt', med_filename='100mW_med_LP.txt', hi_filename='measurement(199).csv',hi_rbw = 100)
+    noise_curves_9213_cl_LP['200mW'] = NoiseCurve('20160629_RIN\\data', 2, lo_filename= '200mW_lo_LP.txt', med_filename='200mW_med_LP.txt', hi_filename='measurement(198).csv',hi_rbw = 100)
+    noise_curves_9213_cl_LP['400mW'] = NoiseCurve('20160629_RIN\\data', 2, lo_filename= '400mW_lo_LP.txt', med_filename='400mW_med_LP.txt', hi_filename='measurement(197).csv',hi_rbw = 100)
+
+    lp_colors = sample_cmap(cmocean.cm.speed, 3, bottom=0.3)[::-1]
+    make_rin_plot(noise_curves_9213_cl_LP, is_save=True, save_name='9213_with_lp', colors=lp_colors)
+
+    #CLOSED LOOP MEASUREMENT
+    noise_curves_9213_cl = collections.OrderedDict()
+    noise_curves_9213_cl['100mW'] = NoiseCurve('20160629_RIN\\data',2, lo_filename= '100mW_lo.txt', med_filename='100mW_med.txt', hi_filename='measurement(194).csv',hi_rbw = 100)
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/noiseplots/NoiseAnalysis20170326_PLL.py

@@ -1,0 +1,26 @@
+'''
+Created on Jan 22, 2016
+
+@author: anton
+'''
+from NoiseCurve import *
+import numpy as np
+
+from collections import OrderedDict
+        
+
+if __name__ == '__main__':
+    
+    noise_curves_PLL = OrderedDict()
+    noise_curves_PLL['noise floor'] = NoiseCurve('20170326_PLL_RIN', 0.240, lo_filename='noise_floor_lo.txt',
+                                             med_filename='noise_floor_med.txt', hi_filename='noise_floor.csv',
+                                             hi_rbw=100, is_freq_normalized_FFTM=True)
+    noise_curves_PLL['PLL'] = NoiseCurve('20170326_PLL_RIN', 0.240, lo_filename='pll_lo_noamp.txt',
+                                            med_filename='pll_med_noamp.txt', hi_filename='high_freq_RIN.csv',
+                                            hi_rbw=100, is_freq_normalized_FFTM=True)
+
+    colors = cb.get_map('OrRd', 'Sequential', 6, reverse=False).mpl_colors[2:]  # Nufern colors
+
+    make_rin_plot(noise_curves_PLL, is_save=True, save_name='pll_rin', x_window=[.8e3, 10e6],
+                  y_window=[-175,-120])
+

### 2017-11-12 LatticeOptics/figure_source_scripts/noiseplots/NoiseAnalysis20170329_DA.py

@@ -1,0 +1,38 @@
+'''
+Created on Jan 22, 2016
+
+@author: anton
+'''
+from NoiseCurve import *
+import numpy as np
+import cmocean
+
+from collections import OrderedDict
+        
+
+if __name__ == '__main__':
+
+    colors = cb.get_map('OrRd', 'Sequential', 6, reverse=False).mpl_colors[2:]  # Nufern colors
+
+    noise_curves_DA = OrderedDict()
+    noise_curves_DA['fixed'] = NoiseCurve('20170329_DA_noise', 1.95, lo_filename='DA_fixed_lo.txt',
+                                            med_filename='DA_fixed_med.txt', hi_filename='fixed_spectrum.csv',
+                                            hi_rbw=100, is_freq_normalized_FFTM=True)
+
+    noise_curves_DA_scanning = OrderedDict()
+    #noise_curves_DA_scanning['DA'] = NoiseCurve('20170329_DA_noise', 1.95, lo_filename='DA_scan_lo.txt',
+    #                                        med_filename='DA_scan_med.txt', hi_filename='sawtooth_spectrum.csv',
+    #                                        hi_rbw=100, is_freq_normalized_FFTM=True, offset=(0, 0, 40))
+
+    noise_curves_DA_scanning['fixed'] = NoiseCurve('20170329_DA_noise', 1.95, lo_filename='DA_fixed_lo.txt',
+                                            med_filename='DA_fixed_med.txt', hi_filename='fixed_spectrum.csv',
+                                            hi_rbw=100, is_freq_normalized_FFTM=True)
+
+    noise_curves_DA_scanning['scanning'] = NoiseCurve('20170414_DA_Scan', 1.75, lo_filename='DA_20ms_ramp_lo.txt',
+                                                med_filename='DA_20ms_ramp_med.txt', hi_filename='measurement(210).csv',
+                                                hi_rbw=100, is_freq_normalized_FFTM=True)
+
+    colors = sample_cmap(cmocean.cm.haline, 2, top=0.6, bottom=0.0)
+    ax = make_rin_plot(noise_curves_DA_scanning, is_save=True, save_name='da_rin_scan', x_window=[.8e3, 10e6],
+                  y_window=[-165, -90], colors = colors)
+

### 2017-11-12 LatticeOptics/figure_source_scripts/noiseplots/NoiseCurve.py

@@ -1,0 +1,190 @@
+'''
+Created on Jan 22, 2016
+
+@author: anton
+'''
+import numpy as np
+import os
+
+import matplotlib.pyplot as plt
+import brewer2mpl as cb
+from matplotlib.backends.backend_pdf import PdfPages
+from plot_tools import *
+from matplotlib import rcParams
+import pylab as pl
+
+
+def find_nearest(array, value):
+    idx = (np.abs(array-value)).argmin()
+    return idx, array[idx]
+
+
+def ensure_dir(f):
+    d = os.path.dirname(f)
+    if not os.path.exists(d):
+        os.makedirs(d)
+
+
+def sample_cmap(cmap, n_pts, bottom=0.0, top=1.0, gamma=1):
+    """
+    Produces n_pts colors sampled from the given cmap
+    :param cmap: colormap to be sampled from. Assume it is a function on [0, 1] that maps to a color tuple
+    :param n_pts: number of points to sample
+    :param bottom: minimum input
+    :param top: maximum input
+    :param gamma: corresponds to nonlinearity
+    :return: list of color tuples sampled from cmap
+    """
+    assert top <= 1
+    assert bottom >= 0
+    assert top >= bottom
+    rng = float(top) - float(bottom)
+    return map(cmap, bottom + rng*np.power(np.linspace(0, 1, n_pts), 1))
+
+
+def make_rin_plot(nc_dict, x_window=[.8e3, 3e6], y_window=[-155,-85],
+                  x_label='Frequency (Hz)', y_label="Rin (dBc/Hz)",
+                  colors=cb.get_map('Set1', 'Qualitative', 4, reverse=True).mpl_colors, linewidth=1,
+                  is_save=False, save_name='RIN', save_dir='plots', is_show=False):
+    """
+    :param nc_dict: dictionary of noise curves
+    :param x_window: window of x axis
+    :param y_window: window of y axis
+    :param x_label: label of x
+    :param y_label: label of y
+    :param colors:
+    :param linewidth:
+    :param is_save:
+    :param save_name:
+    :param save_dir:
+    :param is_show
+    :return:
+    """
+
+    #settings
+    scl = 1/1.61
+    fig_width = 3.37
+    fig_height = scl*fig_width
+
+    rcpars.update({
+        "figure.autolayout": True,
[…]

### 2017-11-12 LatticeOptics/figure_source_scripts/noiseplots/PLL_spectrum.py

@@ -1,0 +1,49 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import pylab as pl
+from plot_tools import *
+import matplotlib as mpl
+import brewer2mpl as cb
+from matplotlib import rcParams
+import brewer2mpl as cb
+import cmocean as cm
+
+if __name__ == "__main__":
+    data_dir = 'pll_spectrum'
+    plot_dir = 'plots'
+    data_file = 'freq_spectrum.csv'
+
+    spectrum = np.genfromtxt('{}//{}'.format(data_dir, data_file), delimiter=',', skip_footer=6, skip_header=226)[:, 1:3]
+    print spectrum
+
+    fig_name = "pll_spectrum"
+    rcParams.update({})
+    scl = 1/1.61
+    fig_width = 3.37
+    fig_height = scl*fig_width
+
+    rcpars.update({
+        "figure.autolayout": True,
+        "figure.figsize": (fig_width, fig_height),
+        "figure.subplot.left": .25,
+        "figure.subplot.right": .94,
+        "figure.subplot.bottom": .2,
+        "figure.subplot.top": .95,
+    })
+
+    pl.rcParams.update(rcpars)
+
+    init_plt()
+    fig = pl.figure()
+    ax = fig.add_subplot(1, 1, 1)
+    colors_val_cb = cb.get_map('RdGy', 'diverging', 5).mpl_colors
+    ax.grid(zorder=0, color=color_grey)
+    ax.plot(spectrum[:, 1], spectrum[:, 0]-np.max(spectrum[:, 0]), color=colors_val_cb[0], zorder=1)
+    ax.set_xlabel('Frequency (MHz)')
+    ax.set_ylabel('Power (dBc)')
+    ax.set_xlim([77.75, 82.25])
+    ax.set_ylim([-105, 5])
+    ax.legend()
+
+    plt.savefig('{0}//{1}.pdf'.format(plot_dir, fig_name))

### 2018-01-31 LatticeOptics/latticeOpticsV4.tex
New RIN data Mephisto MOPA 55W, updated Fig3

@@
 
-Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation \cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.%, strongly correlated systems, quantum state engineering, quantum computing and precision metrology.
+Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation \cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
+%, strongly correlated systems, quantum state engineering, quantum computing and precision metrology.
 Further, the recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian ~\cite{Hubbard1963}.
@@
     \includegraphics{fig/fig3_combined.pdf}
-    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed.
+    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed, as well as an independent Mephisto MOPA 55W (not used for the optical lattice presented in this manuscript).
 (b) Shows the open (OL) and closed (CL) loop behavior of the high power feedback loop.

### 2018-01-31 LatticeOptics/figures/figure3/NoiseAnalysis20160122.py

@@ -8,49 +8,60 @@ import numpy as np
 
 from collections import OrderedDict
         
+# import os
+# print os.path.join('A', 'B')
 
 if __name__ == '__main__':
     
     noise_curves_bg = OrderedDict()
     noise_curves_bg['background'] = NoiseCurve('20160122_RIN', 2.0, lo_filename='background12khz.txt',
-                                               med_filename='background100khz.txt', hi_filename='measurement(144).csv')
+                                               med_filename='background100khz.txt', hi_filename='measurement(144).csv', hi_rbw=10)
     noise_curves_bg['mephisto'] = NoiseCurve('20160122_RIN', 2.0, lo_filename='mephisto12khz.txt',
-                                             med_filename='mephisto100khz.txt', hi_filename='measurement(145).csv')
+                                             med_filename='mephisto100khz.txt', hi_filename='measurement(145).csv', hi_rbw=10)
     
     noise_curves_80048 = OrderedDict()
-    noise_curves_80048['33.7A'] = NoiseCurve('20160122_RIN\\80048', 2.0, lo_filename='33p7_12kHz.txt',
+    noise_curves_80048['Nufern 33.7A'] = NoiseCurve(os.path.join('20160122_RIN', '80048'), 2.0, lo_filename='33p7_12kHz.txt',
                                              med_filename='33p7_100kHz.txt', hi_filename='measurement(150).csv',
                                              hi_rbw=100)
-    noise_curves_80048['30A'] = NoiseCurve('20160122_RIN\\80048', 2.0, lo_filename='30_12kHz.txt',
+    noise_curves_80048['Nufern 30A'] = NoiseCurve(os.path.join('20160122_RIN', '80048'), 2.0, lo_filename='30_12kHz.txt',
                                            med_filename='30_100kHz.txt', hi_filename='measurement(153).csv',
                                            hi_rbw=100)
-    noise_curves_80048['25A'] = NoiseCurve('20160122_RIN\\80048', 2.0, lo_filename='25_12kHz.txt',
+    noise_curves_80048['Nufern 25A'] = NoiseCurve(os.path.join('20160122_RIN', '80048'), 2.0, lo_filename='25_12kHz.txt',
                                            med_filename='25_100kHz.txt', hi_filename='measurement(151).csv', hi_rbw=100)
[…]

### 2018-01-31 LatticeOptics/figures/figure3/NoiseCurve.py

@@ -42,7 +42,7 @@ def sample_cmap(cmap, n_pts, bottom=0.0, top=1.0, gamma=1):
     return map(cmap, bottom + rng*np.power(np.linspace(0, 1, n_pts), 1))
 
 
-def make_rin_plot(nc_dict, x_window=[.8e3, 3e6], y_window=[-155,-85],
+def make_rin_plot(nc_dict, x_window=[.8e3, 3.0e6], y_window=[-155,-85], #[-155,-85]
                   x_label='Frequency (Hz)', y_label="Rin (dBc/Hz)",
                   colors=cb.get_map('Set1', 'Qualitative', 4, reverse=True).mpl_colors, linewidth=1,
                   is_save=False, save_name='RIN', save_dir='plots', is_show=False):
@@ -82,12 +82,11 @@ def make_rin_plot(nc_dict, x_window=[.8e3, 3e6], y_window=[-155,-85],
     ax = fig.add_subplot(1, 1, 1)
 
     for idx, (label, nc) in enumerate(nc_dict.iteritems()):
-        print idx
         ax.plot(nc.mat[:, 0], nc.mat[:, 1], linewidth=linewidth, color=colors[idx], label=label, zorder=idx)
 
     ax.set_xlim(x_window)
     ax.set_ylim(y_window)
-    ax.grid(zorder=-1, color=color_grey)
+    ax.grid(zorder=-1, color=color_grey, linestyle = (4,(2,6)), linewidth = 0.5)
 
     ax.legend()
 
@@ -100,7 +99,8 @@ def make_rin_plot(nc_dict, x_window=[.8e3, 3e6], y_window=[-155,-85],
     # fig.tight_layout()
 
     if is_save:
-        out_name = '%s\\%s' % (save_dir, save_name)
+        # out_name = '%s\\%s' % (save_dir, save_name)
+        out_name = os.path.join('%s', '%s') % (save_dir, save_name)
 
         pp = PdfPages('%s.pdf' % out_name)
         plt.savefig(pp, format='pdf')
@@ -115,9 +115,11 @@ class NoiseCurve(object):
                  optical_power = None, lo_rbw=62.5, med_rbw=500, hi_rbw=10, is_freq_normalized_SA=False,
                  is_freq_normalized_FFTM=False, offset=(0, 0, 0)):
         self.data_dir = data_dir
-        self.lo_filename = "%s\\%s"%(data_dir, lo_filename) if lo_filename is not None else None
[…]

### 2018-04-24 LatticeOptics/figures/figure3/plot_tools.py
Adding Mephisto to RIN Figure

@@ -1,0 +1,1398 @@
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import brewer2mpl
+from matplotlib.ticker import MultipleLocator
+import matplotlib.colors as colors
+from plot_settings import *
+import matplotlib.ticker as mtick
+mpl.use('pdf')
+
+'''
+plt     plot to output to
+th_x    array of theory x points (plotted as line)
+th_y    theory y
+data_x  data x (plotted as points)
+data_y  data y
+err_x   data error x
+err_y   data error y
+cs      start color, i.e. color of first set of points (-1)
+cf      final color
+cpow    exponent to use for nonlinear coloring
+
+Optional:
+xlim    x axis limits
+ylim    y axis limits
+ymax    maximum value for y, will truncate error bars past this
+label   label to place in upper right corner
+tick_format     format of the numbers for each tick
+trunc_marg      margin to truncate points for (in x direction)
+                must set xlim!
+'''
+
+# Global settings
+mew = 0.8  # Marker Edge Width #0.8 #
+ms = 1.2  # Marker Size #1.2 #
+cmap = brewer2mpl.get_map('RdBu', 'Diverging', 11).mpl_colormap
+
+
+def init_plt():
+    plt.rc('font', family='sans-serif')
+    plt.rcParams['font.sans-serif'] = 'Helvetica'
+    plt.rcParams['font.size'] = 7
+    plt.rcParams['mathtext.fontset'] = 'custom'
+
+    plt.rcParams['mathtext.rm'] = 'Helvetica'
+    plt.rcParams['mathtext.it'] = 'Helvetica:italic'
+    plt.rcParams['mathtext.bf'] = 'Helvetica:bold'
+
+    plt.rcParams['legend.frameon'] = False
+
+    plt.rcParams['axes.linewidth'] = 0.4
+    plt.rcParams['xtick.major.width'] = 0.3
+    plt.rcParams['xtick.major.size'] = 1
+    plt.rcParams['ytick.major.width'] = 0.3
+    plt.rcParams['ytick.major.size'] = 1
+
+    plt.rcParams['xtick.minor.width'] = 0.2
+    plt.rcParams['xtick.minor.size'] = 0.8
[…]

### 2018-04-24 LatticeOptics/latticeOpticsV4.tex
Updating text, small edits here and there, repositioning figures, adding fig captions, replacing new figures

@@
 
-\author{A.M., S.B., F.H., M.F.P., C.S.C., G.J., D.G.}
-\author{M. G.}
+\author{A.Mazurenko, S. Blatt, F. Huber, M. F. Parsons, C. S. Chiu, G. Ji, D. Greif}
+\author{M. Greiner}
 \affiliation{
@@
 Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation \cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
-%, strongly correlated systems, quantum state engineering, quantum computing and precision metrology.
-Further, the recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian ~\cite{Hubbard1963}.
+The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over individual atoms at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian ~\cite{Hubbard1963}.
 However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
@@
 Even if the system thermalizes, heating rates can limit the interrogation time available to probe a low-temperature state.
-In a similar vein, experiments that rely on a small number of atoms held by multiple traps place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.%~\cite{Mazurenko2016}.FIXME: CITATIONS
+Similarly, experiments that rely on a small number of atoms held by multiple traps place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.
 
-To address these concerns, we discuss a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
+In this work we discuss a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
 The stability of the lattice position is below the single site level and the stability of the harmonic confinement is at the few site level.
-\begin{figure}
+
+\begin{figure}[t]
   \begin{center}
-    \includegraphics{fig/figure1/figure1.pdf}
+    \includegraphics[width=0.85\columnwidth]{fig/figure1/figure1.pdf}
     \caption{\textbf{High level overview} showing the major components of the lattice laser feedback system.}\label{fig:high_level}
@@
 
+In the following we give an in-depth technical description of the optical lattice setup we developed.
+We start with the laser system itself which includes the seed laser, amplification and optical setup for controlling the laser beam.
+In the next section we provide a detailed description of the two-stage laser power feedback system.
+In the last two sections we conduct a performance analysis of the short- and long-term stability of the optical lattice.
+
 \section{Laser system}
@@
 
+\begin{figure*}
+  \begin{center}
+    \includegraphics{fig/fig3_combined.pdf}
+    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed, as well as an independent Mephisto MOPA 55W (not used for the optical lattice presented in this manuscript).
+(b) Shows the open (OL) and closed (CL) loop behavior of the high power feedback loop.
+(c) Shows open loop behavior of the low power feedback loop after making the modifications.
+(d) Closed loop behavior of the loop system without additional filtering, measured on the same setup as (c).}\label{fig:noises}
+  \end{center}
+\end{figure*}
+
 \subsection{Fiber amplifier system}
@@
 The amplification is performed using a two stage design, where the stages are controlled and powered using separate power supplies and electronics.
+
+\begin{figure*}[t]
+  \begin{center}
+    \includegraphics{fig/optical_layout_wide.pdf}
+    \caption{\textbf{Optical layout of the optical lattice system for beam shaping and modulation.}}\label{fig:optical_layout}
+  \end{center}
+\end{figure*}
 
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics{fig/fig3_combined.pdf}
-    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed, as well as an independent Mephisto MOPA 55W (not used for the optical lattice presented in this manuscript).
-(b) Shows the open (OL) and closed (CL) loop behavior of the high power feedback loop.
-(c) Shows open loop behavior of the low power feedback loop after making the modifications.
-(d) Closed loop behavior of the loop system without additional filtering, measured on the same setup as (c).}\label{fig:noises}
-  \end{center}
-\end{figure*}
-
 The operation of the Nufern fiber amplifiers can be further optimized by finely controlling the cooling water.
@@
 Experimentally, we have found that more power can be gained by running the amplifiers at hotter temperature.
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics{fig/optical_layout_wide.pdf}
-    \caption{\textbf{Optical layout of the optical lattice system for beam shaping and modulation.}}\label{fig:optical_layout}
-  \end{center}
-\end{figure*}
 
@@
 
-\begin{figure*}
+\begin{figure}
   \begin{center}
-    \includegraphics{fig/step_response.pdf}
+    \includegraphics[width=\columnwidth]{fig/step_response.pdf}
     \caption{\textbf{Berek compensator based feedback loop}.
@@
   \end{center}
-\end{figure*}
+\end{figure}
 A key point, as seen in figure \ref{fig:berek}, is that if the waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
@@
 
+\begin{figure*}
+  \begin{center}
+    \includegraphics{fig/low_pass_filters.pdf}
+    \caption{\textbf{Laser noise of the lattice system with and without additional low pass filters} (a) Closed loop laser made a fiber amplifier (different than the one in figure \ref{fig:noises}.
+(b) Noise on the same system as (a), but with extra filters.}\label{fig:low_pass_noises}
+  \end{center}
+\end{figure*}
+
 A common behavior of analog feedback systems with integration components is termed \textit{integral wind-up}~\cite{Bechhoefer2005}, and occurs when the feedback loop is manually broken, meaning that the actuator can no longer adjust the state of the controlled parameter.
@@
 As a result, we added a first order low pass with a $3$ dB frequency of $10$ kHz leading to the improvement shown in figure \ref{fig:low_pass_noises} (the fiber amplifier used to take this data was different from the one used for \ref{fig:noises}, although their performance is comparable.
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics{fig/low_pass_filters.pdf}
-    \caption{\textbf{Laser noise of the lattice system with and without additional low pass filters} (a) Closed loop laser made a fiber amplifier (different than the one in figure \ref{fig:noises}.
-(b) Noise on the same system as (a), but with extra filters.}\label{fig:low_pass_noises}
-  \end{center}
-\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
   \begin{center}
-    \includegraphics[width=\columnwidth]{fig/averaged_mott.png}
+    \includegraphics{fig/AveragedMI.pdf}
     \caption{\textbf{Averaged images of Mott insulators}.
-A series of Mott insulators was created over the course of approximately one hour, and the average image is shown\cite{Greif2016}.
+a) Several Mott insulators were created over the course of approximately one hour, and the average image is shown\cite{Greif2016}.
 If the lattice fluctuated across more than a small fraction of a lattice site, the modulation contrast would be washed out.
-The absence of this effect means that the phase of the optical lattice is stable.}\label{fig:averaged_mott}
+The absence of this effect means that the phase of the optical lattice is stable.
+b) shows an individual image of a Mott insulator.}\label{fig:averaged_mott}
   \end{center}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics{fig/pointing_figure.pdf}
-    \caption{\textbf{Short term positional stability.} (a) A histogram of shot-to-shot step sizes along the transverse and longitudinal directions, with a Gaussian fit.
-(b) Correlations between the step size of subsequent shots.
-(c) Calibration data for the ``affine fit'' of the conversion from camera pixels to lattice dimentions.
-(d) Predicted location versus measured location along the transverse and longitudinal directions.
-(e,f) The measured position and predicted position of the atomic cloud, based on refitting the offset every $20$ experimental realizations.}\label{fig:stability}
-  \end{center}
-\end{figure*}
-
 Changing external conditions can contaminate large datasets if the prepared state sensitively depends on laser pointing. 
@@
 Once this correlation is taken into account, we estimate a drift of $8(1)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the transverse direction and $12(2)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the axial direction, compared to a beam waist of approximately $80$ $\mu$m ($\approx 140$ sites).
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics{fig/pointing_figure.pdf}
+    \caption{\textbf{Short term positional stability.} (a) A histogram of shot-to-shot step sizes along the transverse and longitudinal directions, with a Gaussian fit.
+(b) Correlations between the step size of subsequent shots.
+(c) Calibration data for the ``affine fit'' of the conversion from camera pixels to lattice dimentions.
+(d) Predicted location versus measured location along the transverse and longitudinal directions.
+(e,f) The measured position and predicted position of the atomic cloud, based on refitting the offset every $20$ experimental realizations.}\label{fig:stability}
+  \end{center}
+\end{figure*}
 
@@
 
+\begin{figure}
+\begin{center}
+    \includegraphics[width=\columnwidth]{fig/lattice_stability.pdf}
+    \caption{\textbf{Long term stability over approximately nine months.} The lattice spacing $|\mathrm{v}_x|$ and $|\mathrm{v}_y|$ and the lattice angles $\theta_x$ and $\theta_y$ along the two lattice axes $x$ and $y$ are shown over the duration of almost 1 year.
+}\label{fig:long_term_stability}
+  \end{center}
+\end{figure}
+
 \section{Long-term stability of the lattice structure}
-FIXME: I PROPOSE MOVING THIS INTO THE SUPPLEMENTARY MATERIALS: IT MAY BE INTERESTING TO EXPERTS, BUT IS A LITTLE TOO ``ANECDOTAL'' FOR THE MAINTEXT.
 A benefit of site-resolved imaging is that every measurement of the atomic distribution is also a direct measurement of the underlying lattice structure. 
 As discussed in the supplementary material of~\cite{Parsons2016, Greif2016}, the Fourier transform of an atomic distribution contains distinct peaks corresponding to the lattice structure, and these peaks can be used to extract the phase, relative angle, and spacing of the lattices.
-For this reason, we looked back at nine months of data spanning June 2016 through April 2017 in order to learn how these parameters change over time.
-Several interesting features can be seen from this figure \ref{fig:long_term_stability}.
+For this reason, we recorded a long-term measurement spanning almost one year in order to learn how these parameters change over time, see Fig.~\ref{fig:long_term_stability}.
+Several interesting features can be seen from the observed behavior.
 \begin{enumerate}
-  \item During the summer of 2016, the lattice spacing appears to have slowly varied over as much as 10\%.
-    This can be attributed to unexplained drifts of the optical system that required daily refocusing of the imaging system using an auxiliary lens, which simultaneously changed the magnification. 
+  \item During the first few months the lattice spacing appears to have slowly varied over as much as $10\%$.
+    This might be caused by drifts of the optical system that required daily refocusing of the imaging system using an auxiliary lens, which simultaneously changed the magnification. 
   \item The imaging system was simplified in September 2016, causing a sudden change in the magnification. 
-  \item The system has been more stable in the spring of 2017 - the lattice spacing $|v|$ exhibits fractional fluctuations $\sigma_{|v|}/\mu_{|v|}\leq 0.005$.
+  \item The system has been more stable since then and the lattice spacing $|v|$ exhibits fractional fluctuations $\sigma_{|v|}/\mu_{|v|}\leq 0.005$.
   \item Unlike magnification, which sensitively depends on the imaging system focus, the angle is unlikely to be affected by the imaging system unless the camera is mechanically rotated.
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics{fig/lattice_stability.pdf}
-    \caption{\textbf{Long term positional stability over approximately nine months.}}\label{fig:long_term_stability}
-  \end{center}
-\end{figure*}
-
 \section{Conclusion}
@@
 In this design, key emphasis has been placed on the stability of the pointing and the intensity of the optical lattice, of particular importance to the underlying physics.
-To improve performance, the system can be improved in a variety of ways, such as by:
-\begin{enumerate}
-  \item Replacement of the \textit{Nufern} fiber amplifiers with a lower noise model.
-  \item Replacement of the analog feedback loop by a low-noise digital loop.
-  \item Active stabilization of the laser pointing.
-\end{enumerate}
-Even without these improvements, the system has exhibited robust and reliable performance in performing a wide variety of experiments.
+To improve performance, the system can be upgraded in a variety of ways.
+For example, the \textit{Nufern} fiber amplifiers can be replaced with a lower noise model.
+Or the analog feedback loop can be replaced by a low-noise digital version.
+Additionally, active stabilization of the laser pointing could be implemented in the future.
 

### 2018-06-12 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Added version 5

--- 2018-04-24 LatticeOptics/latticeOpticsV4.tex
@@
 
-%% Keep track of changes
-%\usepackage[final]{changes}
-\usepackage[draft]{changes}
-\definechangesauthor[color=green]{AM}
-\definechangesauthor[color=blue]{SB}
-
-\DeclareMathOperator{\re}{Re}
-\DeclareMathOperator{\im}{Im}
-
-\newcommand\avg[1]{\left\langle#1\right\rangle}
-
 \newcommand\unit[2]{\ensuremath{#1~\mathrm{{#2}}}}
@@
 \newcommand\Li{\Isotope{6}{Li}}
-\newcommand\K{\Isotope{40}{K}}
-\newcommand\Rb{\Isotope{87}{Rb}}
-\newcommand\Sr{\Isotope{87}{Sr}}
-\newcommand\Yb{\Isotope{171}{Yb}}
-\newcommand\Er{\Isotope{167}{Er}}
-\newcommand\Dy{\Isotope{161}{Dy}}
 
@@
 \newcommand\NA{\ensuremath{\mathrm{NA}}}
-\newcommand{\osim}{\ensuremath{\mathord{\sim}}}
-\newcommand{\Erecl}{\ensuremath{E_\mathrm{rec}}}
-\newcommand{\Ereca}{\ensuremath{E_\mathrm{rec}^\mathrm{(a)}}}
 \newcommand\FIXME{{\color{red}\ensuremath{\mathrm{FIXME}}}}
 
-\newcommand\TrapFreq{\ensuremath{\nu_t}}
-\newcommand\RecoilEnergy{\ensuremath{E_\mathrm{rec}}}
-
-\graphicspath{{./figures/}}
 \begin{document}
@@
 
-\author{A.Mazurenko, S. Blatt, F. Huber, M. F. Parsons, C. S. Chiu, G. Ji, D. Greif}
+\author{A. Mazurenko}
+\altaffiliation{
+  Present address: FIXME}
+\author{S. Blatt}
+\altaffiliation{
+  Present address: Max-Planck-Institut f{\"u}r Quantenoptik,
+  Hans-Kopfermann-Stra{\ss}e 1, 85748 Garching, Germany}
+\author{F. Huber}
+\altaffiliation{
+  Present address: IPG Photonics Corporation, Oxford, MA 01540}
+\author{M. F. Parsons}
+\altaffiliation{
+  Present address: FIXME TOO}
+\author{C. S. Chiu}
+\author{G. Ji}
+\author{D. Greif}
 \author{M. Greiner}
@@
 \begin{abstract}
- We describe the design of a stable high power $1064\,$nm laser system for practical use in optical lattice experiments.
+ We describe the design of a stable high power \unit{1064}{nm} laser system for practical use in optical lattice experiments.
 The system is based on a low noise laser amplified by an array of four heavily modified, high-power fiber amplifiers.
@@
 
-Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation \cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
-The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over individual atoms at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian ~\cite{Hubbard1963}.
+Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
+The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over individual atoms at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian~\cite{Hubbard1963}.
 However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
@@
 
-In this work we discuss a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
-The stability of the lattice position is below the single site level and the stability of the harmonic confinement is at the few site level.
+In this work we discuss major improvements to our high power optical lattice system~\cite{Blatt2015} and show levels of intensity noise below \unit{-120}{dBc/Hz} between \unit{1}{kHz} and \unit{3}{MHz} Fourier frequency.
+The stability of the lattice position is below the single site level (over a few hours) and the stability of the harmonic confinement is at the few site level (over nine months).
 
@@
   \begin{center}
-    \includegraphics[width=0.85\columnwidth]{fig/figure1/figure1.pdf}
+    \includegraphics[width=0.85\columnwidth]{Figure1.pdf}
     \caption{\textbf{High level overview} showing the major components of the lattice laser feedback system.}\label{fig:high_level}
@@
 
-The coarse architecture of the system is shown in figure \ref{fig:high_level} and is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Parsons2016}).
+The architecture of the system is shown in Fig.~\ref{fig:high_level} and is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Blatt2015,Parsons2016}).
 These amplifiers generate enough light to perform site resolved imaging~\cite{Parsons2015}, but also substantially increase the level of intensity and pointing noise.
-The fiber amplifier output is controlled by two feedback loops, which stabilize the light in low power and high power regimes, discussed later.
-After intensity stabilization, the laser is mode-shaped to a desired waist.
+The fiber amplifier output is controlled by two feedback loops, which stabilize the light in low power and high power regimes, respectively, as discussed later.
+After intensity stabilization, the laser beam is mode-shaped to a desired waist.
 The optical system is engineered to be passively stable in terms of pointing, but the position and phase of the optical lattice are monitored in real time, and beam pointing can be controlled with remotely actuated mirrors.
@@
 In the following we give an in-depth technical description of the optical lattice setup we developed.
-We start with the laser system itself which includes the seed laser, amplification and optical setup for controlling the laser beam.
+We start with the laser system itself which includes the seed laser, amplification and optical setup for controlling the laser beams.
 In the next section we provide a detailed description of the two-stage laser power feedback system.
-In the last two sections we conduct a performance analysis of the short- and long-term stability of the optical lattice.
+In the last two sections we conduct a performance analysis of the short- and long-term stability of the optical lattices produced by this system.
 
@@
 \subsection{Seed laser system}
-The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately $2\,$W of $1064\,$nm light. 
+The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately \unit{2}{W} of \unit{1064}{nm} light.
 This commercial laser utilizes a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability.
-This source is split into four fibers (Thorlabs PM980-XP), each connected to a fiber amplifier. 
-Three of these fiber amplifiers are used to produce the 3D optical lattice~\cite{Parsons2016}, and a fourth is used for transport~\cite{Huber2014}.
-To avoid interference of the lattice beams, two of the beam paths pass through acousto-optic modulators (AOM), which detune the lattice frequencies from each other.
+This source is split and coupled into four single-mode, polarization-maintaining fibers (Thorlabs PM980-XP), each connected to the input of a fiber amplifier.
+Three of these fiber amplifiers are used to produce the 3D optical lattice~\cite{Blatt2015,Parsons2016}, and a fourth is used for transport~\cite{Huber2014}.
+To avoid interference of the lattice beams, two of the beam paths pass through acousto-optic modulators (AOMs), which detune the lattice frequencies from each other.
 
@@
   \begin{center}
-    \includegraphics{fig/fig3_combined.pdf}
+    \includegraphics{Figure2.pdf}
     \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed, as well as an independent Mephisto MOPA 55W (not used for the optical lattice presented in this manuscript).
@@
 (c) Shows open loop behavior of the low power feedback loop after making the modifications.
-(d) Closed loop behavior of the loop system without additional filtering, measured on the same setup as (c).}\label{fig:noises}
+(d) Closed loop behavior of the loop system without additional filtering, measured on the same setup as panel (c).}\label{fig:noises}
   \end{center}
@@
 \subsection{Fiber amplifier system}
-Quantum gas microscopy of \Li{} requires single site trap frequencies of approximately $1\,$MHz~\cite{Parsons2015} in order to be in the Lamb-Dicke regime necessary for Raman sideband cooling.
+Quantum gas microscopy of \Li{} requires single site trap frequencies of approximately \unit{1}{MHz}~\cite{Parsons2015} to be in the Lamb-Dicke regime necessary for Raman sideband cooling.
 Such trap frequencies may only be attained using tightly focused, high-power beams.
-In practical terms, this requires approximately $30\,$W per lattice axis, which we attain using \textit{Nufern} Fiber amplifiers (NuAmp SUB1174-34).
+In practical terms, this requires approximately $30\,$W per lattice axis, which we attain using Nufern fiber amplifiers (NuAmp SUB1174-34).
 These amplifiers can amplify $150\,$mW of seed light to up to approximately $45\,$W.
@@
   \begin{center}
-    \includegraphics{fig/optical_layout_wide.pdf}
-    \caption{\textbf{Optical layout of the optical lattice system for beam shaping and modulation.}}\label{fig:optical_layout}
+    \includegraphics{Figure3.pdf}
+    \caption{\textbf{Optical layout} of the optical lattice system for beam shaping and modulation.}
+    \label{fig:optical_layout}
   \end{center}
@@
 \begin{enumerate}
-  \item The fiber amplification process is susceptible to many technical noise sources, such as acoustic coupling of the fiber to the environment and electrical design of the amplifier, 
-  \item Stimulates Brillouin scattering (SBS) places a hard lower bound on the noise floor~\cite{Agrawal2013}. 
+  \item The fiber amplification process itself is susceptible to many technical noise sources, such as acoustic coupling of the fiber to the environment and electrical design of the amplifier;
+  \item Stimulated Brillouin scattering (SBS) places a hard lower bound on the relative intensity noise (RIN) floor~\cite{Agrawal2013}.
 \end{enumerate}
@@
 Worse yet, it is suspected of causing ground loops which add noise and interference to the analog systems.
-This added noise can be seen in figure \ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser.
-We solve this problem by replacing the USB control board with a custom-designed solution  that is compatible with our custom control system and engineered to avoid ground loops.
+This added noise can be seen in Fig.~\ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser.
+We solve this problem by replacing the USB control board with a custom-designed solution  that is compatible with our laboratory control system and engineered to avoid ground loops.
 
-Further sources of technicl noise arise from the design of the amplifier.
-There are two power supplies in the fiber amplifier - a general purpose power supply (PSU) for the control electronics and the first, low-power amplification stage and a high power supply for the second, high-power stage.
-Despite the presence of a water-cooled cold-plate for the gain fiber and pump diodes, the high power PSU is air cooled by an internal fan.
-This fan is expected to increase noise at acoustic frequencies and degrade pointing stability by increasing vibrations.
-In order to reduce acoustic coupling and reduce switching power supply noise, both power supplies were removed from the fiber amplifier chassis, and the low power supply was replaced by a linear PSU (Acopian A24MT350M).
-Further, a high current line filter (MPE DS26387) was added to the high-power PSU (Lumina LDD-600-60-10-5VP/M).
+Further sources of technical noise arise from the design of the amplifier.
+There are two power supplies in the fiber amplifier: (1) a general purpose power supply (PSU) for the control electronics and the first, low-power amplification stage and (2) a high-power supply for the second, high-power stage.
+Despite the presence of a water-cooled cold-plate for the gain fiber and pump diodes, the high power PSU is air cooled by an internal fan with variable frequency.
+This fan adds noise at acoustic frequencies and degrades pointing stability by increasing vibrations on the output fiber tip.
+To reduce acoustic coupling and reduce switching power supply noise, both power supplies were removed from the fiber amplifier chassis, and the low-power supply was replaced by a linear PSU (Acopian A24MT350M).
+Further, a high current low-pass filter (MPE DS26387) was added to the high-power PSU (Lumina LDD-600-60-10-5VP/M).
 
-These upgrades serve to suppress many of the noise spurs measured in the relative intensity noise (RIN) of the fiber amplifier. 
-This can be as seen by comparing figure \ref{fig:noises} (a) and (b), particularly in the region of approximately $10$ kHz. 
-The measurements in parts (a)-(d) were carried out on a single fiber amplifier, prior to and after the modifications.
+These upgrades serve to suppress many of the noise spurs measured in the fiber amplifier RIN.
+The effects can be as seen by comparing Fig.~\ref{fig:noises} (a) and (b), particularly in the region of approximately \unit{10}{kHz} Fourier frequency.
+The measurements in panels (a)-(d) were carried out on a single fiber amplifier, prior to and following the modifications.
 The initial and final noise spectra were verified to be consistent between amplifiers coming from the same manufacturing batch.
 The figure is based on fiber amplifiers from a relatively new batch, which, even in its unmodified configuration does not exhibit a large switching supply spur.
-This is not the case for certain older batches, where the spur is approximately 30 dB higher than the background.
+This is not the case for certain older batches, where the spur is approximately \unit{30}{dB} above the background.
 
@@
 However, since it is a function of fiber length and optical power, it can be minimized.
-To this end, we use custom-ordered amplifiers with a $0.5\,$m length output fiber, compared to the few meter standard lengths.
-In addition, we set the lowest pump diode current that yields enough power to perform imaging. 
-The rise of the noise floor as a function of the pump diode current can be seen in figure \ref{fig:noises}(a).
+To this end, we use custom-ordered amplifiers with a \unit{50}{cm} long output fiber, compared to the standard length of a few meters.
+In addition, we use the lowest pump diode current that yields enough power to perform imaging.
+The rise of the noise floor as a function of the pump diode current can be seen in Fig.~\ref{fig:noises}(a) at Fourier frequencies above \unit{100}{kHz}.
 
@@
 This is possible because the pump diodes are fixed directly to the water-cooling plate without additional temperature regulation.
-Adding a Peltier TEC and regulating to the optimal wavelength is possible, but technically challenging (requiring cooling power of $\approx100\,$W per each of the three pump diodes).
+Adding a thermoelectric cooler and regulating to the optimal wavelength is possible, but technically challenging (requiring cooling power of $\approx$\unit{100}{W} for each of the three pump diodes).
 We use a single, dedicated heat exchanger (TermoTek P21518970) to supply cooling water to an array of four fiber amplifiers.
-We tune the water temperature such that the average power supplied by the amplifiers supplying the $X$ and $Y$ lattices is optimized, while simultaneously keeping all reported amplifier temperatures below $\leq 30^\circ\mathrm{C}$\footnote{As recommended by a \textit{Nuferm} support engineer.}.
-Experimentally, we have found that more power can be gained by running the amplifiers at hotter temperature.
+We tune the water temperature such that the average power supplied by the amplifiers supplying the $X$ and $Y$ lattices is optimized, while simultaneously keeping all reported amplifier temperatures below \unit{30}{^\circ{}C}, as recommended by a Nufern support engineer.
+Experimentally, we have found that more power can be gained by running the amplifiers at even hotter temperatures.
 
@@
 
-In order to address these challenges, we use a carefully engineered the optical system shown in figure \ref{fig:optical_layout}.
+To address these challenges, we use a carefully engineered optical system shown in Fig.~\ref{fig:optical_layout}.
 This system collimates and polarizes the beam, controls its intensity and ensures good pointing stability.
 Due to the high laser power, fused silica glass and IBS coatings are used wherever possible.
-Since reflections pose a danger to the users and equipment, all undesired beams above $100\,$ mW are directed to water cooled beam-dumps (to prevent temperature gradients on the table) placed as far as practical from critical beam paths.
+Since reflections pose a danger to the users and equipment, all undesired beams above \unit{100}{mW} are directed to water cooled beam-dumps (to prevent temperature gradients on the table) placed as far as practical from critical beam paths.
 Weaker beams are dumped on uncooled diffusive beam catchers.
 
-The large-diameter fiber tip at the output of the fiber amplifier is mounted in a monolithic mount made from oxygen-depleted copper.
-The beam is collimated using an $f=20\,$mm fused-silica, air-spaced triplet collimator (Opto-Sigma HFTLSQ-15-20PF1).
-The polarization is set using an IBS coated thin-film plate polarizer (Precision photonics PO1056-FY), which has the added benefit of rejecting the undesired cladding modes of the fiber, which carry about $1\,$W of light.
+The large-diameter fiber tip at the output of the fiber amplifier is mounted in a monolithic mount made from copper.
+The beam is collimated using an $f=\unit{20}{mm}$ fused-silica, air-spaced triplet collimator (Opto-Sigma HFTLSQ-15-20PF1) angled with respect to and centered on the angle-cleaved fiber tip.
+The polarization is set using an IBS coated thin-film plate polarizer (Precision photonics PO1056-FY), which has the added benefit of rejecting the undesired cladding modes of the fiber, which carry about \unit{1}{W} of light.
 The fact that the lattice is retro-reflected, combined with the observation that optical isolation falls with applied optical power~\cite{Yoshida1999} means that two stages of optical isolators must be used.
-The optical isolators are based on $5$ mm diameter isolators from Thorlabs (IO-5-1064-VHP), with the default cube polarizers replaced by IBS coated thin-film plate polarizers. 
-The isolators are located approximately $1\,$m away from the ultracold atoms which are susceptible to  undesired stray fields.
+The optical isolators are based on \unit{5}{mm} aperture terbium gallium garnet (TGG) isolators (Thorlabs IO-5-1064-VHP), where we replaced the default polarizers (BK7 Brewster plates) by IBS-coated fused silica plate polarizers.
+The isolators are located approximately \unit{1}{m} away from the ultracold atoms which are susceptible to stray magnetic fields.
 To overcome this problem the isolators are enclosed in mu-metal shielding.
-Actuation of the power is performed after the optical isolators, meaning that the full fiber amplifier output is continually passed through them. 
-This is advantageous because there are no thermalization transients introduced during the experimental sequence.
+Actuation of the power is performed after the optical isolators, such that the full fiber amplifier output continuously passes through them, minimizing thermal transients during the experimental sequence.
 
@@
 \begin{enumerate}
-\item The lattice power must be continuously tunable from around $10$ $\mu$W to around $20$ W, corresponding to lattice depths in the approximate range of $10^-3$ to $2(10^3)\,E_R$. 
-\item The location of the minimum Gaussian beam waist must be accurately positioned to overlap the other lattices and dipole traps present in the experiment, and must remain there for the duration of the collection process (hours to days).
+\item The lattice power must be continuously tunable from around \unit{10}{\mu{}W} to around \unit{20}{W}, corresponding to lattice depths in the approximate range of $10^-3$ to $2 \times 10^3 E_R$, where $E_R$ is the geometric recoil energy corresponding to the lattice spacing~\cite{Blatt2015}.
+\item The location of the minimum Gaussian beam waist must be accurately positioned to overlap the other lattices and dipole traps present in the experiment, and must remain aligned for the duration of the data collection process (hours to days).
 \end{enumerate}
@@
 Two stages are used because the experiment typically operates in one of two regimes, which we term \textit{detection} and \textit{interaction}.
-In the interaction phase of the experiment, the lattice is relatively shallow ($\approx 100\,$mW, corresponding to depths of $\approx 10 E_R$, where $E_R$ is the geometric recoil of the lattice), allowing atoms to tunnel and interact with each other.
-In this regime, fine and potentially fast control is required.
-In the detection phase, the depth of the lattice is dramatically raised ($\approx 2000 E_R$), isolating atoms in their individual wells so that Raman sideband imaging can be performed~\cite{Parsons2015}.
-In the detection regime, the control need not be fast, and the passive stability of the Mephisto laser ensures that noise is low at relevant frequency scales ($\approx 2$ MHz).
-Thus, two control loops are utilized, a fast loop that uses an acousto-optic modulator to actuate the laser power at low powers, and a slow loop which uses a Berek compensator to actuate the laser in high power mode.
+In the interaction phase of the experiment, the lattice is relatively shallow ($\approx \unit{100}{mW}$, corresponding to depths of $\approx 10 E_R$), which allows atoms to tunnel and interact with each other.
+In this regime, precise and potentially fast control is required.
+In the detection phase, the depth of the lattice is dramatically raised (to $\approx 2000 E_R$), which isolates atoms in their individual wells so that Raman sideband imaging can be performed~\cite{Parsons2015}.
+In the detection regime, the control need not be fast, and the passive stability of the Mephisto laser ensures that noise is low at relevant frequency scales ($\approx\unit{2}{MHz}$ Fourier frequency).
+Thus, two control loops are used, a fast loop based on an acousto-optic modulator that controls the laser at low powers, and a slow loop which uses a Berek compensator to control the laser at high powers.
 
-After the isolation stage, we use the sequence of optical elements shown in figure \ref{fig:optical_layout}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs GVS002, or Camtech 8320K, depending on beam path) half-wave plate, and polarizer.
-The Berek compensator is a $z$-cut quartz plate coated to be anti-reflecting at $1064\,$nm. 
+After the isolation stage, we use the sequence of optical elements shown in Fig.~\ref{fig:optical_layout}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs GVS002, or Camtech 8320K, depending on the beam path) half-wave plate, and polarizer.
+The Berek compensator is a $z$-cut quartz plate anti-reflection-coated at \unit{1064}{nm}.
 By tilting the plate about its vertical axis by a few degrees, the extraordinary axis is mixed into the propagation of the beam, leading to  tilt-dependent birefringence that can be tuned from a zero-wave plate past a half-wave plate, represented by a retardation angle $\phi$.
-Combined with the subsequent polarization optics, rotation of the Berek compensator can vary the transmitted power with perfect contrast. 
-Figure \ref{fig:berek} shows the transmitted power as a function of retrardation angle $\phi$ and fast-axis angle $\theta$ of the waveplates surrounding the compensator.
+Combined with the subsequent polarization optics, rotation of the Berek compensator can vary the transmitted power with a contrast of $\sim$1000:1.
+Figure~\ref{fig:berek} shows the transmitted power as a function of retardation angle $\phi$ and fast-axis angle $\theta$ of the waveplates surrounding the compensator.
 \begin{figure}
   \begin{center}
-    \includegraphics{fig/berek_sim.pdf}
-    \caption{\textbf{Berek compensator} transmission as a function of the Berek tilt angle $\phi$ and waveplate tilt angles.}\label{fig:berek}
+    \includegraphics{Figure4.pdf}
+    \caption{\textbf{Berek compensator} transmission as a function of the Berek compensator's tilt angle $\phi$ and waveplate rotation angles $\theta$.}
+    \label{fig:berek}
   \end{center}
@@
 
-Full modulation contrast is achieved when $\theta=22.5^\circ$ to the rotation axis of the Berek compensator.
+Full modulation contrast is achieved when $\theta=\pi/8$ with respect to the rotation axis of the Berek compensator.
 This contrast can be reduced by varying $\theta$, to the limiting case where $\theta=0$, where the rotation of the Berek compensator does nothing, since the polarization of the light is parallel to the rotation axis of the quartz plate.
@@
 \end{figure}
-A key point, as seen in figure \ref{fig:berek}, is that if the waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
+A key point, as seen in Fig.~\ref{fig:berek}, is that if the waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
 The waveplates are detuned such that the maximum power needed in \textit{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator.
@@
 This feedback loop regulates the lattice between $1$ W of optical power and its maximum value (which depends on the amplifier, but is $\approx20$ W).
-The step response and corresponding Bode plots~\cite{Bechhoefer2005} are shown in figure \ref{fig:berek_step_response}.
+The step response and corresponding Bode plots~\cite{Bechhoefer2005} are shown in Fig.~\ref{fig:berek_step_response}.
 A polarization rotation by $2 \pi$ is produced by approximately $3^\circ$ of axial rotation of the quartz plate.
@@
 \end{figure}
-The feedback circuit is shown in figure \ref{fig:circuits}a.
-As seen in figure \ref{fig:optical_layout}, a pair of low noise photodiodes measures the optical power of the beam sampled with a weakly reflective optic (Thorlabs BSF10-C).
+The feedback circuit is shown in Fig.~\ref{fig:circuits}a.
+As seen in Fig.~\ref{fig:optical_layout}, a pair of low noise photodiodes measures the optical power of the beam sampled with a weakly reflective optic (Thorlabs BSF10-C).
 The beam sampler is wedged in such a way that the two reflections diverge from one another, allowing us to illuminate both photodiodes.
@@
 
-The spectrum and relative intensity noise of the PLL can be found in figure \ref{fig:pll}. 
+The spectrum and relative intensity noise of the PLL can be found in Fig.~\ref{fig:pll}.
 Vitally, the spectrum of the PLL exhibits phase noise comparable to (albeit worse than) that of a typical VCO, without the slow frequency drift characteristic to these devices.
@@
     \includegraphics{fig/pll.pdf}
-    \caption{\textbf{PLL performance} (a) The spectrum of the PLL, exhibiting phase noise of better than $-90$ dBc $100$ kHz away from the carrier.
+    \caption{\textbf{PLL performance} (a) The spectrum of the PLL, exhibiting phase noise of better than $-90$ dBc/Hz at $100$~kHz away from the carrier.
 (b) The RIN of the local oscillator based on the PLL.
@@
 The chosen photodiode (Hamamatsu G8370-01) is an InGaS based, small-area, low-noise design with a high efficiency at 1064 nm.
-Prior to use, the protective window is removed from the photodiode to prevent interference effects, as seen in figure \ref{fig:cut_pd}.
+Prior to use, the protective window is removed from the photodiode to prevent interference effects, as seen in Fig.~\ref{fig:cut_pd}.
 Further, to reduce the capacitance of the system, a reverse bias of $6.9\,$V is applied to the photodiode by a temperature-stabilized voltage reference (Linear Technology LM399).
-The trans-impedance circuit is shown in figure \ref{fig:circuits}. 
+The trans-impedance circuit is shown in Fig.~\ref{fig:circuits}.
 It converts the photo-current supplied by the photodiode to a voltage signal using the low noise Texas Instruments OPA843 op-amp.
@@
 By definition, an ideal control loop would translate any noise on the analog signal from the DAC to the laser light, meaning that a poorly designed DAC would inherently limit the lattice laser performance.
-The noise on the DAC, when it is programmed to output a constant voltage is shown in figure \ref{fig:da_rin}, and is found to be roughly constant at a level of $-150$ dBc - more than acceptable.
+The noise on the DAC, when it is programmed to output a constant voltage is shown in Fig.~\ref{fig:da_rin}, and is found to be roughly constant at a level of $-150$ dBc - more than acceptable.
 When the state of the DAC is changed, such as during a ramp, this noise level may be higher, due to the so-called ``glitch'' energy, as seen in the figure.
@@
 The connection between the actuation and monitoring mechanisms of the feedback system is the loop filter, which compares the \textit{set-point} signal, $v_s(t)$, supplied by the experimental control system and the monitoring signals $v_m(t)$, to adjust the actuation accordingly.
-We use a simple, purely integrating design based in three stages, as seen in figure \ref{fig:circuits}, based on TI's OPA211 op-amp.
+We use a simple, purely integrating design based in three stages, as seen in Fig.~\ref{fig:circuits}, based on TI's OPA211 op-amp.
 The first stage computes and amplifies an error signal, $e(t)=v_m(t)-v_s(t)$, which is integrated by the second stage.
@@
 Naturally, the voltage drop over the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode ($3.3\,$V).
-Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in figure \ref{fig:bandwidth}.
+Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in Fig.~\ref{fig:bandwidth}.
 Were it not for the linearization, the gain of the mixer would change by a factor of $10$ over a dynamic range spanning two orders of magnitude.
-Another function of the last stage is to clamp the voltage to be strictly $>0$, in order to prevent an unstable positive feedback behavior, which is done using diode clamp on the output arm~\cite{Horowitz2015}.
+Another function of the last stage is to clamp the voltage to be strictly $>0$, to prevent an unstable positive feedback behavior, which is done using diode clamp on the output arm~\cite{Horowitz2015}.
 Last of all, since the mixer is a current driven device, the last stage of the feedback loop uses TI's OPA627 op-amp which is able to supply tens of mA of current at an output impedance of $50\,\Omega$.
@@
     \includegraphics{fig/low_pass_filters.pdf}
-    \caption{\textbf{Laser noise of the lattice system with and without additional low pass filters} (a) Closed loop laser made a fiber amplifier (different than the one in figure \ref{fig:noises}.
+    \caption{\textbf{Laser noise of the lattice system with and without additional low pass filters} (a) Closed loop laser made a fiber amplifier (different than the one in figure~\ref{fig:noises}.
 (b) Noise on the same system as (a), but with extra filters.}\label{fig:low_pass_noises}
@@
 Although it is an essential part of the system, the loop filter is also one of its major limitations.
-Figure \ref{fig:noises} shows the noise performance of the output of the fiber amplifiers in open loop as compared to the noise in closed loop.
+Figure~\ref{fig:noises} shows the noise performance of the output of the fiber amplifiers in open loop as compared to the noise in closed loop.
 Although noise near DC is lowered (as expected from a closed loop system), noise outside the loop bandwidth is increased in the range of $10$ to $450$ kHz as seen in subfigures (c) and (d).
@@
 When this was determined to be a problem, we decided that a bandwidth of higher than $10\,$ kHz was not required in the foreseeable future.
-As a result, we added a first order low pass with a $3$ dB frequency of $10$ kHz leading to the improvement shown in figure \ref{fig:low_pass_noises} (the fiber amplifier used to take this data was different from the one used for \ref{fig:noises}, although their performance is comparable.
+As a result, we added a first order low pass with a $3$ dB frequency of $10$ kHz leading to the improvement shown in Fig.~\ref{fig:low_pass_noises} (the fiber amplifier used to take this data was different from the one used for~\ref{fig:noises}, although their performance is comparable.
 
@@
 We focus the lattice to a $70-90$\,$\mu$m waist at the position of the atoms.
-In order to verify that the waist is positioned correctly, we use a temporary mirror to redirect the beam away from the glass cell and onto a camera positioned in the plane corresponding to the position of the atoms.
+To verify that the waist is positioned correctly, we use a temporary mirror to redirect the beam away from the glass cell and onto a camera positioned in the plane corresponding to the position of the atoms.
 %The resulting beam at the atoms has an $m^2\leq1.4$.
@@
 This is ensured via careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately $3\,$cm from the atoms~\cite{Huber2014}.
-We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours, as seen in figure \ref{fig:averaged_mott}.
+We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours, as seen in Fig.~\ref{fig:averaged_mott}.
 
@@
 The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement.
-In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in \cite{Mazurenko2016} or \cite{Choi2016}), drift or fluctuation of the lattice position is important.
+In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in~\cite{Mazurenko2016} or~\cite{Choi2016}), drift or fluctuation of the lattice position is important.
 
@@
 Changing external conditions can contaminate large datasets if the prepared state sensitively depends on laser pointing.
-In order to watch for this contamination, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
+To watch for this contamination, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
 This monitoring system could potentially allow us to eliminate (via post-selection) experimental realizations when the system was in an undesired state.
@@
 First, we characterized the passive stability of the optical axis along the transverse $x_t$ and longitudinal $x_l$ directions.
-Figure \ref{fig:stability} a shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$($0.98(4)$) sites along the $x_t$($x_l$) directions.
+Figure~\ref{fig:stability} a shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$($0.98(4)$) sites along the $x_t$($x_l$) directions.
 The difference between displacements along is a geometric effect consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
@@
 If the trap followed a random walk with these step sizes, the experiment would be in trouble, since after only $100$ experimental shots, the trap would move by more than $10$ lattice sites.
-The situation is more fortunate, however, since subsequent steps are correlated, as shown in figure \ref{fig:stability} (b).
+The situation is more fortunate, however, since subsequent steps are correlated, as shown in Fig.~\ref{fig:stability} (b).
 Once this correlation is taken into account, we estimate a drift of $8(1)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the transverse direction and $12(2)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the axial direction, compared to a beam waist of approximately $80$ $\mu$m ($\approx 140$ sites).
@@
 In a real experiment, we cannot directly measure the position of the atoms and must rely on the measurement performed by the camera, related by an affine transformation.
-To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in figure \ref{fig:stability} (c).
+To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in Fig.~\ref{fig:stability} (c).
 
@@
 The large blocks were treated as ``masked'' data, which we tried to predict, while the small blocks were treated as ``updating'' events used to update the calibration offsets.
-The results are shown in figure \ref{fig:stability} (d-f), showing a large degree of tracking between the predicted positions and measured position - the average displacement between the predicted position and measured position was $0.7\,$lattice sites.
+The results are shown in Fig.~\ref{fig:stability} (d-f), showing a large degree of tracking between the predicted positions and measured position - the average displacement between the predicted position and measured position was $0.7\,$lattice sites.
 
@@
 As discussed in the supplementary material of~\cite{Parsons2016, Greif2016}, the Fourier transform of an atomic distribution contains distinct peaks corresponding to the lattice structure, and these peaks can be used to extract the phase, relative angle, and spacing of the lattices.
-For this reason, we recorded a long-term measurement spanning almost one year in order to learn how these parameters change over time, see Fig.~\ref{fig:long_term_stability}.
+For this reason, we recorded a long-term measurement spanning almost one year to learn how these parameters change over time, see Fig.~\ref{fig:long_term_stability}.
 Several interesting features can be seen from the observed behavior.
@@
 To improve performance, the system can be upgraded in a variety of ways.
-For example, the \textit{Nufern} fiber amplifiers can be replaced with a lower noise model.
+For example, the Nufern fiber amplifiers can be replaced with a lower noise model.
 Or the analog feedback loop can be replaced by a low-noise digital version.
@@
 
-\bibliography{LatticeOpticsV4}
+\bibliography{LatticeOpticsV5}
 

### 2018-06-12 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Cleaned up figures

@@
     \includegraphics{Figure4.pdf}
-    \caption{\textbf{Berek compensator} transmission as a function of the Berek compensator's tilt angle $\phi$ and waveplate rotation angles $\theta$.}
+    \caption{\textbf{Berek compensator} transmission as a function of the Berek compensator's retardation angle $\phi$ and waveplate rotation angles $\theta$.}
     \label{fig:berek}
@@
   \begin{center}
-    \includegraphics[width=\columnwidth]{fig/step_response.pdf}
+    \includegraphics[width=\columnwidth]{Figure5.pdf}
     \caption{\textbf{Berek compensator based feedback loop}.
@@
   \begin{center}
-    \includegraphics{fig/circuits.pdf}
+    \includegraphics{Figure6.pdf}
     \caption{\textbf{Feedback circuits.} (a) The reverse-biased photodiode.
@@
   \begin{center}
-    \includegraphics{fig/pll.pdf}
+    \includegraphics{Figure7.pdf}
     \caption{\textbf{PLL performance} (a) The spectrum of the PLL, exhibiting phase noise of better than $-90$ dBc/Hz at $100$~kHz away from the carrier.
@@
   \begin{center}
-    \includegraphics[width=\columnwidth]{fig/cut_photodiode.jpg}
+    \includegraphics[width=\columnwidth]{Figure8.jpg}
     \caption{\textbf{Photodiode photo} showing that the ``can'' of the photodiode has been cut, to prevent etalon-like behavior.}\label{fig:cut_pd}
@@
   \begin{center}
-    \includegraphics{fig/da_rin_scan.pdf}
+    \includegraphics{Figure9.pdf}
     \caption{\textbf{Relative intensity noise of the digital to analog converter} at a fixed output voltage and while changing values.
@@
   \begin{center}
-    \includegraphics{fig/low_power_bandwidths.pdf}
+    \includegraphics{Figure10.pdf}
     \caption{\textbf{Loop bandwidth dependence on the set-point}. (a) shows the $3$ dB and $\pi$ phase shift points for the $X$ lattice. (b) shows the same for the $Y$ lattice.}\label{fig:bandwidth}
@@
   \begin{center}
-    \includegraphics{fig/low_pass_filters.pdf}
+    \includegraphics{Figure11.pdf}
     \caption{\textbf{Laser noise of the lattice system with and without additional low pass filters} (a) Closed loop laser made a fiber amplifier (different than the one in figure~\ref{fig:noises}.
@@
   \begin{center}
-    \includegraphics{fig/AveragedMI.pdf}
+    \includegraphics{Figure12.pdf}
     \caption{\textbf{Averaged images of Mott insulators}.
@@
   \begin{center}
-    \includegraphics{fig/pointing_figure.pdf}
+    \includegraphics{Figure13.pdf}
     \caption{\textbf{Short term positional stability.} (a) A histogram of shot-to-shot step sizes along the transverse and longitudinal directions, with a Gaussian fit.
@@
 \begin{center}
-    \includegraphics[width=\columnwidth]{fig/lattice_stability.pdf}
+    \includegraphics[width=\columnwidth]{Figure14.pdf}
     \caption{\textbf{Long term stability over approximately nine months.} The lattice spacing $|\mathrm{v}_x|$ and $|\mathrm{v}_y|$ and the lattice angles $\theta_x$ and $\theta_y$ along the two lattice axes $x$ and $y$ are shown over the duration of almost 1 year.

### 2018-06-12 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Fixed and updated references

@@
 Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
-The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over individual atoms at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian~\cite{Hubbard1963}.
+The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2017} has enabled studies that exhibit unprecedented control over individual atoms at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian~\cite{Hubbard1963}.
 However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
@@
 This Berek compensator based feedback loop is used to vary the beam intensity at relatively high power.
-(a) Shows the small signal impulse response and (b-c) show the corresponding Bode plots.}\label{fig:berek_step_response}
+(a) Shows the small signal impulse response and (b-c) show the corresponding Bode plots of the transfer function $G$.}\label{fig:berek_step_response}
   \end{center}
@@
 This is the case because within relevant frequency ranges, the AOM can be coarsely approximated by a pure time delay process (with delay given by the RF travel time across the crystal $\approx 1 \mu\mathrm{s}$).
-In this scenario, the $P$ term must be small to avoid instability at the $\pi$ phase shift point, and a pure $I$ controller is optimal~\cite{Skogestad2001}.
+In this scenario, the $P$ term must be small to avoid instability at the $\pi$ phase shift point, and a pure $I$ controller is optimal~\cite{Skogestad2003}.
 For debugging purposes, the loop filter features buffered photodiode monitor and error signal monitor outputs.

### 2018-06-13 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Many changes to abstract, text, fixes to figures

@@
 \newcommand\unit[2]{\ensuremath{#1~\mathrm{{#2}}}}
-
-\newcommand\Ket[1]{\ensuremath{|{#1}\rangle}}
-\newcommand\Bra[1]{\ensuremath{\langle{#1}|}}
-
-\newcommand\Isotope[2]{\ensuremath{^{#1}\mathrm{#2}}}
-\newcommand\Li{\Isotope{6}{Li}}
-
-\renewcommand{\vec}[1]{\ensuremath{\bm{#1}}}
-
-\newcommand\NA{\ensuremath{\mathrm{NA}}}
 \newcommand\FIXME{{\color{red}\ensuremath{\mathrm{FIXME}}}}
@@
 \altaffiliation{
-  Present address: FIXME}
+  Present address: \FIXME{}}
 \author{S. Blatt}
@@
 \altaffiliation{
-  Present address: FIXME TOO}
+  Present address: \FIXME{} TOO}
 \author{C. S. Chiu}
@@
 \begin{abstract}
- We describe the design of a stable high power \unit{1064}{nm} laser system for practical use in optical lattice experiments.
-The system is based on a low noise laser amplified by an array of four heavily modified, high-power fiber amplifiers.
-The beam intensity is stabilized with a nonlinear feedback loop.
-The position of the produced optical lattice is monitored in real time and its stability is characterized.
+  We describe the design and implementation of a stable high-power \unit{1064}{nm} laser system for use in experiments with ultracold atoms trapped in optical lattices.
+The system is based on a low-noise laser amplified by an array of four heavily modified, high-power fiber amplifiers.
+The beam intensity is stabilized and controlled with a nonlinear feedback loop.
+Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1\% of the lattice spacing and a long-term (six month) relative stability of 0.5\% RMS of the lattice spacing.
 \end{abstract}
@@
 
-Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
-The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2017} has enabled studies that exhibit unprecedented control over individual atoms at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian~\cite{Hubbard1963}.
+Optical lattices holding arrays of ultracold atoms have become a powerful experimental platform for quantum simulations~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
+The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2017} has enabled studies with unprecedented control over individual atoms in many-body systems governed by the Hubbard Hamiltonian~\cite{Hubbard1963}, resulting in extremely low energy scales~\cite{Mazurenko2017}.
 However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
-For example, heating due to the intensity noise cannot be allowed to approach the longest thermalization timescales, lest the system fail to thermalize~\cite{Savard1997}.
-Even if the system thermalizes, heating rates can limit the interrogation time available to probe a low-temperature state.
-Similarly, experiments that rely on a small number of atoms held by multiple traps place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.
+Even if the systems thermalize, heating rates can limit the interrogation time available to probe low-temperature states~\cite{Blatt2015}.
+In particular, experiments that rely on a small number of atoms held by multiple traps~\cite{Preiss2015, Choi2016, Mazurenko2017} place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.
 
-In this work we discuss major improvements to our high power optical lattice system~\cite{Blatt2015} and show levels of intensity noise below \unit{-120}{dBc/Hz} between \unit{1}{kHz} and \unit{3}{MHz} Fourier frequency.
-The stability of the lattice position is below the single site level (over a few hours) and the stability of the harmonic confinement is at the few site level (over nine months).
+In this work we discuss major improvements to our high power optical lattice system~\cite{Blatt2015} and show levels of intensity noise below \unit{-115}{dBc/Hz} between \unit{1}{kHz} and \unit{3}{MHz} Fourier frequency.
+In addition to the intensity stability, we demonstrate a short-term (shot-to-shot) stability of the lattice position at 1\% of the optical lattice spacing, and a long-term (six month) relative stability of 0.5\% RMS of the lattice spacing itself.
 
@@
 
-The architecture of the system is shown in Fig.~\ref{fig:high_level} and is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Blatt2015,Parsons2016}).
+The architecture of the system, shown in Fig.~\ref{fig:high_level}, is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Blatt2015,Parsons2016}).
 These amplifiers generate enough light to perform site resolved imaging~\cite{Parsons2015}, but also substantially increase the level of intensity and pointing noise.
@@
 The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately \unit{2}{W} of \unit{1064}{nm} light.
-This commercial laser utilizes a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability.
+This commercial laser uses a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability.
 This source is split and coupled into four single-mode, polarization-maintaining fibers (Thorlabs PM980-XP), each connected to the input of a fiber amplifier.
@@
     \includegraphics{Figure2.pdf}
-    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed, as well as an independent Mephisto MOPA 55W (not used for the optical lattice presented in this manuscript).
-(b) Shows the open (OL) and closed (CL) loop behavior of the high power feedback loop.
-(c) Shows open loop behavior of the low power feedback loop after making the modifications.
-(d) Closed loop behavior of the loop system without additional filtering, measured on the same setup as panel (c).}\label{fig:noises}
+    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified and free-running Nufern fiber amplifiers and the Mephisto seed, as well as an independent Mephisto MOPA 55W (not used for the optical lattice presented in this manuscript).
+(b) Shows the open-loop and closed-loop behavior of the high-power feedback loop using the  modified fiber amplifiers, as described in the main text.
+(c) Shows the open-loop behavior of the low-power feedback loop using the modified fiber amplifiers, including an additional low-pass filtering stage to limit the loop bandwidth.
+(d) Closed-loop behavior of the low-power feedback loop without additional low-pass filtering, measured on the same setup as panel (c).}\label{fig:noises}
   \end{center}
@@
 \subsection{Fiber amplifier system}
-Quantum gas microscopy of \Li{} requires single site trap frequencies of approximately \unit{1}{MHz}~\cite{Parsons2015} to be in the Lamb-Dicke regime necessary for Raman sideband cooling.
+Quantum gas microscopy of Li$^6$ requires single site trap frequencies of approximately \unit{1}{MHz}~\cite{Parsons2015} to be in the Lamb-Dicke regime necessary for Raman sideband cooling.
 Such trap frequencies may only be attained using tightly focused, high-power beams.
-In practical terms, this requires approximately $30\,$W per lattice axis, which we attain using Nufern fiber amplifiers (NuAmp SUB1174-34).
-These amplifiers can amplify $150\,$mW of seed light to up to approximately $45\,$W.
-They use a length of doped fiber pumped with $808\,$nm light from fiber coupled diode sources to amplify $1064\,$nm light.
-The amplification is performed using a two stage design, where the stages are controlled and powered using separate power supplies and electronics.
+In practical terms, this requires approximately \unit{30}{W} per lattice axis, which we attain using Yb-doped fiber amplifiers (Nufern NuAmp SUB1174-34).
+These amplifiers can amplify \unit{150}{mW} of seed light to up to approximately \unit{45}{W}.
+They use a length of doped fiber pumped with \unit{808}{nm} light from fiber coupled diode sources to amplify the \unit{1064}{nm} seed light.
+The amplification is performed using a two-stage design, where the stages are controlled and powered using separate power supplies and electronics.
 
@@
     \includegraphics{Figure3.pdf}
-    \caption{\textbf{Optical layout} of the optical lattice system for beam shaping and modulation.}
-    \label{fig:optical_layout}
+    \caption{\textbf{Optical layout} of the optical lattice system for beam shaping and modulation.}\label{fig:optical_layout}
   \end{center}
@@
 Further sources of technical noise arise from the design of the amplifier.
-There are two power supplies in the fiber amplifier: (1) a general purpose power supply (PSU) for the control electronics and the first, low-power amplification stage and (2) a high-power supply for the second, high-power stage.
-Despite the presence of a water-cooled cold-plate for the gain fiber and pump diodes, the high power PSU is air cooled by an internal fan with variable frequency.
+There are two power supplies in the fiber amplifier: (1) a general purpose power supply for the control electronics and the first, low-power amplification stage and (2) a high-power supply for the second, high-power stage.
+Despite the presence of a water-cooled cold-plate for the gain fiber and pump diodes, the high power supply is air cooled by an internal fan with variable frequency.
 This fan adds noise at acoustic frequencies and degrades pointing stability by increasing vibrations on the output fiber tip.
-To reduce acoustic coupling and reduce switching power supply noise, both power supplies were removed from the fiber amplifier chassis, and the low-power supply was replaced by a linear PSU (Acopian A24MT350M).
-Further, a high current low-pass filter (MPE DS26387) was added to the high-power PSU (Lumina LDD-600-60-10-5VP/M).
+To reduce acoustic coupling and reduce switching power supply noise, both power supplies were removed from the fiber amplifier chassis, and the low-power supply was replaced by a linear power supply (Acopian A24MT350M).
+Further, a high current low-pass filter (MPE DS26387) was added to the high-power supply (Lumina LDD-600-60-10-5VP/M).
 
 These upgrades serve to suppress many of the noise spurs measured in the fiber amplifier RIN.
-The effects can be as seen by comparing Fig.~\ref{fig:noises} (a) and (b), particularly in the region of approximately \unit{10}{kHz} Fourier frequency.
+The effects can be seen when comparing Fig.~\ref{fig:noises}(a) and (b), particularly in the region of approximately \unit{10}{kHz} Fourier frequency.
 The measurements in panels (a)-(d) were carried out on a single fiber amplifier, prior to and following the modifications.
 The initial and final noise spectra were verified to be consistent between amplifiers coming from the same manufacturing batch.
-The figure is based on fiber amplifiers from a relatively new batch, which, even in its unmodified configuration does not exhibit a large switching supply spur.
+The figure is based on fiber amplifiers from a relatively new batch, which even in its unmodified configuration does not exhibit a large switching supply spur.
 This is not the case for certain older batches, where the spur is approximately \unit{30}{dB} above the background.
@@
 The SBS noise is fundamental to the fiber amplifier architecture and cannot be entirely avoided.
-However, since it is a function of fiber length and optical power, it can be minimized.
+However, since it is a function of fiber length and optical power~\cite{Agrawal2013}, it can be minimized.
 To this end, we use custom-ordered amplifiers with a \unit{50}{cm} long output fiber, compared to the standard length of a few meters.
@@
 
-The operation of the Nufern fiber amplifiers can be further optimized by finely controlling the cooling water.
+The operation of the Nufern fiber amplifiers can be further optimized by finely controlling the cooling water temperature.
 The water temperature tunes the wavelength of the light supplied by the diodes that optically pump the gain fiber.
@@
 The fact that the lattice is retro-reflected, combined with the observation that optical isolation falls with applied optical power~\cite{Yoshida1999} means that two stages of optical isolators must be used.
-The optical isolators are based on \unit{5}{mm} aperture terbium gallium garnet (TGG) isolators (Thorlabs IO-5-1064-VHP), where we replaced the default polarizers (BK7 Brewster plates) by IBS-coated fused silica plate polarizers.
+The optical isolators are based on \unit{5}{mm} aperture Tb$_3$Ga$_5$O$_12$ (TGG) isolators (Thorlabs IO-5-1064-VHP), where we replaced the default polarizers (BK7 Brewster plates) by IBS-coated fused silica plate polarizers.
 The isolators are located approximately \unit{1}{m} away from the ultracold atoms which are susceptible to stray magnetic fields.
@@
 To satisfy the first of these requirements, a two-stage feedback system is implemented.
-Two stages are used because the experiment typically operates in one of two regimes, which we term \textit{detection} and \textit{interaction}.
+Two stages are used because the experiment typically operates in one of two regimes, which we term \emph{detection} and \emph{interaction}.
 In the interaction phase of the experiment, the lattice is relatively shallow ($\approx \unit{100}{mW}$, corresponding to depths of $\approx 10 E_R$), which allows atoms to tunnel and interact with each other.
@@
     \includegraphics{Figure4.pdf}
-    \caption{\textbf{Berek compensator} transmission as a function of the Berek compensator's retardation angle $\phi$ and waveplate rotation angles $\theta$.}
-    \label{fig:berek}
+    \caption{\textbf{Berek compensator} transmission as a function of the Berek compensator's retardation angle $\phi$ and waveplate rotation angles $\theta$.}\label{fig:berek}
   \end{center}
@@
 A key point, as seen in Fig.~\ref{fig:berek}, is that if the waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
-The waveplates are detuned such that the maximum power needed in \textit{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator.
+The waveplates are detuned such that the maximum power needed in \emph{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator.
 Naturally, rotation of a parallel plate in the beam path induces a shift of the beam, but this is acceptable because the Berek compensator is only active during the imaging phase of the experiment, when the position of the underlying harmonic trap is largely irrelevant.
@@
 This system functions as the actuator arm of a digital feedback loop, where the power of the beam is measured using a low noise photodiode.
-This feedback loop regulates the lattice between $1$ W of optical power and its maximum value (which depends on the amplifier, but is $\approx20$ W).
+This feedback loop regulates the lattice between \unit{1}{W} of optical power and its maximum value (which depends on the amplifier, but is $\approx$\unit{20}{W}).
 The step response and corresponding Bode plots~\cite{Bechhoefer2005} are shown in Fig.~\ref{fig:berek_step_response}.
@@
 Since we never need to rotate the plate outside this range, the position is constrained to this window in software.
-Since two feedback loops are present in the system (the second one detailed in the next section), care must be taken so that they do not function simultaneously.
-To accomplish this, the low power loop is always manually railed to its high extreme when the high power loop is active, and the digital high power loop is disabled when the low power loop is active.
 
-\subsection{Low power feedback}
-The high power feedback used in the \textit{imaging} phase of the experiment is exceedingly robust because the heating rate from scattered resonant imaging light far exceeds any technical heating from the loop.
+Because two feedback loops are present in the system (the second one detailed in the next section), care must be taken so that they do not function simultaneously.
+To accomplish this, the low-power loop is always manually railed to its high extreme when the high-power loop is active, and the digital high-power loop is disabled when the low-power loop is active.
+
+\subsection{Low-power feedback}
+The high-power feedback used in the \emph{imaging} phase of the experiment is exceedingly robust because the heating rate from scattered resonant imaging light far exceeds any technical heating from the loop~\cite{Blatt2015}.
 Even if the loop was exceedingly noisy, the heating would be entirely compensated by the simultaneous Raman cooling~\cite{Parsons2015}.
 
-In contrast, the low power loop that controls the lattice laser during the \textit{interaction} phase of the experiment is critically important:
+In contrast, the low-power loop that controls the lattice laser during the \emph{interaction} phase of the experiment is critically important:
 \begin{enumerate}
-  \item Its RIN can limit the system temperature.
+  \item Its effect on the RIN can limit the system temperature.
   \item It can affect the pointing.
-  \item It must have closed loop bandwidths of $\geq1\mathrm{\,kHz}$, and open loop modulation bandwidths $\geq 100\mathrm{\,kHz}$.
+  \item It must have closed-loop bandwidths of $\geq\unit{1}{kHz}$, and open-loop modulation bandwidths $\geq \unit{100}{kHz}$.
 \end{enumerate}
-To this end, we use an all-custom loop based on a TeO$_2$ AOM (Gooch \& Housego AOMO 3080-198), where the power of the RF supplied to the AOM is used to actuate the fast, low power feedback loop.
+To this end, we use an all-custom loop based on a TeO$_2$ AOM (Gooch \& Housego AOMO 3080-198), where the power of the RF supplied to the AOM is used to actuate the fast, low-power feedback loop.
 The AOM was chosen for its low thermal lensing and easily-accessible RF powers.
-It is mounted on a custom-built, monolithic, water-cooled flexure mount that allows optimization of the AOM efficiency, that has been found to remain stable over years of operation.
+It is mounted on a monolithic, water-cooled flexure mount that allows optimization of the AOM efficiency, while remaining stable over years of operation.
 
@@
 \end{figure}
-The feedback circuit is shown in Fig.~\ref{fig:circuits}a.
-As seen in Fig.~\ref{fig:optical_layout}, a pair of low noise photodiodes measures the optical power of the beam sampled with a weakly reflective optic (Thorlabs BSF10-C).
+The feedback circuit is shown in Fig.~\ref{fig:circuits}(c).
+As seen in Fig.~\ref{fig:optical_layout}, a pair of low-noise photodiodes [Fig.~\ref{fig:circuits}(a)] measures the optical power of the beam sampled with a weakly reflective optic (Thorlabs BSF10-C).
 The beam sampler is wedged in such a way that the two reflections diverge from one another, allowing us to illuminate both photodiodes.
-One of the sampled beams is attenuated by an additional factor of $20\times$ by reflection off of an uncoated fused silica glass plate, such that the dynamic range of its photodiode covers $0-20$ W of the beam directed at the atoms, and controls the Berek compensator based, high-power feedback loop.
-The other beam is not attenuated, save by the beam sampler, and its dynamic range covers $0-1$ W.
-To prevent damage to the low power photodiode when the system is at its highest powers, a shutter (Stanford Research Systems SR475) blocks the light when the high power loop is in use.
-The low power photodiode passes its signal $V_{\mathrm{pd}}$ to a loop filter circuit, which compares it to the control system's set-point, generated by digital to analog converter.
-The loop filter's output controls the IF port of a microwave mixer (Minicircuits ZFM-2-S+), effectively modulating the RF power supplied by a low noise phase-locked loop (PLL).
+One of the sampled beams is attenuated by an additional factor of 20 by reflection off of an uncoated fused silica glass plate, such that the dynamic range of its photodiode covers \unit{0-20}{W} of the beam directed at the atoms, and controls the Berek-compensator-based, high-power feedback loop.
+The other beam is not attenuated, save by the beam sampler, and its dynamic range covers \unit{0-1}{W}.
+To prevent damage to the low-power photodiode when the system is at its highest powers, a shutter (Stanford Research Systems SR475) blocks the light when the high-power loop is in use.
+The low-power photodiode passes its signal $V_{\mathrm{pd}}$ to a loop filter circuit [Fig.~\ref{fig:circuits}(c)], which compares it to the control system's set-point, generated by a digital-to-analog converter.
+The loop filter's output controls the IF port of a microwave mixer [Minicircuits ZFM-2-S+, see Fig.~\ref{fig:circuits}(d)], to modulate the RF power supplied by a low-noise phase-locked loop [PLL, see Fig.~\ref{fig:circuits}(b)].
 The resulting RF signal is then amplified and sent to the AOM.
@@
 \subsubsection{Phase-locked loop (PLL)}
-The local oscillator (LO) RF source is a custom-built printed circuit board (PCB) implementing a phase locked loop (PLL) based on the ADF4002 IC and Crystek's CVCO55CL-0060-0110 voltage controlled oscillator (VCO), preamplified with a low noise amplifier (Minicircuits PSA4-5043+).
-To ensure frequency stability (which translates directly into beam pointing of the laser), the PLL is locked to the $10$ MHz clock distributed around the lab.
-In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total isolation exceeding $90$ dB.
+The local oscillator (LO) RF source is a custom-built printed circuit board (PCB), schematically shown in Fig.~\ref{fig:circuits}(b), that implements a phase locked loop (PLL) based on the ADF4002 IC and a low-phase-noise voltage-controlled oscillator (VCO, Crystek CVCO55CL-0060-0110), preamplified with a low-noise amplifier (Minicircuits PSA4-5043+).
+To ensure frequency stability (which translates directly into beam pointing of the laser), the PLL is locked to the \unit{10}{MHz} frequency reference distributed around the lab.
+In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total isolation exceeding \unit{90}{dB}.
 
+We need to maintain the relatively low phase-noise characteristics of the VCO to prevent phase- to amplitude-noise conversion in the AOM, which partially downconverts the VCO phase noise to RIN at acoustic frequencies.
 The spectrum and relative intensity noise of the PLL can be found in Fig.~\ref{fig:pll}.
-Vitally, the spectrum of the PLL exhibits phase noise comparable to (albeit worse than) that of a typical VCO, without the slow frequency drift characteristic to these devices.
+Vitally, the spectrum of the PLL exhibits phase noise comparable to that of a typical VCO, without the slow frequency drift characteristic to these devices.
 Elimination of the carrier drift is worth the added phase noise, however, because any drift of the frequency affects the pointing of the laser beam passing through the AOM, which would misalign the optical lattice.
@@
     \includegraphics[width=\columnwidth]{Figure8.jpg}
-    \caption{\textbf{Photodiode photo} showing that the ``can'' of the photodiode has been cut, to prevent etalon-like behavior.}\label{fig:cut_pd}
+    \caption{\textbf{Photodiode photo} showing that the ``can'' of the photodiode has been cut, to suppress etalon-like behavior between the cover glass and the sensor.}\label{fig:cut_pd}
   \end{center}
@@
 Fast, low-noise photodiodes are required both to provide the monitoring arm of the feedback loop and to characterize the RIN of the system.
-An ideal device would have a bandwidth up to approximately 3 MHz (since trap frequencies in the system are $\approx1.5\,$MHz), with a noise floor below approximately -150 dBc over that range.
-To approach these specifications, we use a custom designed PCB that implements a simple trans-impedance amplifier~\cite{Graeme1995} in a convenient physical package, providing a bandwidths in the 0.1-10 MHz range, depending on the trans-impedance gain set by a resistor.
-The photodiode can be safely operated up to incident powers of approximately 10 mW, which sets a -164 dBc/Hz shot noise limit on the RIN that can be detected.
-In practice, we typically operate the photodiodes with $\approx 1-5$ mW of incident power.
-A photodiode with a bandwidth (BW) of 6 MHz is used to characterize the system, while photodiodes with a bandwidth of 330 kHz (and correspondingly higher gain) are used to perform the feedback.
+An ideal device would have a bandwidth up to approximately \unit{3}{MHz} (since trap frequencies in the system are \unit{1.5}{MHz}), with a noise floor below approximately \unit{-150}{dBc/Hz} over that range~\cite{Blatt2015}.
+To approach these specifications, we use a custom-designed PCB that implements a simple transimpedance amplifier~\cite{Graeme1995} in a convenient physical package, providing a bandwidths in the \unit{0.1-10}{MHz} range, depending on the transimpedance gain set by a resistor.
+The photodiode can be safely operated up to incident powers of approximately \unit{10}{mW}, which sets a \unit{-164}{dBc/Hz} shot noise limit on the RIN that can be detected.
+In practice, we typically operate the photodiodes with $\approx$\unit{1-5}{mW} of incident power.
+A photodiode with a bandwidth (BW) of \unit{6}{MHz} is used to characterize the system, while photodiodes with a bandwidth of \unit{330}{kHz} (and correspondingly higher gain) are used to perform the feedback.
 
-The chosen photodiode (Hamamatsu G8370-01) is an InGaS based, small-area, low-noise design with a high efficiency at 1064 nm.
+The chosen photodiode (Hamamatsu G8370-01) is an InGaS based, small-area, low-noise design with a high efficiency and low thermal sensitivity at \unit{1064}{nm}.
 Prior to use, the protective window is removed from the photodiode to prevent interference effects, as seen in Fig.~\ref{fig:cut_pd}.
-Further, to reduce the capacitance of the system, a reverse bias of $6.9\,$V is applied to the photodiode by a temperature-stabilized voltage reference (Linear Technology LM399).
-The trans-impedance circuit is shown in Fig.~\ref{fig:circuits}.
-It converts the photo-current supplied by the photodiode to a voltage signal using the low noise Texas Instruments OPA843 op-amp.
+Further, to reduce the capacitance of the system, a reverse bias of \unit{6.9}{V} is applied to the photodiode by a temperature-stabilized voltage reference (Linear Technology LM399H).
+The transimpedance circuit is shown in Fig.~\ref{fig:circuits}(a).
+It converts the photo current supplied by the photodiode to a voltage signal using a low-noise and high-bandwidth op-amp (Texas Instruments OPA843).
 To reduce electrical pickup and prevent ground loops, the electronic assembly is housed in a metal enclosure and mounted to the optical table using electrically insulating mica posts.
 
-Light is focused onto the photodiode using a $25.4\,$mm lens such that the beam at the photodiode is significantly smaller than the photodiode diameter, to prevent pointing fluctuations from registering as amplitude fluctuations.
+Light is focused onto the photodiode using an $f=\unit{25.4}{mm}$ lens such that the beam at the photodiode is significantly smaller than the photodiode diameter, to prevent pointing fluctuations from registering as amplitude fluctuations.
 An iris and interference filter (Semrock FF01-1020/LP25) are used to eliminate stray sources of light.
 
-\subsubsection{Digital to analog converter}
-The digital to analog converter (DAC, Texas Instruments DAC9881) connects the experimental digital control system to the analog control loop for the lattice.
+\subsubsection{Digital-to-analog converter}
+The digital-to-analog converter (DAC, Texas Instruments DAC9881) connects the experimental digital control system to the analog control loop for the lattice.
 By definition, an ideal control loop would translate any noise on the analog signal from the DAC to the laser light, meaning that a poorly designed DAC would inherently limit the lattice laser performance.
-The noise on the DAC, when it is programmed to output a constant voltage is shown in Fig.~\ref{fig:da_rin}, and is found to be roughly constant at a level of $-150$ dBc - more than acceptable.
+The noise on the DAC, when it is programmed to output a constant voltage is shown in Fig.~\ref{fig:da_rin}, and is found to be roughly constant at a level of \unit{-150}{dBc/Hz} --- more than acceptable.
 When the state of the DAC is changed, such as during a ramp, this noise level may be higher, due to the so-called ``glitch'' energy, as seen in the figure.
-The transient noise, while unfortunate, is mitigated by two factors: (1) it is only present when the lattice power is changing, which does not happen for most of the sequence, and a lattice at fixed power will have negligible RIN contributions.
-Further, (2) the loop filter eliminates the noise at higher frequencies.
+This transient noise, while unfortunate, is mitigated by two factors: (1) it is only present when the lattice power is changing, which does not happen for most of the sequence, and a lattice at fixed power will have negligible RIN contributions.
+Further, (2) the loop filter strongly reduces the noise at higher Fourier frequencies.
 
@@
     \caption{\textbf{Relative intensity noise of the digital to analog converter} at a fixed output voltage and while changing values.
-To measure the transient RIN, a $20$ ms, triangle wave with a DC offset and modulation depth of $15$\% of the DC offset was produced by the device.
+To measure the transient RIN, a triangle wave with \unit{20}{ms} period, a DC offset, and a modulation depth of 15\% of the DC offset was produced by the device.
 The triangle wave accounts for the series of spurs at low frequencies that fall with increasing frequencies.
-At frequencies above approximately $4$ kHz, the spectrum is dominated by noise due to transient ``glitches'' that emerge when the device changes its output state.}\label{fig:da_rin}
+At frequencies above approximately \unit{4}{kHz}, the spectrum is dominated by noise due to transient ``glitches'' that emerge when the device changes its output state.}\label{fig:da_rin}
   \end{center}
@@
 
-The connection between the actuation and monitoring mechanisms of the feedback system is the loop filter, which compares the \textit{set-point} signal, $v_s(t)$, supplied by the experimental control system and the monitoring signals $v_m(t)$, to adjust the actuation accordingly.
-We use a simple, purely integrating design based in three stages, as seen in Fig.~\ref{fig:circuits}, based on TI's OPA211 op-amp.
-The first stage computes and amplifies an error signal, $e(t)=v_m(t)-v_s(t)$, which is integrated by the second stage.
+The connection between the actuation and monitoring mechanisms of the feedback system is the loop filter, which compares the \emph{set-point} signal, $V_\mathrm{SP}(t)$, supplied by the experimental control system and the photodiode signals $V_\mathrm{PD}(t)$, to adjust the actuation accordingly.
+We use a simple, purely integrating design based in three stages, as seen in Fig.~\ref{fig:circuits}(c), based on a low-noise op-amp (Texas Instruments OPA211).
+The first stage computes and amplifies an error signal, $e(t)=V_\mathrm{SP}(t)-V_\mathrm{PD}(t)$, which is integrated by the second stage.
 The integral gain is set using a low-drift trim-pot.
-This is the case because within relevant frequency ranges, the AOM can be coarsely approximated by a pure time delay process (with delay given by the RF travel time across the crystal $\approx 1 \mu\mathrm{s}$).
-In this scenario, the $P$ term must be small to avoid instability at the $\pi$ phase shift point, and a pure $I$ controller is optimal~\cite{Skogestad2003}.
+This is the case because within relevant frequency ranges, the AOM can be coarsely approximated by a pure time delay process, given by the acoustic wave transit time of $\approx$\unit{1}{\mu{}s} across the active region of the AOM crystal.
+In this scenario, the proportional term must be small to avoid instability at the $\pi$ phase shift point, and a pure integral controller is optimal~\cite{Skogestad2003}.
 For debugging purposes, the loop filter features buffered photodiode monitor and error signal monitor outputs.
 
-The third stage of the loop filter is used to accommodate the fact that the actuation arm is nonlinear - the optical power transmitted by the AOM is proportional to the RF power incident on it $P_{\mathrm{rf}}\propto v_{if}^2$, where $v_{if}$ is the actuation signal supplied to the IF port of the mixer.
+The third stage of the loop filter is used to accommodate the fact that the actuation arm is nonlinear: the optical power transmitted by the AOM is proportional to the RF power incident on it $P_{\mathrm{rf}}\propto V_{IF}^2$, where $V_{IF}$ is the actuation signal supplied to the IF port of the mixer.
 In effect, if the rest of the feedback system was linear, this would correspond to a quadratically increasing gain until the AOM is saturated, which could lead to slow behavior at low signal levels and ringing at higher signal levels.
-Even worse, since the mixer is insensitive to the sign of the voltage applied, the gain is actually negative for negative voltages, resulting in an unstable system, which thus requires a current clamp.
-This stage linearizes the response by increasing the gain at low signal levels and suppressing it at high signal levels by using a diode (Digi-Key BAT54S) in the feedback arm.
-This can be seen by considering two extreme cases - far below the diode drop, the diode is an open circuit and the gain is set by $R_l$, where above the diode drop it is a closed circuit where the gain is set by the resistor $R_h$.
-Naturally, the voltage drop over the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode ($3.3\,$V).
+Even worse, since the mixer is insensitive to the sign of the voltage applied, the gain is becomes negative for negative voltages, resulting in an unstable system.
+
+To achieve the desired functionality, the final op-amp stage linearizes the response by increasing the gain at low signal levels and suppressing it at high signal levels by including a fast Schottky diode (ON Semiconductor BAT54S) in the feedback arm.
+This can be seen by considering two extreme cases: far below the diode drop, the diode is an open circuit and the gain is set by $R_l$; above the diode drop it is a closed circuit where the gain is set by the resistor $R_h$.
+Naturally, the voltage drop across the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode (\unit{3.3}{V}).
 Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in Fig.~\ref{fig:bandwidth}.
-Were it not for the linearization, the gain of the mixer would change by a factor of $10$ over a dynamic range spanning two orders of magnitude.
-Another function of the last stage is to clamp the voltage to be strictly $>0$, to prevent an unstable positive feedback behavior, which is done using diode clamp on the output arm~\cite{Horowitz2015}.
-Last of all, since the mixer is a current driven device, the last stage of the feedback loop uses TI's OPA627 op-amp which is able to supply tens of mA of current at an output impedance of $50\,\Omega$.
+Were it not for the linearization, the gain of the mixer would change by a factor of 10 over a dynamic range spanning two orders of magnitude.
+Another function of the last stage is to clamp the voltage to be strictly positive by including a diode clamp on the output to prevent unstable positive feedback behavior~\cite{Horowitz2015}.
+Finally, since the mixer is a current driven device, the last stage of the feedback loop uses the low-noise OPA627 (Texas Instruments) op-amp which is able to supply tens of mA of current into an output impedance of \unit{50}{\Omega}.
 
@@
     \includegraphics{Figure10.pdf}
-    \caption{\textbf{Loop bandwidth dependence on the set-point}. (a) shows the $3$ dB and $\pi$ phase shift points for the $X$ lattice. (b) shows the same for the $Y$ lattice.}\label{fig:bandwidth}
+    \caption{\textbf{Loop bandwidth dependence on the set-point}.
+(a) shows the \unit{3}{dB} and $\pi$ phase shift points for the $X$ lattice.
+(b) shows the same for the $Y$ lattice.}\label{fig:bandwidth}
   \end{center}
@@
     \includegraphics{Figure11.pdf}
-    \caption{\textbf{Laser noise of the lattice system with and without additional low pass filters} (a) Closed loop laser made a fiber amplifier (different than the one in figure~\ref{fig:noises}.
-(b) Noise on the same system as (a), but with extra filters.}\label{fig:low_pass_noises}
+    \caption{\textbf{Laser noise of the lattice system with and without additional low pass filtering.} (a) Closed-loop low-power server using a different fiber amplifier than the one in Fig.~\ref{fig:noises}(d).
+(b) Noise on the same system as in panel (a), but with additional low-pass filters.}\label{fig:low_pass_noises}
   \end{center}
@@
 
-A common behavior of analog feedback systems with integration components is termed \textit{integral wind-up}~\cite{Bechhoefer2005}, and occurs when the feedback loop is manually broken, meaning that the actuator can no longer adjust the state of the controlled parameter.
-In this regime, the integrator accumulates a large positive or negative value, such that when control is restored, the system appears to briefly rail, before control is restored.
-In our case, \textit{integrator wind-up} occurs when the high-isolation RF switch is open during the state preparation procedure, and closed when the lattice is desired.
-Since the lattice must usually be applied to the atoms adiabatically, fast transients due to this windup can result in heating.
+A common undesired behavior of analog feedback systems with integral gain is \emph{integrator wind-up}~\cite{Bechhoefer2005}, which can occur when the feedback loop is manually broken, meaning that the actuator can no longer adjust the state of the controlled parameter.
+In this regime, the integrator accumulates a large positive or negative voltage, such that when control is restored, the system appears to briefly rail before control is restored.
+In our case, \emph{integrator wind-up} occurs when the high-isolation RF switch is open during the state preparation procedure, and closed when the optical lattice is desired.
+In most cases, the optical lattice must be turned on adiabatically, to avoid heating the trapped atoms due to fast transients resulting from integrator windup.
 To solve this issue, a bypass switch (Maxim MAX4503) is placed across the capacitor of the second stage of the feedback circuit, which siphons off the charge when the lattice is inactive.
 Even when the switch is closed, its resistance is nonzero (due to a protection resistor that limits the current that can pass through the switch), the conditions leading to integral windup in an unprotected system still lead to charge accumulation on the integral capacitor, albeit at a much reduced level.
-Thus, in addition to the switch, when the system is inactive, the set-point is set to within ($\approx 200\,\mu$V) of the dark signal from the photodiode, making the error signal very small.
+Thus, in addition to the switch, when the system is inactive, the set-point is set to the dark signal from the photodiode ($\approx$\unit{200}{\mu{}V}), making the error signal very small.
 
-To avoid a so-called ``servo bump'' in the noise spectrum, and because there is little need for fast, closed-loop control, the loop filter is tuned very conservatively, to a bandwidth of approximately $10\,$kHz over most of the range.
-However, a small amount of tuning can raise this to up to $\approx150$ kHz, which is limited by the acoustic wave propagation delay of the AOM.
+To avoid a so-called ``servo bump'' in the noise spectrum, and because there is little need for fast, closed-loop control, the loop filter is tuned very conservatively, to a bandwidth of approximately \unit{10}{kHz} over most of the range.
+However, a small amount of tuning can increase the bandwidth up to $\approx$\unit{150}{kHz}, which is limited by the propagation delay of the AOM.
 Although fast, closed-loop control is not available in the current configuration, the last stage of the loop filter features an adder connected to an optional ``feed-forward'' port.
@@
 Although it is an essential part of the system, the loop filter is also one of its major limitations.
-Figure~\ref{fig:noises} shows the noise performance of the output of the fiber amplifiers in open loop as compared to the noise in closed loop.
-Although noise near DC is lowered (as expected from a closed loop system), noise outside the loop bandwidth is increased in the range of $10$ to $450$ kHz as seen in subfigures (c) and (d).
-This can be explained by the Johnson noise~\cite{Horowitz2015} on the $1$ k$\Omega$ input resistors, amplified by the amplification stages of the loop filter.
-The sharp drop off at the $450$ kHz point is due to a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.
-When this was determined to be a problem, we decided that a bandwidth of higher than $10\,$ kHz was not required in the foreseeable future.
-As a result, we added a first order low pass with a $3$ dB frequency of $10$ kHz leading to the improvement shown in Fig.~\ref{fig:low_pass_noises} (the fiber amplifier used to take this data was different from the one used for~\ref{fig:noises}, although their performance is comparable.
+Figure~\ref{fig:noises} shows the noise performance of the output of the fiber amplifiers in open-loop compared to the noise in closed-loop.
+Although noise near DC is lowered (as expected from a closed-loop system), noise outside the loop bandwidth is increased in the range of 10 to \unit{450}{kHz} as seen in subfigures (c) and (d).
+This can be explained by the Johnson noise~\cite{Horowitz2015} on the \unit{1}{k\Omega} input resistors, amplified by the amplification stages of the loop filter.
+The sharp drop off at the \unit{450}{kHz} point is due to a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.
+When the broadband noise below \unit{450}{kHz} was determined to be a problem, we decided that a bandwidth of higher than \unit{10}{kHz} was not required in the foreseeable future.
+As a result, we added a first-order low pass with a \unit{3}{dB} frequency of \unit{10}{kHz} leading to the improvement shown in Fig.~\ref{fig:low_pass_noises}.
+The fiber amplifier used to take this data was different from the one used for~\ref{fig:noises}, although their performance is comparable.
 
@@
 To that end, we use a $2f$ telescope of short focal length triplet collimator lenses to expand the beam, and then focus it with a long focal length singlet lens.
-We focus the lattice to a $70-90$\,$\mu$m waist at the position of the atoms.
-To verify that the waist is positioned correctly, we use a temporary mirror to redirect the beam away from the glass cell and onto a camera positioned in the plane corresponding to the position of the atoms.
-%The resulting beam at the atoms has an $m^2\leq1.4$.
+We focus the lattice to a \unit{70-90}{\mu{}m} waist at the position of the atoms.
+To verify that the waist is positioned correctly, we use a temporary mirror to redirect the beam away from the vacuum chamber (a glass cell) and onto a camera positioned in the plane corresponding to the position of the atoms.
 
 To prevent unwanted interference, the lattice beams enter the glass cell at an angle.
-Unfortunately, due to the angle of incidence, the beam contains both $S$ and $P$ polarizations, which are reflected differently, altering the polarization state of the beam.
+Unfortunately, due to the angle of incidence, the beam contains both $S$ and $P$ polarizations, which are reflected differently at the glass cell wall, thus altering the polarization state of the beam.
 Even worse, this happens on both the initial and retro-reflected pass through the glass cell.
-For this reason, we use a QWP and HWP to optimize the interference contrast of each lattice.
+For this reason, we use a combination of quarter waveplate (QWP) and half waveplate (HWP) to optimize the interference contrast of each lattice.
 This is done by optimizing the on-site trap frequency of lattice, measured using parametric heating.
@@
 \section{Beam monitoring and alignment}
-Improved spatial resolution and control have given experimentalists the ability to use relatively few atoms~\cite{Preiss2015, Choi2016, Mazurenko2016} that are simultaneously addressed by multiple beams and held by multiple traps.
-Such experiments place stringent bounds on the requisite stability.
+Improved spatial resolution and control have given experimentalists the ability to use relatively few atoms~\cite{Preiss2015, Choi2016, Mazurenko2017} that are simultaneously addressed by multiple beams and held by multiple traps.
+Such experiments place stringent bounds on the required beam pointing stability.
 
-The absolute positions of lattice sites cannot be allowed to change by more than a small fraction ($\approx 10\%$) from experimental shot to shot.
-This is ensured via careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately $3\,$cm from the atoms~\cite{Huber2014}.
+The absolute positions of lattice sites cannot be allowed to change by more than a small fraction ($\approx 10\%$) between experimental shots.
+This is ensured by careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately \unit{5}{cm} from the atoms~\cite{Huber2014}.
 We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours, as seen in Fig.~\ref{fig:averaged_mott}.
@@
     \caption{\textbf{Averaged images of Mott insulators}.
-a) Several Mott insulators were created over the course of approximately one hour, and the average image is shown\cite{Greif2016}.
-If the lattice fluctuated across more than a small fraction of a lattice site, the modulation contrast would be washed out.
+(a) Several Mott insulators were created over the course of approximately one hour, and the average image is shown~\cite{Greif2016}.
+If the lattice pattern would have fluctuated by more than a small fraction of a lattice site, the modulation contrast would have been washed out.
 The absence of this effect means that the phase of the optical lattice is stable.
-b) shows an individual image of a Mott insulator.}\label{fig:averaged_mott}
+(b) shows an individual image of a Mott insulator.}\label{fig:averaged_mott}
   \end{center}
@@
 The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement.
-In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in~\cite{Mazurenko2016} or~\cite{Choi2016}), drift or fluctuation of the lattice position is important.
+In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in Refs.~\cite{Choi2016,Mazurenko2017}), drift or fluctuation of the lattice position is important.
 
 The required positional stability of the underlying harmonic trap is achieved through a combination of passive stability and active monitoring.
-Passive stability is ensured by using stable optomechanics (largely from the Thorlabs Polaris line), mounted on short optical posts ($2$ in beam height relative to the floated optical table).
-To further improve stability, the beam is enclosed with $1\,$in aluminum tubes throughout its path and the entire setup is covered by metal plates.
+Passive stability is ensured by using stable optomechanics (largely from the Thorlabs Polaris line), mounted on short optical posts (\unit{2}{inch} beam height relative to the floated optical table).
+To limit sensitivity to air currents and further improve stability, the beam is enclosed with \unit{1}{inch} aluminum tubes throughout its path and the entire setup is covered by metal plates.
 As a final measure to isolate the experimental setup, the optical table is contained within an aluminum enclosure.
@@
 
-Passive stability alone has been found to be insufficient to ensure smooth operation over many hours.
-Changes in weather conditions, load on the water-cooling systems and other external conditions can lead to a slow drift in the laser pointing.
-The situation is further complicated by the fact that opening the enclosure changes the thermal state of the system, meaning that manual alignment can induce misalignment.
+Generally, changes in environmental conditions (such as temperature and relative humidity), load on the water-cooling systems and other external conditions can lead to a slow drift in the laser pointing over long timescales.
+The situation is further complicated by the fact that opening the enclosure of the experiment changes the thermal state of the system.
 For these reasons, each lattice axis is fitted with a remotely actuated mirror, controlled by the experimental control software over the lab network, allowing for non-invasive, digital alignment of the system.
-The remote actuators are Newport brand ``Picomotors'' (model 8302), fitted into a customized $2$ in mirror mount.
-They work in a ``fire and forget'' manner, remaining passively stable when not in active use.
+The remote actuators are ``Picomotors'' (Newport 8302), fitted into a customized \unit{2}{inch} mirror mounts.
+They work in a ``fire-and-forget'' manner, remaining passively stable when not in active use.
 
@@
 This monitoring system could potentially allow us to eliminate (via post-selection) experimental realizations when the system was in an undesired state.
-A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the plane corresponding to the atomic system, producing a Gaussian image identical to that of the optical lattice.
+A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the plane corresponding to the atomic system, imaging a Gaussian beam identical to that of the optical lattice.
 Naturally, the position of the atoms is dictated by the light field of both the incoming and retro-reflected beams, while the monitoring camera only observes the position of the in-going beam.
-To verify that the monitor camera could predict the true position of the harmonic trap, the beam and the atoms were imaged simultaneously while a purposeful misalignment of the incoming beams was introduced.
+To verify that the monitor camera can predict the true position of the harmonic trap, the beam and the atoms were imaged simultaneously while a purposeful misalignment of the incoming beams was introduced.
 During this process, one of the lattice beams was adiabatically loaded, ensuring that the atoms settled to its center, prior to performing site-resolved imaging~\cite{Parsons2015}.
@@
 First, we characterized the passive stability of the optical axis along the transverse $x_t$ and longitudinal $x_l$ directions.
-Figure~\ref{fig:stability} a shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$($0.98(4)$) sites along the $x_t$($x_l$) directions.
-The difference between displacements along is a geometric effect consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
-The distributions are centered within $1\sigma$ of zero along both directions ($-.03(4)$ and $0.01(5)$ sites for transverse and longitudinal, respectively).
+Figure~\ref{fig:stability}(a) shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$ [$0.98(4)$] sites along the $x_t$ [$x_l$] direction.
+The difference between displacements is a geometric effect consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
+The distributions are centered within 1-$\sigma$ of zero along both directions: $-0.03(4)$ and $0.01(5)$ sites for transverse and longitudinal axes, respectively.
 If the trap followed a random walk with these step sizes, the experiment would be in trouble, since after only $100$ experimental shots, the trap would move by more than $10$ lattice sites.
-The situation is more fortunate, however, since subsequent steps are correlated, as shown in Fig.~\ref{fig:stability} (b).
-Once this correlation is taken into account, we estimate a drift of $8(1)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the transverse direction and $12(2)\times 10^{-3}\mathrm{sites}/\mathrm{realization}$ in the axial direction, compared to a beam waist of approximately $80$ $\mu$m ($\approx 140$ sites).
+The situation is more fortunate, however, since subsequent steps are correlated, as shown in Fig.~\ref{fig:stability}(b).
+Once this correlation is taken into account, we estimate a drift of \unit{8(1)\times 10^{-3}}{sites/realization} in the transverse direction and \unit{12(2)\times 10^{-3}}{sites/realization} in the axial direction, compared to a beam waist of $\approx$\unit{80}{\mu{}m} ($\approx$140 sites).
 
-\begin{figure*}
+\begin{figure}
   \begin{center}
-    \includegraphics{Figure13.pdf}
+    \includegraphics[width=\columnwidth]{Figure13.pdf}
     \caption{\textbf{Short term positional stability.} (a) A histogram of shot-to-shot step sizes along the transverse and longitudinal directions, with a Gaussian fit.
 (b) Correlations between the step size of subsequent shots.
-(c) Calibration data for the ``affine fit'' of the conversion from camera pixels to lattice dimentions.
-(d) Predicted location versus measured location along the transverse and longitudinal directions.
-(e,f) The measured position and predicted position of the atomic cloud, based on refitting the offset every $20$ experimental realizations.}\label{fig:stability}
+(c) Calibration data for the ``affine fit'' of the conversion from camera pixels to lattice dimensions.
+(d) Predicted versus measured location along the transverse and longitudinal directions.
+(e,f) Measured  and predicted position of the atomic cloud, based on refitting the offset every $20$ experimental realizations.}\label{fig:stability}
   \end{center}
-\end{figure*}
+\end{figure}
+
+\FIXME{} SB: I think I understand what you are doing, but the wording makes little sense: We cannot measure the atoms, so we measure the atoms?
+Need to make clear distinction between beam-monitoring camera and iXon.
 
 In a real experiment, we cannot directly measure the position of the atoms and must rely on the measurement performed by the camera, related by an affine transformation.
-To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in Fig.~\ref{fig:stability} (c).
+To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in Fig.~\ref{fig:stability}(c).
 
-Unfortunately, while this fit is acceptable for a short while ($\approx30\mathrm{ shots}$), the quality of the fit degrades over time, correspondingly degrading the predictive power.
-The most likely culprit is thermal drift of the camera, since a displacement of only a pixel caused the predicted position to change by approximately $1\,$site, and each camera pixel is about $3\,\mu$m accross.
-The camera housing is not engineered for low drift mounting, and the camera heats up by a few degrees Celcius, making a few $\mu$m drift very possible.
-To deal with this problem, we point out that the affine transform is composed of three distinct parts - the rotation, scaling and offset.
+Unfortunately, while this fit is acceptable for a short while ($\approx$ 30 shots), the quality of the fit degrades over time, correspondingly degrading its predictive power.
+The most likely culprit is thermal drift of the beam-monitoring camera, since a displacement of only a pixel caused the predicted position to change by approximately 1~site, and each camera pixel is about \unit{3}{\mu{}m} across.
+The camera housing is not engineered for low drift mounting, and the camera heats up by a few $^\circ$C, making a few $\mu$m drift very possible.
+To deal with this problem, we point out that the affine transform is composed of three distinct parts: the rotation, the scaling and the offset.
 Of these, only the offset is likely to drift with time.
-As a result, we developed a way of updating the calibration over time.
-To test this procedure, we analyzed the data set of camera measurements and atomic positions in the following way: we split the data set into sequential blocks of $20$ shots, each followed by a block of $8$ shots.
-The large blocks were treated as ``masked'' data, which we tried to predict, while the small blocks were treated as ``updating'' events used to update the calibration offsets.
-The results are shown in Fig.~\ref{fig:stability} (d-f), showing a large degree of tracking between the predicted positions and measured position - the average displacement between the predicted position and measured position was $0.7\,$lattice sites.
-
-The purpose of developing this system was twofold - to reduce measurement noise by filtering experimental shots that suffered any sort of positional fluctuation of either lattice beam, and to minimize the frequency of such events.
-As it stands, for the purpose of most measurements, the experiment can perform hundreds of cycles before the thermal drift becomes a problem.
-Further, if future experiments require the optical lattice to be more positionally stable than it is now, the monitoring and actuation system could be used in closed loop with no hardware changes to the experiment.
-Naturally, the transfer function of any such loop would have to be carefully engineered to account for the correlated behavior of the jumps and the timescale of the drift.
+As a result, we developed a method to update the calibration over time.
+To test this procedure, we analyze the data set of camera measurements and atomic positions in the following way: we split the data set into sequential blocks of $20$ shots, each followed by a block of $8$ shots.
+The large blocks are treated as ``masked'' data, which we try to predict, while the small blocks are treated as ``updating'' events used to update the calibration offsets.
+The results are shown in Fig.~\ref{fig:stability}(d-f), showing a large degree of tracking between the predicted positions and measured position.
+The average displacement between the predicted position and measured position is 0.7~lattice sites.
 
@@
     \includegraphics[width=\columnwidth]{Figure14.pdf}
-    \caption{\textbf{Long term stability over approximately nine months.} The lattice spacing $|\mathrm{v}_x|$ and $|\mathrm{v}_y|$ and the lattice angles $\theta_x$ and $\theta_y$ along the two lattice axes $x$ and $y$ are shown over the duration of almost 1 year.
-}\label{fig:long_term_stability}
+    \caption{\textbf{Long term stability over approximately ten months.} The lattice spacings $|\mathrm{v}_x|$ and $|\mathrm{v}_y|$ and the lattice angles $\theta_x$ and $\theta_y$ along the two lattice axes $x$ and $y$ (cf.
+Fig.~\ref{fig:averaged_mott}) are shown over a period of ten months.}\label{fig:long_term_stability}
   \end{center}
@@
 Several interesting features can be seen from the observed behavior.
-\begin{enumerate}
-  \item During the first few months the lattice spacing appears to have slowly varied over as much as $10\%$.
-    This might be caused by drifts of the optical system that required daily refocusing of the imaging system using an auxiliary lens, which simultaneously changed the magnification.
-  \item The imaging system was simplified in September 2016, causing a sudden change in the magnification.
-  \item The system has been more stable since then and the lattice spacing $|v|$ exhibits fractional fluctuations $\sigma_{|v|}/\mu_{|v|}\leq 0.005$.
-  \item Unlike magnification, which sensitively depends on the imaging system focus, the angle is unlikely to be affected by the imaging system unless the camera is mechanically rotated.
-We measure that in the spring of 2017, the relative angle of the lattices has exhibited fluctuations with an RMS of $0.06^\circ$.
-\end{enumerate}
+In the first few months the lattice spacing changed by around 10\%.
+Experimentally, this drift was accompanied by the necessity of refocussing the imaging system.
+The sudden jump in September 2016 was caused by a simplification of the imaging system.
+Afterwards, the lattice spacing seemed more stable (fractional changes of $\leq 0.005$).
+Unlike the lattice spacing, the angle is observed to be mostly unaffected and remains very stable (for example, an RMS of 0.06$^\circ$ in Spring 2017).
 
 \section{Conclusion}
-We have presented the design and specifications of an optical lattice system that has been successfully used for quantum gas microscopy of low temperature phases of the Hubbard model.
-In this design, key emphasis has been placed on the stability of the pointing and the intensity of the optical lattice, of particular importance to the underlying physics.
-To improve performance, the system can be upgraded in a variety of ways.
+We have presented the design and specifications of an optical lattice system that has been successfully used for quantum gas microscopy of low-temperature phases of the Hubbard model.
+In this design, key emphasis has been placed on the stability of the pointing and the intensity of the optical lattice, of particular importance to observe the underlying physics.
+To further improve the system's performance, the system can be upgraded in a variety of ways.
 For example, the Nufern fiber amplifiers can be replaced with a lower noise model.
-Or the analog feedback loop can be replaced by a low-noise digital version.
+The analog feedback loop can be replaced by a low-noise digital version.
 Additionally, active stabilization of the laser pointing could be implemented in the future.

### 2018-06-13 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Abstract rewording

@@
 The beam intensity is stabilized and controlled with a nonlinear feedback loop.
-Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1\% of the lattice spacing and a long-term (six month) relative stability of 0.5\% RMS of the lattice spacing.
+Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
 \end{abstract}

### 2018-06-13 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Abstract rewording

@@
 \begin{abstract}
-  We describe the design and implementation of a stable high-power \unit{1064}{nm} laser system for use in experiments with ultracold atoms trapped in optical lattices.
+  We describe the design and implementation of a stable high-power \unit{1064}{nm} laser system to generate optical lattices for experiments with ultracold quantum gases.
 The system is based on a low-noise laser amplified by an array of four heavily modified, high-power fiber amplifiers.

### 2018-06-14 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
pushed
Daniel putting his changes that he forgot to commit (minor things)

@@
 \author{A. Mazurenko}
-\altaffiliation{
-  Present address: \FIXME{}}
 \author{S. Blatt}
@@
 \author{M. F. Parsons}
-\altaffiliation{
-  Present address: \FIXME{} TOO}
 \author{C. S. Chiu}
@@
 
-Optical lattices holding arrays of ultracold atoms have become a powerful experimental platform for quantum simulations~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
+Optical lattices holding arrays of ultracold atoms have become a powerful experimental platform for quantum simulations~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Greif2013, Drewes2016, Murmann2015}.
 The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2017} has enabled studies with unprecedented control over individual atoms in many-body systems governed by the Hubbard Hamiltonian~\cite{Hubbard1963}, resulting in extremely low energy scales~\cite{Mazurenko2017}.
@@
 Quantum gas microscopy of Li$^6$ requires single site trap frequencies of approximately \unit{1}{MHz}~\cite{Parsons2015} to be in the Lamb-Dicke regime necessary for Raman sideband cooling.
+
 Such trap frequencies may only be attained using tightly focused, high-power beams. 
-In practical terms, this requires approximately \unit{30}{W} per lattice axis, which we attain using Yb-doped fiber amplifiers (Nufern NuAmp SUB1174-34).
+In practical terms, this requires approximately \unit{20}{W} per lattice axis for a beam waist of around $80 \mu\mathrm{m}$ and the four-fold enhancement in optical depth provided by the reflection from the superpolished substrate.
+We achieve such high laser powers using Yb-doped fiber amplifiers (Nufern NuAmp SUB1174-34).
 These amplifiers can amplify \unit{150}{mW} of seed light to up to approximately \unit{45}{W}.
@@
 When the state of the DAC is changed, such as during a ramp, this noise level may be higher, due to the so-called ``glitch'' energy, as seen in the figure.
-This transient noise, while unfortunate, is mitigated by two factors: (1) it is only present when the lattice power is changing, which does not happen for most of the sequence, and a lattice at fixed power will have negligible RIN contributions.
+This transient noise is mitigated by two factors: (1) it is only present when the lattice power is changing, which does not happen for most of the sequence, and a lattice at fixed power will have negligible RIN contributions.
 Further, (2) the loop filter strongly reduces the noise at higher Fourier frequencies.
@@
 As a result, we added a first-order low pass with a \unit{3}{dB} frequency of \unit{10}{kHz} leading to the improvement shown in Fig.~\ref{fig:low_pass_noises}.
-The fiber amplifier used to take this data was different from the one used for~\ref{fig:noises}, although their performance is comparable.
+The fiber amplifier used to take this data was different from the one used for Fig.~\ref{fig:noises}, although their performance is comparable.
 

### 2018-06-20 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Daniel fixing beam-monitoring section (and combining Antons suggestions)

@@
 
-The absolute positions of lattice sites cannot be allowed to change by more than a small fraction ($\approx 10\%$) between experimental shots.
-This is ensured by careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately \unit{5}{cm} from the atoms~\cite{Huber2014}.
-We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours, as seen in Fig.~\ref{fig:averaged_mott}.
+Several applications require the positions of lattice sites to not change by more than a small fraction ($\approx 10\%$) between experimental shots.
+In our setup this is ensured by careful design of the optical assembly, where the phase of the retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately \unit{5}{cm} from the atoms~\cite{Huber2014}.
+This phase determines the location of the sites of the optical lattice. 
+We have characterized the phase stability of the optical lattice by recording a long sequence of densely populated images with our imaging camera.
+We found that the phase varies by much less than one lattice site over the course of hours, as seen in Fig.~\ref{fig:averaged_mott}.
 
@@
 
-The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement.
-In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in Refs.~\cite{Choi2016,Mazurenko2017}), drift or fluctuation of the lattice position is important.
+The position of the atomic cloud, however, is not determined by the phase difference of the retro-reflecting lattice beam, but by the underlying harmonic confinement.
+The stability of this confinement is governed by the pointing stability of the optical lattice laser beams. 
+In experiments where the entire cloud is addressed by beams auxiliary to the lattice, which can be used for example for enhanced entropy redistribution~\cite{Mazurenko2017}, reducing drifts and fluctuations of the lattice position is important.
 
@@
 
-Changing external conditions can contaminate large datasets if the prepared state sensitively depends on laser pointing.
-To watch for this contamination, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
-This monitoring system could potentially allow us to eliminate (via post-selection) experimental realizations when the system was in an undesired state.
-A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the plane corresponding to the atomic system, imaging a Gaussian beam identical to that of the optical lattice.
-Naturally, the position of the atoms is dictated by the light field of both the incoming and retro-reflected beams, while the monitoring camera only observes the position of the in-going beam.
-To verify that the monitor camera can predict the true position of the harmonic trap, the beam and the atoms were imaged simultaneously while a purposeful misalignment of the incoming beams was introduced.
-During this process, one of the lattice beams was adiabatically loaded, ensuring that the atoms settled to its center, prior to performing site-resolved imaging~\cite{Parsons2015}.
-
-Over the course of 250 sequential experimental realizations, we monitored the position of the beam on the camera and the position of the atoms.
-First, we characterized the passive stability of the optical axis along the transverse $x_t$ and longitudinal $x_l$ directions.
-Figure~\ref{fig:stability}(a) shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$ [$0.98(4)$] sites along the $x_t$ [$x_l$] direction.
-The difference between displacements is a geometric effect consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
-The distributions are centered within 1-$\sigma$ of zero along both directions: $-0.03(4)$ and $0.01(5)$ sites for transverse and longitudinal axes, respectively.
-If the trap followed a random walk with these step sizes, the experiment would be in trouble, since after only $100$ experimental shots, the trap would move by more than $10$ lattice sites.
+We characterized the passive stability of the optical lattice by monitoring the position over the course of 250 sequential experimental realizations. 
+To analyse the data we decomposed the recorded positions into the transverse $x_t$ and longitudinal $x_l$ components as compared to the optical axis (i.e.
+rotated by $45^\circ$ as compared to the lattice directions $x$ and $y$).
+During this measurement we found that the drift of the atom position is about $1-2$ lattice site, see red data in Fig.~\ref{fig:stability}(e+f).  
+For a more in-depth analysis, we also studied the histogram of displacements of atoms between subsequent experimental realizations, see Fig.~\ref{fig:stability}(a). 
+This shows a RMS displacement of $0.54(3)$ [$0.98(4)$] sites along the $x_t$ [$x_l$] direction.
+The difference between the displacements is a geometric consequence of the mechanical assembly of the experiment~\cite{Huber2014}.
+The distributions are centered within 1-$\sigma$ of zero along both directions: $-0.03(4)$ and $0.01(5)$ sites for transverse and longitudinal axes, respectively, indicating the absence of strong drift.
+If the trap followed a random walk with these step sizes, the optical assembly would have to be frequently realigned, since after only $100$ experimental shots the trap would move by more than $10$ lattice sites.
 The situation is more fortunate, however, since subsequent steps are correlated, as shown in Fig.~\ref{fig:stability}(b).
-Once this correlation is taken into account, we estimate a drift of \unit{8(1)\times 10^{-3}}{sites/realization} in the transverse direction and \unit{12(2)\times 10^{-3}}{sites/realization} in the axial direction, compared to a beam waist of $\approx$\unit{80}{\mu{}m} ($\approx$140 sites).
+Once this correlation is taken into account, we estimate an RMS drift of \unit{8(1)} [12(2)] {sites/ 1000 realizations} in the transverse [axial] direction, compared to a beam waist of $\approx$140 sites.
 
@@
 
-\FIXME{} SB: I think I understand what you are doing, but the wording makes little sense: We cannot measure the atoms, so we measure the atoms?
-Need to make clear distinction between beam-monitoring camera and iXon.
+As an additional measure, we have implemented a monitoring system to independently verify appropriate pointing of the lattice laser beams.
+This is particularly useful when performing experiments where imaging the atoms does note allow determining the original center of the atoms in the harmonic trap. 
+Additionally, this beam-monitoring system could allow us to eliminate (via post-selection) experimental realizations when the system was in an undesired state -- or designing a feedback loop on the lattice beam pointing to ensure long-term stability.
+A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the plane corresponding to the atomic system, imaging a Gaussian beam identical to that of the optical lattice.
+Naturally, the position of the atoms is dictated by the light field of both the incoming and retro-reflected beams, while the monitoring camera only observes the position of the in-going beam (this is found to not be a limitation in practice).
 
-In a real experiment, we cannot directly measure the position of the atoms and must rely on the measurement performed by the camera, related by an affine transformation.
-To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in Fig.~\ref{fig:stability}(c).
-
-Unfortunately, while this fit is acceptable for a short while ($\approx$ 30 shots), the quality of the fit degrades over time, correspondingly degrading its predictive power.
-The most likely culprit is thermal drift of the beam-monitoring camera, since a displacement of only a pixel caused the predicted position to change by approximately 1~site, and each camera pixel is about \unit{3}{\mu{}m} across.
-The camera housing is not engineered for low drift mounting, and the camera heats up by a few $^\circ$C, making a few $\mu$m drift very possible.
-To deal with this problem, we point out that the affine transform is composed of three distinct parts: the rotation, the scaling and the offset.
-Of these, only the offset is likely to drift with time.
-As a result, we developed a method to update the calibration over time.
-To test this procedure, we analyze the data set of camera measurements and atomic positions in the following way: we split the data set into sequential blocks of $20$ shots, each followed by a block of $8$ shots.
-The large blocks are treated as ``masked'' data, which we try to predict, while the small blocks are treated as ``updating'' events used to update the calibration offsets.
-The results are shown in Fig.~\ref{fig:stability}(d-f), showing a large degree of tracking between the predicted positions and measured position.
-The average displacement between the predicted position and measured position is 0.7~lattice sites.
+As a first step, we calibrated the beam-monitoring system by simultaneously recording the position of the atoms on the imaging camera (Andor iStar) and the lattice beam position on the beam-monitoring camera (Point Grey Chameleon).
+By additionally varying the laser beam position and the lattice anisotropy we were able to obtain a reliable calibration, see Fig.~\ref{fig:stability} (c).
+However, we found that this calibration changes after a short while ($\approx$ 30 shots) and there is an offset between the recordings of the beam-monitoring camera and the atoms camera. 
+This is most likely caused by thermal drifts of the beam-monitoring camera housing: the camera heats up by a few $^\circ$C owing to the absence of active cooling.
+This can easily lead to a few $\mu$m drift due to the plastic mounting between the post holder mounted to the optical table and the CCD chip.
+While this could be easily fixed with an improved camera design, we implemented an alternative approach: by recalibrating the offset every 20 shots, this effect can be taken into account. 
+After correcting for this changing offset of the beam-monitoring camera, we find very good agreement between the recorded atom position with the imaging camera and the predicted atom position based on the beam-monitoring camera, see Fig.~\ref{fig:stability}(d-f).
+The average $L_1$ displacement between the predicted position and measured position is 0.7~lattice sites.
+The beam-monitoring system is thus sufficiently sensitive to detect lattice misalignments that are on the order of a few lattice sites or more, making it useful as a non-invasive check of the alignment of the experimental apparatus.
 

### 2018-06-21 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
Included Anton's comments

--- 2018-06-14 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
@@
 The beam intensity is stabilized and controlled with a nonlinear feedback loop.
-Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
+Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1.4\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
 \end{abstract}
@@
 Optical lattices holding arrays of ultracold atoms have become a powerful experimental platform for quantum simulations~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Greif2013, Drewes2016, Murmann2015}.
-The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2017} has enabled studies with unprecedented control over individual atoms in many-body systems governed by the Hubbard Hamiltonian~\cite{Hubbard1963}, resulting in extremely low energy scales~\cite{Mazurenko2017}.
+The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2017} has enabled studies with unprecedented control over individual atoms in many-body systems governed by the Hubbard Hamiltonian~\cite{Hubbard1963}, resulting in extremely low energy scales~\cite{Mazurenko2017, Chiu2018}.
 However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
 Even if the systems thermalize, heating rates can limit the interrogation time available to probe low-temperature states~\cite{Blatt2015}.
-In particular, experiments that rely on a small number of atoms held by multiple traps~\cite{Preiss2015, Choi2016, Mazurenko2017} place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.
+In particular, experiments that rely on a small number of atoms held by multiple traps~\cite{Preiss2015, Choi2016, Mazurenko2017, Chiu2018} place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.
 
 In this work we discuss major improvements to our high power optical lattice system~\cite{Blatt2015} and show levels of intensity noise below \unit{-115}{dBc/Hz} between \unit{1}{kHz} and \unit{3}{MHz} Fourier frequency.
-In addition to the intensity stability, we demonstrate a short-term (shot-to-shot) stability of the lattice position at 1\% of the optical lattice spacing, and a long-term (six month) relative stability of 0.5\% RMS of the lattice spacing itself.
+In addition to the intensity stability, we demonstrate a short-term (shot-to-shot) stability of the lattice position at 1.4\% of the optical lattice spacing, and a long-term (six month) relative stability of 0.5\% RMS of the lattice spacing itself.
 
@@
 
-Changing external conditions can contaminate large datasets if the prepared state sensitively depends on laser pointing.
-To watch for this contamination, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
-This monitoring system could potentially allow us to eliminate (via post-selection) experimental realizations when the system was in an undesired state.
-A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the plane corresponding to the atomic system, imaging a Gaussian beam identical to that of the optical lattice.
-Naturally, the position of the atoms is dictated by the light field of both the incoming and retro-reflected beams, while the monitoring camera only observes the position of the in-going beam.
-To verify that the monitor camera can predict the true position of the harmonic trap, the beam and the atoms were imaged simultaneously while a purposeful misalignment of the incoming beams was introduced.
-During this process, one of the lattice beams was adiabatically loaded, ensuring that the atoms settled to its center, prior to performing site-resolved imaging~\cite{Parsons2015}.
+Variation in external conditions can contaminate large datasets if the prepared state sensitively depends on laser pointing.
+To guard against such contamination, we have implemented an independent monitoring system to verify appropriate pointing of both lattice laser beams.
+This monitoring system allows us to eliminate (via post-selection) experimental realizations during which the system was in an undesired state.
+A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a monitoring camera located in the plane corresponding to the atomic system, imaging a Gaussian beam corresponding to the optical lattice.
+Naturally, the position of the atoms is dictated by the light field of both the incoming and retroreflected beams, while the monitoring camera only observes the position of the incoming beam.
 
-Over the course of 250 sequential experimental realizations, we monitored the position of the beam on the camera and the position of the atoms.
-First, we characterized the passive stability of the optical axis along the transverse $x_t$ and longitudinal $x_l$ directions.
+In our experiments, the position of the Gaussian beam envelope of the optical lattice is impossible to determine from the site-resolved image of the atoms, because the atoms may not occupy the central part of the envelope depending on the specefics of the lattice loading procedure.
+In addition, the atomic distributions are governed by the sum of the incident lattices and thus cannot be used to reliably infer the degree of overlap between the lattice beams.
+Nevertheless, it is possible to adiabatically load a strongly anisotropic optical lattice by lowering the power of one of the lattice beams, resulting in an atomic distribution that closely matches the trap produced by the high-power beam~\cite{Parsons2015}.
+This procedure yields the correct position of the Gaussian beam envelope in the atom plane, which we can use to analyze each beam's passive stability and its relationship to the beam-monitoring camera.
+
+We first characterize the passive stability of the optical lattice along one dimension by monitoring its position over the course of 250 experimental realizations.
+We decompose the lattice position into the transverse $x_t$ and the longitudinal $x_l$ components with respect to the optical axis.
 Figure~\ref{fig:stability}(a) shows a histogram of displacements of atoms between subsequent experimental realizations, showing that the RMS displacement is $0.54(3)$ [$0.98(4)$] sites along the $x_t$ [$x_l$] direction.
-The difference between displacements is a geometric effect consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
+The variation of the displacements is a geometric effect consistent with the mechanical assembly of the experiment~\cite{Huber2014}.
 The distributions are centered within 1-$\sigma$ of zero along both directions: $-0.03(4)$ and $0.01(5)$ sites for transverse and longitudinal axes, respectively.
-If the trap followed a random walk with these step sizes, the experiment would be in trouble, since after only $100$ experimental shots, the trap would move by more than $10$ lattice sites.
-The situation is more fortunate, however, since subsequent steps are correlated, as shown in Fig.~\ref{fig:stability}(b).
-Once this correlation is taken into account, we estimate a drift of \unit{8(1)\times 10^{-3}}{sites/realization} in the transverse direction and \unit{12(2)\times 10^{-3}}{sites/realization} in the axial direction, compared to a beam waist of $\approx$\unit{80}{\mu{}m} ($\approx$140 sites).
+If the trap had followed a random walk with these step sizes, the optical lattice would have to be realigned frequently, since after only $100$ experimental shots, the trap would have moved by more than $10$ lattice sites.
+However, the situation is more fortunate, since subsequent steps are correlated, as shown in Fig.~\ref{fig:stability}(b).
+Once this correlation is taken into account, we estimate an RMS drift of 8(1)~sites over 1000~realizations in the transverse direction and 12(2)~sites over 1000~realizations in the axial direction.
+This drift corresponds to an RMS displacement of $\unit{14(3)\times 10^{-3}}{sites / realization}$, compared to a beam waist of $\approx$\unit{80}{\mu{}m} ($\approx$140 sites).
 
@@
 
-\FIXME{} SB: I think I understand what you are doing, but the wording makes little sense: We cannot measure the atoms, so we measure the atoms?
-Need to make clear distinction between beam-monitoring camera and iXon.
+In general, we cannot extract the lattice position from the atomic distribution directly, but rely on the monitor camera picture, which is related to the lattice position in the atom plane by an affine transformation, consisting of a rotation, a scaling, and an offset.
+To determine the parameters of this affine transform, we use the remote actuators to purposely misalign the lattice beams and correlate the monitor camera image with the atom image obtained by fluorescence imaging~\cite{Parsons2015}.
+The corresponding least-squares fit is shown in Fig.~\ref{fig:stability}(c).
+The quality of this fit remains acceptable for $\approx$30 repetitions of the experiment, but it degrades for longer times.
+This effect is most likely due to thermal drift of the beam-monitoring camera, since a displacement of a one pixel (\unit{3}{\mu{}m}) on the monitoring camera is equivalent to a displacement of one lattice site in the atom plane.
+The most likely parameter of the affine transform susceptible to thermal drift over a few experimental cycles is the offset.
 
-In a real experiment, we cannot directly measure the position of the atoms and must rely on the measurement performed by the camera, related by an affine transformation.
-To determine the parameters of the affine transform, we use the remote actuators to purposefully misalign the lattice beams for a small number of shots, and simultaneously measure the atomic positions and the camera reading, then perform a least-squares fit, shown in Fig.~\ref{fig:stability}(c).
+For this reason, we developed a procedure to periodically update the affine transform relating the beam-monitoring camera to the atom plane.
+We test this procedure, we analyze the data set of monitoring-camera measurements and atomic positions (shown in Fig.~\ref{fig:stability}) in the following way: we split the data set into sequential blocks of 20 shots, each followed by a block of 8 shots.
+We try to predict the larger blocks, by analyzing the smaller blocks to derive the updates to the affine transform.
+The results are shown in Fig.~\ref{fig:stability}(d-f) and display a large degree of tracking between the predicted and measured atom positions.
+The average taxicab distance between the predicted position and the measured position is 0.7~lattice sites.
 
-Unfortunately, while this fit is acceptable for a short while ($\approx$ 30 shots), the quality of the fit degrades over time, correspondingly degrading its predictive power.
-The most likely culprit is thermal drift of the beam-monitoring camera, since a displacement of only a pixel caused the predicted position to change by approximately 1~site, and each camera pixel is about \unit{3}{\mu{}m} across.
-The camera housing is not engineered for low drift mounting, and the camera heats up by a few $^\circ$C, making a few $\mu$m drift very possible.
-To deal with this problem, we point out that the affine transform is composed of three distinct parts: the rotation, the scaling and the offset.
-Of these, only the offset is likely to drift with time.
-As a result, we developed a method to update the calibration over time.
-To test this procedure, we analyze the data set of camera measurements and atomic positions in the following way: we split the data set into sequential blocks of $20$ shots, each followed by a block of $8$ shots.
-The large blocks are treated as ``masked'' data, which we try to predict, while the small blocks are treated as ``updating'' events used to update the calibration offsets.
-The results are shown in Fig.~\ref{fig:stability}(d-f), showing a large degree of tracking between the predicted positions and measured position.
-The average displacement between the predicted position and measured position is 0.7~lattice sites.
+In conclusion: the beam-monitoring camera is sufficiently sensitive to detect lattice misalignments on the order of a few lattice sites, making it useful as a noninvasive check of the lattice position.
 
@@
 \section{Long-term stability of the lattice structure}
-A benefit of site-resolved imaging is that every measurement of the atomic distribution is also a direct measurement of the underlying lattice structure.
-As discussed in the supplementary material of~\cite{Parsons2016, Greif2016}, the Fourier transform of an atomic distribution contains distinct peaks corresponding to the lattice structure, and these peaks can be used to extract the phase, relative angle, and spacing of the lattices.
+A benefit of site-resolved imaging is that every measurement of the atomic distribution is also a direct measurement of the underlying lattice structure (except for the short-term and small-scale displacement discussed in the last section).
+As discussed in the supplementary material of~\cite{Parsons2016, Greif2016}, the Fourier transform of an atomic distribution contains distinct peaks corresponding to the lattice structure, and these peaks can be used to extract the relative angle and the spacing of the lattices.
 For this reason, we recorded a long-term measurement spanning almost one year to learn how these parameters change over time, see Fig.~\ref{fig:long_term_stability}.
@@
 To further improve the system's performance, the system can be upgraded in a variety of ways.
-For example, the Nufern fiber amplifiers can be replaced with a lower noise model.
-The analog feedback loop can be replaced by a low-noise digital version.
-Additionally, active stabilization of the laser pointing could be implemented in the future.
+For example, the Nufern fiber amplifiers can be replaced with a lower noise model [such as the MOPA system shown in Fig.~\ref{fig:noises}(a)].
+The nonlinear analog feedback loop can also be replaced by a lower-noise digital version.
+Active stabilization of the laser pointing can improve the pointing stability further.
+The high degree of lattice stability demonstrated here has already enabled first investigations of entropy redistribution schemes involving multiple traps that made it possible to observe antiferromagnetic ordering in two-dimensional Fermi gases~\cite{Mazurenko2017} and to engineer low-entropy quantum states~\cite{Chiu2018}.
 

### 2018-06-21 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex

@@
 
-The absolute positions of lattice sites cannot be allowed to change by more than a small fraction ($\approx 10\%$) between experimental shots.
-This is ensured by careful design of the optical assembly, since the phase of a retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately \unit{5}{cm} from the atoms~\cite{Huber2014}.
-We have characterized the phase stability of the optical lattice by looking at a long sequence of densely populated images, and found that the phase varies by much less than one lattice site over the course of hours, as seen in Fig.~\ref{fig:averaged_mott}.
+Several applications require the positions of lattice sites to not change by more than a small fraction ($\approx 10\%$) between experimental shots.
+In our setup this is ensured by careful design of the optical assembly, where the phase of the retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately \unit{5}{cm} from the atoms~\cite{Huber2014}.
+This phase determines the location of the sites of the optical lattice.
+We have characterized the phase stability of the optical lattice by recording a long sequence of densely populated images with our imaging camera.
+We found that the phase varies by much less than one lattice site over the course of hours, as seen in Fig.~\ref{fig:averaged_mott}.
 
@@
 
-The position of the atomic cloud, however, is not determined by the phase of the lattice, but by the underlying harmonic confinement.
-In experiments where the entire cloud is addressed by beams auxiliary to the lattice (such as in Refs.~\cite{Choi2016,Mazurenko2017}), drift or fluctuation of the lattice position is important.
+The position of the atomic cloud, however, is not determined by the phase difference of the retro-reflecting lattice beam, but by the underlying harmonic confinement.
+The stability of this confinement is governed by the pointing stability of the optical lattice laser beams.
+In experiments where the entire cloud is addressed by beams auxiliary to the lattice, which can be used for example for enhanced entropy redistribution~\cite{Mazurenko2017}, reducing drifts and fluctuations of the lattice position is important.
 
@@
 
+\FIXME{}: begin Sebastian's version
+{\color{red}
 Variation in external conditions can contaminate large datasets if the prepared state sensitively depends on laser pointing.
@@
 This drift corresponds to an RMS displacement of $\unit{14(3)\times 10^{-3}}{sites / realization}$, compared to a beam waist of $\approx$\unit{80}{\mu{}m} ($\approx$140 sites).
+}
+\FIXME{}: Begin Daniel's version
+{\color{green}
+We characterized the passive stability of the optical lattice by monitoring the position over the course of 250 sequential experimental realizations.
+To analyse the data we decomposed the recorded positions into the transverse $x_t$ and longitudinal $x_l$ components as compared to the optical axis (i.e.
+rotated by $45^\circ$ as compared to the lattice directions $x$ and $y$).
+During this measurement we found that the drift of the atom position is about $1-2$ lattice site, see red data in Fig.~\ref{fig:stability}(e+f).
+For a more in-depth analysis, we also studied the histogram of displacements of atoms between subsequent experimental realizations, see Fig.~\ref{fig:stability}(a).
+This shows a RMS displacement of $0.54(3)$ [$0.98(4)$] sites along the $x_t$ [$x_l$] direction.
+The difference between the displacements is a geometric consequence of the mechanical assembly of the experiment~\cite{Huber2014}.
+The distributions are centered within 1-$\sigma$ of zero along both directions: $-0.03(4)$ and $0.01(5)$ sites for transverse and longitudinal axes, respectively, indicating the absence of strong drift.
+If the trap followed a random walk with these step sizes, the optical assembly would have to be frequently realigned, since after only $100$ experimental shots the trap would move by more than $10$ lattice sites.
+The situation is more fortunate, however, since subsequent steps are correlated, as shown in Fig.~\ref{fig:stability}(b).
+Once this correlation is taken into account, we estimate an RMS drift of \unit{8(1)} [12(2)] {sites/ 1000 realizations} in the transverse [axial] direction, compared to a beam waist of $\approx$140 sites.
+}
 
@@
 
+\FIXME{}: Begin Sebastian's version
+{\color{red}
 In general, we cannot extract the lattice position from the atomic distribution directly, but rely on the monitor camera picture, which is related to the lattice position in the atom plane by an affine transformation, consisting of a rotation, a scaling, and an offset.
@@
 In conclusion: the beam-monitoring camera is sufficiently sensitive to detect lattice misalignments on the order of a few lattice sites, making it useful as a noninvasive check of the lattice position.
+}
+\FIXME{}: Begin Daniel's version
+{\color{green}
+As an additional measure, we have implemented a monitoring system to independently verify appropriate pointing of the lattice laser beams.
+This is particularly useful when performing experiments where imaging the atoms does note allow determining the original center of the atoms in the harmonic trap.
+Additionally, this beam-monitoring system could allow us to eliminate (via post-selection) experimental realizations when the system was in an undesired state -- or designing a feedback loop on the lattice beam pointing to ensure long-term stability.
+A beam-sampler (Thorlabs BSF10-C) reflects a small portion of the beam shortly before it reaches the atoms and images it onto a camera located in the plane corresponding to the atomic system, imaging a Gaussian beam identical to that of the optical lattice.
+Naturally, the position of the atoms is dictated by the light field of both the incoming and retro-reflected beams, while the monitoring camera only observes the position of the in-going beam (this is found to not be a limitation in practice).
+
+As a first step, we calibrated the beam-monitoring system by simultaneously recording the position of the atoms on the imaging camera (Andor iStar) and the lattice beam position on the beam-monitoring camera (Point Grey Chameleon).
+By additionally varying the laser beam position and the lattice anisotropy we were able to obtain a reliable calibration, see Fig.~\ref{fig:stability} (c).
+However, we found that this calibration changes after a short while ($\approx$ 30 shots) and there is an offset between the recordings of the beam-monitoring camera and the atoms camera.
+This is most likely caused by thermal drifts of the beam-monitoring camera housing: the camera heats up by a few $^\circ$C owing to the absence of active cooling.
+This can easily lead to a few $\mu$m drift due to the plastic mounting between the post holder mounted to the optical table and the CCD chip.
+While this could be easily fixed with an improved camera design, we implemented an alternative approach: by recalibrating the offset every 20 shots, this effect can be taken into account.
+After correcting for this changing offset of the beam-monitoring camera, we find very good agreement between the recorded atom position with the imaging camera and the predicted atom position based on the beam-monitoring camera, see Fig.~\ref{fig:stability}(d-f).
+The average $L_1$ displacement between the predicted position and measured position is 0.7~lattice sites.
+The beam-monitoring system is thus sufficiently sensitive to detect lattice misalignments that are on the order of a few lattice sites or more, making it useful as a non-invasive check of the alignment of the experimental apparatus.
+}
 

### 2018-06-21 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
- decided for Sebastian's version of beam-monitoring section - revision of abstract - repositioning of figures for formatting

--- 2018-06-21 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
@@
 The beam intensity is stabilized and controlled with a nonlinear feedback loop.
-Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1.4\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
+%Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1.4\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
+Using real-time monitoring of the resulting optical lattice, we find the stability of the lattice site positions to be well below the lattice spacing for several hours.
+The pointing stability of the optical lattice beams is around one lattice spacing and the long-term (six month) relative stability of the lattice spacing itself is 0.5\% RMS.
 \end{abstract}
@@
   \begin{center}
-    \includegraphics[width=0.85\columnwidth]{Figure1.pdf}
+    \includegraphics[width=0.8\columnwidth]{Figure1.pdf}
     \caption{\textbf{High level overview} showing the major components of the lattice laser feedback system.}\label{fig:high_level}
@@
 
-\begin{figure*}[t]
-  \begin{center}
-    \includegraphics{Figure3.pdf}
-    \caption{\textbf{Optical layout} of the optical lattice system for beam shaping and modulation.}\label{fig:optical_layout}
-  \end{center}
-\end{figure*}
-
-The high optical powers supplied by the fiber amplifiers raise two engineering difficulties:
-\begin{enumerate}
-  \item The fiber amplification process itself is susceptible to many technical noise sources, such as acoustic coupling of the fiber to the environment and electrical design of the amplifier;
-  \item Stimulated Brillouin scattering (SBS) places a hard lower bound on the relative intensity noise (RIN) floor~\cite{Agrawal2013}.
-\end{enumerate}
-
 The NuAmp suffers from several technical problems.
@@
 Further, a high current low-pass filter (MPE DS26387) was added to the high-power supply (Lumina LDD-600-60-10-5VP/M).
+
+The high optical powers supplied by the fiber amplifiers raise two engineering difficulties:
+\begin{enumerate}
+  \item The fiber amplification process itself is susceptible to many technical noise sources, such as acoustic coupling of the fiber to the environment and electrical design of the amplifier;
+  \item Stimulated Brillouin scattering (SBS) places a hard lower bound on the relative intensity noise (RIN) floor~\cite{Agrawal2013}.
+\end{enumerate}
 
@@
   \end{enumerate}
+
+\begin{figure*}[t]
+  \begin{center}
+    \includegraphics{Figure3.pdf}
+    \caption{\textbf{Optical layout} of the optical lattice system for beam shaping and modulation.}\label{fig:optical_layout}
+  \end{center}
+\end{figure*}
 
@@
 
+\begin{figure}
+\begin{center}
+    \includegraphics[width=\columnwidth]{Figure14.pdf}
+    \caption{\textbf{Long term stability over approximately ten months.} The lattice spacings $|\mathrm{v}_x|$ and $|\mathrm{v}_y|$ and the lattice angles $\theta_x$ and $\theta_y$ along the two lattice axes $x$ and $y$ (cf.
+Fig.~\ref{fig:averaged_mott}) are shown over a period of ten months.}\label{fig:long_term_stability}
+  \end{center}
+\end{figure}
+
 For this reason, we developed a procedure to periodically update the affine transform relating the beam-monitoring camera to the atom plane.
@@
 In conclusion: the beam-monitoring camera is sufficiently sensitive to detect lattice misalignments on the order of a few lattice sites, making it useful as a noninvasive check of the lattice position.
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=\columnwidth]{Figure14.pdf}
-    \caption{\textbf{Long term stability over approximately ten months.} The lattice spacings $|\mathrm{v}_x|$ and $|\mathrm{v}_y|$ and the lattice angles $\theta_x$ and $\theta_y$ along the two lattice axes $x$ and $y$ (cf.
-Fig.~\ref{fig:averaged_mott}) are shown over a period of ten months.}\label{fig:long_term_stability}
-  \end{center}
-\end{figure}
 

### 2018-06-24 LatticeOptics/submission_arxiv/latticeoptics.tex
Added arxiv and prapplied submissions

--- 2018-06-21 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
@@
-\documentclass[twocolumn,aps,pra,showpacs,preprintnumbers,bibnotes]{revtex4-1}
+\documentclass[twocolumn,aps,pra,preprintnumbers,bibnotes]{revtex4-1}
 
@@
 \newcommand\unit[2]{\ensuremath{#1~\mathrm{{#2}}}}
-\newcommand\FIXME{{\color{red}\ensuremath{\mathrm{FIXME}}}}
 
@@
 The beam intensity is stabilized and controlled with a nonlinear feedback loop.
-%Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1.4\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
 Using real-time monitoring of the resulting optical lattice, we find the stability of the lattice site positions to be well below the lattice spacing for several hours.
@@
 
-Optical lattices holding arrays of ultracold atoms have become a powerful experimental platform for quantum simulations~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Greif2013, Drewes2016, Murmann2015}.
+Optical lattices holding arrays of ultracold atoms have become a powerful experimental platform for quantum simulations~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Greif2013, Murmann2015, Drewes2017}.
 The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2017} has enabled studies with unprecedented control over individual atoms in many-body systems governed by the Hubbard Hamiltonian~\cite{Hubbard1963}, resulting in extremely low energy scales~\cite{Mazurenko2017, Chiu2018}.
@@
 
-\bibliography{LatticeOpticsV5}
+% \bibliography{latticeoptics}
+
+% merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{34}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Friedenauer}\ \emph {et~al.}(2008)\citenamefont
+  {Friedenauer}, \citenamefont {Schmitz}, \citenamefont {Glueckert},
+  \citenamefont {Porras},\ and\ \citenamefont {Schaetz}}]{Friedenauer2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Friedenauer}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Schmitz}}, \bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
+  {Glueckert}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Porras}}, \
+  and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Schaetz}},\ }\href
+  {\doibase 10.1038/nphys1032} {\bibfield  {journal} {\bibinfo  {journal}
+  {Nature Physics}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {757}
+  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kim}\ \emph {et~al.}(2010)\citenamefont {Kim},
+  \citenamefont {Chang}, \citenamefont {Korenblit}, \citenamefont {Islam},
+  \citenamefont {Edwards}, \citenamefont {Freericks}, \citenamefont {Lin},
+  \citenamefont {Duan},\ and\ \citenamefont {Monroe}}]{Kim2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Kim}}, \bibinfo {author} {\bibfnamefont {M.-S.}\ \bibnamefont {Chang}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Korenblit}}, \bibinfo
+  {author} {\bibfnamefont {R.}~\bibnamefont {Islam}}, \bibinfo {author}
+  {\bibfnamefont {E.~E.}\ \bibnamefont {Edwards}}, \bibinfo {author}
+  {\bibfnamefont {J.~K.}\ \bibnamefont {Freericks}}, \bibinfo {author}
+  {\bibfnamefont {G.-D.}\ \bibnamefont {Lin}}, \bibinfo {author} {\bibfnamefont
+  {L.-M.}\ \bibnamefont {Duan}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Monroe}},\ }\href {\doibase 10.1038/nature09071}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
+  {volume} {465}},\ \bibinfo {pages} {590} (\bibinfo {year}
+  {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Struck}\ \emph {et~al.}(2011)\citenamefont {Struck},
+  \citenamefont {{\"{O}}lschl{\"{a}}ger}, \citenamefont {{Le Targat}},
+  \citenamefont {Soltan-Panahi}, \citenamefont {Eckardt}, \citenamefont
+  {Lewenstein}, \citenamefont {Windpassinger},\ and\ \citenamefont
+  {Sengstock}}]{Struck2011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Struck}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {{\"{O}}lschl{\"{a}}ger}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {{Le Targat}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Soltan-Panahi}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Eckardt}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Lewenstein}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Windpassinger}}, \ and\
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Sengstock}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {333}},\ \bibinfo {pages} {996} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Simon}\ \emph {et~al.}(2011)\citenamefont {Simon},
+  \citenamefont {Bakr}, \citenamefont {Ma}, \citenamefont {Tai}, \citenamefont
+  {Preiss},\ and\ \citenamefont {Greiner}}]{Simon2011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Simon}}, \bibinfo {author} {\bibfnamefont {W.~S.}\ \bibnamefont {Bakr}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ma}}, \bibinfo {author}
+  {\bibfnamefont {M.~E.}\ \bibnamefont {Tai}}, \bibinfo {author} {\bibfnamefont
+  {P.~M.}\ \bibnamefont {Preiss}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1038/nature09994}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
+  {volume} {472}},\ \bibinfo {pages} {307} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yan}\ \emph {et~al.}(2013)\citenamefont {Yan},
+  \citenamefont {Moses}, \citenamefont {Gadway}, \citenamefont {Covey},
+  \citenamefont {Hazzard}, \citenamefont {Rey}, \citenamefont {Jin},\ and\
+  \citenamefont {Ye}}]{Yan2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Yan}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont {Moses}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Gadway}}, \bibinfo
+  {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Covey}}, \bibinfo {author}
+  {\bibfnamefont {K.~R.~A.}\ \bibnamefont {Hazzard}}, \bibinfo {author}
+  {\bibfnamefont {A.~M.}\ \bibnamefont {Rey}}, \bibinfo {author} {\bibfnamefont
+  {D.~S.}\ \bibnamefont {Jin}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Ye}},\ }\href {\doibase 10.1038/nature12483} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {501}},\
+  \bibinfo {pages} {521} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Greif}\ \emph {et~al.}(2013)\citenamefont {Greif},
+  \citenamefont {Uehlinger}, \citenamefont {Jotzu}, \citenamefont {Tarruell},\
+  and\ \citenamefont {Esslinger}}]{Greif2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Greif}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Uehlinger}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Jotzu}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Tarruell}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Esslinger}},\ }\href {\doibase
+  10.1126/science.1236362} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {340}},\ \bibinfo {pages} {1307}
+  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Murmann}\ \emph {et~al.}(2015)\citenamefont
+  {Murmann}, \citenamefont {Deuretzbacher}, \citenamefont {Z{\"{u}}rn},
+  \citenamefont {Bjerlin}, \citenamefont {Reimann}, \citenamefont {Santos},
+  \citenamefont {Lompe},\ and\ \citenamefont {Jochim}}]{Murmann2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Murmann}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Deuretzbacher}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Z{\"{u}}rn}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Bjerlin}},
+  \bibinfo {author} {\bibfnamefont {S.~M.}\ \bibnamefont {Reimann}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Santos}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Lompe}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Jochim}},\ }\href {\doibase
+  10.1103/PhysRevLett.115.215301} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {115}},\ \bibinfo {pages}
+  {215301} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Drewes}\ \emph {et~al.}(2017)\citenamefont {Drewes},
+  \citenamefont {Miller}, \citenamefont {Cocchi}, \citenamefont {Chan},
+  \citenamefont {Wurz}, \citenamefont {Gall}, \citenamefont {Pertot},
+  \citenamefont {Brennecke},\ and\ \citenamefont {K{\"{o}}hl}}]{Drewes2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
+  {Drewes}}, \bibinfo {author} {\bibfnamefont {L.~A.}\ \bibnamefont {Miller}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Cocchi}}, \bibinfo
+  {author} {\bibfnamefont {C.~F.}\ \bibnamefont {Chan}}, \bibinfo {author}
+  {\bibfnamefont {N.}~\bibnamefont {Wurz}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Gall}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Pertot}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Brennecke}}, \
+  and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {K{\"{o}}hl}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
+  }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {170401} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bakr}\ \emph {et~al.}(2009)\citenamefont {Bakr},
+  \citenamefont {Gillen}, \citenamefont {Peng}, \citenamefont {F{\"{o}}lling},\
+  and\ \citenamefont {Greiner}}]{Bakr2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~S.}\ \bibnamefont
+  {Bakr}}, \bibinfo {author} {\bibfnamefont {J.~I.}\ \bibnamefont {Gillen}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Peng}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {F{\"{o}}lling}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
+  10.1038/nature08482} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\
+  }\textbf {\bibinfo {volume} {462}},\ \bibinfo {pages} {74} (\bibinfo {year}
+  {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sherson}\ \emph {et~al.}(2010)\citenamefont
+  {Sherson}, \citenamefont {Weitenberg}, \citenamefont {Endres}, \citenamefont
+  {Cheneau}, \citenamefont {Bloch},\ and\ \citenamefont {Kuhr}}]{Sherson2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
+  {Sherson}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Weitenberg}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Endres}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Cheneau}}, \bibinfo {author}
+  {\bibfnamefont {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Kuhr}},\ }\href {\doibase
+  10.1038/nature09378} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\
+  }\textbf {\bibinfo {volume} {467}},\ \bibinfo {pages} {68} (\bibinfo {year}
+  {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Haller}\ \emph {et~al.}(2015)\citenamefont {Haller},
+  \citenamefont {Hudson}, \citenamefont {Kelly}, \citenamefont {Cotta},
+  \citenamefont {Peaudecerf}, \citenamefont {Bruce},\ and\ \citenamefont
+  {Kuhr}}]{Haller2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Haller}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Hudson}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kelly}}, \bibinfo
+  {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Cotta}}, \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Peaudecerf}}, \bibinfo {author}
+  {\bibfnamefont {G.~D.}\ \bibnamefont {Bruce}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Kuhr}},\ }\href {\doibase
+  10.1038/nphys3403} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Physics}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages} {738}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cheuk}\ \emph {et~al.}(2015)\citenamefont {Cheuk},
+  \citenamefont {Nichols}, \citenamefont {Okan}, \citenamefont {Gersdorf},
+  \citenamefont {Ramasesh}, \citenamefont {Bakr}, \citenamefont {Lompe},\ and\
+  \citenamefont {Zwierlein}}]{Cheuk2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
+  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Gersdorf}}, \bibinfo {author}
+  {\bibfnamefont {V.~V.}\ \bibnamefont {Ramasesh}}, \bibinfo {author}
+  {\bibfnamefont {W.~S.}\ \bibnamefont {Bakr}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Lompe}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.~W.}\ \bibnamefont {Zwierlein}},\ }\href {\doibase
+  10.1103/PhysRevLett.114.193001} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
+  {193001} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parsons}\ \emph {et~al.}(2015)\citenamefont
+  {Parsons}, \citenamefont {Huber}, \citenamefont {Mazurenko}, \citenamefont
+  {Chiu}, \citenamefont {Setiawan}, \citenamefont {Wooley-Brown}, \citenamefont
+  {Blatt},\ and\ \citenamefont {Greiner}}]{Parsons2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont
+  {Parsons}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Huber}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo
+  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Setiawan}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Wooley-Brown}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Blatt}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
+  10.1103/PhysRevLett.114.213002} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
+  {213002} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Edge}\ \emph {et~al.}(2015)\citenamefont {Edge},
+  \citenamefont {Anderson}, \citenamefont {Jervis}, \citenamefont {McKay},
+  \citenamefont {Day}, \citenamefont {Trotzky},\ and\ \citenamefont
+  {Thywissen}}]{Edge2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~J.~A.}\
+  \bibnamefont {Edge}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Anderson}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Jervis}},
+  \bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont {McKay}}, \bibinfo
+  {author} {\bibfnamefont {R.}~\bibnamefont {Day}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Trotzky}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.~H.}\ \bibnamefont {Thywissen}},\ }\href {\doibase
+  10.1103/PhysRevA.92.063406} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. A}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages} {063406}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Omran}\ \emph {et~al.}(2015)\citenamefont {Omran},
+  \citenamefont {Boll}, \citenamefont {Hilker}, \citenamefont {Kleinlein},
+  \citenamefont {Salomon}, \citenamefont {Bloch},\ and\ \citenamefont
+  {Gross}}]{Omran2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Omran}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Boll}},
+  \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Hilker}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Kleinlein}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Salomon}}, \bibinfo {author} {\bibfnamefont
+  {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Gross}},\ }\href {\doibase 10.1103/PhysRevLett.115.263001}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {115}},\ \bibinfo {pages} {263001} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Greif}\ \emph {et~al.}(2016)\citenamefont {Greif},
+  \citenamefont {Parsons}, \citenamefont {Mazurenko}, \citenamefont {Chiu},
+  \citenamefont {Blatt}, \citenamefont {Huber}, \citenamefont {Ji},\ and\
+  \citenamefont {Greiner}}]{Greif2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Greif}}, \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo
+  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Blatt}}, \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Huber}}, \bibinfo {author} {\bibfnamefont
+  {G.}~\bibnamefont {Ji}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1126/science.aad9041}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {351}},\ \bibinfo {pages} {953} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cheuk}\ \emph
+  {et~al.}(2016{\natexlab{a}})\citenamefont {Cheuk}, \citenamefont {Nichols},
+  \citenamefont {Lawrence}, \citenamefont {Okan}, \citenamefont {Zhang},\ and\
+  \citenamefont {Zwierlein}}]{Cheuk2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
+  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
+  \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont {Lawrence}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Zhang}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.~W.}\ \bibnamefont {Zwierlein}},\ }\href
+  {https://journals.aps.org/prl/pdf/10.1103/PhysRevLett.116.235301} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett}\ }\textbf {\bibinfo {volume}
+  {116}},\ \bibinfo {pages} {235301} (\bibinfo {year}
+  {2016}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parsons}\ \emph {et~al.}(2016)\citenamefont
+  {Parsons}, \citenamefont {Mazurenko}, \citenamefont {Chiu}, \citenamefont
+  {Ji}, \citenamefont {Greif},\ and\ \citenamefont {Greiner}}]{Parsons2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont
+  {Parsons}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}},
+  \bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo
+  {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
+  10.1126/science.aag1430} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {353}},\ \bibinfo {pages} {1253}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Boll}\ \emph {et~al.}(2016)\citenamefont {Boll},
+  \citenamefont {Hilker}, \citenamefont {Salomon}, \citenamefont {Omran},
+  \citenamefont {Nespolo}, \citenamefont {Pollet}, \citenamefont {Bloch},\ and\
+  \citenamefont {Gross}}]{Boll2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Boll}}, \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Hilker}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Salomon}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Omran}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Nespolo}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Pollet}}, \bibinfo {author} {\bibfnamefont
+  {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Gross}},\ }\href {\doibase 10.1126/science.aag1635}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {353}},\ \bibinfo {pages} {1257} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cheuk}\ \emph
+  {et~al.}(2016{\natexlab{b}})\citenamefont {Cheuk}, \citenamefont {Nichols},
+  \citenamefont {Lawrence}, \citenamefont {Okan}, \citenamefont {Zhang},
+  \citenamefont {Khatami}, \citenamefont {Trivedi}, \citenamefont {Paiva},
+  \citenamefont {Rigol},\ and\ \citenamefont {Zwierlein}}]{Cheuk2016a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
+  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
+  \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont {Lawrence}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Khatami}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Trivedi}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Paiva}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Rigol}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~W.}\
+  \bibnamefont {Zwierlein}},\ }\href {\doibase 10.1126/science.aag3349}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {353}},\ \bibinfo {pages} {1260} (\bibinfo {year}
+  {2016}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Brown}\ \emph {et~al.}(2017)\citenamefont {Brown},
+  \citenamefont {Mitra}, \citenamefont {Guardado-Sanchez}, \citenamefont
+  {Schau{\ss}}, \citenamefont {Kondov}, \citenamefont {Khatami}, \citenamefont
+  {Paiva}, \citenamefont {Trivedi}, \citenamefont {Huse},\ and\ \citenamefont
+  {Bakr}}]{Brown2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~T.}\ \bibnamefont
+  {Brown}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Mitra}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Guardado-Sanchez}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Schau{\ss}}}, \bibinfo
+  {author} {\bibfnamefont {S.~S.}\ \bibnamefont {Kondov}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Khatami}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Paiva}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Trivedi}}, \bibinfo {author} {\bibfnamefont {D.~A.}\
+  \bibnamefont {Huse}}, \ and\ \bibinfo {author} {\bibfnamefont {W.~S.}\
+  \bibnamefont {Bakr}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Science}\ }\textbf {\bibinfo {volume} {357}},\ \bibinfo {pages}
+  {1385} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hubbard}(1963)}]{Hubbard1963}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Hubbard}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Proc.
+  Roy. Soc. A: Mathematical, Physical and Engineering Sciences}\ }\textbf
+  {\bibinfo {volume} {276}},\ \bibinfo {pages} {238} (\bibinfo {year}
+  {1963})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mazurenko}\ \emph {et~al.}(2017)\citenamefont
+  {Mazurenko}, \citenamefont {Chiu}, \citenamefont {Ji}, \citenamefont
+  {Parsons}, \citenamefont {Kan{\'{a}}sz-Nagy}, \citenamefont {Schmidt},
+  \citenamefont {Grusdt}, \citenamefont {Demler}, \citenamefont {Greif},\ and\
+  \citenamefont {Greiner}}]{Mazurenko2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Mazurenko}}, \bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo {author}
+  {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Kan{\'{a}}sz-Nagy}}, \bibinfo {author}
+  {\bibfnamefont {R.}~\bibnamefont {Schmidt}}, \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Grusdt}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Demler}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1038/nature22362}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
+  {volume} {545}},\ \bibinfo {pages} {462} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chiu}\ \emph {et~al.}(2018)\citenamefont {Chiu},
+  \citenamefont {Ji}, \citenamefont {Mazurenko}, \citenamefont {Greif},\ and\
+  \citenamefont {Greiner}}]{Chiu2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont
+  {Chiu}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {120}},\ \bibinfo {pages} {243201} (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Blatt}\ \emph {et~al.}(2015)\citenamefont {Blatt},
+  \citenamefont {Mazurenko}, \citenamefont {Parsons}, \citenamefont {Chiu},
+  \citenamefont {Huber},\ and\ \citenamefont {Greiner}}]{Blatt2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Blatt}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}},
+  \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}}, \bibinfo
+  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
+  {\bibfnamefont {F.}~\bibnamefont {Huber}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
+  10.1103/PhysRevA.92.021402} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review A}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages}
+  {021402(R)} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Preiss}\ \emph {et~al.}(2015)\citenamefont {Preiss},
+  \citenamefont {Ma}, \citenamefont {Tai}, \citenamefont {Lukin}, \citenamefont
+  {Rispoli}, \citenamefont {Zupancic}, \citenamefont {Lahini}, \citenamefont
+  {Islam},\ and\ \citenamefont {Greiner}}]{Preiss2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
+  {Preiss}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ma}}, \bibinfo
+  {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Tai}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Lukin}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Rispoli}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Zupancic}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Lahini}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Islam}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Greiner}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+   {journal} {Science}\ }\textbf {\bibinfo {volume} {347}} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Choi}\ \emph {et~al.}(2016)\citenamefont {Choi},
+  \citenamefont {Hild}, \citenamefont {Zeiher}, \citenamefont {Schau{\ss}},
+  \citenamefont {Rubio-Abadal}, \citenamefont {Yefsah}, \citenamefont
+  {Khemani}, \citenamefont {Huse}, \citenamefont {Bloch},\ and\ \citenamefont
+  {Gross}}]{Choi2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-Y.}\ \bibnamefont
+  {Choi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Hild}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Zeiher}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Schau{\ss}}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Rubio-Abadal}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Yefsah}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Khemani}}, \bibinfo {author} {\bibfnamefont {D.~A.}\
+  \bibnamefont {Huse}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Gross}},\ }\href {http://science.sciencemag.org/content/352/6293/1547}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {352}},\ \bibinfo {pages} {1547} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huber}(2014)}]{Huber2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Huber}},\ }\emph {\bibinfo {title} {{Site-Resolved Imaging with the Fermi
+  Gas Microscope}}},\ \href@noop {} {Ph.D. thesis},\ \bibinfo  {school}
+  {Harvard University} (\bibinfo {year} {2014})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Agrawal}(2013)}]{Agrawal2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Agrawal}},\ }\href@noop {} {\emph {\bibinfo {title} {{Nonlinear Fiber
+  Optics}}}},\ \bibinfo {edition} {5th}\ ed.\ (\bibinfo  {publisher} {Academic
+  Press},\ \bibinfo {year} {2013})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yoshida}\ \emph {et~al.}(1999)\citenamefont
+  {Yoshida}, \citenamefont {Gorlenko}, \citenamefont {Tanner}, \citenamefont
+  {Reitze}, \citenamefont {Mansell}, \citenamefont {Khazanov},\ and\
+  \citenamefont {Kulagin}}]{Yoshida1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Yoshida}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gorlenko}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Tanner}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Reitze}}, \bibinfo {author}
+  {\bibfnamefont {J.~D.}\ \bibnamefont {Mansell}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Khazanov}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Kulagin}},\ }\href
+  {http://www.phys.ufl.edu/{~}tanner/PDFS/Yoshida99spie-ComponentsLIGO-abs.pdf}
+  {\bibfield  {journal} {\bibinfo  {journal} {SPIE}\ }\textbf {\bibinfo
+  {volume} {3736}},\ \bibinfo {pages} {430} (\bibinfo {year}
+  {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bechhoefer}(2005)}]{Bechhoefer2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Bechhoefer}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo {pages} {783}
+  (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Graeme}(1995)}]{Graeme1995}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Graeme}},\ }\href@noop {} {\emph {\bibinfo {title} {{Photodiode
+  Amplifiers}}}}\ (\bibinfo  {publisher} {McGraw Hill},\ \bibinfo {year}
+  {1995})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Skogestad}(2003)}]{Skogestad2003}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Skogestad}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Process Control}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {291}
+  (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Horowitz}\ and\ \citenamefont
+  {Hill}(2015)}]{Horowitz2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Horowitz}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Hill}},\ }\href@noop {} {\emph {\bibinfo {title} {{The Art of
+  Electronics}}}},\ \bibinfo {edition} {3rd}\ ed.\ (\bibinfo  {publisher}
+  {Cambridge University Press},\ \bibinfo {address} {New York},\ \bibinfo
+  {year} {2015})\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2018-09-25 LatticeOptics/submission_rev_sci_inst/latticeoptics.tex
rev sci inst submission reviewer 1 addressed

--- 2018-06-24 LatticeOptics/submission_arxiv/latticeoptics.tex
@@
 (b) Shows the open-loop and closed-loop behavior of the high-power feedback loop using the  modified fiber amplifiers, as described in the main text.
-(c) Shows the open-loop behavior of the low-power feedback loop using the modified fiber amplifiers, including an additional low-pass filtering stage to limit the loop bandwidth.
+(c) Shows the open-loop behavior of the low-power feedback loop using the modified fiber amplifiers, including an additional low-pass filtering stage to limit the loop bandwidth at various constant powers.
 (d) Closed-loop behavior of the low-power feedback loop without additional low-pass filtering, measured on the same setup as panel (c).}\label{fig:noises}
@@
 Worse yet, it is suspected of causing ground loops which add noise and interference to the analog systems.
-This added noise can be seen in Fig.~\ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser.
+This added noise can be seen in Fig.~\ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser, particularly near \unit{10}{kHz}.
 We solve this problem by replacing the USB control board with a custom-designed solution  that is compatible with our laboratory control system and engineered to avoid ground loops.
@@
 The beam is collimated using an $f=\unit{20}{mm}$ fused-silica, air-spaced triplet collimator (Opto-Sigma HFTLSQ-15-20PF1) angled with respect to and centered on the angle-cleaved fiber tip.
-The polarization is set using an IBS coated thin-film plate polarizer (Precision photonics PO1056-FY), which has the added benefit of rejecting the undesired cladding modes of the fiber, which carry about \unit{1}{W} of light.
+The polarization is set using an IBS coated thin-film plate polarizer (Precision photonics PO1056-FY), with the added benefit of rejecting the undesired cladding modes of the fiber, which carry about \unit{1}{W} of light.
+A thin-film polarizer was used to minimize the number of normal and backreflecting surfaces near the output of the fiber in addition to providing excellent polarization performance.
 The fact that the lattice is retro-reflected, combined with the observation that optical isolation falls with applied optical power~\cite{Yoshida1999} means that two stages of optical isolators must be used.
@@
 
-After the isolation stage, we use the sequence of optical elements shown in Fig.~\ref{fig:optical_layout}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs GVS002, or Camtech 8320K, depending on the beam path) half-wave plate, and polarizer.
+After the isolation stage, we use the sequence of optical elements shown in Fig.~\ref{fig:optical_layout}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs GVS002, or Camtech 8320K, depending on the beam path), half-wave plate, and polarizer.
 The Berek compensator is a $z$-cut quartz plate anti-reflection-coated at \unit{1064}{nm}.
@@
 This Berek compensator based feedback loop is used to vary the beam intensity at relatively high power.
-(a) Shows the small signal impulse response and (b-c) show the corresponding Bode plots of the transfer function $G$.}\label{fig:berek_step_response}
+(a) Shows the small signal impulse response of the feedback loop (step size of $\approx 2$ W) and (b-c) show the corresponding Bode plots of the closed loop transfer function $G$.}\label{fig:berek_step_response}
   \end{center}
@@
 A key point, as seen in Fig.~\ref{fig:berek}, is that if the waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
-The waveplates are detuned such that the maximum power needed in \emph{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator.
+The waveplates are detuned such that the maximum power needed in \emph{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator, since the slope of transmission with respect to the Berek angle is $0$ at this point.
 Naturally, rotation of a parallel plate in the beam path induces a shift of the beam, but this is acceptable because the Berek compensator is only active during the imaging phase of the experiment, when the position of the underlying harmonic trap is largely irrelevant.
@@
 Because two feedback loops are present in the system (the second one detailed in the next section), care must be taken so that they do not function simultaneously.
-To accomplish this, the low-power loop is always manually railed to its high extreme when the high-power loop is active, and the digital high-power loop is disabled when the low-power loop is active.
+To accomplish this, the low-power loop is always manually railed to its high extreme when the high-power loop is active.
+This is done by shuttering the photodiode and directing the set-point to a high value, which quickly winds up the integrator to its maximum output.
+The digital high-power loop is disabled in software when the low-power loop is active.
 
@@
 The connection between the actuation and monitoring mechanisms of the feedback system is the loop filter, which compares the \emph{set-point} signal, $V_\mathrm{SP}(t)$, supplied by the experimental control system and the photodiode signals $V_\mathrm{PD}(t)$, to adjust the actuation accordingly.
-We use a simple, purely integrating design based in three stages, as seen in Fig.~\ref{fig:circuits}(c), based on a low-noise op-amp (Texas Instruments OPA211).
+We use a simple, purely integrating design in three stages, as seen in Fig.~\ref{fig:circuits}(c), based on a low-noise op-amp (Texas Instruments OPA211).
 The first stage computes and amplifies an error signal, $e(t)=V_\mathrm{SP}(t)-V_\mathrm{PD}(t)$, which is integrated by the second stage.
@@
 In effect, if the rest of the feedback system was linear, this would correspond to a quadratically increasing gain until the AOM is saturated, which could lead to slow behavior at low signal levels and ringing at higher signal levels.
-Even worse, since the mixer is insensitive to the sign of the voltage applied, the gain is becomes negative for negative voltages, resulting in an unstable system.
+Even worse, since the mixer is insensitive to the sign of the voltage applied, the gain is negative for negative voltages, resulting in an unstable system.
 
@@
 For these reasons, each lattice axis is fitted with a remotely actuated mirror, controlled by the experimental control software over the lab network, allowing for non-invasive, digital alignment of the system.
-The remote actuators are ``Picomotors'' (Newport 8302), fitted into a customized \unit{2}{inch} mirror mounts.
+The remote actuators are ``Picomotors'' (Newport 8302), fitted into customized \unit{2}{inch} mirror mounts.
 They work in a ``fire-and-forget'' manner, remaining passively stable when not in active use.
@@
 
-In our experiments, the position of the Gaussian beam envelope of the optical lattice is impossible to determine from the site-resolved image of the atoms, because the atoms may not occupy the central part of the envelope depending on the specefics of the lattice loading procedure.
+In our experiments, the position of the Gaussian beam envelope of the optical lattice is impossible to determine from the site-resolved image of the atoms, because the atoms may not occupy the central part of the envelope depending on the specifics of the lattice loading procedure.
 In addition, the atomic distributions are governed by the sum of the incident lattices and thus cannot be used to reliably infer the degree of overlap between the lattice beams.
@@
 For this reason, we developed a procedure to periodically update the affine transform relating the beam-monitoring camera to the atom plane.
-We test this procedure, we analyze the data set of monitoring-camera measurements and atomic positions (shown in Fig.~\ref{fig:stability}) in the following way: we split the data set into sequential blocks of 20 shots, each followed by a block of 8 shots.
+To test this procedure, we analyze the data set of monitoring-camera measurements and atomic positions (shown in Fig.~\ref{fig:stability}) in the following way: we split the data set into sequential blocks of 20 shots, each followed by a block of 8 shots.
 We try to predict the larger blocks, by analyzing the smaller blocks to derive the updates to the affine transform.
@@
 The average taxicab distance between the predicted position and the measured position is 0.7~lattice sites.
+This result shows that recalibrating the affine transformation every 20 shots bounds the tracking error to an acceptable level.
+In practical applications, larger blocks of shots containing scientific measurements are interleaved with small recalibration blocks.
 

### 2018-09-30 LatticeOptics/submission_rev_sci_inst/latticeoptics.tex
reviewer2 specific comments

@@
 In the last two sections we conduct a performance analysis of the short- and long-term stability of the optical lattices produced by this system.
+Naturally, the laser system presented here is tailored to suit the experiment's specific lattice geometry~\cite{Huber2014} and exact requirements. 
+However, we expect that the technical upgrades, design practices and engineering choices will be widely applicable to experimentalists working with performant optical lattices.
 
@@
 Such trap frequencies may only be attained using tightly focused, high-power beams.
-In practical terms, this requires approximately \unit{20}{W} per lattice axis for a beam waist of around $80 \mu\mathrm{m}$ and the four-fold enhancement in optical depth provided by the reflection from the superpolished substrate.
+In practical terms, this requires approximately \unit{20}{W} per lattice axis for a beam waist of around $80 \mu\mathrm{m}$ and the four-fold enhancement in optical depth provided by the reflection from the superpolished substrate~\cite{Huber2014}.
 We achieve such high laser powers using Yb-doped fiber amplifiers (Nufern NuAmp SUB1174-34).
@@
 
-The high optical powers supplied by the fiber amplifiers raise two engineering difficulties:
-\begin{enumerate}
-  \item The fiber amplification process itself is susceptible to many technical noise sources, such as acoustic coupling of the fiber to the environment and electrical design of the amplifier;
-  \item Stimulated Brillouin scattering (SBS) places a hard lower bound on the relative intensity noise (RIN) floor~\cite{Agrawal2013}.
-\end{enumerate}
-
 These upgrades serve to suppress many of the noise spurs measured in the fiber amplifier RIN.
@@
 This is not the case for certain older batches, where the spur is approximately \unit{30}{dB} above the background.
+
+The high optical powers supplied by the fiber amplifiers raise two engineering difficulties:
+\begin{enumerate}
+  \item The fiber amplification process itself is susceptible to many technical noise sources, such as acoustic coupling of the fiber to the environment and electrical design of the amplifier;
+  \item Stimulated Brillouin scattering (SBS) places a hard lower bound on the relative intensity noise (RIN) floor~\cite{Agrawal2013}.
+\end{enumerate}
 
@@
 
-We need to maintain the relatively low phase-noise characteristics of the VCO to prevent phase- to amplitude-noise conversion in the AOM, which partially downconverts the VCO phase noise to RIN at acoustic frequencies.
+%We need to maintain the relatively low phase-noise characteristics of the VCO to prevent phase- to amplitude-noise conversion in the AOM, which partially downconverts the VCO phase noise to RIN at acoustic frequencies.
+This device allows us to drive the AOM with a single, clean tone.
 The spectrum and relative intensity noise of the PLL can be found in Fig.~\ref{fig:pll}.
@@
 An ideal device would have a bandwidth up to approximately \unit{3}{MHz} (since trap frequencies in the system are \unit{1.5}{MHz}), with a noise floor below approximately \unit{-150}{dBc/Hz} over that range~\cite{Blatt2015}.
-To approach these specifications, we use a custom-designed PCB that implements a simple transimpedance amplifier~\cite{Graeme1995} in a convenient physical package, providing a bandwidths in the \unit{0.1-10}{MHz} range, depending on the transimpedance gain set by a resistor.
+To approach these specifications, we use a custom-designed PCB that implements a simple transimpedance amplifier~\cite{Graeme1995} in a convenient physical package, providing bandwidths in the \unit{0.1-10}{MHz} range, depending on the transimpedance gain set by a resistor.
 The photodiode can be safely operated up to incident powers of approximately \unit{10}{mW}, which sets a \unit{-164}{dBc/Hz} shot noise limit on the RIN that can be detected.
@@
 The connection between the actuation and monitoring mechanisms of the feedback system is the loop filter, which compares the \emph{set-point} signal, $V_\mathrm{SP}(t)$, supplied by the experimental control system and the photodiode signals $V_\mathrm{PD}(t)$, to adjust the actuation accordingly.
-We use a simple, purely integrating design in three stages, as seen in Fig.~\ref{fig:circuits}(c), based on a low-noise op-amp (Texas Instruments OPA211).
+We use a simple, primarily integrating design in three stages, as seen in Fig.~\ref{fig:circuits}(c), based on a low-noise op-amp (Texas Instruments OPA211).
 The first stage computes and amplifies an error signal, $e(t)=V_\mathrm{SP}(t)-V_\mathrm{PD}(t)$, which is integrated by the second stage.
@@
 
-Several applications require the positions of lattice sites to not change by more than a small fraction ($\approx 10\%$) between experimental shots.
+Several applications require the positions of lattice sites to not change by more than a small fraction ($\approx 10\%$ of the lattice constant) between experimental shots.
 In our setup this is ensured by careful design of the optical assembly, where the phase of the retro-reflected lattice is set by the retro-reflecting mirror, which is placed approximately \unit{5}{cm} from the atoms~\cite{Huber2014}.
@@
 Several interesting features can be seen from the observed behavior.
-In the first few months the lattice spacing changed by around 10\%.
-Experimentally, this drift was accompanied by the necessity of refocussing the imaging system.
+In the first few months the apparent lattice spacing (as imaged through the microscope) changed by around 10\%.
+Experimentally, this drift was accompanied by the necessity of refocusing the imaging system.
 The sudden jump in September 2016 was caused by a simplification of the imaging system.
-Afterwards, the lattice spacing seemed more stable (fractional changes of $\leq 0.005$).
+Afterwards, the lattice spacing seemed more stable (fractional changes of $\leq 0.005$ and limited by the imaging system magnification drift).
 Unlike the lattice spacing, the angle is observed to be mostly unaffected and remains very stable (for example, an RMS of 0.06$^\circ$ in Spring 2017).

### 2018-10-13 LatticeOptics/submission_rev_sci_inst/latticeoptics.tex
referee reviews

@@
 The beam intensity is stabilized and controlled with a nonlinear feedback loop.
-Using real-time monitoring of the resulting optical lattice, we find the stability of the lattice site positions to be well below the lattice spacing for several hours.
+Using real-time monitoring of the resulting optical lattice, we find the stability of the lattice site positions to be well below the lattice spacing over the course of hours.
 The pointing stability of the optical lattice beams is around one lattice spacing and the long-term (six month) relative stability of the lattice spacing itself is 0.5\% RMS.
@@
 The architecture of the system, shown in Fig.~\ref{fig:high_level}, is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Blatt2015,Parsons2016}).
-These amplifiers generate enough light to perform site resolved imaging~\cite{Parsons2015}, but also substantially increase the level of intensity and pointing noise.
+These amplifiers generate sufficient light to perform site resolved imaging~\cite{Parsons2015}, but also substantially increase the level of intensity and pointing noise.
 The fiber amplifier output is controlled by two feedback loops, which stabilize the light in low power and high power regimes, respectively, as discussed later.
 After intensity stabilization, the laser beam is mode-shaped to a desired waist.
-The optical system is engineered to be passively stable in terms of pointing, but the position and phase of the optical lattice are monitored in real time, and beam pointing can be controlled with remotely actuated mirrors.
+The optical system is engineered to be passively stable in terms of pointing, but the position and phase of the optical lattice are monitored in real time and beam pointing can be controlled with remotely actuated mirrors.
 
@@
 Naturally, the laser system presented here is tailored to suit the experiment's specific lattice geometry~\cite{Huber2014} and exact requirements. 
-However, we expect that the technical upgrades, design practices and engineering choices will be widely applicable to experimentalists working with performant optical lattices.
+We expect, however, that both the specific engineering choices and the general design practices detailed in this work will be widely applicable to experimentalists working with performant optical lattices used for a variety of purposes.
 
@@
 \subsection{Seed laser system}
-The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately \unit{2}{W} of \unit{1064}{nm} light.
+The lattice laser system is seeded by an Innolight Mephisto laser providing approximately \unit{2}{W} of \unit{1064}{nm} light.
 This commercial laser uses a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability.
@@
 It is controlled via a USB interface, which complicates communications with an array of these devices.
-Worse yet, it is suspected of causing ground loops which add noise and interference to the analog systems.
+Worse yet, the digital control system is suspected of causing ground loops that add noise and interference to the analog systems.
 This added noise can be seen in Fig.~\ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser, particularly near \unit{10}{kHz}.
@@
 Despite the presence of a water-cooled cold-plate for the gain fiber and pump diodes, the high power supply is air cooled by an internal fan with variable frequency.
-This fan adds noise at acoustic frequencies and degrades pointing stability by increasing vibrations on the output fiber tip.
+This fan adds noise at acoustic frequencies and degrades pointing stability by increasing vibration of the output fiber tip.
 To reduce acoustic coupling and reduce switching power supply noise, both power supplies were removed from the fiber amplifier chassis, and the low-power supply was replaced by a linear power supply (Acopian A24MT350M).
@@
 We tune the water temperature such that the average power supplied by the amplifiers supplying the $X$ and $Y$ lattices is optimized, while simultaneously keeping all reported amplifier temperatures below \unit{30}{^\circ{}C}, as recommended by a Nufern support engineer.
-Experimentally, we have found that more power can be gained by running the amplifiers at even hotter temperatures.
+Experimentally, we have found that more power can be gained by running the amplifiers at even hotter temperatures, possibly at the expense of a shortened lifetime.
 
@@
 \begin{enumerate}
-\item The lattice power must be continuously tunable from around \unit{10}{\mu{}W} to around \unit{20}{W}, corresponding to lattice depths in the approximate range of $10^-3$ to $2 \times 10^3 E_R$, where $E_R$ is the geometric recoil energy corresponding to the lattice spacing~\cite{Blatt2015}.
+\item The lattice power must be continuously tunable from around \unit{10}{\mu{}W} to around \unit{20}{W}, corresponding to lattice depths in the approximate range of $10^{-3}$ to $2 \times 10^3 E_R$, where $E_R$ is the geometric recoil energy corresponding to the lattice spacing~\cite{Blatt2015}.
 \item The location of the minimum Gaussian beam waist must be accurately positioned to overlap the other lattices and dipole traps present in the experiment, and must remain aligned for the duration of the data collection process (hours to days).
@@
 Naturally, rotation of a parallel plate in the beam path induces a shift of the beam, but this is acceptable because the Berek compensator is only active during the imaging phase of the experiment, when the position of the underlying harmonic trap is largely irrelevant.
-Fortunately, the spatial phase of the optical lattice is set by the retro-reflector mirror, which does not move, and is not affected by the rotation of the Berek compensator.
+The spatial phase of the optical lattice is set by the retro-reflector mirror, which does not move, and is not affected by the rotation of the Berek compensator.
 This system functions as the actuator arm of a digital feedback loop, where the power of the beam is measured using a low noise photodiode.
@@
 The step response and corresponding Bode plots~\cite{Bechhoefer2005} are shown in Fig.~\ref{fig:berek_step_response}.
-A polarization rotation by $2 \pi$ is produced by approximately $3^\circ$ of axial rotation of the quartz plate.
+A polarization rotation of $2 \pi$ is produced by approximately $3^\circ$ of axial rotation of the quartz plate.
 Since we never need to rotate the plate outside this range, the position is constrained to this window in software.
@@
 This is done by shuttering the photodiode and directing the set-point to a high value, which quickly winds up the integrator to its maximum output.
-The digital high-power loop is disabled in software when the low-power loop is active.
+Conversely, the digital high-power loop is disabled in software when the low-power loop is active.
 
@@
 The high-power feedback used in the \emph{imaging} phase of the experiment is exceedingly robust because the heating rate from scattered resonant imaging light far exceeds any technical heating from the loop~\cite{Blatt2015}.
-Even if the loop was exceedingly noisy, the heating would be entirely compensated by the simultaneous Raman cooling~\cite{Parsons2015}.
+Even if the loop was noisy, the heating would be entirely compensated by the simultaneous Raman cooling~\cite{Parsons2015}.
 
@@
 \begin{enumerate}
-  \item Its effect on the RIN can limit the system temperature.
-  \item It can affect the pointing.
+  \item Its effect on the RIN can limit the system temperature and set heating rate. This can limit the amount of time available for atom interaction~\cite{Blatt2015}. 
+  \item It needs to avoid varying the the beam pointing because the trap position matters during this phase of the experiment.
   \item It must have closed-loop bandwidths of $\geq\unit{1}{kHz}$, and open-loop modulation bandwidths $\geq \unit{100}{kHz}$.
@@
 The local oscillator (LO) RF source is a custom-built printed circuit board (PCB), schematically shown in Fig.~\ref{fig:circuits}(b), that implements a phase locked loop (PLL) based on the ADF4002 IC and a low-phase-noise voltage-controlled oscillator (VCO, Crystek CVCO55CL-0060-0110), preamplified with a low-noise amplifier (Minicircuits PSA4-5043+).
-To ensure frequency stability (which translates directly into beam pointing of the laser), the PLL is locked to the \unit{10}{MHz} frequency reference distributed around the lab.
+%To ensure frequency stability (which translates directly into beam pointing of the laser), the PLL is locked to the \unit{10}{MHz} frequency reference distributed around the lab.
+The PLL is locked to the \unit{10}{MHz} frequency reference distributed around the lab to ensure absolute frequency stability.
 In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total isolation exceeding \unit{90}{dB}.
@@
 The spectrum and relative intensity noise of the PLL can be found in Fig.~\ref{fig:pll}.
-Vitally, the spectrum of the PLL exhibits phase noise comparable to that of a typical VCO, without the slow frequency drift characteristic to these devices.
-Elimination of the carrier drift is worth the added phase noise, however, because any drift of the frequency affects the pointing of the laser beam passing through the AOM, which would misalign the optical lattice.
+Vitally, the spectrum of the PLL exhibits phase noise comparable to that of a typical VCO but without the slow frequency drift characteristic to these devices.
+Elimination of the carrier drift is worth the added phase noise because any drift of the frequency affects the pointing of the laser beam passing through the AOM, which would misalign the optical lattice.
 
@@
 Were it not for the linearization, the gain of the mixer would change by a factor of 10 over a dynamic range spanning two orders of magnitude.
+The loop transfer function is sensitive to the specific tuning parameters of the nonlinear controller resulting in slightly different transfer functions for the two axes, although both exhibit approximately constant behavior over the desired range of setpoints.
 Another function of the last stage is to clamp the voltage to be strictly positive by including a diode clamp on the output to prevent unstable positive feedback behavior~\cite{Horowitz2015}.
@@
 A common undesired behavior of analog feedback systems with integral gain is \emph{integrator wind-up}~\cite{Bechhoefer2005}, which can occur when the feedback loop is manually broken, meaning that the actuator can no longer adjust the state of the controlled parameter.
-In this regime, the integrator accumulates a large positive or negative voltage, such that when control is restored, the system appears to briefly rail before control is restored.
+In this regime, the integrator accumulates a large positive or negative voltage, such that when the loop is mended, the system appears to briefly rail before control is restored.
 In our case, \emph{integrator wind-up} occurs when the high-isolation RF switch is open during the state preparation procedure, and closed when the optical lattice is desired.
@@
 Even when the switch is closed, its resistance is nonzero (due to a protection resistor that limits the current that can pass through the switch), the conditions leading to integral windup in an unprotected system still lead to charge accumulation on the integral capacitor, albeit at a much reduced level.
-Thus, in addition to the switch, when the system is inactive, the set-point is set to the dark signal from the photodiode ($\approx$\unit{200}{\mu{}V}), making the error signal very small.
+Thus, in addition to the switch, when the system is inactive, the set-point is set to the dark signal from the photodiode ($\approx$\unit{200}{\mu{}V}, calibrated specifically to each photodiode), making the error signal very small.
 
 To avoid a so-called ``servo bump'' in the noise spectrum, and because there is little need for fast, closed-loop control, the loop filter is tuned very conservatively, to a bandwidth of approximately \unit{10}{kHz} over most of the range.
-However, a small amount of tuning can increase the bandwidth up to $\approx$\unit{150}{kHz}, which is limited by the propagation delay of the AOM.
+However, a small amount of tuning can increase the bandwidth up to $\approx$\unit{150}{kHz}, which is limited by the propagation delay of the acoustic wave in the AOM.
 Although fast, closed-loop control is not available in the current configuration, the last stage of the loop filter features an adder connected to an optional ``feed-forward'' port.
@@
 Figure~\ref{fig:noises} shows the noise performance of the output of the fiber amplifiers in open-loop compared to the noise in closed-loop.
-Although noise near DC is lowered (as expected from a closed-loop system), noise outside the loop bandwidth is increased in the range of 10 to \unit{450}{kHz} as seen in subfigures (c) and (d).
+Noise near DC is lowered (as expected from a closed-loop system), noise outside the loop bandwidth is increased in the range of 10 to \unit{450}{kHz} as seen in subfigures (c) and (d).
 This can be explained by the Johnson noise~\cite{Horowitz2015} on the \unit{1}{k\Omega} input resistors, amplified by the amplification stages of the loop filter.
@@
 Even worse, this happens on both the initial and retro-reflected pass through the glass cell.
-For this reason, we use a combination of quarter waveplate (QWP) and half waveplate (HWP) to optimize the interference contrast of each lattice.
-This is done by optimizing the on-site trap frequency of lattice, measured using parametric heating.
+For this reason, we use a combination of quarter waveplate (QWP) and half waveplate (HWP) to optimize the interference contrast of each lattice axis.
+This is done by optimizing the on-site trap frequency of lattice, measured using lattice-modulation spectroscopy.
 

### 2018-10-14 LatticeOptics/latticeOpticsV4.tex

@@
 
-\author{A.Mazurenko, S. Blatt, F. Huber, M. F. Parsons, C. S. Chiu, G. Ji, D. Greif}
+\author{A. Mazurenko, S. Blatt, F. Huber, M. F. Parsons, C. S. Chiu, G. Ji, D. Greif}
 \author{M. Greiner}
@@
 \begin{abstract}
- We describe the design of a stable high power $1064\,$nm laser system for practical use in optical lattice experiments.
+ We describe the design of a stable high power 1064~nm laser system for practical use in optical lattice experiments.
 The system is based on a low noise laser amplified by an array of four heavily modified, high-power fiber amplifiers.
@@
 
-Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation \cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
+Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation~\cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.
 The recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over individual atoms at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian ~\cite{Hubbard1963}.
@@
 
-In this work we discuss a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc between $1\,$kHz and $3\,$MHz.
+In this work we discuss a high power optical lattice system that exhibits levels of intensity noise below $-120\,$dBc/Hz between $1\,$kHz and $3\,$MHz Fourier frequency.
 The stability of the lattice position is below the single site level and the stability of the harmonic confinement is at the few site level.
@@
 
-The coarse architecture of the system is shown in figure \ref{fig:high_level} and is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Parsons2016}).
+The coarse architecture of the system is shown in Fig.~\ref{fig:high_level} and is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Parsons2016}).
 These amplifiers generate enough light to perform site resolved imaging~\cite{Parsons2015}, but also substantially increase the level of intensity and pointing noise.
@@
 Worse yet, it is suspected of causing ground loops which add noise and interference to the analog systems.
-This added noise can be seen in figure \ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser.
+This added noise can be seen in Fig.~\ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser.
 We solve this problem by replacing the USB control board with a custom-designed solution  that is compatible with our custom control system and engineered to avoid ground loops.
@@
 These upgrades serve to suppress many of the noise spurs measured in the relative intensity noise (RIN) of the fiber amplifier.
-This can be as seen by comparing figure \ref{fig:noises} (a) and (b), particularly in the region of approximately $10$ kHz. 
+This can be as seen by comparing Fig.~\ref{fig:noises} (a) and (b), particularly in the region of approximately $10$ kHz.
 The measurements in parts (a)-(d) were carried out on a single fiber amplifier, prior to and after the modifications.
@@
 In addition, we set the lowest pump diode current that yields enough power to perform imaging.
-The rise of the noise floor as a function of the pump diode current can be seen in figure \ref{fig:noises}(a).
+The rise of the noise floor as a function of the pump diode current can be seen in Fig.~\ref{fig:noises}(a).
 
@@
 
-In order to address these challenges, we use a carefully engineered the optical system shown in figure \ref{fig:optical_layout}.
+In order to address these challenges, we use a carefully engineered the optical system shown in Fig.~\ref{fig:optical_layout}.
 This system collimates and polarizes the beam, controls its intensity and ensures good pointing stability.
@@
 
-After the isolation stage, we use the sequence of optical elements shown in figure \ref{fig:optical_layout}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs GVS002, or Camtech 8320K, depending on beam path) half-wave plate, and polarizer.
+After the isolation stage, we use the sequence of optical elements shown in Fig.~\ref{fig:optical_layout}, consisting of a polarizer, half-wave plate (HWP), Berek compensator mounted on a precision galvo (Thorlabs GVS002, or Camtech 8320K, depending on beam path) half-wave plate, and polarizer.
 The Berek compensator is a $z$-cut quartz plate coated to be anti-reflecting at $1064\,$nm.
@@
 Combined with the subsequent polarization optics, rotation of the Berek compensator can vary the transmitted power with perfect contrast.
-Figure \ref{fig:berek} shows the transmitted power as a function of retrardation angle $\phi$ and fast-axis angle $\theta$ of the waveplates surrounding the compensator.
+Figure~\ref{fig:berek} shows the transmitted power as a function of retrardation angle $\phi$ and fast-axis angle $\theta$ of the waveplates surrounding the compensator.
 \begin{figure}
@@
 Naturally, the voltage drop over the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode ($3.3\,$V).
-Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in figure \ref{fig:bandwidth}.
+Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in Fig.~\ref{fig:bandwidth}.
 Were it not for the linearization, the gain of the mixer would change by a factor of $10$ over a dynamic range spanning two orders of magnitude.

### 2018-10-15 LatticeOptics/submission_rev_sci_inst/latticeoptics.tex
Updated paper style to RSI

@@
-\documentclass[twocolumn,aps,pra,preprintnumbers,bibnotes]{revtex4-1}
+\documentclass[twocolumn,aip,rsi,reprint,bibnotes]{revtex4-1}
 
@@
 The architecture of the system, shown in Fig.~\ref{fig:high_level}, is based on a single low-power, low-noise seed laser that supplies light to an array of four high-power fiber amplifiers (one for a transport beam~\cite{Huber2014}, and one each for the $X,Y,Z$ lattices~\cite{Blatt2015,Parsons2016}).
-These amplifiers generate sufficient light to perform site resolved imaging~\cite{Parsons2015}, but also substantially increase the level of intensity and pointing noise.
+These amplifiers generate sufficient light to perform site-resolved imaging~\cite{Parsons2015}, but also substantially increase the level of intensity and pointing noise.
 The fiber amplifier output is controlled by two feedback loops, which stabilize the light in low power and high power regimes, respectively, as discussed later.
@@
 Naturally, the laser system presented here is tailored to suit the experiment's specific lattice geometry~\cite{Huber2014} and exact requirements.
-We expect, however, that both the specific engineering choices and the general design practices detailed in this work will be widely applicable to experimentalists working with performant optical lattices used for a variety of purposes.
+We expect, however, that both the specific engineering choices and the general design practices detailed in this work will be widely applicable to experimentalists working with low-noise and stable optical lattices used for quantum many-body physics, precision measurement, and quantum engineering.
 
@@
 \subsection{Fiber amplifier system}
-Quantum gas microscopy of Li$^6$ requires single site trap frequencies of approximately \unit{1}{MHz}~\cite{Parsons2015} to be in the Lamb-Dicke regime necessary for Raman sideband cooling.
+Quantum gas microscopy of $^6$Li requires single-site trap frequencies of approximately \unit{1}{MHz} to be in the Lamb-Dicke regime necessary for Raman sideband cooling~\cite{Parsons2015}.
 
 Such trap frequencies may only be attained using tightly focused, high-power beams.
-In practical terms, this requires approximately \unit{20}{W} per lattice axis for a beam waist of around $80 \mu\mathrm{m}$ and the four-fold enhancement in optical depth provided by the reflection from the superpolished substrate~\cite{Huber2014}.
+In practical terms, this requires approximately \unit{20}{W} per lattice axis for a beam waist of around \unit{80}{\mu m} and the four-fold enhancement in lattice depth provided by the reflection from the superpolished substrate~\cite{Huber2014}.
 We achieve such high laser powers using Yb-doped fiber amplifiers (Nufern NuAmp SUB1174-34).
@@
 It is controlled via a USB interface, which complicates communications with an array of these devices.
-Worse yet, the digital control system is suspected of causing ground loops that add noise and interference to the analog systems.
+Worse yet, the digital control system causes ground loops that add noise and interference to the analog systems.
 This added noise can be seen in Fig.~\ref{fig:noises}, where the fiber-amplified light exhibits many more spurs in the intensity noise spectrum than the seed laser, particularly near \unit{10}{kHz}.
@@
 There are two power supplies in the fiber amplifier: (1) a general purpose power supply for the control electronics and the first, low-power amplification stage and (2) a high-power supply for the second, high-power stage.
-Despite the presence of a water-cooled cold-plate for the gain fiber and pump diodes, the high power supply is air cooled by an internal fan with variable frequency.
+Despite the presence of a water-cooled cold-plate for the gain fiber and pump diodes, the high power supply is air-cooled by an internal fan with variable frequency.
 This fan adds noise at acoustic frequencies and degrades pointing stability by increasing vibration of the output fiber tip.
@@
 This system collimates and polarizes the beam, controls its intensity and ensures good pointing stability.
-Due to the high laser power, fused silica glass and IBS coatings are used wherever possible.
+Due to the high laser power, fused silica glass and ion-beam-sputtered (IBS) coatings are used wherever possible.
 Since reflections pose a danger to the users and equipment, all undesired beams above \unit{100}{mW} are directed to water cooled beam-dumps (to prevent temperature gradients on the table) placed as far as practical from critical beam paths.
@@
 The beam is collimated using an $f=\unit{20}{mm}$ fused-silica, air-spaced triplet collimator (Opto-Sigma HFTLSQ-15-20PF1) angled with respect to and centered on the angle-cleaved fiber tip.
-The polarization is set using an IBS coated thin-film plate polarizer (Precision photonics PO1056-FY), with the added benefit of rejecting the undesired cladding modes of the fiber, which carry about \unit{1}{W} of light.
+The polarization is set using an IBS-coated thin-film plate polarizer (Precision photonics PO1056-FY), with the added benefit of rejecting the undesired cladding modes of the fiber, which carry about \unit{1}{W} of light.
 A thin-film polarizer was used to minimize the number of normal and backreflecting surfaces near the output of the fiber in addition to providing excellent polarization performance.
 The fact that the lattice is retro-reflected, combined with the observation that optical isolation falls with applied optical power~\cite{Yoshida1999} means that two stages of optical isolators must be used.
-The optical isolators are based on \unit{5}{mm} aperture Tb$_3$Ga$_5$O$_12$ (TGG) isolators (Thorlabs IO-5-1064-VHP), where we replaced the default polarizers (BK7 Brewster plates) by IBS-coated fused silica plate polarizers.
+The optical isolators are based on \unit{5}{mm} aperture Tb$_3$Ga$_5$O$_{12}$ (TGG) isolators (Thorlabs IO-5-1064-VHP), where we replaced the default polarizers (BK7 Brewster plates) by IBS-coated fused silica plate polarizers.
 The isolators are located approximately \unit{1}{m} away from the ultracold atoms which are susceptible to stray magnetic fields.
@@
 A key point, as seen in Fig.~\ref{fig:berek}, is that if the waveplates are rotated together, the maximum transmitted power is fixed, while the minimum can be raised.
-The waveplates are detuned such that the maximum power needed in \emph{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator, since the slope of transmission with respect to the Berek angle is $0$ at this point.
+The waveplates are detuned such that the maximum power needed in \emph{interaction} mode is the minimum power transmitted by the Berek compensator system, strongly suppressing fluctuations due to angle positioning noise of the Berek compensator, since the slope of transmission with respect to the Berek angle vanishes at this point.
 Naturally, rotation of a parallel plate in the beam path induces a shift of the beam, but this is acceptable because the Berek compensator is only active during the imaging phase of the experiment, when the position of the underlying harmonic trap is largely irrelevant.
@@
 To accomplish this, the low-power loop is always manually railed to its high extreme when the high-power loop is active.
-This is done by shuttering the photodiode and directing the set-point to a high value, which quickly winds up the integrator to its maximum output.
+This is done by closing a mechanical shutter in front of the photodiode and setting the set-point to a high value, which quickly winds up the integrator to its maximum output.
 Conversely, the digital high-power loop is disabled in software when the low-power loop is active.
@@
 \begin{enumerate}
-  \item Its effect on the RIN can limit the system temperature and set heating rate. This can limit the amount of time available for atom interaction~\cite{Blatt2015}. 
-  \item It needs to avoid varying the the beam pointing because the trap position matters during this phase of the experiment.
-  \item It must have closed-loop bandwidths of $\geq\unit{1}{kHz}$, and open-loop modulation bandwidths $\geq \unit{100}{kHz}$.
+  \item Its effect on the RIN can limit the system temperature and dominate heating rates, limiting the amount of time available for atom interaction~\cite{Blatt2015}.
+  \item It needs to avoid varying the beam pointing because the trap position matters during this phase of the experiment.
+  \item It must have closed-loop bandwidths $\geq\unit{1}{kHz}$, and open-loop modulation bandwidths $\geq \unit{100}{kHz}$.
 \end{enumerate}
@@
 The local oscillator (LO) RF source is a custom-built printed circuit board (PCB), schematically shown in Fig.~\ref{fig:circuits}(b), that implements a phase locked loop (PLL) based on the ADF4002 IC and a low-phase-noise voltage-controlled oscillator (VCO, Crystek CVCO55CL-0060-0110), preamplified with a low-noise amplifier (Minicircuits PSA4-5043+).
-%To ensure frequency stability (which translates directly into beam pointing of the laser), the PLL is locked to the \unit{10}{MHz} frequency reference distributed around the lab.
-The PLL is locked to the \unit{10}{MHz} frequency reference distributed around the lab to ensure absolute frequency stability.
+The PLL is locked to the \unit{10}{MHz} frequency reference distributed throughout the lab to ensure absolute frequency stability.
 In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total isolation exceeding \unit{90}{dB}.
-
-%We need to maintain the relatively low phase-noise characteristics of the VCO to prevent phase- to amplitude-noise conversion in the AOM, which partially downconverts the VCO phase noise to RIN at acoustic frequencies.
 This device allows us to drive the AOM with a single, clean tone.
@@
 The connection between the actuation and monitoring mechanisms of the feedback system is the loop filter, which compares the \emph{set-point} signal, $V_\mathrm{SP}(t)$, supplied by the experimental control system and the photodiode signals $V_\mathrm{PD}(t)$, to adjust the actuation accordingly.
-We use a simple, primarily integrating design in three stages, as seen in Fig.~\ref{fig:circuits}(c), based on a low-noise op-amp (Texas Instruments OPA211).
+We use a simple integrating design in three stages, as seen in Fig.~\ref{fig:circuits}(c), based on a low-noise op-amp (Texas Instruments OPA211).
 The first stage computes and amplifies an error signal, $e(t)=V_\mathrm{SP}(t)-V_\mathrm{PD}(t)$, which is integrated by the second stage.
@@
 The third stage of the loop filter is used to accommodate the fact that the actuation arm is nonlinear: the optical power transmitted by the AOM is proportional to the RF power incident on it $P_{\mathrm{rf}}\propto V_{IF}^2$, where $V_{IF}$ is the actuation signal supplied to the IF port of the mixer.
-In effect, if the rest of the feedback system was linear, this would correspond to a quadratically increasing gain until the AOM is saturated, which could lead to slow behavior at low signal levels and ringing at higher signal levels.
+In effect, if the rest of the feedback system was linear, this would correspond to a quadratically increasing gain until the AOM is saturated, which leads to slow behavior at low signal levels and ringing at higher signal levels.
 Even worse, since the mixer is insensitive to the sign of the voltage applied, the gain is negative for negative voltages, resulting in an unstable system.
@@
 A common undesired behavior of analog feedback systems with integral gain is \emph{integrator wind-up}~\cite{Bechhoefer2005}, which can occur when the feedback loop is manually broken, meaning that the actuator can no longer adjust the state of the controlled parameter.
-In this regime, the integrator accumulates a large positive or negative voltage, such that when the loop is mended, the system appears to briefly rail before control is restored.
+In this regime, the integrator accumulates a large positive or negative voltage, such that when the loop is mended, the system briefly rails before control is restored.
 In our case, \emph{integrator wind-up} occurs when the high-isolation RF switch is open during the state preparation procedure, and closed when the optical lattice is desired.
@@
 For this reason, we use a combination of quarter waveplate (QWP) and half waveplate (HWP) to optimize the interference contrast of each lattice axis.
-This is done by optimizing the on-site trap frequency of lattice, measured using lattice-modulation spectroscopy.
+This is done by optimizing the on-site trap frequency of lattice, measured using lattice-modulation spectroscopy~\cite{Blatt2015}.
 
@@
 
-The position of the atomic cloud, however, is not determined by the phase difference of the retro-reflecting lattice beam, but by the underlying harmonic confinement.
+The position of the atomic cloud, however, is not determined by the phase difference of the retro-reflecting lattice beams, but by the underlying harmonic confinement generated by their transverse Gaussian profiles.
 The stability of this confinement is governed by the pointing stability of the optical lattice laser beams.

### 2018-12-10 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
revisions rev sci inst v1

--- 2018-10-15 LatticeOptics/submission_rev_sci_inst/latticeoptics.tex
@@
 Using real-time monitoring of the resulting optical lattice, we find the stability of the lattice site positions to be well below the lattice spacing over the course of hours.
-The pointing stability of the optical lattice beams is around one lattice spacing and the long-term (six month) relative stability of the lattice spacing itself is 0.5\% RMS.
+The stability of the underlying harmonic trap produced by the optical lattice beams is around one lattice spacing and the long-term (six month) relative RMS stability of the lattice spacing itself is 0.5\%.
 \end{abstract}
@@
 (b) Shows the open-loop and closed-loop behavior of the high-power feedback loop using the  modified fiber amplifiers, as described in the main text.
-(c) Shows the open-loop behavior of the low-power feedback loop using the modified fiber amplifiers, including an additional low-pass filtering stage to limit the loop bandwidth at various constant powers.
-(d) Closed-loop behavior of the low-power feedback loop without additional low-pass filtering, measured on the same setup as panel (c).}\label{fig:noises}
+(c) Shows the open-loop behavior of the low-power feedback loop using the modified fiber amplifiers at various constant powers.
+(d) Closed-loop behavior of the low-power feedback loop (without additional low-pass filtering), measured on the same setup as panel (c).}\label{fig:noises}
   \end{center}
@@
 To accomplish this, the low-power loop is always manually railed to its high extreme when the high-power loop is active.
-This is done by closing a mechanical shutter in front of the photodiode and setting the set-point to a high value, which quickly winds up the integrator to its maximum output.
+This is done by closing a mechanical shutter (Stanford Research Systems SR475) in front of the photodiode and setting the set-point to a high value, which quickly winds up the integrator to its maximum output.
 Conversely, the digital high-power loop is disabled in software when the low-power loop is active.
@@
 \end{enumerate}
-To this end, we use an all-custom loop based on a TeO$_2$ AOM (Gooch \& Housego AOMO 3080-198), where the power of the RF supplied to the AOM is used to actuate the fast, low-power feedback loop.
+To this end, we use an nonlinear feedback loop based on a TeO$_2$ AOM (Gooch \& Housego AOMO 3080-198), where the power of the RF supplied to the AOM is used to actuate the fast, low-power feedback loop.
 The AOM was chosen for its low thermal lensing and easily-accessible RF powers.
@@
 The other beam is not attenuated, save by the beam sampler, and its dynamic range covers \unit{0-1}{W}.
-To prevent damage to the low-power photodiode when the system is at its highest powers, a shutter (Stanford Research Systems SR475) blocks the light when the high-power loop is in use.
+%To prevent damage to the low-power photodiode when the system is at its highest powers, a shutter (Stanford Research Systems SR475) blocks the light when the high-power loop is in use.
 The low-power photodiode passes its signal $V_{\mathrm{pd}}$ to a loop filter circuit [Fig.~\ref{fig:circuits}(c)], which compares it to the control system's set-point, generated by a digital-to-analog converter.
@@
 The PLL is locked to the \unit{10}{MHz} frequency reference distributed throughout the lab to ensure absolute frequency stability.
-In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total isolation exceeding \unit{90}{dB}.
+In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total RF isolation exceeding \unit{90}{dB}.
 This device allows us to drive the AOM with a single, clean tone.
-The spectrum and relative intensity noise of the PLL can be found in Fig.~\ref{fig:pll}.
+%The spectrum and relative intensity noise of the PLL can be found in Fig.~\ref{fig:pll}.
 Vitally, the spectrum of the PLL exhibits phase noise comparable to that of a typical VCO but without the slow frequency drift characteristic to these devices.
@@
 
-\begin{figure}
-  \begin{center}
-    \includegraphics{Figure7.pdf}
-    \caption{\textbf{PLL performance} (a) The spectrum of the PLL, exhibiting phase noise of better than $-90$ dBc/Hz at $100$~kHz away from the carrier.
+%\begin{figure}
+%  \begin{center}
+%    \includegraphics{Figure7.pdf}
+%    \caption{\textbf{PLL performance} (a) The spectrum of the PLL, exhibiting phase noise of better than $-90$ dBc/Hz at $100$~kHz away from the carrier.
 (b) The RIN of the local oscillator based on the PLL.
 The noise level is seen to be at or below the noise floor of the measurement device.}\label{fig:pll}
-  \end{center}
-\end{figure}
+%  \end{center}
+%\end{figure}
 
@@
 
-The chosen photodiode (Hamamatsu G8370-01) is an InGaS based, small-area, low-noise design with a high efficiency and low thermal sensitivity at \unit{1064}{nm}.
+The chosen photodiode (Hamamatsu G8370-01) is an InGaAs based, small-area, low-noise design with a high efficiency and low thermal sensitivity at \unit{1064}{nm}.
 Prior to use, the protective window is removed from the photodiode to prevent interference effects, as seen in Fig.~\ref{fig:cut_pd}.

### 2018-12-29 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
reviewer comments rev sci inst

@@
 In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total RF isolation exceeding \unit{90}{dB}.
-This device allows us to drive the AOM with a single, clean tone.
+This device allows us to drive the AOM with a single, clean tone ($<$\unit{90}{dBc/Hz} at \unit{200}{kHz} away from the carrier).
 %The spectrum and relative intensity noise of the PLL can be found in Fig.~\ref{fig:pll}.
-Vitally, the spectrum of the PLL exhibits phase noise comparable to that of a typical VCO but without the slow frequency drift characteristic to these devices.
+Thus, the spectrum of the PLL exhibits phase noise comparable to that of a typical VCO but without the slow frequency drift characteristic to these devices.
 Elimination of the carrier drift is worth the added phase noise because any drift of the frequency affects the pointing of the laser beam passing through the AOM, which would misalign the optical lattice.
@@
 Noise near DC is lowered (as expected from a closed-loop system), noise outside the loop bandwidth is increased in the range of 10 to \unit{450}{kHz} as seen in subfigures (c) and (d).
-This can be explained by the Johnson noise~\cite{Horowitz2015} on the \unit{1}{k\Omega} input resistors, amplified by the amplification stages of the loop filter.
+This can be explained by the Johnson noise~\cite{Horowitz2015} on the \unit{1}{k\Omega} op-amp input resistors, amplified by the amplification stages of the loop filter.
 The sharp drop off at the \unit{450}{kHz} point is due to a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.

### 2019-01-27 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
Updated referee comments

@@
 Another function of the last stage is to clamp the voltage to be strictly positive by including a diode clamp on the output to prevent unstable positive feedback behavior~\cite{Horowitz2015}.
-Finally, since the mixer is a current driven device, the last stage of the feedback loop uses the low-noise OPA627 (Texas Instruments) op-amp which is able to supply tens of mA of current into an output impedance of \unit{50}{\Omega}.
+Finally, since the mixer is a current driven device, the last stage of the feedback loop uses the low-noise OPA627 (Texas Instruments) op-amp which is able to supply tens of mA of current into an input impedance of \unit{50}{\Omega}.
 

### 2019-01-27 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
Added paragraph

@@
 In addition to the intensity stability, we demonstrate a short-term (shot-to-shot) stability of the lattice position at 1.4\% of the optical lattice spacing, and a long-term (six month) relative stability of 0.5\% RMS of the lattice spacing itself.
+
+For context, typical high-power, low-noise \unit{1064}{nm} laser systems are based amplifying a seed laser with either a fiber or solid-state amplifier.
+Solid-state amplifiers can attain impressive performance.
+For example, the laser system used for gravitational wave detection at advanced LIGO exceeds \unit{-150}{dBc/Hz} in the \unit{10}{Hz} - \unit{1}{kHz} frequency range for a constant output power~\cite{kwee12}.
+In this work, we achieve \unit{-120}{dBc/Hz} intensity stability in the \unit{1}{kHz} - \unit{2}{MHz} frequency range, and maintain this performance over six orders of magnitude in output power.
+Our modifications to the fiber amplifier hardware allow us to rival and exceed the power and noise performance of more modern commercial fiber amplifiers~\cite{guiraud16}.
 
@@
 
-% \bibliography{latticeoptics}
-
-% merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
-%Control: key (0)
-%Control: author (8) initials jnrlst
-%Control: editor formatted (1) identically to author
-%Control: production of article title (-1) disabled
-%Control: page (0) single
-%Control: year (1) truncated
-%Control: production of eprint (0) enabled
-\begin{thebibliography}{34}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Friedenauer}\ \emph {et~al.}(2008)\citenamefont
-  {Friedenauer}, \citenamefont {Schmitz}, \citenamefont {Glueckert},
-  \citenamefont {Porras},\ and\ \citenamefont {Schaetz}}]{Friedenauer2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Friedenauer}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Schmitz}}, \bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
-  {Glueckert}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Porras}}, \
-  and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Schaetz}},\ }\href
-  {\doibase 10.1038/nphys1032} {\bibfield  {journal} {\bibinfo  {journal}
-  {Nature Physics}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {757}
-  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kim}\ \emph {et~al.}(2010)\citenamefont {Kim},
-  \citenamefont {Chang}, \citenamefont {Korenblit}, \citenamefont {Islam},
-  \citenamefont {Edwards}, \citenamefont {Freericks}, \citenamefont {Lin},
-  \citenamefont {Duan},\ and\ \citenamefont {Monroe}}]{Kim2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Kim}}, \bibinfo {author} {\bibfnamefont {M.-S.}\ \bibnamefont {Chang}},
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Korenblit}}, \bibinfo
-  {author} {\bibfnamefont {R.}~\bibnamefont {Islam}}, \bibinfo {author}
-  {\bibfnamefont {E.~E.}\ \bibnamefont {Edwards}}, \bibinfo {author}
-  {\bibfnamefont {J.~K.}\ \bibnamefont {Freericks}}, \bibinfo {author}
-  {\bibfnamefont {G.-D.}\ \bibnamefont {Lin}}, \bibinfo {author} {\bibfnamefont
-  {L.-M.}\ \bibnamefont {Duan}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {Monroe}},\ }\href {\doibase 10.1038/nature09071}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-  {volume} {465}},\ \bibinfo {pages} {590} (\bibinfo {year}
-  {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Struck}\ \emph {et~al.}(2011)\citenamefont {Struck},
-  \citenamefont {{\"{O}}lschl{\"{a}}ger}, \citenamefont {{Le Targat}},
-  \citenamefont {Soltan-Panahi}, \citenamefont {Eckardt}, \citenamefont
-  {Lewenstein}, \citenamefont {Windpassinger},\ and\ \citenamefont
-  {Sengstock}}]{Struck2011}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Struck}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {{\"{O}}lschl{\"{a}}ger}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {{Le Targat}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Soltan-Panahi}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Eckardt}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Lewenstein}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Windpassinger}}, \ and\
-  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Sengstock}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {333}},\ \bibinfo {pages} {996} (\bibinfo {year}
-  {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Simon}\ \emph {et~al.}(2011)\citenamefont {Simon},
-  \citenamefont {Bakr}, \citenamefont {Ma}, \citenamefont {Tai}, \citenamefont
-  {Preiss},\ and\ \citenamefont {Greiner}}]{Simon2011}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Simon}}, \bibinfo {author} {\bibfnamefont {W.~S.}\ \bibnamefont {Bakr}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ma}}, \bibinfo {author}
-  {\bibfnamefont {M.~E.}\ \bibnamefont {Tai}}, \bibinfo {author} {\bibfnamefont
-  {P.~M.}\ \bibnamefont {Preiss}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1038/nature09994}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-  {volume} {472}},\ \bibinfo {pages} {307} (\bibinfo {year}
-  {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Yan}\ \emph {et~al.}(2013)\citenamefont {Yan},
-  \citenamefont {Moses}, \citenamefont {Gadway}, \citenamefont {Covey},
-  \citenamefont {Hazzard}, \citenamefont {Rey}, \citenamefont {Jin},\ and\
-  \citenamefont {Ye}}]{Yan2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Yan}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont {Moses}},
-  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Gadway}}, \bibinfo
-  {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Covey}}, \bibinfo {author}
-  {\bibfnamefont {K.~R.~A.}\ \bibnamefont {Hazzard}}, \bibinfo {author}
-  {\bibfnamefont {A.~M.}\ \bibnamefont {Rey}}, \bibinfo {author} {\bibfnamefont
-  {D.~S.}\ \bibnamefont {Jin}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Ye}},\ }\href {\doibase 10.1038/nature12483} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {501}},\
-  \bibinfo {pages} {521} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Greif}\ \emph {et~al.}(2013)\citenamefont {Greif},
-  \citenamefont {Uehlinger}, \citenamefont {Jotzu}, \citenamefont {Tarruell},\
-  and\ \citenamefont {Esslinger}}]{Greif2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Greif}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Uehlinger}},
-  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Jotzu}}, \bibinfo
-  {author} {\bibfnamefont {L.}~\bibnamefont {Tarruell}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {T.}~\bibnamefont {Esslinger}},\ }\href {\doibase
-  10.1126/science.1236362} {\bibfield  {journal} {\bibinfo  {journal}
-  {Science}\ }\textbf {\bibinfo {volume} {340}},\ \bibinfo {pages} {1307}
-  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Murmann}\ \emph {et~al.}(2015)\citenamefont
-  {Murmann}, \citenamefont {Deuretzbacher}, \citenamefont {Z{\"{u}}rn},
-  \citenamefont {Bjerlin}, \citenamefont {Reimann}, \citenamefont {Santos},
-  \citenamefont {Lompe},\ and\ \citenamefont {Jochim}}]{Murmann2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Murmann}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Deuretzbacher}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Z{\"{u}}rn}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Bjerlin}},
-  \bibinfo {author} {\bibfnamefont {S.~M.}\ \bibnamefont {Reimann}}, \bibinfo
-  {author} {\bibfnamefont {L.}~\bibnamefont {Santos}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Lompe}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Jochim}},\ }\href {\doibase
-  10.1103/PhysRevLett.115.215301} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {115}},\ \bibinfo {pages}
-  {215301} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Drewes}\ \emph {et~al.}(2017)\citenamefont {Drewes},
-  \citenamefont {Miller}, \citenamefont {Cocchi}, \citenamefont {Chan},
-  \citenamefont {Wurz}, \citenamefont {Gall}, \citenamefont {Pertot},
-  \citenamefont {Brennecke},\ and\ \citenamefont {K{\"{o}}hl}}]{Drewes2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
-  {Drewes}}, \bibinfo {author} {\bibfnamefont {L.~A.}\ \bibnamefont {Miller}},
-  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Cocchi}}, \bibinfo
-  {author} {\bibfnamefont {C.~F.}\ \bibnamefont {Chan}}, \bibinfo {author}
-  {\bibfnamefont {N.}~\bibnamefont {Wurz}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Gall}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Pertot}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Brennecke}}, \
-  and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {K{\"{o}}hl}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
-  }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {170401} (\bibinfo
-  {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bakr}\ \emph {et~al.}(2009)\citenamefont {Bakr},
-  \citenamefont {Gillen}, \citenamefont {Peng}, \citenamefont {F{\"{o}}lling},\
-  and\ \citenamefont {Greiner}}]{Bakr2009}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~S.}\ \bibnamefont
-  {Bakr}}, \bibinfo {author} {\bibfnamefont {J.~I.}\ \bibnamefont {Gillen}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Peng}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {F{\"{o}}lling}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
-  10.1038/nature08482} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\
-  }\textbf {\bibinfo {volume} {462}},\ \bibinfo {pages} {74} (\bibinfo {year}
-  {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sherson}\ \emph {et~al.}(2010)\citenamefont
-  {Sherson}, \citenamefont {Weitenberg}, \citenamefont {Endres}, \citenamefont
-  {Cheneau}, \citenamefont {Bloch},\ and\ \citenamefont {Kuhr}}]{Sherson2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
-  {Sherson}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Weitenberg}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Endres}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Cheneau}}, \bibinfo {author}
-  {\bibfnamefont {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Kuhr}},\ }\href {\doibase
-  10.1038/nature09378} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\
-  }\textbf {\bibinfo {volume} {467}},\ \bibinfo {pages} {68} (\bibinfo {year}
-  {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Haller}\ \emph {et~al.}(2015)\citenamefont {Haller},
-  \citenamefont {Hudson}, \citenamefont {Kelly}, \citenamefont {Cotta},
-  \citenamefont {Peaudecerf}, \citenamefont {Bruce},\ and\ \citenamefont
-  {Kuhr}}]{Haller2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Haller}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Hudson}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kelly}}, \bibinfo
-  {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Cotta}}, \bibinfo {author}
-  {\bibfnamefont {B.}~\bibnamefont {Peaudecerf}}, \bibinfo {author}
-  {\bibfnamefont {G.~D.}\ \bibnamefont {Bruce}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Kuhr}},\ }\href {\doibase
-  10.1038/nphys3403} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages} {738}
-  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cheuk}\ \emph {et~al.}(2015)\citenamefont {Cheuk},
-  \citenamefont {Nichols}, \citenamefont {Okan}, \citenamefont {Gersdorf},
-  \citenamefont {Ramasesh}, \citenamefont {Bakr}, \citenamefont {Lompe},\ and\
-  \citenamefont {Zwierlein}}]{Cheuk2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
-  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Gersdorf}}, \bibinfo {author}
-  {\bibfnamefont {V.~V.}\ \bibnamefont {Ramasesh}}, \bibinfo {author}
-  {\bibfnamefont {W.~S.}\ \bibnamefont {Bakr}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Lompe}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.~W.}\ \bibnamefont {Zwierlein}},\ }\href {\doibase
-  10.1103/PhysRevLett.114.193001} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
-  {193001} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Parsons}\ \emph {et~al.}(2015)\citenamefont
-  {Parsons}, \citenamefont {Huber}, \citenamefont {Mazurenko}, \citenamefont
-  {Chiu}, \citenamefont {Setiawan}, \citenamefont {Wooley-Brown}, \citenamefont
-  {Blatt},\ and\ \citenamefont {Greiner}}]{Parsons2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont
-  {Parsons}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Huber}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo
-  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
-  {\bibfnamefont {W.}~\bibnamefont {Setiawan}}, \bibinfo {author}
-  {\bibfnamefont {K.}~\bibnamefont {Wooley-Brown}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Blatt}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
-  10.1103/PhysRevLett.114.213002} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
-  {213002} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Edge}\ \emph {et~al.}(2015)\citenamefont {Edge},
-  \citenamefont {Anderson}, \citenamefont {Jervis}, \citenamefont {McKay},
-  \citenamefont {Day}, \citenamefont {Trotzky},\ and\ \citenamefont
-  {Thywissen}}]{Edge2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~J.~A.}\
-  \bibnamefont {Edge}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Anderson}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Jervis}},
-  \bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont {McKay}}, \bibinfo
-  {author} {\bibfnamefont {R.}~\bibnamefont {Day}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Trotzky}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {J.~H.}\ \bibnamefont {Thywissen}},\ }\href {\doibase
-  10.1103/PhysRevA.92.063406} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. A}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages} {063406}
-  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Omran}\ \emph {et~al.}(2015)\citenamefont {Omran},
-  \citenamefont {Boll}, \citenamefont {Hilker}, \citenamefont {Kleinlein},
-  \citenamefont {Salomon}, \citenamefont {Bloch},\ and\ \citenamefont
-  {Gross}}]{Omran2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Omran}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Boll}},
-  \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Hilker}}, \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Kleinlein}}, \bibinfo {author}
-  {\bibfnamefont {G.}~\bibnamefont {Salomon}}, \bibinfo {author} {\bibfnamefont
-  {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {Gross}},\ }\href {\doibase 10.1103/PhysRevLett.115.263001}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {115}},\ \bibinfo {pages} {263001} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Greif}\ \emph {et~al.}(2016)\citenamefont {Greif},
-  \citenamefont {Parsons}, \citenamefont {Mazurenko}, \citenamefont {Chiu},
-  \citenamefont {Blatt}, \citenamefont {Huber}, \citenamefont {Ji},\ and\
-  \citenamefont {Greiner}}]{Greif2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Greif}}, \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo
-  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Blatt}}, \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {Huber}}, \bibinfo {author} {\bibfnamefont
-  {G.}~\bibnamefont {Ji}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1126/science.aad9041}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {351}},\ \bibinfo {pages} {953} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cheuk}\ \emph
-  {et~al.}(2016{\natexlab{a}})\citenamefont {Cheuk}, \citenamefont {Nichols},
-  \citenamefont {Lawrence}, \citenamefont {Okan}, \citenamefont {Zhang},\ and\
-  \citenamefont {Zwierlein}}]{Cheuk2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
-  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
-  \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont {Lawrence}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Zhang}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.~W.}\ \bibnamefont {Zwierlein}},\ }\href
-  {https://journals.aps.org/prl/pdf/10.1103/PhysRevLett.116.235301} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. Lett}\ }\textbf {\bibinfo {volume}
-  {116}},\ \bibinfo {pages} {235301} (\bibinfo {year}
-  {2016}{\natexlab{a}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Parsons}\ \emph {et~al.}(2016)\citenamefont
-  {Parsons}, \citenamefont {Mazurenko}, \citenamefont {Chiu}, \citenamefont
-  {Ji}, \citenamefont {Greif},\ and\ \citenamefont {Greiner}}]{Parsons2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont
-  {Parsons}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}},
-  \bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo
-  {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
-  10.1126/science.aag1430} {\bibfield  {journal} {\bibinfo  {journal}
-  {Science}\ }\textbf {\bibinfo {volume} {353}},\ \bibinfo {pages} {1253}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Boll}\ \emph {et~al.}(2016)\citenamefont {Boll},
-  \citenamefont {Hilker}, \citenamefont {Salomon}, \citenamefont {Omran},
-  \citenamefont {Nespolo}, \citenamefont {Pollet}, \citenamefont {Bloch},\ and\
-  \citenamefont {Gross}}]{Boll2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Boll}}, \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Hilker}},
-  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Salomon}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Omran}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Nespolo}}, \bibinfo {author} {\bibfnamefont
-  {L.}~\bibnamefont {Pollet}}, \bibinfo {author} {\bibfnamefont
-  {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {Gross}},\ }\href {\doibase 10.1126/science.aag1635}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {353}},\ \bibinfo {pages} {1257} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cheuk}\ \emph
-  {et~al.}(2016{\natexlab{b}})\citenamefont {Cheuk}, \citenamefont {Nichols},
-  \citenamefont {Lawrence}, \citenamefont {Okan}, \citenamefont {Zhang},
-  \citenamefont {Khatami}, \citenamefont {Trivedi}, \citenamefont {Paiva},
-  \citenamefont {Rigol},\ and\ \citenamefont {Zwierlein}}]{Cheuk2016a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
-  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
-  \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont {Lawrence}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Khatami}}, \bibinfo {author} {\bibfnamefont
-  {N.}~\bibnamefont {Trivedi}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Paiva}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Rigol}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~W.}\
-  \bibnamefont {Zwierlein}},\ }\href {\doibase 10.1126/science.aag3349}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {353}},\ \bibinfo {pages} {1260} (\bibinfo {year}
-  {2016}{\natexlab{b}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Brown}\ \emph {et~al.}(2017)\citenamefont {Brown},
-  \citenamefont {Mitra}, \citenamefont {Guardado-Sanchez}, \citenamefont
-  {Schau{\ss}}, \citenamefont {Kondov}, \citenamefont {Khatami}, \citenamefont
-  {Paiva}, \citenamefont {Trivedi}, \citenamefont {Huse},\ and\ \citenamefont
-  {Bakr}}]{Brown2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~T.}\ \bibnamefont
-  {Brown}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Mitra}},
-  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Guardado-Sanchez}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Schau{\ss}}}, \bibinfo
-  {author} {\bibfnamefont {S.~S.}\ \bibnamefont {Kondov}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Khatami}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Paiva}}, \bibinfo {author} {\bibfnamefont
-  {N.}~\bibnamefont {Trivedi}}, \bibinfo {author} {\bibfnamefont {D.~A.}\
-  \bibnamefont {Huse}}, \ and\ \bibinfo {author} {\bibfnamefont {W.~S.}\
-  \bibnamefont {Bakr}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Science}\ }\textbf {\bibinfo {volume} {357}},\ \bibinfo {pages}
-  {1385} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hubbard}(1963)}]{Hubbard1963}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Hubbard}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Proc.
-  Roy. Soc. A: Mathematical, Physical and Engineering Sciences}\ }\textbf
-  {\bibinfo {volume} {276}},\ \bibinfo {pages} {238} (\bibinfo {year}
-  {1963})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mazurenko}\ \emph {et~al.}(2017)\citenamefont
-  {Mazurenko}, \citenamefont {Chiu}, \citenamefont {Ji}, \citenamefont
-  {Parsons}, \citenamefont {Kan{\'{a}}sz-Nagy}, \citenamefont {Schmidt},
-  \citenamefont {Grusdt}, \citenamefont {Demler}, \citenamefont {Greif},\ and\
-  \citenamefont {Greiner}}]{Mazurenko2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mazurenko}}, \bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}},
-  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo {author}
-  {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Kan{\'{a}}sz-Nagy}}, \bibinfo {author}
-  {\bibfnamefont {R.}~\bibnamefont {Schmidt}}, \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {Grusdt}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Demler}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1038/nature22362}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-  {volume} {545}},\ \bibinfo {pages} {462} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chiu}\ \emph {et~al.}(2018)\citenamefont {Chiu},
-  \citenamefont {Ji}, \citenamefont {Mazurenko}, \citenamefont {Greif},\ and\
-  \citenamefont {Greiner}}]{Chiu2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont
-  {Chiu}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
-  {volume} {120}},\ \bibinfo {pages} {243201} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Blatt}\ \emph {et~al.}(2015)\citenamefont {Blatt},
-  \citenamefont {Mazurenko}, \citenamefont {Parsons}, \citenamefont {Chiu},
-  \citenamefont {Huber},\ and\ \citenamefont {Greiner}}]{Blatt2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Blatt}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}},
-  \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}}, \bibinfo
-  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
-  {\bibfnamefont {F.}~\bibnamefont {Huber}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
-  10.1103/PhysRevA.92.021402} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physical Review A}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages}
-  {021402(R)} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Preiss}\ \emph {et~al.}(2015)\citenamefont {Preiss},
-  \citenamefont {Ma}, \citenamefont {Tai}, \citenamefont {Lukin}, \citenamefont
-  {Rispoli}, \citenamefont {Zupancic}, \citenamefont {Lahini}, \citenamefont
-  {Islam},\ and\ \citenamefont {Greiner}}]{Preiss2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
-  {Preiss}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ma}}, \bibinfo
-  {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Tai}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Lukin}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Rispoli}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Zupancic}}, \bibinfo {author} {\bibfnamefont
-  {Y.}~\bibnamefont {Lahini}}, \bibinfo {author} {\bibfnamefont
-  {R.}~\bibnamefont {Islam}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Greiner}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-   {journal} {Science}\ }\textbf {\bibinfo {volume} {347}} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Choi}\ \emph {et~al.}(2016)\citenamefont {Choi},
-  \citenamefont {Hild}, \citenamefont {Zeiher}, \citenamefont {Schau{\ss}},
-  \citenamefont {Rubio-Abadal}, \citenamefont {Yefsah}, \citenamefont
-  {Khemani}, \citenamefont {Huse}, \citenamefont {Bloch},\ and\ \citenamefont
-  {Gross}}]{Choi2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-Y.}\ \bibnamefont
-  {Choi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Hild}}, \bibinfo
-  {author} {\bibfnamefont {J.}~\bibnamefont {Zeiher}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Schau{\ss}}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Rubio-Abadal}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Yefsah}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Khemani}}, \bibinfo {author} {\bibfnamefont {D.~A.}\
-  \bibnamefont {Huse}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Gross}},\ }\href {http://science.sciencemag.org/content/352/6293/1547}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {352}},\ \bibinfo {pages} {1547} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Huber}(2014)}]{Huber2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Huber}},\ }\emph {\bibinfo {title} {{Site-Resolved Imaging with the Fermi
-  Gas Microscope}}},\ \href@noop {} {Ph.D. thesis},\ \bibinfo  {school}
-  {Harvard University} (\bibinfo {year} {2014})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Agrawal}(2013)}]{Agrawal2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Agrawal}},\ }\href@noop {} {\emph {\bibinfo {title} {{Nonlinear Fiber
-  Optics}}}},\ \bibinfo {edition} {5th}\ ed.\ (\bibinfo  {publisher} {Academic
-  Press},\ \bibinfo {year} {2013})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Yoshida}\ \emph {et~al.}(1999)\citenamefont
-  {Yoshida}, \citenamefont {Gorlenko}, \citenamefont {Tanner}, \citenamefont
-  {Reitze}, \citenamefont {Mansell}, \citenamefont {Khazanov},\ and\
-  \citenamefont {Kulagin}}]{Yoshida1999}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Yoshida}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gorlenko}},
-  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Tanner}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Reitze}}, \bibinfo {author}
-  {\bibfnamefont {J.~D.}\ \bibnamefont {Mansell}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Khazanov}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {O.}~\bibnamefont {Kulagin}},\ }\href
-  {http://www.phys.ufl.edu/{~}tanner/PDFS/Yoshida99spie-ComponentsLIGO-abs.pdf}
-  {\bibfield  {journal} {\bibinfo  {journal} {SPIE}\ }\textbf {\bibinfo
-  {volume} {3736}},\ \bibinfo {pages} {430} (\bibinfo {year}
-  {1999})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bechhoefer}(2005)}]{Bechhoefer2005}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Bechhoefer}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo {pages} {783}
-  (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Graeme}(1995)}]{Graeme1995}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Graeme}},\ }\href@noop {} {\emph {\bibinfo {title} {{Photodiode
-  Amplifiers}}}}\ (\bibinfo  {publisher} {McGraw Hill},\ \bibinfo {year}
-  {1995})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Skogestad}(2003)}]{Skogestad2003}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Skogestad}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
-  Process Control}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {291}
-  (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Horowitz}\ and\ \citenamefont
-  {Hill}(2015)}]{Horowitz2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Horowitz}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Hill}},\ }\href@noop {} {\emph {\bibinfo {title} {{The Art of
-  Electronics}}}},\ \bibinfo {edition} {3rd}\ ed.\ (\bibinfo  {publisher}
-  {Cambridge University Press},\ \bibinfo {address} {New York},\ \bibinfo
-  {year} {2015})\BibitemShut {NoStop}%
-\end{thebibliography}%
+\bibliography{latticeoptics}
 

### 2019-01-28 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
Updated referee reply

@@
 Using real-time monitoring of the resulting optical lattice, we find the stability of the lattice site positions to be well below the lattice spacing over the course of hours.
-The stability of the underlying harmonic trap produced by the optical lattice beams is around one lattice spacing and the long-term (six month) relative RMS stability of the lattice spacing itself is 0.5\%.
+The position of the harmonic trap produced by the Gaussian envelope of the lattice beams is stable to about one lattice spacing and the long-term (six-month) relative RMS stability of the lattice spacing itself is 0.5\%.
 \end{abstract}
@@
 
-For context, typical high-power, low-noise \unit{1064}{nm} laser systems are based amplifying a seed laser with either a fiber or solid-state amplifier.
-Solid-state amplifiers can attain impressive performance.
-For example, the laser system used for gravitational wave detection at advanced LIGO exceeds \unit{-150}{dBc/Hz} in the \unit{10}{Hz} - \unit{1}{kHz} frequency range for a constant output power~\cite{kwee12}.
-In this work, we achieve \unit{-120}{dBc/Hz} intensity stability in the \unit{1}{kHz} - \unit{2}{MHz} frequency range, and maintain this performance over six orders of magnitude in output power.
-Our modifications to the fiber amplifier hardware allow us to rival and exceed the power and noise performance of more modern commercial fiber amplifiers~\cite{guiraud16}.
+For context, typical high-power, low-noise \unit{1064}{nm} laser systems are based on amplification of a seed laser with either a fiber or a solid-state amplifier.
+For example, the laser system used for gravitational wave detection at advanced LIGO exceeds \unit{-150}{dBc/Hz} in the \unit{10}{Hz} -- \unit{1}{kHz} frequency range for a constant output power~\cite{kwee12}.
+In this work, we achieve \unit{-120}{dBc/Hz} intensity stability in the \unit{1}{kHz} -- \unit{2}{MHz} frequency range, and maintain this performance over six orders of magnitude in output power.
+Our modifications to the fiber amplifier hardware allow us to rival and exceed the noise performance of state-of-the-art commercial fiber amplifiers~\cite{guiraud16}.
 
@@
 
-To achieve the desired functionality, the final op-amp stage linearizes the response by increasing the gain at low signal levels and suppressing it at high signal levels by including a fast Schottky diode (ON Semiconductor BAT54S) in the feedback arm.
+To achieve the desired functionality, the final op-amp stage linearizes the response by increasing the gain at low signal levels and suppressing it at high signal levels by including a fast Schottky diode (ON Semiconductor BAT54S) in the feedback arm~\cite{Horowitz2015}.
 This can be seen by considering two extreme cases: far below the diode drop, the diode is an open circuit and the gain is set by $R_l$; above the diode drop it is a closed circuit where the gain is set by the resistor $R_h$.

### 2019-01-29 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
Updated referee comments

@@
 Noise near DC is lowered (as expected from a closed-loop system), noise outside the loop bandwidth is increased in the range of 10 to \unit{450}{kHz} as seen in subfigures (c) and (d).
-This can be explained by the Johnson noise~\cite{Horowitz2015} on the \unit{1}{k\Omega} op-amp input resistors, amplified by the amplification stages of the loop filter.
+This can be explained by the noise gain of the op-amp circuits in combination with the speed limitations of the nonlinear output stage~\cite{Horowitz2015}.
 The sharp drop off at the \unit{450}{kHz} point is due to a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.

### 2019-01-30 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
very minor typo fixes

@@
 For example, the laser system used for gravitational wave detection at advanced LIGO exceeds \unit{-150}{dBc/Hz} in the \unit{10}{Hz} -- \unit{1}{kHz} frequency range for a constant output power~\cite{kwee12}.
-In this work, we achieve \unit{-120}{dBc/Hz} intensity stability in the \unit{1}{kHz} -- \unit{2}{MHz} frequency range, and maintain this performance over six orders of magnitude in output power.
+In this work, we achieve approximately \unit{-120}{dBc/Hz} intensity stability in the \unit{1}{kHz} -- \unit{2}{MHz} frequency range, and maintain this performance over six orders of magnitude in output power.
 Our modifications to the fiber amplifier hardware allow us to rival and exceed the noise performance of state-of-the-art commercial fiber amplifiers~\cite{guiraud16}.
@@
 In addition to PLL functionality, the board also contains two digitally-controlled, high-isolation RF switches, giving a total RF isolation exceeding \unit{90}{dB}.
-This device allows us to drive the AOM with a single, clean tone ($<$\unit{90}{dBc/Hz} at \unit{200}{kHz} away from the carrier).
+This device allows us to drive the AOM with a single, clean tone ($<$\unit{-90}{dBc/Hz} at \unit{200}{kHz} away from the carrier).
 %The spectrum and relative intensity noise of the PLL can be found in Fig.~\ref{fig:pll}.

### 2019-01-30 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
Re-added new bibliography

@@
 
-\bibliography{latticeoptics}
+% \bibliography{latticeoptics}
+
+%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{36}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Friedenauer}\ \emph {et~al.}(2008)\citenamefont
+  {Friedenauer}, \citenamefont {Schmitz}, \citenamefont {Glueckert},
+  \citenamefont {Porras},\ and\ \citenamefont {Schaetz}}]{Friedenauer2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Friedenauer}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Schmitz}}, \bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
+  {Glueckert}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Porras}}, \
+  and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Schaetz}},\ }\href
+  {\doibase 10.1038/nphys1032} {\bibfield  {journal} {\bibinfo  {journal}
+  {Nature Physics}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {757}
+  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kim}\ \emph {et~al.}(2010)\citenamefont {Kim},
+  \citenamefont {Chang}, \citenamefont {Korenblit}, \citenamefont {Islam},
+  \citenamefont {Edwards}, \citenamefont {Freericks}, \citenamefont {Lin},
+  \citenamefont {Duan},\ and\ \citenamefont {Monroe}}]{Kim2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Kim}}, \bibinfo {author} {\bibfnamefont {M.-S.}\ \bibnamefont {Chang}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Korenblit}}, \bibinfo
+  {author} {\bibfnamefont {R.}~\bibnamefont {Islam}}, \bibinfo {author}
+  {\bibfnamefont {E.~E.}\ \bibnamefont {Edwards}}, \bibinfo {author}
+  {\bibfnamefont {J.~K.}\ \bibnamefont {Freericks}}, \bibinfo {author}
+  {\bibfnamefont {G.-D.}\ \bibnamefont {Lin}}, \bibinfo {author} {\bibfnamefont
+  {L.-M.}\ \bibnamefont {Duan}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Monroe}},\ }\href {\doibase 10.1038/nature09071}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
+  {volume} {465}},\ \bibinfo {pages} {590} (\bibinfo {year}
+  {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Struck}\ \emph {et~al.}(2011)\citenamefont {Struck},
+  \citenamefont {{\"{O}}lschl{\"{a}}ger}, \citenamefont {{Le Targat}},
+  \citenamefont {Soltan-Panahi}, \citenamefont {Eckardt}, \citenamefont
+  {Lewenstein}, \citenamefont {Windpassinger},\ and\ \citenamefont
+  {Sengstock}}]{Struck2011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Struck}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {{\"{O}}lschl{\"{a}}ger}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {{Le Targat}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Soltan-Panahi}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Eckardt}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Lewenstein}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Windpassinger}}, \ and\
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Sengstock}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {333}},\ \bibinfo {pages} {996} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Simon}\ \emph {et~al.}(2011)\citenamefont {Simon},
+  \citenamefont {Bakr}, \citenamefont {Ma}, \citenamefont {Tai}, \citenamefont
+  {Preiss},\ and\ \citenamefont {Greiner}}]{Simon2011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Simon}}, \bibinfo {author} {\bibfnamefont {W.~S.}\ \bibnamefont {Bakr}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ma}}, \bibinfo {author}
+  {\bibfnamefont {M.~E.}\ \bibnamefont {Tai}}, \bibinfo {author} {\bibfnamefont
+  {P.~M.}\ \bibnamefont {Preiss}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1038/nature09994}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
+  {volume} {472}},\ \bibinfo {pages} {307} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yan}\ \emph {et~al.}(2013)\citenamefont {Yan},
+  \citenamefont {Moses}, \citenamefont {Gadway}, \citenamefont {Covey},
+  \citenamefont {Hazzard}, \citenamefont {Rey}, \citenamefont {Jin},\ and\
+  \citenamefont {Ye}}]{Yan2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Yan}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont {Moses}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Gadway}}, \bibinfo
+  {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Covey}}, \bibinfo {author}
+  {\bibfnamefont {K.~R.~A.}\ \bibnamefont {Hazzard}}, \bibinfo {author}
+  {\bibfnamefont {A.~M.}\ \bibnamefont {Rey}}, \bibinfo {author} {\bibfnamefont
+  {D.~S.}\ \bibnamefont {Jin}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Ye}},\ }\href {\doibase 10.1038/nature12483} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {501}},\
+  \bibinfo {pages} {521} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Greif}\ \emph {et~al.}(2013)\citenamefont {Greif},
+  \citenamefont {Uehlinger}, \citenamefont {Jotzu}, \citenamefont {Tarruell},\
+  and\ \citenamefont {Esslinger}}]{Greif2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Greif}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Uehlinger}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Jotzu}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Tarruell}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Esslinger}},\ }\href {\doibase
+  10.1126/science.1236362} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {340}},\ \bibinfo {pages} {1307}
+  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Murmann}\ \emph {et~al.}(2015)\citenamefont
+  {Murmann}, \citenamefont {Deuretzbacher}, \citenamefont {Z{\"{u}}rn},
+  \citenamefont {Bjerlin}, \citenamefont {Reimann}, \citenamefont {Santos},
+  \citenamefont {Lompe},\ and\ \citenamefont {Jochim}}]{Murmann2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Murmann}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Deuretzbacher}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Z{\"{u}}rn}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Bjerlin}},
+  \bibinfo {author} {\bibfnamefont {S.~M.}\ \bibnamefont {Reimann}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Santos}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Lompe}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Jochim}},\ }\href {\doibase
+  10.1103/PhysRevLett.115.215301} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {115}},\ \bibinfo {pages}
+  {215301} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Drewes}\ \emph {et~al.}(2017)\citenamefont {Drewes},
+  \citenamefont {Miller}, \citenamefont {Cocchi}, \citenamefont {Chan},
+  \citenamefont {Wurz}, \citenamefont {Gall}, \citenamefont {Pertot},
+  \citenamefont {Brennecke},\ and\ \citenamefont {K{\"{o}}hl}}]{Drewes2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
+  {Drewes}}, \bibinfo {author} {\bibfnamefont {L.~A.}\ \bibnamefont {Miller}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Cocchi}}, \bibinfo
+  {author} {\bibfnamefont {C.~F.}\ \bibnamefont {Chan}}, \bibinfo {author}
+  {\bibfnamefont {N.}~\bibnamefont {Wurz}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Gall}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Pertot}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Brennecke}}, \
+  and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {K{\"{o}}hl}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
+  }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {170401} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bakr}\ \emph {et~al.}(2009)\citenamefont {Bakr},
+  \citenamefont {Gillen}, \citenamefont {Peng}, \citenamefont {F{\"{o}}lling},\
+  and\ \citenamefont {Greiner}}]{Bakr2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~S.}\ \bibnamefont
+  {Bakr}}, \bibinfo {author} {\bibfnamefont {J.~I.}\ \bibnamefont {Gillen}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Peng}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {F{\"{o}}lling}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
+  10.1038/nature08482} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\
+  }\textbf {\bibinfo {volume} {462}},\ \bibinfo {pages} {74} (\bibinfo {year}
+  {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sherson}\ \emph {et~al.}(2010)\citenamefont
+  {Sherson}, \citenamefont {Weitenberg}, \citenamefont {Endres}, \citenamefont
+  {Cheneau}, \citenamefont {Bloch},\ and\ \citenamefont {Kuhr}}]{Sherson2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
+  {Sherson}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Weitenberg}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Endres}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Cheneau}}, \bibinfo {author}
+  {\bibfnamefont {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Kuhr}},\ }\href {\doibase
+  10.1038/nature09378} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\
+  }\textbf {\bibinfo {volume} {467}},\ \bibinfo {pages} {68} (\bibinfo {year}
+  {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Haller}\ \emph {et~al.}(2015)\citenamefont {Haller},
+  \citenamefont {Hudson}, \citenamefont {Kelly}, \citenamefont {Cotta},
+  \citenamefont {Peaudecerf}, \citenamefont {Bruce},\ and\ \citenamefont
+  {Kuhr}}]{Haller2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Haller}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Hudson}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kelly}}, \bibinfo
+  {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Cotta}}, \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Peaudecerf}}, \bibinfo {author}
+  {\bibfnamefont {G.~D.}\ \bibnamefont {Bruce}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Kuhr}},\ }\href {\doibase
+  10.1038/nphys3403} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Physics}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages} {738}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cheuk}\ \emph {et~al.}(2015)\citenamefont {Cheuk},
+  \citenamefont {Nichols}, \citenamefont {Okan}, \citenamefont {Gersdorf},
+  \citenamefont {Ramasesh}, \citenamefont {Bakr}, \citenamefont {Lompe},\ and\
+  \citenamefont {Zwierlein}}]{Cheuk2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
+  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Gersdorf}}, \bibinfo {author}
+  {\bibfnamefont {V.~V.}\ \bibnamefont {Ramasesh}}, \bibinfo {author}
+  {\bibfnamefont {W.~S.}\ \bibnamefont {Bakr}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Lompe}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.~W.}\ \bibnamefont {Zwierlein}},\ }\href {\doibase
+  10.1103/PhysRevLett.114.193001} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
+  {193001} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parsons}\ \emph {et~al.}(2015)\citenamefont
+  {Parsons}, \citenamefont {Huber}, \citenamefont {Mazurenko}, \citenamefont
+  {Chiu}, \citenamefont {Setiawan}, \citenamefont {Wooley-Brown}, \citenamefont
+  {Blatt},\ and\ \citenamefont {Greiner}}]{Parsons2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont
+  {Parsons}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Huber}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo
+  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Setiawan}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Wooley-Brown}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Blatt}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
+  10.1103/PhysRevLett.114.213002} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
+  {213002} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Edge}\ \emph {et~al.}(2015)\citenamefont {Edge},
+  \citenamefont {Anderson}, \citenamefont {Jervis}, \citenamefont {McKay},
+  \citenamefont {Day}, \citenamefont {Trotzky},\ and\ \citenamefont
+  {Thywissen}}]{Edge2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~J.~A.}\
+  \bibnamefont {Edge}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Anderson}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Jervis}},
+  \bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont {McKay}}, \bibinfo
+  {author} {\bibfnamefont {R.}~\bibnamefont {Day}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Trotzky}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.~H.}\ \bibnamefont {Thywissen}},\ }\href {\doibase
+  10.1103/PhysRevA.92.063406} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. A}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages} {063406}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Omran}\ \emph {et~al.}(2015)\citenamefont {Omran},
+  \citenamefont {Boll}, \citenamefont {Hilker}, \citenamefont {Kleinlein},
+  \citenamefont {Salomon}, \citenamefont {Bloch},\ and\ \citenamefont
+  {Gross}}]{Omran2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Omran}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Boll}},
+  \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Hilker}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Kleinlein}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Salomon}}, \bibinfo {author} {\bibfnamefont
+  {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Gross}},\ }\href {\doibase 10.1103/PhysRevLett.115.263001}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {115}},\ \bibinfo {pages} {263001} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Greif}\ \emph {et~al.}(2016)\citenamefont {Greif},
+  \citenamefont {Parsons}, \citenamefont {Mazurenko}, \citenamefont {Chiu},
+  \citenamefont {Blatt}, \citenamefont {Huber}, \citenamefont {Ji},\ and\
+  \citenamefont {Greiner}}]{Greif2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Greif}}, \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo
+  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Blatt}}, \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Huber}}, \bibinfo {author} {\bibfnamefont
+  {G.}~\bibnamefont {Ji}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1126/science.aad9041}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {351}},\ \bibinfo {pages} {953} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cheuk}\ \emph
+  {et~al.}(2016{\natexlab{a}})\citenamefont {Cheuk}, \citenamefont {Nichols},
+  \citenamefont {Lawrence}, \citenamefont {Okan}, \citenamefont {Zhang},\ and\
+  \citenamefont {Zwierlein}}]{Cheuk2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
+  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
+  \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont {Lawrence}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Zhang}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.~W.}\ \bibnamefont {Zwierlein}},\ }\href
+  {https://journals.aps.org/prl/pdf/10.1103/PhysRevLett.116.235301} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett}\ }\textbf {\bibinfo {volume}
+  {116}},\ \bibinfo {pages} {235301} (\bibinfo {year}
+  {2016}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parsons}\ \emph {et~al.}(2016)\citenamefont
+  {Parsons}, \citenamefont {Mazurenko}, \citenamefont {Chiu}, \citenamefont
+  {Ji}, \citenamefont {Greif},\ and\ \citenamefont {Greiner}}]{Parsons2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont
+  {Parsons}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}},
+  \bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo
+  {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
+  10.1126/science.aag1430} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {353}},\ \bibinfo {pages} {1253}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Boll}\ \emph {et~al.}(2016)\citenamefont {Boll},
+  \citenamefont {Hilker}, \citenamefont {Salomon}, \citenamefont {Omran},
+  \citenamefont {Nespolo}, \citenamefont {Pollet}, \citenamefont {Bloch},\ and\
+  \citenamefont {Gross}}]{Boll2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Boll}}, \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Hilker}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Salomon}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Omran}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Nespolo}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Pollet}}, \bibinfo {author} {\bibfnamefont
+  {I.}~\bibnamefont {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Gross}},\ }\href {\doibase 10.1126/science.aag1635}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {353}},\ \bibinfo {pages} {1257} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cheuk}\ \emph
+  {et~al.}(2016{\natexlab{b}})\citenamefont {Cheuk}, \citenamefont {Nichols},
+  \citenamefont {Lawrence}, \citenamefont {Okan}, \citenamefont {Zhang},
+  \citenamefont {Khatami}, \citenamefont {Trivedi}, \citenamefont {Paiva},
+  \citenamefont {Rigol},\ and\ \citenamefont {Zwierlein}}]{Cheuk2016a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
+  {Cheuk}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Nichols}},
+  \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont {Lawrence}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Okan}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Khatami}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Trivedi}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Paiva}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Rigol}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~W.}\
+  \bibnamefont {Zwierlein}},\ }\href {\doibase 10.1126/science.aag3349}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {353}},\ \bibinfo {pages} {1260} (\bibinfo {year}
+  {2016}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Brown}\ \emph {et~al.}(2017)\citenamefont {Brown},
+  \citenamefont {Mitra}, \citenamefont {Guardado-Sanchez}, \citenamefont
+  {Schau{\ss}}, \citenamefont {Kondov}, \citenamefont {Khatami}, \citenamefont
+  {Paiva}, \citenamefont {Trivedi}, \citenamefont {Huse},\ and\ \citenamefont
+  {Bakr}}]{Brown2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~T.}\ \bibnamefont
+  {Brown}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Mitra}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Guardado-Sanchez}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Schau{\ss}}}, \bibinfo
+  {author} {\bibfnamefont {S.~S.}\ \bibnamefont {Kondov}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Khatami}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Paiva}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Trivedi}}, \bibinfo {author} {\bibfnamefont {D.~A.}\
+  \bibnamefont {Huse}}, \ and\ \bibinfo {author} {\bibfnamefont {W.~S.}\
+  \bibnamefont {Bakr}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Science}\ }\textbf {\bibinfo {volume} {357}},\ \bibinfo {pages}
+  {1385} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hubbard}(1963)}]{Hubbard1963}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Hubbard}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Proc.
+  Roy. Soc. A: Mathematical, Physical and Engineering Sciences}\ }\textbf
+  {\bibinfo {volume} {276}},\ \bibinfo {pages} {238} (\bibinfo {year}
+  {1963})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mazurenko}\ \emph {et~al.}(2017)\citenamefont
+  {Mazurenko}, \citenamefont {Chiu}, \citenamefont {Ji}, \citenamefont
+  {Parsons}, \citenamefont {Kan{\'{a}}sz-Nagy}, \citenamefont {Schmidt},
+  \citenamefont {Grusdt}, \citenamefont {Demler}, \citenamefont {Greif},\ and\
+  \citenamefont {Greiner}}]{Mazurenko2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Mazurenko}}, \bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo {author}
+  {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Kan{\'{a}}sz-Nagy}}, \bibinfo {author}
+  {\bibfnamefont {R.}~\bibnamefont {Schmidt}}, \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Grusdt}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Demler}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Greiner}},\ }\href {\doibase 10.1038/nature22362}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
+  {volume} {545}},\ \bibinfo {pages} {462} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chiu}\ \emph {et~al.}(2018)\citenamefont {Chiu},
+  \citenamefont {Ji}, \citenamefont {Mazurenko}, \citenamefont {Greif},\ and\
+  \citenamefont {Greiner}}]{Chiu2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont
+  {Chiu}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Ji}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}}, \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Greif}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {120}},\ \bibinfo {pages} {243201} (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Blatt}\ \emph {et~al.}(2015)\citenamefont {Blatt},
+  \citenamefont {Mazurenko}, \citenamefont {Parsons}, \citenamefont {Chiu},
+  \citenamefont {Huber},\ and\ \citenamefont {Greiner}}]{Blatt2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Blatt}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mazurenko}},
+  \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Parsons}}, \bibinfo
+  {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Chiu}}, \bibinfo {author}
+  {\bibfnamefont {F.}~\bibnamefont {Huber}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Greiner}},\ }\href {\doibase
+  10.1103/PhysRevA.92.021402} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review A}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages}
+  {021402(R)} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Preiss}\ \emph {et~al.}(2015)\citenamefont {Preiss},
+  \citenamefont {Ma}, \citenamefont {Tai}, \citenamefont {Lukin}, \citenamefont
+  {Rispoli}, \citenamefont {Zupancic}, \citenamefont {Lahini}, \citenamefont
+  {Islam},\ and\ \citenamefont {Greiner}}]{Preiss2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
+  {Preiss}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ma}}, \bibinfo
+  {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Tai}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Lukin}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Rispoli}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Zupancic}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Lahini}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Islam}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Greiner}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+   {journal} {Science}\ }\textbf {\bibinfo {volume} {347}} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Choi}\ \emph {et~al.}(2016)\citenamefont {Choi},
+  \citenamefont {Hild}, \citenamefont {Zeiher}, \citenamefont {Schau{\ss}},
+  \citenamefont {Rubio-Abadal}, \citenamefont {Yefsah}, \citenamefont
+  {Khemani}, \citenamefont {Huse}, \citenamefont {Bloch},\ and\ \citenamefont
+  {Gross}}]{Choi2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-Y.}\ \bibnamefont
+  {Choi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Hild}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Zeiher}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Schau{\ss}}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Rubio-Abadal}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Yefsah}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Khemani}}, \bibinfo {author} {\bibfnamefont {D.~A.}\
+  \bibnamefont {Huse}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Bloch}}, \ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Gross}},\ }\href {http://science.sciencemag.org/content/352/6293/1547}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {352}},\ \bibinfo {pages} {1547} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kwee}\ \emph {et~al.}(2012)\citenamefont {Kwee},
+  \citenamefont {Bogan}, \citenamefont {Danzmann}, \citenamefont {Frede},
+  \citenamefont {Kim}, \citenamefont {King}, \citenamefont {P{\"o}ld},
+  \citenamefont {Puncken}, \citenamefont {Savage}, \citenamefont {Seifert},
+  \citenamefont {Wessels}, \citenamefont {Winkelmann},\ and\ \citenamefont
+  {Willke}}]{kwee12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Kwee}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Bogan}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Danzmann}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Frede}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {King}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {P{\"o}ld}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Puncken}},
+  \bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont {Savage}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Seifert}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Wessels}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Winkelmann}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {B.}~\bibnamefont {Willke}},\ }\href {\doibase 10.1364/OE.20.010617}
+  {\bibfield  {journal} {\bibinfo  {journal} {Optics Express}\ }\textbf
+  {\bibinfo {volume} {20}},\ \bibinfo {pages} {10617} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Guiraud}, \citenamefont {Traynor},\ and\
+  \citenamefont {Santarelli}(2016)}]{guiraud16}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Guiraud}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Traynor}}, \
+  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Santarelli}},\
+  }\href {\doibase 10.1364/OL.41.004040} {\bibfield  {journal} {\bibinfo
+  {journal} {Optics Letters}\ }\textbf {\bibinfo {volume} {41}},\ \bibinfo
+  {pages} {4040} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huber}(2014)}]{Huber2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Huber}},\ }\emph {\bibinfo {title} {{Site-Resolved Imaging with the Fermi
+  Gas Microscope}}},\ \href@noop {} {Ph.D. thesis},\ \bibinfo  {school}
+  {Harvard University} (\bibinfo {year} {2014})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Agrawal}(2013)}]{Agrawal2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Agrawal}},\ }\href@noop {} {\emph {\bibinfo {title} {{Nonlinear Fiber
+  Optics}}}},\ \bibinfo {edition} {5th}\ ed.\ (\bibinfo  {publisher} {Academic
+  Press},\ \bibinfo {year} {2013})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yoshida}\ \emph {et~al.}(1999)\citenamefont
+  {Yoshida}, \citenamefont {Gorlenko}, \citenamefont {Tanner}, \citenamefont
+  {Reitze}, \citenamefont {Mansell}, \citenamefont {Khazanov},\ and\
+  \citenamefont {Kulagin}}]{Yoshida1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Yoshida}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gorlenko}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Tanner}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Reitze}}, \bibinfo {author}
+  {\bibfnamefont {J.~D.}\ \bibnamefont {Mansell}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Khazanov}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Kulagin}},\ }\href
+  {http://www.phys.ufl.edu/{~}tanner/PDFS/Yoshida99spie-ComponentsLIGO-abs.pdf}
+  {\bibfield  {journal} {\bibinfo  {journal} {SPIE}\ }\textbf {\bibinfo
+  {volume} {3736}},\ \bibinfo {pages} {430} (\bibinfo {year}
+  {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bechhoefer}(2005)}]{Bechhoefer2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Bechhoefer}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo {pages} {783}
+  (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Graeme}(1995)}]{Graeme1995}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Graeme}},\ }\href@noop {} {\emph {\bibinfo {title} {{Photodiode
+  Amplifiers}}}}\ (\bibinfo  {publisher} {McGraw Hill},\ \bibinfo {year}
+  {1995})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Skogestad}(2003)}]{Skogestad2003}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Skogestad}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Process Control}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {291}
+  (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Horowitz}\ and\ \citenamefont
+  {Hill}(2015)}]{Horowitz2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Horowitz}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Hill}},\ }\href@noop {} {\emph {\bibinfo {title} {{The Art of
+  Electronics}}}},\ \bibinfo {edition} {3rd}\ ed.\ (\bibinfo  {publisher}
+  {Cambridge University Press},\ \bibinfo {address} {New York},\ \bibinfo
+  {year} {2015})\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2019-01-30 LatticeOptics/submission_rev_sci_inst_revised/response_to_referees.txt
Reflect resubmission and arxiv version

General comments
================

We are glad to hear that both reviewers enjoyed reading our paper and are indebted especially to Referee #1 for the many constructive suggestions he or she provided. We have modified our manuscript accordingly.

Please find attached our responses to the referees' questions and comments as well as a detailed list of changes to the text. Thank you for your help in improving our paper.

Sincerely,

The Authors

Reviewer #1
===========

[...] The nonlinear correction to the their control loop, which is realized using a Schottky diode, for the compensation of nonlinearities of the AOM actuator is presented as original. However, years ago I have already seen such a "trick" employed in the photodiode electronics developed at the MPQ. Since I have never been affiliated with MPQ, I am not sure who should be credited for this development. Nonetheless I think that the authors should add a footnote giving the credits to previous work.

We completely agree with the referee that the nonlinear op-amp circuit using a Schottky diode is not a new idea. In fact, we looked up the idea in Horowitz and Hill v2 in 2011, who themselves got it from an unspecified op-amp application note in the 1980s. To prevent giving the wrong impression, we have changed the text to also cite Horowitz and Hill (the new Ref. [36]) in the corresponding sentence. On a side note: the linearization of such a feedback loop can also be done digitally by combining a logarithmic photodetector with an exponential amplifier, a technique that has been used in the Greiner group for many years. In 2011, we decided to try the analog version because we thought that it might lead to lower noise and higher bandwidth. It turns out, however, that both techniques share the same issue: the linearization decreases the bandwidth dramatically (see comment about bandwidth below).

One of the coauthors currently works at MPQ where a similar nonlinear AOM compensation based on a Schottky diode is frequently used. We traced back the idea of using a Schottky diode in the MPQ circuit by at least ten years. However, there does not seem to have been a publication or thesis that we can cite.

We have modified the sentence as follows:

"To achieve the desired functionality, the final op-amp stage linearizes the response by increasing the gain at low signal levels and suppressing it at high signal levels by including a fast Schottky diode (ON Semiconductor BAT54S) in the feedback arm~\cite{HorowitzHill}."

> In genereal, the intensity stability in the range [-135,-115] dBc/Hz for the bandwidth [1kHz,1MHz] is not exceptional. However, the real merit here is that it is achieved starting from a relatively noisy (but perhaps more affordable) fiber amplifier. The authors themselves show that even better stability can be achieved with Mephisto MOPA laser without almost requiring any active stabilization.

> Concerning the intensity stabilization electronics of the low-intensity lattice, it is somehow disappointing that it only reaches 10 kHz bandwith. With a shotnoise limit at -160 dBz/Hz, one could have expected that there is enough signal to noise to achieve much larger bandwidth. In fact, the reader is guided through a detailed explanation how the different elements are judiciously chosen to allow MHz bandwidth. Unfortunately, for some reasons, the overall servo loop was found to inject more noise above 10 kHz. The authors explain that it originates from Johnson noise on the 1 kOhm input resistors. However, it remains unclear to me what the "input resistor" is. Perhaps the transimpedance? Furthermore, I have the feeling that 1 kOhm generally comes with little low Johnson noise.

To clarify which part of the circuit contributes most to the observed noise spectra, we have created a SPICE model of the feedback loop. As the referee states, the signal bandwidth of the servo transfer function is limited by the integrator. Unfortunately, the signal bandwidth is (in general) not the same as the noise bandwidth. The op-amp input voltage noise, input current noise, the Johnson noise of all resistors, and the 1/f flicker noise of the Schottky diodes contribute to the output noise. In general, the input voltage noise transfer function (1 + Z2/Z1) of an inverting amplifier with source (feedback) impedance Z1 (Z2) is different than its signal transfer function -Z2/Z1. The SPICE model can account for all of the above contributions and we find that the circuit produces a noise spectrum which is white between 1 kHz and 500 kHz. The noise spectrum also exhibits a peak around 1 MHz and then falls off. The low-pass filter between the output of the loop filter and the IF port of the mixer cuts off this spectrum around 450 kHz as can be seen from the closed-loop traces in Fig. 2d. In contrast to the noise transfer function, the signal transfer function of the full servo decays as an integrator that leads to the noise-eating behavior below 10 kHz in Fig. 2D.

However, the signal bandwidth is not (in principle) limited by the integrator because we could just use a different RC combination. Instead, the signal bandwidth is limited by the transfer function of the nonlinear output stage. In our model, the signal bandwidth of the output stage shows two plateaus. The first plateau extends from DC to around ~10 kHz, where the gain drops to the second plateau, before it falls off around 1 MHz. These two plateaus correspond to the two different gains between which the Schottky diode in the feedback arm interpolates. Even though we use a high-speed Schottky diode, placing this nonlinear element in the op amp feedback arm makes the circuit inherently slow. This is an effect that can be seen in all active rectifier circuits: they are much slower than the diode speed suggests.

With this in mind, we have changed the wording in the corresponding paragraph to:

"This can be explained by the noise gain of the op-amp circuits in combination with the speed limitations of the nonlinear output stage~\cite{Horowitz2015}."

> - I did not understand the statement in the last sentence of the abstract. They report on a short-term pointing stability of about one lattice site. This seems too big instability to me. In the text, other values at around 1% of the lattice site.

There are 3 notions of stability that matter - the lattice spacing, the lattice position, and the position of the underlying harmonic trap. The number the reviewer is referring to refers to the underlying harmonic trap, which is the hardest to control. A stability of one lattice site  corresponds to a position stability of ~1% of the beam waist.

We have changed the last sentence of the abstract to

"The position of the harmonic trap produced by the Gaussian envelope of the lattice beams is stable to about one lattice spacing and the long-term (six-month) relative RMS stability of the lattice spacing itself is 0.5\%."

> In addition, "relative stability of the lattice spacing itself is 0.5% RMS" seems to me confusing. One reads it as 0.5% of an RMS. Probably the authors meant a relative RMS stability of 0.5%.

We have adopted the referee's formulation (see above).

> - The level of -115 dBc/Hz seems very remarkable in relation to the utilization of fiber amplifiers. Using other laser systems, it is not uncommon to reach <-150 dBc/Hz in the same bandwidth. I would encourage the authors to make a comment right from the beginning helping the reader realize what is expected for a good intensity stability, and how to gauge the result obtained here with respect to other laser systems.

We thank the referee for pointing out this missed opportunity to put our work in a broader context.

Unfortunately, we were not able to find laser systems with RIN that is better than -150 dBc/Hz between 1 kHz and 1 MHz Fourier frequency and would be grateful if the referee could point us to the corresponding literature. It is our understanding that the NPRO lasers are the most intensity-stable lasers currently available. The seed laser used in this work (an Innolight Mephisto with 2 W output) shows a RIN of -140 dBc/Hz at 1 kHz Fourier frequency. According to the original specification, this should decrease to -155 dBc/Hz at 1 MHz Fourier frequency. As shown in Fig. 2a, this is not the case, and the laser after a few years of operation exhibits -145 dBc/Hz at 1 MHz.

The most useful comparison with another system can be drawn by looking at relatively recent papers from the Advanced LIGO community, where an NPRO seed laser in a MOPA configuration reaches -128 dBc/Hz around 10 kHz Fourier frequency. To improve its performance the authors use a much more elaborate active feedback system than ours. When we started constructing the laser system around 2011, we were inspired by the ideas developed for LIGO.

However, since the LIGO project cares mostly about a small Fourier frequency window between 10 Hz and 1 kHz, it is difficult to find data on their RIN (in the actively stabilized case) in the region we care very much about: between 10 kHz and 1 MHz, where the relaxation oscillation peak of the NPRO laser lies.

Our analog feedback loop has to produce acceptable performance over a rather large window in frequency space, as we demonstrated in Ref. [25]. For this reason, we were very conservative in tuning the loop, but still eat noise over 10 kHz for *all* set points. Clearly there is room for improvement in our system, but getting good performance over such a large region in Fourier space and for all values of the setpoint of a nonlinear circuit may be asking for too much.

To make the above points more clear and to give more credit to the large body of work from the LIGO community, we have added the following paragraph to the introduction:

"For context, typical high-power, low-noise 1064 nm laser systems are based on amplification of a seed laser with either a fiber or a solid-state amplifier. For example, the laser system used for gravitational wave detection at advanced LIGO exceeds -150 dBc/Hz in the 10 Hz -- 1 kHz frequency range for a constant output power~\cite{kwee12}.
In this work, we achieve -120 dBc/Hz intensity stability in the 1 kHz -- 2 MHz frequency range, and maintain this performance over six orders of magnitude in output power. Our modifications to the fiber amplifier hardware allow us to rival and exceed the noise performance of state-of-the-art commercial fiber amplifiers~\cite{guiraud16}."

We added two references that show the RIN of the advanced LIGO laser

  Kwee et al. Opt. Express 20, 10617 (2012)

and the RIN of the most modern commercial fiber-amplifier-based system

  Guiraud et al. Opt. Lett. 41, 4040 (2016)

> - In Fig. 2(b), it seems that the high-power intensity stabilization makes no difference. Was that measured with an out-of-loop photodiode? It seems that the closed-loop noise spectral density is even higher at low frequencies, where instead one should expect a clear improvement. It seems that the high-power digital feedback offers no advantage with respect to a pure feedforward driving based on a lookup table.

These measurements were carried out with an out-of-loop photodiode. However, please note that the RIN plot minimum is nearly out of band with respect to the high power loop.
We disagree with the point that a lookup system could do better. For the Raman sideband cooling to work, the laser power must be within a particular range for the majority of the cooling/imaging time - 100's of ms.
The purpose of the loop is to ensure stability at those scales without introducing excessive noise at all higher frequencies. The figure in question demonstrates the latter.

> - Concerning Fig.2(c), it is said that it is an open-loop characterization. The authors also say that it includes "an additional low-pass filtering stage to limit the loop bandwidth." Thus, it is not clear how the low-pass filter should affect these results if there is no loop here. Perhaps the remark about the low pass filtering belong to Fig.2(d)?

We apologize for the oversight. The reference to the low pass was a mistake. Panels (c) and (d) mean to compare open and closed loop performance of the unmodified loop, and the addition of an extra filter is characterized in Fig 11. The caption has been fixed.

> - Resistors seem to be missing from Fig.6(c). Before and after the integrator stage there should be resistors. Otherwise I do not see how the circuit can run stably, since the virtual ground principle cannot be realized.

Thank you for finding this important mistake, we appreciate the comment. The circuit diagram of Fig. 6 is of course strongly simplified and the input resistors to the integrator and buffer stage got lost in the process. We have fixed the figure to include all important resistors.

> - Where the authors say "we use an all-custom loop based on a TeO_2 AOM", what do they mean by "all-custom"? I suggest to remove this expression, since the english is not so clear, and their approach using an AOM is rather standard in the field of ultracold atoms, and it is also quite widespread practice to develop the electronics in-house for such an application.

We agree and have changed the expression "all-custom" to "nonlinear", referring to the electronics.

> - "To prevent damage to the low-power photodiode when the system is at its highest powers, a shutter (Stanford Research Systems SR475) blocks the light when the high-power loop is in use." tends to repeat what has been said in the previous page. Perhaps this sentence can be merged with the previous one.

This has been fixed.

> - "...giving a total isolation exceeding 90 dB." Do the authors mean a total isolation of the RF power or of the laser intensity? Probably the former.

That is correct and has been fixed.

> - I am not exactly sure why Fig.7 has been shown. What is its goal? Phase-stability value of -90 dBc/Hz at 100 kHz is not so impressive if compared with modern DDS chips like AD9915, where almost -160 dBc/Hz is reachable. Probably for the authors' application, a good but not exceptional stability of -90 dBc/Hz suffice. Moreover, I would say that Fig. 7(b) should be plotted with a different vertical scale to allow the reader to see the details. And why are there jumps between different scanning decades? Were the different scans properly corrected by the resolution bandwidth of the spectrum analyzer before stitching them together?

We agree with the reviewer that this is not an essential figure. The reviewer is completely correct that for our application, this is not exceptional, but sufficient. We have removed the figure and only cite the relevant numbers.

> - "... an InGaS based," It cannot be sulphur. There is probably a typo as it is "InGaAs".

Fixed.

> - "uses the low-noise OPA627 (Texas Instruments) op-amp which is able to supply tens of mA of current into an output impedance of 50 Ohm." Did they authors mean "current into a input impedance of 50 Ohm"? Or "through an output impedance of 50 Ohm"? Probably both. Whereas, to me, "into an output impedance" makes no sense.

Yes, corrected.

> - "... input resistors, amplified by the amplification stages of the loop filter." As I have already remarked it, I could not figure out what the input resistor is. The transimpedance? Or the resistor after V_SP?

Clarified to mean the op-amp input resistors, not the transimpedance gain resistor.

> - "If the trap had followed a random walk with these step sizes, the optical lattice would have to be realigned frequently, since after only 100 experimental shots, the trap would have moved by more than 10 lattice sites. However, the situation is more fortunate, since subsequent steps are correlated, ... "
>
> If the authors are interested, they could (optionally) run a detrended fluctuation analysis to determine the Hurst exponent H. Values 0<H<1 correspond to stationary fractional Gaussian noise, while for 1<H<2 one has fractional Brownian motion. Besides Wikipedia, an introduction to the topic can be found in
>
> N. Scafetta and B. J. West, "Multiscaling comparative analysis of time series and geophysical phenomena," Complexity 10, 51 (2005)

We thank the reviewer for pointing out this interesting analysis method and we agree that it would be worthwhile to apply it to our data. The method seems to be very similar to standard analyses of time series done in the frequency standards community, where the Allan variance is typically used to characterize a clock's frequency stability (linear drifts are often removed before doing such an analysis). Here, one can identify different noise processes by the power-law exponent of the Allan deviation as a function of averaging time. A very good introduction to this field can be found in the NIST technical note 1337 (available online)

  NIST TN1337: Characterization of Clocks and Oscillators
  D.B. Sullivan, D.W. Allan, DA. Howe, F.L. Walls

However, we feel that to do this effect justice and to understand the underlying stochastic process, more data should be taken. We would like to reserve this for a future project.

Reviewer #2
===========

> I would just ask the authors to address the following curiosity: in the conclusions they mention about the possibility of stabilizing actively the beam pointing. May the authors expand this concept? How are they planning to implement this beam stabilization?

We thank the reviewer for the favorable feedback. While we agree that live, active stabilization would be an amazing technical upgrade, the note in the conclusion merely referred to a less ambitious goal. Since we receive, as a matter of course, one positional measurement per experimental cycle, one could imagine a slow feedback process based on these measurements. It would necessarily be limited to one update every cycle, but that is more than fast enough to catch thermal drifts.
